---
title: "Raw Talent Data Administration"
format:
  dashboard:
    orientation: rows
server: shiny
execute:
  echo: false
  warning: false
  message: false
---

<style>
.admin-path {
  overflow-wrap: anywhere;
  font-family: var(--bs-font-monospace);
  font-size: 0.78rem;
}

.admin-note {
  color: var(--bs-secondary-color);
  font-size: 0.86rem;
}

.dataTables_wrapper {
  font-size: 0.80rem;
}

@media (max-width: 768px) {
  .dashboard-page .card,
  .dashboard-page .card:not(.bslib-value-box) {
    height: auto !important;
    min-height: 0 !important;
  }

  .bslib-value-box .value-box-value {
    font-size: 1.4rem;
  }

  .dataTables_wrapper {
    font-size: 0.72rem;
  }
}
</style>

```{r}
#| label: setup
#| context: setup
#| include: false

knitr::opts_knit$set(
  root.dir = normalizePath(getwd(), winslash = "/", mustWork = TRUE)
)

dashboard_machine_library <- file.path(
  path.expand("~/R"),
  paste0(R.version$platform, "-library"),
  paste(R.version$major, sub("\\..*$", "", R.version$minor), sep = ".")
)
if (dir.exists(dashboard_machine_library)) {
  .libPaths(unique(c(.libPaths(), dashboard_machine_library)))
}

suppressPackageStartupMessages({
  library(here)
  library(shiny)
  library(dplyr)
  library(tidyr)
  library(DT)
  library(plotly)
  library(bslib)
  library(scales)
})

source(here::here("r_scripts", "lib", "utils", "repo_env.R"))
source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "duckdb", "db_connect.R"))
source(
  here::here(
    "r_scripts",
    "lib",
    "dashboard",
    "data",
    "raw_data_admin.R"
  )
)

load_repo_env()
raw_admin_database_path <- talent_lakehouse_db_path()

raw_admin_value <- function(value, fallback = "—") {
  if (length(value) == 0L || is.na(value[[1]]) || !nzchar(as.character(value[[1]]))) {
    return(fallback)
  }
  as.character(value[[1]])
}

raw_admin_time <- function(value) {
  if (length(value) == 0L || is.na(value[[1]])) return("Not available")
  parsed <- as.POSIXct(value[[1]], tz = "UTC")
  if (is.na(parsed)) return("Not available")
  format(parsed, "%Y-%m-%d %H:%M:%S UTC", tz = "UTC")
}

raw_admin_times <- function(values) {
  parsed <- as.POSIXct(values, tz = "UTC")
  formatted <- format(parsed, "%Y-%m-%d %H:%M:%S UTC", tz = "UTC")
  formatted[is.na(parsed)] <- "Not available"
  formatted
}

raw_admin_value_box <- function(title, value) {
  bslib::value_box(title = title, value = raw_admin_value(value))
}

raw_admin_input <- function(value, fallback) {
  if (is.null(value) || length(value) == 0L) fallback else value
}

raw_admin_table <- function(data, page_length = 10L, filter = "top") {
  if (nrow(data) == 0L) {
    data <- data.frame(message = "No rows are available for this view.")
    filter <- "none"
  }
  DT::datatable(
    data,
    rownames = FALSE,
    filter = filter,
    escape = TRUE,
    options = list(
      pageLength = page_length,
      scrollX = TRUE,
      autoWidth = TRUE,
      dom = "tip"
    )
  )
}

raw_admin_empty_plot <- function(message) {
  plotly::plot_ly() |>
    plotly::layout(
      xaxis = list(visible = FALSE),
      yaxis = list(visible = FALSE),
      annotations = list(list(
        text = message,
        x = 0.5,
        y = 0.5,
        xref = "paper",
        yref = "paper",
        showarrow = FALSE
      ))
    )
}
```

# {.sidebar}

```{r}
actionButton("refresh_data", "Refresh database", class = "btn-primary")

checkboxInput(
  "auto_refresh",
  "Refresh every five minutes",
  value = TRUE
)

uiOutput("database_freshness")
hr()
uiOutput("relation_selector")
uiOutput("talent_filter")
textInput("video_filter", "Exact video ID", value = "")
numericInput(
  "row_limit",
  "Maximum preview rows",
  value = 500,
  min = 25,
  max = 5000,
  step = 25
)
actionButton("load_preview", "Load preview")
hr()
helpText(
  "Filters apply when the selected relation contains talent_code or video_id. ",
  "All database connections are read-only."
)
```

# Overview

The overview inventories the in-scope talent catalog, analytics, subtitle,
chat, and operational relations. Counts and timestamps come directly from the
unified lakehouse.

## Row {height=18%}

```{r}
#| title: "Scoped Relations"
uiOutput("relation_count")
```

```{r}
#| title: "Active Talents"
uiOutput("active_talent_count")
```

```{r}
#| title: "Catalog Videos"
uiOutput("video_count")
```

```{r}
#| title: "Checks Needing Review"
uiOutput("issue_count")
```

## Row {height=40%}

```{r}
#| title: "Rows by Relation"
plotlyOutput("relation_rows_plot", height = "100%")
```

```{r}
#| title: "Videos with Analytics, Subtitles, or Chat"
plotlyOutput("coverage_plot", height = "100%")
```

## Row {height=42%}

```{r}
#| title: "Relation Inventory and Recency"
DTOutput("relation_inventory")
```

# Data Health

These checks focus on broken catalog relationships, missing lineage, blank text,
invalid count metrics, unresolved collection failures, and failed relevant
pipeline runs. A nonzero result is a signal to investigate, not an automatic
repair instruction.

## Row {height=18%}

```{r}
#| title: "Critical Checks"
uiOutput("critical_count")
```

```{r}
#| title: "Warnings"
uiOutput("warning_count")
```

```{r}
#| title: "Passing Checks"
uiOutput("passing_count")
```

## Row {height=82%}

```{r}
#| title: "Health Check Results"
DTOutput("health_checks")
```

# Explore Relations

Choose a relation and optional exact talent or video filter in the sidebar.
The preview is deliberately row-limited; the download contains the same rows
shown in the current preview.

## Row {height=18%}

```{r}
#| title: "Selected Relation"
uiOutput("selected_relation_name")
```

```{r}
#| title: "Relation Rows"
uiOutput("selected_relation_rows")
```

```{r}
#| title: "Relation Columns"
uiOutput("selected_relation_columns")
```

```{r}
#| title: "Preview Export"
div(
  class = "p-3",
  downloadButton("download_preview", "Download preview CSV"),
  tags$p(
    class = "admin-note mt-3",
    "The export respects the relation, filters, and row limit."
  )
)
```

## Row {height=82%}

```{r}
#| title: "Relation Contents"
DTOutput("relation_preview")
```

# Descriptive Statistics

Column profiles report nulls and approximate distinct counts. Numeric summaries
report minimum, mean, median, and maximum. Profiling can scan a large relation,
so it only reruns when requested.

## Row {height=14%}

```{r}
#| title: "Profile Controls"
div(
  class = "p-3",
  actionButton("profile_relation", "Profile selected relation", class = "btn-primary"),
  tags$span(class = "admin-note ms-3", textOutput("profiled_relation", inline = TRUE))
)
```

## Row {height=43%}

```{r}
#| title: "Column Completeness and Cardinality"
DTOutput("column_profile")
```

## Row {height=43%}

```{r}
#| title: "Numeric Summary"
DTOutput("numeric_profile")
```

# Talent Coverage

This page compares catalog membership with analytics, subtitle, and chat
coverage for each talent. Zeroes can be valid when a source does not apply, but
they make gaps easy to spot.

## Row {height=42%}

```{r}
#| title: "Distinct Videos by Available Data Type"
plotlyOutput("talent_coverage_plot", height = "100%")
```

## Row {height=58%}

```{r}
#| title: "Talent Coverage Detail"
DTOutput("talent_coverage")
```

# Recent Activity

Relevant pipeline runs exclude classification, qualitative coding, and summary
generation. Ingestion events are retained when their destination is in
`catalog`, `clean`, `analytics`, or `text`.

## Row {height=48%}

```{r}
#| title: "Recent Relevant Pipeline Runs"
DTOutput("recent_runs")
```

## Row {height=52%}

```{r}
#| title: "Recent Ingestion Events"
DTOutput("recent_events")
```

```{r}
#| label: server
#| context: server
#| include: false

raw_admin_snapshot <- reactive({
  input$refresh_data
  if (isTRUE(input$auto_refresh)) {
    invalidateLater(5 * 60 * 1000, session)
  }
  withProgress(message = "Refreshing raw-data administration", value = 0, {
    incProgress(0.15, detail = "Inventorying relations")
    snapshot <- raw_data_admin_snapshot(raw_admin_database_path)
    incProgress(0.85, detail = "Preparing health and coverage views")
    snapshot
  })
})

output$database_freshness <- renderUI({
  snapshot <- raw_admin_snapshot()
  htmltools::tagList(
    tags$small(
      class = "text-muted",
      paste("Dashboard refreshed", raw_admin_time(snapshot$refreshed_at))
    ),
    tags$br(),
    tags$small(
      class = "text-muted",
      paste("DuckDB modified", raw_admin_time(snapshot$database_modified_at))
    ),
    tags$br(),
    tags$small(
      class = "text-muted admin-path",
      snapshot$database_path
    )
  )
})

output$relation_selector <- renderUI({
  relations <- raw_admin_snapshot()$relations
  choices <- stats::setNames(
    relations$relation,
    paste(relations$domain, relations$relation, sep = " • ")
  )
  selected <- isolate(input$selected_relation)
  if (is.null(selected) || !selected %in% relations$relation) {
    preferred <- "analytics.video_latest_performance"
    selected <- if (preferred %in% relations$relation) preferred else relations$relation[[1]]
  }
  selectInput("selected_relation", "Explore relation", choices, selected = selected)
})

output$talent_filter <- renderUI({
  coverage <- raw_admin_snapshot()$talent_coverage
  choices <- c(
    "All talents" = "",
    stats::setNames(
      coverage$talent_code,
      paste(coverage$talent_code, coverage$talent_name, sep = " • ")
    )
  )
  selectizeInput("selected_talent", "Exact talent", choices, selected = "")
})

selected_relation_metadata <- reactive({
  relations <- raw_admin_snapshot()$relations
  relation <- input$selected_relation
  if (is.null(relation) || !relation %in% relations$relation) {
    relation <- relations$relation[[1]]
  }
  relations[relations$relation == relation, , drop = FALSE]
})

preview_data <- eventReactive(
  input$load_preview,
  {
    metadata <- selected_relation_metadata()
    withProgress(message = "Loading relation preview", value = 0.4, {
      data <- raw_data_admin_preview(
        database_path = raw_admin_database_path,
        relation = metadata$relation[[1]],
        talent_code = raw_admin_input(input$selected_talent, ""),
        video_id = raw_admin_input(input$video_filter, ""),
        limit = raw_admin_input(input$row_limit, 500L)
      )
      incProgress(0.6)
      data
    })
  },
  ignoreNULL = FALSE
)

profile_data <- eventReactive(
  input$profile_relation,
  {
    metadata <- selected_relation_metadata()
    withProgress(message = "Profiling selected relation", value = 0.2, {
      profile <- raw_data_admin_profile(
        raw_admin_database_path,
        metadata$relation[[1]]
      )
      incProgress(0.8)
      list(relation = metadata$relation[[1]], profile = profile)
    })
  },
  ignoreNULL = FALSE
)

output$relation_count <- renderUI({
  raw_admin_value_box("In-scope relations", nrow(raw_admin_snapshot()$relations))
})

output$active_talent_count <- renderUI({
  coverage <- raw_admin_snapshot()$talent_coverage
  raw_admin_value_box("Active talents", scales::comma(sum(coverage$active, na.rm = TRUE)))
})

output$video_count <- renderUI({
  relation <- raw_admin_snapshot()$relations |>
    filter(.data$relation == "catalog.videos")
  raw_admin_value_box("Catalog videos", scales::comma(relation$row_count))
})

output$issue_count <- renderUI({
  checks <- raw_admin_snapshot()$health_checks
  count <- sum(checks$status %in% c("Critical", "Review", "Unavailable"))
  raw_admin_value_box("Checks needing review", count)
})

output$critical_count <- renderUI({
  checks <- raw_admin_snapshot()$health_checks
  raw_admin_value_box("Critical checks", sum(checks$status == "Critical"))
})

output$warning_count <- renderUI({
  checks <- raw_admin_snapshot()$health_checks
  raw_admin_value_box(
    "Warnings or unavailable",
    sum(checks$status %in% c("Review", "Unavailable"))
  )
})

output$passing_count <- renderUI({
  checks <- raw_admin_snapshot()$health_checks
  raw_admin_value_box("Passing checks", sum(checks$status == "Pass"))
})

output$relation_rows_plot <- renderPlotly({
  relations <- raw_admin_snapshot()$relations |>
    filter(!is.na(.data$row_count), .data$row_count > 0) |>
    arrange(.data$row_count)
  if (nrow(relations) == 0L) return(raw_admin_empty_plot("No relation counts available."))
  plotly::plot_ly(
    relations,
    x = ~row_count,
    y = ~stats::reorder(relation, row_count),
    color = ~domain,
    type = "bar",
    orientation = "h",
    hovertemplate = "%{y}<br>%{x:,} rows<extra></extra>"
  ) |>
    plotly::layout(
      xaxis = list(title = "Rows", type = "log"),
      yaxis = list(title = ""),
      legend = list(orientation = "h"),
      margin = list(l = 205, r = 20, t = 10, b = 50)
    )
})

output$coverage_plot <- renderPlotly({
  coverage <- raw_admin_snapshot()$talent_coverage
  columns <- intersect(
    c("videos_with_analytics", "videos_with_subtitles", "videos_with_chat"),
    names(coverage)
  )
  if (nrow(coverage) == 0L || length(columns) == 0L) {
    return(raw_admin_empty_plot("No talent coverage data available."))
  }
  long <- coverage |>
    select(.data$talent_code, all_of(columns)) |>
    pivot_longer(-.data$talent_code, names_to = "data_type", values_to = "videos")
  plotly::plot_ly(
    long,
    x = ~talent_code,
    y = ~videos,
    color = ~data_type,
    type = "bar",
    hovertemplate = "%{x}<br>%{fullData.name}: %{y:,}<extra></extra>"
  ) |>
    plotly::layout(
      barmode = "group",
      xaxis = list(title = "Talent"),
      yaxis = list(title = "Distinct videos"),
      legend = list(orientation = "h"),
      margin = list(l = 65, r = 20, t = 10, b = 75)
    )
})

output$relation_inventory <- renderDT({
  data <- raw_admin_snapshot()$relations |>
    transmute(
      .data$domain,
      .data$relation,
      type = .data$table_type,
      rows = .data$row_count,
      columns = .data$column_count,
      recency_field = .data$recency_column,
      earliest = .data$earliest_value,
      latest = .data$latest_value,
      .data$description
    )
  raw_admin_table(data, page_length = 20L)
})

output$health_checks <- renderDT({
  checks <- raw_admin_snapshot()$health_checks
  raw_admin_table(checks, page_length = 20L)
})

output$selected_relation_name <- renderUI({
  raw_admin_value_box("Selected relation", selected_relation_metadata()$relation)
})

output$selected_relation_rows <- renderUI({
  raw_admin_value_box(
    "Relation rows",
    scales::comma(selected_relation_metadata()$row_count)
  )
})

output$selected_relation_columns <- renderUI({
  raw_admin_value_box("Relation columns", selected_relation_metadata()$column_count)
})

output$relation_preview <- renderDT({
  raw_admin_table(preview_data(), page_length = 25L)
})

output$download_preview <- downloadHandler(
  filename = function() {
    paste0(gsub("[.]", "_", selected_relation_metadata()$relation), "_preview.csv")
  },
  content = function(file) {
    utils::write.csv(preview_data(), file, row.names = FALSE, na = "")
  }
)

output$profiled_relation <- renderText({
  paste("Current profile:", profile_data()$relation)
})

output$column_profile <- renderDT({
  raw_admin_table(profile_data()$profile$columns, page_length = 25L)
})

output$numeric_profile <- renderDT({
  raw_admin_table(profile_data()$profile$numeric, page_length = 25L)
})

output$talent_coverage_plot <- renderPlotly({
  coverage <- raw_admin_snapshot()$talent_coverage
  columns <- intersect(
    c("videos_with_analytics", "videos_with_subtitles", "videos_with_chat"),
    names(coverage)
  )
  if (nrow(coverage) == 0L || length(columns) == 0L) {
    return(raw_admin_empty_plot("No talent coverage data available."))
  }
  long <- coverage |>
    select(.data$talent_code, all_of(columns)) |>
    pivot_longer(-.data$talent_code, names_to = "data_type", values_to = "videos")
  plotly::plot_ly(
    long,
    x = ~talent_code,
    y = ~videos,
    color = ~data_type,
    type = "bar",
    hovertemplate = "%{x}<br>%{fullData.name}: %{y:,}<extra></extra>"
  ) |>
    plotly::layout(
      barmode = "group",
      xaxis = list(title = "Talent"),
      yaxis = list(title = "Distinct videos"),
      legend = list(orientation = "h")
    )
})

output$talent_coverage <- renderDT({
  raw_admin_table(raw_admin_snapshot()$talent_coverage, page_length = 25L)
})

output$recent_runs <- renderDT({
  runs <- raw_admin_snapshot()$recent_runs
  if (nrow(runs) > 0L) {
    runs <- runs |>
      mutate(
        started_at = raw_admin_times(.data$started_at),
        completed_at = raw_admin_times(.data$completed_at)
      )
  }
  raw_admin_table(runs, page_length = 15L)
})

output$recent_events <- renderDT({
  events <- raw_admin_snapshot()$recent_events
  if (nrow(events) > 0L) {
    events <- events |>
      mutate(event_at = raw_admin_times(.data$event_at))
  }
  raw_admin_table(events, page_length = 15L)
})
```
