---
title: "Talent Data Administration"
format:
  dashboard:
    orientation: rows
server: shiny
execute:
  echo: false
  warning: false
  message: false
---

<style>
.admin-path {
  overflow-wrap: anywhere;
  font-family: var(--bs-font-monospace);
  font-size: 0.78rem;
}

.admin-note {
  color: var(--bs-secondary-color);
  font-size: 0.86rem;
}

.admin-global-toolbar {
  align-items: center;
  display: flex;
  flex-wrap: wrap;
  gap: 0.75rem 1rem;
  width: 100%;
}

.admin-global-toolbar .form-group {
  margin-bottom: 0;
}

.admin-refresh-status {
  align-items: center;
  color: var(--bs-secondary-color);
  display: flex;
  flex-wrap: wrap;
  font-size: 0.82rem;
  gap: 0.35rem 1rem;
}

.admin-section-heading {
  border-bottom: 1px solid var(--bs-border-color);
  font-size: 1.15rem;
  margin: 1.1rem 0 0.5rem;
  padding-bottom: 0.35rem;
}

.dataTables_wrapper {
  font-size: 0.80rem;
}

.transcript-workflow {
  color: var(--bs-secondary-color);
  font-size: 0.82rem;
  font-weight: 600;
  margin-bottom: 0.75rem;
}

.transcript-processes-layout {
  display: grid;
  grid-template-columns: minmax(0, 2fr) minmax(0, 3fr);
  gap: 1rem;
  align-items: stretch;
  width: 100%;
}

.transcript-processes-layout > .transcript-browser-pane,
.transcript-processes-layout > .transcript-detail-pane {
  display: block;
  min-width: 0;
  overflow: hidden;
  border: 1px solid var(--bs-border-color);
  border-radius: var(--bs-border-radius);
  padding: 1rem;
}

.transcript-processes-layout .html-fill-item {
  flex: 0 0 auto;
}

.transcript-processes-layout .transcript-header-actions {
  flex-direction: row;
}

.transcript-processes-layout .nav-tabs {
  display: flex;
  flex-direction: row;
  gap: 1rem;
}

.transcript-processes-layout h3 {
  font-size: 1rem;
  margin: 0 0 1rem;
}

.transcript-detail-pane .tab-content {
  max-height: 68vh;
  overflow: auto;
}

@media (max-width: 900px) {
  .transcript-processes-layout {
    grid-template-columns: minmax(0, 1fr);
  }
}

.transcript-batch-summary,
.transcript-video-metadata {
  display: grid;
  gap: 0.55rem 0.9rem;
  grid-template-columns: repeat(2, minmax(0, 1fr));
}

.transcript-summary-item,
.transcript-metadata-item {
  min-width: 0;
}

.transcript-summary-label,
.transcript-metadata-label {
  color: var(--bs-secondary-color);
  display: block;
  font-size: 0.72rem;
  font-weight: 600;
  letter-spacing: 0.025em;
  text-transform: uppercase;
}

.transcript-summary-value,
.transcript-metadata-value {
  display: block;
  font-size: 0.88rem;
  overflow-wrap: anywhere;
}

.transcript-summary-wide {
  grid-column: 1 / -1;
}

.transcript-panel-divider {
  border-top: 1px solid var(--bs-border-color);
  margin: 0.85rem 0;
}

.transcript-video-heading {
  margin-bottom: 0.8rem;
}

.transcript-video-heading h4 {
  font-size: 1.12rem;
  margin-bottom: 0.2rem;
}

.transcript-video-id {
  color: var(--bs-secondary-color);
  font-family: var(--bs-font-monospace);
  font-size: 0.78rem;
}

.transcript-header-actions {
  align-items: flex-start;
  display: flex;
  gap: 1rem;
  justify-content: space-between;
  margin-bottom: 0.75rem;
}

.transcript-header-actions > :first-child {
  flex: 1 1 auto;
  min-width: 0;
}

.transcript-header-actions .btn {
  flex: 0 0 auto;
  white-space: nowrap;
}

#transcript_tracks table.dataTable td {
  vertical-align: top;
  white-space: normal;
}

.transcript-reading-list {
  max-height: 68vh;
  overflow-y: auto;
  padding-right: 0.35rem;
}

.transcript-reading-row {
  border-bottom: 1px solid var(--bs-border-color);
  display: grid;
  gap: 0.8rem;
  grid-template-columns: 6.5rem minmax(0, 1fr);
  padding: 0.7rem 0.25rem;
}

.transcript-reading-time {
  color: var(--bs-primary);
  font-family: var(--bs-font-monospace);
  font-size: 0.78rem;
  font-weight: 600;
  white-space: nowrap;
}

.transcript-reading-text {
  font-size: 0.96rem;
  line-height: 1.5;
}

.transcript-empty-state {
  color: var(--bs-secondary-color);
  padding: 1.5rem 0.5rem;
  text-align: center;
}

@media (max-width: 768px) {
  .dashboard-page .card,
  .dashboard-page .card:not(.bslib-value-box) {
    height: auto !important;
    min-height: 0 !important;
  }

  .bslib-value-box .value-box-value {
    font-size: 1.4rem;
  }

  .dataTables_wrapper {
    font-size: 0.72rem;
  }

  .transcript-header-actions {
    display: block;
  }

  .transcript-header-actions .btn {
    margin-top: 0.5rem;
  }

  .transcript-reading-row {
    gap: 0.35rem;
    grid-template-columns: 1fr;
  }
}
</style>

```{r}
#| label: setup
#| context: setup
#| include: false

knitr::opts_knit$set(
  root.dir = normalizePath(getwd(), winslash = "/", mustWork = TRUE)
)

dashboard_machine_library <- file.path(
  path.expand("~/R"),
  paste0(R.version$platform, "-library"),
  paste(R.version$major, sub("\\..*$", "", R.version$minor), sep = ".")
)
if (dir.exists(dashboard_machine_library)) {
  .libPaths(unique(c(.libPaths(), dashboard_machine_library)))
}

suppressPackageStartupMessages({
  library(here)
  library(shiny)
  library(dplyr)
  library(tidyr)
  library(DT)
  library(plotly)
  library(bslib)
  library(scales)
})

source(here::here("r_scripts", "lib", "utils", "repo_env.R"))
source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "duckdb", "db_connect.R"))
source(
  here::here(
    "r_scripts",
    "lib",
    "dashboard",
    "data",
    "raw_data_admin.R"
  )
)
source(
  here::here(
    "r_scripts",
    "lib",
    "dashboard",
    "data",
    "classification_admin.R"
  )
)

load_repo_env()
raw_admin_database_path <- talent_lakehouse_db_path()
admin_database_path <- raw_admin_database_path
admin_run_root <- classification_admin_resolve_run_root()

raw_admin_value <- function(value, fallback = "—") {
  if (length(value) == 0L || is.na(value[[1]]) || !nzchar(as.character(value[[1]]))) {
    return(fallback)
  }
  as.character(value[[1]])
}

raw_admin_values <- function(values, fallback = "—") {
  values <- as.character(values)
  values[is.na(values) | !nzchar(values)] <- fallback
  values
}

raw_admin_time <- function(value) {
  if (length(value) == 0L || is.na(value[[1]])) return("Not available")
  parsed <- as.POSIXct(value[[1]], tz = "UTC")
  if (is.na(parsed)) return("Not available")
  format(parsed, "%Y-%m-%d %H:%M:%S UTC", tz = "UTC")
}

raw_admin_times <- function(values) {
  parsed <- as.POSIXct(values, tz = "UTC")
  formatted <- format(parsed, "%Y-%m-%d %H:%M:%S UTC", tz = "UTC")
  formatted[is.na(parsed)] <- "Not available"
  formatted
}

raw_admin_value_box <- function(title, value) {
  bslib::value_box(title = title, value = raw_admin_value(value))
}

raw_admin_input <- function(value, fallback) {
  if (is.null(value) || length(value) == 0L) fallback else value
}

raw_admin_disabled_input <- function(input) {
  tags$fieldset(
    disabled = "disabled",
    style = "border: 0; margin: 0; padding: 0;",
    input
  )
}

raw_admin_metadata_item <- function(label, value, wide = FALSE) {
  tags$div(
    class = paste(
      "transcript-metadata-item",
      if (isTRUE(wide)) "transcript-summary-wide" else ""
    ),
    tags$span(class = "transcript-metadata-label", label),
    tags$span(class = "transcript-metadata-value", raw_admin_value(value))
  )
}

raw_admin_timestamp <- function(value) {
  if (length(value) == 0L || is.na(value[[1]])) return("—")
  seconds <- suppressWarnings(as.numeric(value[[1]]))
  if (is.na(seconds) || seconds < 0) return("—")
  whole_seconds <- floor(seconds)
  hours <- whole_seconds %/% 3600L
  minutes <- (whole_seconds %% 3600L) %/% 60L
  remaining_seconds <- whole_seconds %% 60L
  if (hours > 0L) {
    sprintf("%02d:%02d:%02d", hours, minutes, remaining_seconds)
  } else {
    sprintf("%02d:%02d", minutes, remaining_seconds)
  }
}

raw_admin_table <- function(
    data,
    page_length = 10L,
    filter = "top",
    selection = "none") {
  if (nrow(data) == 0L) {
    data <- data.frame(message = "No rows are available for this view.")
    filter <- "none"
  }
  DT::datatable(
    data,
    rownames = FALSE,
    filter = filter,
    selection = selection,
    escape = TRUE,
    options = list(
      pageLength = page_length,
      scrollX = TRUE,
      autoWidth = TRUE,
      dom = "tip"
    )
  )
}

raw_admin_empty_plot <- function(message) {
  plotly::plot_ly(type = "scatter", mode = "markers") |>
    plotly::layout(
      xaxis = list(visible = FALSE),
      yaxis = list(visible = FALSE),
      annotations = list(list(
        text = message,
        x = 0.5,
        y = 0.5,
        xref = "paper",
        yref = "paper",
        showarrow = FALSE
      ))
    )
}

admin_format_time <- function(value) {
  if (length(value) == 0L) return("Not available")
  value <- value[[1]]
  if (is.na(value)) return("Not available")
  if (!inherits(value, "POSIXt")) {
    value <- classification_admin_parse_time(value)
  }
  if (is.na(value)) return("Not available")
  format(value, "%Y-%m-%d %H:%M:%S UTC", tz = "UTC")
}

admin_format_times <- function(values) {
  parsed <- classification_admin_parse_time(values)
  formatted <- format(parsed, "%Y-%m-%d %H:%M:%S UTC", tz = "UTC")
  formatted[is.na(parsed)] <- "Not available"
  formatted
}

admin_value <- function(value, fallback = "—") {
  if (length(value) == 0L || is.na(value[[1]]) || !nzchar(as.character(value[[1]]))) {
    return(fallback)
  }
  as.character(value[[1]])
}

admin_value_box <- function(title, value) {
  bslib::value_box(title = title, value = admin_value(value))
}

admin_empty_plot <- function(message) {
  raw_admin_empty_plot(message)
}

admin_bar_plot <- function(data, label, value, x_title = "Titles") {
  if (nrow(data) == 0L) return(admin_empty_plot("No data are available."))
  data <- data[order(data[[value]], decreasing = FALSE), , drop = FALSE]
  plotly::plot_ly(
    data,
    x = data[[value]],
    y = stats::reorder(data[[label]], data[[value]]),
    type = "bar",
    orientation = "h",
    text = data[[value]],
    textposition = "auto",
    hovertemplate = paste0("%{y}<br>", x_title, ": %{x:,}<extra></extra>")
  ) |>
    plotly::layout(
      xaxis = list(title = x_title),
      yaxis = list(title = ""),
      margin = list(l = 100, r = 20, t = 10, b = 45)
    )
}

admin_datatable <- function(data, page_length = 10L, filter = "top", scroll_x = TRUE) {
  if (nrow(data) == 0L) {
    data <- data.frame(message = "No rows matched the current selection.")
    filter <- "none"
  }
  names(data) <- tools::toTitleCase(
    gsub("_", " ", names(data), fixed = TRUE)
  )
  DT::datatable(
    data,
    rownames = FALSE,
    filter = filter,
    options = list(
      pageLength = page_length,
      scrollX = scroll_x,
      autoWidth = TRUE,
      dom = "tip"
    )
  )
}

admin_display_runs <- function(runs) {
  if (nrow(runs) == 0L) return(data.frame())
  runs |>
    transmute(
      run_id = .data$run_id,
      status = .data$status,
      created_utc = admin_format_times(.data$created_at),
      titles = .data$title_count,
      talents = .data$talents,
      model = .data$model,
      results_applied = .data$result_count,
      unique_tags = .data$tag_count,
      failed = .data$failed_count
    )
}
```

# {.toolbar}

```{r}
div(
  class = "admin-global-toolbar",
  actionButton("refresh_dashboard", "Refresh dashboard", class = "btn-primary"),
  uiOutput("database_freshness"),
  tags$span(class = "admin-note", "Read-only administration")
)
```

# Data {scrolling="true"}

The overview inventories the in-scope talent catalog, analytics, subtitle,
chat, and operational relations. Counts and timestamps come directly from the
unified lakehouse.

## Row {height=18%}

```{r}
#| title: "Scoped Relations"
uiOutput("relation_count")
```

```{r}
#| title: "Active Talents"
uiOutput("active_talent_count")
```

```{r}
#| title: "Catalog Videos"
uiOutput("video_count")
```

```{r}
#| title: "Checks Needing Review"
uiOutput("issue_count")
```

## Row {height=40%}

```{r}
#| title: "Rows by Relation"
plotlyOutput("relation_rows_plot", height = "100%")
```

```{r}
#| title: "Videos with Analytics, Subtitles, or Chat"
plotlyOutput("coverage_plot", height = "100%")
```

## Row {height=42%}

```{r}
#| title: "Relation Inventory and Recency"
DTOutput("relation_inventory")
```

<h2 class="admin-section-heading">Data Health</h2>

These checks focus on broken catalog relationships, missing lineage, blank text,
invalid count metrics, unresolved collection failures, and failed relevant
pipeline runs. A nonzero result is a signal to investigate, not an automatic
repair instruction.

## Row {height=18%}

```{r}
#| title: "Critical Checks"
uiOutput("critical_count")
```

```{r}
#| title: "Warnings"
uiOutput("warning_count")
```

```{r}
#| title: "Passing Checks"
uiOutput("passing_count")
```

## Row {height=82%}

```{r}
#| title: "Health Check Results"
DTOutput("health_checks")
```

<h2 class="admin-section-heading">Explore Relations</h2>

Choose a relation and optional exact talent or video filter on this page.
The preview is deliberately row-limited; the download contains the same rows
shown in the current preview.

## Row {height=22%}

```{r}
#| title: "Relation Preview Controls"
fluidRow(
  column(3, uiOutput("relation_selector")),
  column(3, uiOutput("talent_filter")),
  column(3, uiOutput("video_filter")),
  column(
    3,
    numericInput(
      "row_limit",
      "Maximum preview rows",
      value = 500,
      min = 25,
      max = 5000,
      step = 25
    ),
    actionButton("load_preview", "Load preview")
  )
)
```

## Row {height=18%}

```{r}
#| title: "Loaded Relation"
uiOutput("selected_relation_name")
```

```{r}
#| title: "Relation Rows"
uiOutput("selected_relation_rows")
```

```{r}
#| title: "Relation Columns"
uiOutput("selected_relation_columns")
```

```{r}
#| title: "Preview Export"
div(
  class = "p-3",
  uiOutput("preview_download"),
  tags$p(
    class = "admin-note mt-3",
    textOutput("preview_load_status", inline = TRUE)
  )
)
```

## Row {height=60%}

```{r}
#| title: "Relation Contents"
DTOutput("relation_preview")
```

<h2 class="admin-section-heading">Descriptive Statistics</h2>

Column profiles report nulls and approximate distinct counts. Numeric summaries
report minimum, mean, median, and maximum. Profiling can scan a large relation,
so it only reruns when requested.

## Row {height=14%}

```{r}
#| title: "Profile Controls"
div(
  class = "p-3",
  uiOutput("profile_relation_selector"),
  actionButton("profile_relation_action", "Profile selected relation", class = "btn-primary"),
  tags$span(class = "admin-note ms-3", textOutput("profiled_relation", inline = TRUE))
)
```

## Row {height=43%}

```{r}
#| title: "Column Completeness and Cardinality"
DTOutput("column_profile")
```

## Row {height=43%}

```{r}
#| title: "Numeric Summary"
DTOutput("numeric_profile")
```

<h2 class="admin-section-heading">Talent Coverage</h2>

This page compares catalog membership with analytics, subtitle, and chat
coverage for each talent. Zeroes can be valid when a source does not apply, but
they make gaps easy to spot.

## Row {height=42%}

```{r}
#| title: "Distinct Videos by Available Data Type"
plotlyOutput("talent_coverage_plot", height = "100%")
```

## Row {height=58%}

```{r}
#| title: "Talent Coverage Detail"
DTOutput("talent_coverage")
```

# Processing {scrolling="true"}

The processing workspace combines transcript inspection with recent pipeline
and ingestion activity. Choose a processing batch, review every recorded video
attempt in that batch, then search by video ID, title, talent, or result. Times
are UTC.

```{r}
#| title: "Browse and Inspect Transcripts"
div(
  class = "transcript-processes-layout",
  div(
    class = "transcript-browser-pane",
    tags$h3("Batch and Videos"),
    tags$p(
      class = "transcript-workflow",
      "Choose batch → Search/filter videos → Select video"
    ),
    selectInput(
      "transcript_run",
      "Processing batch",
      choices = character(),
      width = "100%"
    ),
    uiOutput("transcript_run_summary"),
    tags$div(class = "transcript-panel-divider"),
    textInput(
      "transcript_batch_search",
      "Search this batch",
      value = "",
      placeholder = "For example: 6dm9kUCCfhM, RIU5, or Failed",
      width = "100%"
    ),
    uiOutput("transcript_search_summary"),
    DTOutput("transcript_tracks", height = "auto", fill = FALSE)
  ),
  div(
    class = "transcript-detail-pane",
    tags$h3("Selected Video Transcript"),
    div(
      class = "transcript-header-actions",
      uiOutput("selected_transcript_video"),
      downloadButton("download_transcript", "Download full transcript CSV")
    ),
    tabsetPanel(
      id = "transcript_view",
      type = "tabs",
      tabPanel("Reading View", uiOutput("transcript_reading")),
      tabPanel(
        "Audit / Table View",
        DTOutput("transcript_sentences", height = "auto", fill = FALSE)
      )
    )
  )
)
```

<h2 class="admin-section-heading">Recent Activity</h2>

Relevant pipeline runs exclude classification, qualitative coding, and summary
generation. Ingestion events are retained when their destination is in
`catalog`, `clean`, `analytics`, or `text`.

## Row {height=48%}

```{r}
#| title: "Recent Relevant Pipeline Runs"
DTOutput("recent_runs")
```

## Row {height=52%}

```{r}
#| title: "Recent Ingestion Events"
DTOutput("recent_events")
```

# Classification {scrolling="true"}

The classification diagnostics report the newest traceable Batch run and
current active-version coverage. Batch status reflects the scheduler's most
recent check; this dashboard does not poll OpenAI directly.

## Row {height=18%}

```{r}
#| title: "Current Run"
uiOutput("latest_status")
```

```{r}
#| title: "Titles in Run"
uiOutput("latest_titles")
```

```{r}
#| title: "Current Pending Titles"
uiOutput("current_pending")
```

```{r}
#| title: "Last Checked"
uiOutput("latest_checked")
```

## Row {height=38%}

```{r}
#| title: "Titles by Talent in Latest Run"
plotlyOutput("latest_talent_plot", height = "100%")
```

```{r}
#| title: "Current Active-Version Coverage"
plotlyOutput("classification_coverage_plot", height = "100%")
```

## Row {height=44%}

```{r}
#| title: "Recent Classification Runs"
DTOutput("run_history")
```

<h2 class="admin-section-heading">Classification Run Details</h2>

Select a run below to inspect its essential metrics, talents, tags,
and titles.

## Row {height=16%}

```{r}
#| title: "Run Controls"
fluidRow(
  column(8, uiOutput("run_selector")),
  column(
    4,
    div(
      class = "p-3",
      downloadButton("download_selected_run", "Download selected run")
    )
  )
)
```

## Row {height=36%}

```{r}
#| title: "Selected Run Summary"
DTOutput("selected_run_summary")
```

```{r}
#| title: "Talent Membership"
plotlyOutput("selected_run_talents", height = "100%")
```

```{r}
#| title: "Tag Frequency"
plotlyOutput("selected_run_tags", height = "100%")
```

## Row {height=64%}

```{r}
#| title: "Titles in Selected Run"
DTOutput("selected_run_titles")
```

<h2 class="admin-section-heading">Classification Results</h2>

This page exposes all classification rows, including older migrated versions.

## Row {height=28%}

```{r}
#| title: "Data Filters"
uiOutput("classification_filters")
```

```{r}
#| title: "Filtered Rows"
uiOutput("filtered_count")
```

```{r}
#| title: "Filtered Export"
div(
  class = "p-3",
  downloadButton("download_filtered_results", "Download filtered data"),
  tags$p(
    class = "admin-note mt-3",
    "The download includes all classification fields and lineage identifiers."
  )
)
```

## Row {height=72%}

```{r}
#| title: "All Classification Results"
DTOutput("classification_results")
```

<h2 class="admin-section-heading">Classification Topics &amp; Tags</h2>

Counts include every retained title version, not only the active version or
most recent run.

## Row {height=18%}

```{r}
#| title: "Topics"
uiOutput("topic_inventory_count")
```

```{r}
#| title: "Tags"
uiOutput("tag_inventory_count")
```

## Row {height=41%}

```{r}
#| title: "All Topics"
DTOutput("topic_inventory")
```

## Row {height=41%}

```{r}
#| title: "All Tags"
DTOutput("tag_inventory")
```

```{r}
#| label: server
#| context: server
#| include: false


transcript_runs <- reactive({
  input$refresh_dashboard
  tryCatch(
    raw_data_admin_transcript_runs(raw_admin_database_path),
    error = function(error) {
      validate(need(FALSE, paste("Transcript runs unavailable:", conditionMessage(error))))
    }
  )
})

observe({
  runs <- transcript_runs()
  if (nrow(runs) == 0L) return()
  attempted <- vapply(
    runs$error_summary,
    raw_data_admin_transcript_run_metric,
    numeric(1),
    keys = c("attempted", "new_started", "examined")
  )
  attempt_label <- ifelse(
    is.na(attempted),
    "attempt count unavailable",
    paste(format(attempted, big.mark = ",", trim = TRUE), "attempted")
  )
  choices <- stats::setNames(
    runs$pipeline_run_id,
    paste(
      raw_admin_times(runs$started_at),
      toupper(runs$status),
      attempt_label,
      sep = " • "
    )
  )
  current <- isolate(input$transcript_run)
  selected <- if (!is.null(current) && current %in% runs$pipeline_run_id) {
    current
  } else {
    runs$pipeline_run_id[[1]]
  }
  updateSelectInput(
    session,
    "transcript_run",
    choices = choices,
    selected = selected
  )
})

selected_transcript_run <- reactive({
  runs <- transcript_runs()
  req(nrow(runs) > 0L)
  run_id <- raw_admin_input(input$transcript_run, runs$pipeline_run_id[[1]])
  if (!run_id %in% runs$pipeline_run_id) run_id <- runs$pipeline_run_id[[1]]
  run <- runs[runs$pipeline_run_id == run_id, , drop = FALSE]
  req(nrow(run) == 1L)
  run
})

output$transcript_run_summary <- renderUI({
  run <- selected_transcript_run()
  details <- raw_data_admin_transcript_run_details(run$error_summary)
  duration <- if (!is.na(run$duration_seconds[[1]])) {
    paste(round(run$duration_seconds[[1]] / 60, 1), "minutes")
  } else {
    "Not recorded (batch may still be running or may have stopped unexpectedly)"
  }
  summary_item <- function(label, value, wide = FALSE) {
    tags$div(
      class = paste(
        "transcript-summary-item",
        if (isTRUE(wide)) "transcript-summary-wide" else ""
      ),
      tags$span(class = "transcript-summary-label", label),
      tags$span(class = "transcript-summary-value", value)
    )
  }
  tagList(
    tags$div(
      class = "transcript-batch-summary",
      summary_item("Status", toupper(raw_admin_value(run$status))),
      summary_item("Duration", duration),
      summary_item("Started", raw_admin_time(run$started_at)),
      summary_item("Finished", raw_admin_time(run$completed_at)),
      summary_item("Batch counts", details$counts, wide = TRUE)
    ),
    if (!is.na(details$issues)) {
      tags$details(
        class = "admin-note mt-2",
        tags$summary("Recorded issues"),
        tags$p(details$issues)
      )
    }
  )
})

transcript_tracks_all <- reactive({
  run <- selected_transcript_run()
  tryCatch(
    raw_data_admin_transcript_tracks(raw_admin_database_path, run$pipeline_run_id[[1]]),
    error = function(error) {
      validate(need(FALSE, paste("Transcript records unavailable:", conditionMessage(error))))
    }
  )
})

transcript_tracks <- reactive({
  raw_data_admin_filter_transcript_tracks(
    transcript_tracks_all(),
    raw_admin_input(input$transcript_batch_search, "")
  )
})

output$transcript_search_summary <- renderUI({
  total <- nrow(transcript_tracks_all())
  shown <- nrow(transcript_tracks())
  tags$p(
    class = "admin-note",
    paste0("Showing ", shown, " of ", total, " recorded videos in this batch.")
  )
})

output$transcript_tracks <- renderDT({
  tracks <- transcript_tracks()
  if (nrow(tracks) == 0L) {
    return(raw_admin_table(data.frame(message = "No matching videos."), filter = "none"))
  }
  talent_name <- raw_admin_values(tracks$talent_name)
  talent_code <- raw_admin_values(tracks$talent_code)
  talent <- ifelse(
    talent_name == "—",
    talent_code,
    ifelse(talent_code == "—", talent_name, paste0(talent_name, " (", talent_code, ")"))
  )
  display <- data.frame(
    Title = raw_admin_values(tracks$title, "Untitled video"),
    Talent = talent,
    Result = raw_admin_values(tracks$result),
    Language = raw_admin_values(tracks$subtitle_language),
    `Video ID` = raw_admin_values(tracks$video_id),
    check.names = FALSE
  )
  DT::datatable(
    display,
    rownames = FALSE,
    filter = "none",
    selection = "single",
    escape = TRUE,
    class = "compact stripe hover row-border transcript-video-table",
    options = list(
      dom = "t",
      ordering = FALSE,
      paging = FALSE,
      scrollY = "46vh",
      scrollCollapse = TRUE,
      autoWidth = FALSE,
      columnDefs = list(
        list(width = "38%", targets = 0L),
        list(width = "24%", targets = 1L),
        list(width = "14%", targets = 2L),
        list(width = "10%", targets = 3L),
        list(width = "14%", targets = 4L)
      )
    )
  )
})

selected_transcript_track <- reactive({
  tracks <- transcript_tracks()
  selected <- input$transcript_tracks_rows_selected
  req(length(selected) == 1L, selected >= 1L, selected <= nrow(tracks))
  tracks[selected, , drop = FALSE]
})

output$selected_transcript_video <- renderUI({
  tracks <- transcript_tracks()
  selected <- input$transcript_tracks_rows_selected
  if (nrow(tracks) == 0L) {
    return(tags$p(
      class = "transcript-empty-state",
      "No videos match the current batch search."
    ))
  }
  if (length(selected) != 1L || selected < 1L || selected > nrow(tracks)) {
    return(tags$p(
      class = "transcript-empty-state",
      "Select one video on the left to inspect its transcript."
    ))
  }
  track <- tracks[selected, , drop = FALSE]
  talent_name <- raw_admin_value(track$talent_name)
  talent_code <- raw_admin_value(track$talent_code)
  talent <- if (talent_name == "—") {
    talent_code
  } else if (talent_code == "—") {
    talent_name
  } else {
    paste0(talent_name, " (", talent_code, ")")
  }
  transcript_size <- paste(
    raw_admin_value(track$sentences, "0"), "sentences •",
    raw_admin_value(track$blocks, "0"), "blocks"
  )
  block_health <- paste(
    raw_admin_value(track$failed_blocks, "0"), "failed •",
    raw_admin_value(track$incomplete_blocks, "0"), "incomplete"
  )
  tagList(
    tags$div(
      class = "transcript-video-heading",
      tags$h4(raw_admin_value(track$title, "Untitled video")),
      tags$span(class = "transcript-video-id", raw_admin_value(track$video_id))
    ),
    tags$div(
      class = "transcript-video-metadata",
      raw_admin_metadata_item("Talent", talent),
      raw_admin_metadata_item("Result", track$result),
      raw_admin_metadata_item("Subtitle language", track$subtitle_language),
      raw_admin_metadata_item("Track type", track$subtitle_track_type),
      raw_admin_metadata_item("Transcript size", transcript_size),
      raw_admin_metadata_item("Block health", block_health),
      raw_admin_metadata_item("Source scope", track$source_scope),
      raw_admin_metadata_item("Pipeline", track$pipeline_version),
      raw_admin_metadata_item("Approximate alignment", track$approximate_alignment)
    ),
    if ("block_errors" %in% names(track) && !is.na(track$block_errors[[1]])) {
      tags$details(
        class = "admin-note mt-2",
        tags$summary("Recorded processing error"),
        tags$p(track$block_errors[[1]])
      )
    }
  )
})

transcript_sentences <- reactive({
  track <- selected_transcript_track()
  tryCatch(
    raw_data_admin_transcript_text(
      raw_admin_database_path, selected_transcript_run()$pipeline_run_id[[1]],
      track
    ),
    error = function(error) {
      validate(need(FALSE, paste("Transcript text unavailable:", conditionMessage(error))))
    }
  )
})

output$transcript_reading <- renderUI({
  selected <- input$transcript_tracks_rows_selected
  validate(need(
    length(selected) == 1L,
    "Select one video on the left to view its transcript."
  ))
  sentences <- transcript_sentences()
  validate(need(
    nrow(sentences) > 0L,
    "This video did not publish transcript text in the selected batch."
  ))
  rows <- lapply(seq_len(nrow(sentences)), function(index) {
    approximate <- isTRUE(sentences$timestamps_approximate[[index]])
    timestamp <- paste0(
      if (approximate) "~" else "",
      raw_admin_timestamp(sentences$start_sec[index]),
      "–",
      raw_admin_timestamp(sentences$end_sec[index])
    )
    audit_hint <- paste(
      "Block", raw_admin_value(sentences$block_number[index]),
      "• Sentence", raw_admin_value(sentences$sentence_number[index]),
      "•", raw_admin_value(sentences$source_alignment_status[index])
    )
    tags$div(
      class = "transcript-reading-row",
      title = audit_hint,
      tags$span(class = "transcript-reading-time", timestamp),
      tags$span(
        class = "transcript-reading-text",
        raw_admin_value(sentences$sentence_text[index], "")
      )
    )
  })
  tags$div(class = "transcript-reading-list", rows)
})

output$transcript_sentences <- renderDT({
  selected <- input$transcript_tracks_rows_selected
  validate(need(
    length(selected) == 1L,
    "Select one video row in the batch table above to view its transcript."
  ))
  sentences <- transcript_sentences()
  validate(need(
    nrow(sentences) > 0L,
    "This video did not publish transcript text in the selected batch."
  ))
  raw_admin_table(sentences, page_length = 25L)
})

output$download_transcript <- downloadHandler(
  filename = function() "processed_transcript.csv",
  content = function(file) {
    text <- transcript_sentences()
    validate(need(nrow(text) > 0L, "No published transcript to download."))
    track <- selected_transcript_track()
    metadata <- track[rep(1L, nrow(text)), c("video_id", "title", "talent_code", "talent_name")]
    run_id <- selected_transcript_run()$pipeline_run_id[[1]]
    utils::write.csv(cbind(pipeline_run_id = run_id, metadata, text),
                     file, row.names = FALSE, na = "")
  }
)

raw_admin_snapshot <- reactive({
  input$refresh_dashboard
  withProgress(message = "Refreshing raw-data administration", value = 0, {
    incProgress(0.15, detail = "Inventorying relations")
    snapshot <- raw_data_admin_snapshot(raw_admin_database_path)
    incProgress(0.85, detail = "Preparing health and coverage views")
    snapshot
  })
})

output$database_freshness <- renderUI({
  snapshot <- raw_admin_snapshot()
  tags$div(
    class = "admin-refresh-status",
    tags$span(paste("Refreshed", raw_admin_time(snapshot$refreshed_at))),
    tags$span(paste("DuckDB modified", raw_admin_time(snapshot$database_modified_at))),
    tags$span(
      class = "admin-path",
      title = snapshot$database_path,
      basename(snapshot$database_path)
    )
  )
})

output$relation_selector <- renderUI({
  relations <- raw_admin_snapshot()$relations
  choices <- stats::setNames(
    relations$relation,
    paste(relations$domain, relations$relation, sep = " • ")
  )
  selected <- isolate(input$selected_relation)
  if (is.null(selected) || !selected %in% relations$relation) {
    preferred <- "analytics.video_latest_performance"
    selected <- if (preferred %in% relations$relation) preferred else relations$relation[[1]]
  }
  selectInput("selected_relation", "Explore relation", choices, selected = selected)
})

selected_relation_metadata <- reactive({
  relations <- raw_admin_snapshot()$relations
  relation <- input$selected_relation
  if (is.null(relation) || !relation %in% relations$relation) {
    relation <- relations$relation[[1]]
  }
  relations[relations$relation == relation, , drop = FALSE]
})

selected_relation_columns <- reactive({
  metadata <- selected_relation_metadata()
  con <- raw_data_admin_connect(raw_admin_database_path)
  on.exit(raw_data_admin_disconnect(con), add = TRUE)
  resolved <- raw_data_admin_resolve_relation(con, metadata$relation[[1]])
  resolved$columns$column_name
})

output$talent_filter <- renderUI({
  supported <- "talent_code" %in% selected_relation_columns()
  if (!supported) {
    return(raw_admin_disabled_input(selectInput(
      "selected_talent",
      "Exact talent (not available for this relation)",
      choices = c("Not applicable" = "")
    )))
  }
  coverage <- raw_admin_snapshot()$talent_coverage
  choices <- c(
    "All talents" = "",
    stats::setNames(
      coverage$talent_code,
      paste(coverage$talent_code, coverage$talent_name, sep = " • ")
    )
  )
  selected <- isolate(raw_admin_input(input$selected_talent, ""))
  if (!selected %in% unname(choices)) selected <- ""
  selectizeInput("selected_talent", "Exact talent", choices, selected = selected)
})

output$video_filter <- renderUI({
  supported <- "video_id" %in% selected_relation_columns()
  value <- isolate(raw_admin_input(input$video_filter, ""))
  input <- textInput(
    "video_filter",
    if (supported) "Exact video ID" else "Exact video ID (not available for this relation)",
    value = if (supported) value else ""
  )
  if (supported) input else raw_admin_disabled_input(input)
})

output$profile_relation_selector <- renderUI({
  relations <- raw_admin_snapshot()$relations
  choices <- stats::setNames(
    relations$relation,
    paste(relations$domain, relations$relation, sep = " • ")
  )
  selected <- isolate(input$profile_relation)
  if (is.null(selected) || !selected %in% relations$relation) {
    selected <- selected_relation_metadata()$relation[[1]]
  }
  selectInput("profile_relation", "Profile relation", choices, selected = selected)
})

preview_state <- reactiveVal(NULL)

observeEvent(input$load_preview, {
  metadata <- selected_relation_metadata()
  state <- withProgress(message = "Loading relation preview", value = 0.4, {
    data <- raw_data_admin_preview(
      database_path = raw_admin_database_path,
      relation = metadata$relation[[1]],
      talent_code = raw_admin_input(input$selected_talent, ""),
      video_id = raw_admin_input(input$video_filter, ""),
      limit = raw_admin_input(input$row_limit, 500L)
    )
    incProgress(0.6)
    list(
      metadata = metadata,
      talent_code = raw_admin_input(input$selected_talent, ""),
      video_id = raw_admin_input(input$video_filter, ""),
      limit = raw_admin_input(input$row_limit, 500L),
      data = data
    )
  })
  preview_state(state)
}, ignoreInit = TRUE)

profile_state <- reactiveVal(NULL)

observeEvent(input$profile_relation_action, {
  req(input$profile_relation)
  relations <- raw_admin_snapshot()$relations
  metadata <- relations[
    relations$relation == input$profile_relation,
    ,
    drop = FALSE
  ]
  req(nrow(metadata) == 1L)
  state <- withProgress(message = "Profiling selected relation", value = 0.2, {
    profile <- raw_data_admin_profile(
      raw_admin_database_path,
      metadata$relation[[1]]
    )
    incProgress(0.8)
    list(relation = metadata$relation[[1]], profile = profile)
  })
  profile_state(state)
}, ignoreInit = TRUE)

preview_controls_changed <- reactive({
  state <- preview_state()
  if (is.null(state)) return(TRUE)
  current_relation <- selected_relation_metadata()$relation[[1]]
  !identical(current_relation, state$metadata$relation[[1]]) ||
    !identical(raw_admin_input(input$selected_talent, ""), state$talent_code) ||
    !identical(raw_admin_input(input$video_filter, ""), state$video_id) ||
    !identical(as.numeric(raw_admin_input(input$row_limit, 500L)), as.numeric(state$limit))
})

output$relation_count <- renderUI({
  raw_admin_value_box("In-scope relations", nrow(raw_admin_snapshot()$relations))
})

output$active_talent_count <- renderUI({
  coverage <- raw_admin_snapshot()$talent_coverage
  raw_admin_value_box("Active talents", scales::comma(sum(coverage$active, na.rm = TRUE)))
})

output$video_count <- renderUI({
  relation <- raw_admin_snapshot()$relations |>
    filter(.data$relation == "catalog.videos")
  raw_admin_value_box("Catalog videos", scales::comma(relation$row_count))
})

output$issue_count <- renderUI({
  checks <- raw_admin_snapshot()$health_checks
  count <- sum(checks$status %in% c("Critical", "Review", "Unavailable"))
  raw_admin_value_box("Checks needing review", count)
})

output$critical_count <- renderUI({
  checks <- raw_admin_snapshot()$health_checks
  raw_admin_value_box("Critical checks", sum(checks$status == "Critical"))
})

output$warning_count <- renderUI({
  checks <- raw_admin_snapshot()$health_checks
  raw_admin_value_box(
    "Warnings or unavailable",
    sum(checks$status %in% c("Review", "Unavailable"))
  )
})

output$passing_count <- renderUI({
  checks <- raw_admin_snapshot()$health_checks
  raw_admin_value_box("Passing checks", sum(checks$status == "Pass"))
})

output$relation_rows_plot <- renderPlotly({
  relations <- raw_admin_snapshot()$relations |>
    filter(!is.na(.data$row_count), .data$row_count > 0) |>
    arrange(.data$row_count)
  if (nrow(relations) == 0L) return(raw_admin_empty_plot("No relation counts available."))
  plotly::plot_ly(
    relations,
    x = ~row_count,
    y = ~stats::reorder(relation, row_count),
    color = ~domain,
    type = "bar",
    orientation = "h",
    hovertemplate = "%{y}<br>%{x:,} rows<extra></extra>"
  ) |>
    plotly::layout(
      xaxis = list(title = "Rows", type = "log"),
      yaxis = list(title = ""),
      legend = list(orientation = "h"),
      margin = list(l = 205, r = 20, t = 10, b = 50)
    )
})

output$coverage_plot <- renderPlotly({
  coverage <- raw_admin_snapshot()$talent_coverage
  columns <- intersect(
    c("videos_with_analytics", "videos_with_subtitles", "videos_with_chat"),
    names(coverage)
  )
  if (nrow(coverage) == 0L || length(columns) == 0L) {
    return(raw_admin_empty_plot("No talent coverage data available."))
  }
  long <- coverage |>
    select("talent_code", all_of(columns)) |>
    pivot_longer(-all_of("talent_code"), names_to = "data_type", values_to = "videos") |>
    mutate(
      data_type = dplyr::recode(
        .data$data_type,
        videos_with_analytics = "Analytics",
        videos_with_subtitles = "Subtitles",
        videos_with_chat = "Chat"
      )
    )
  plotly::plot_ly(
    long,
    x = ~talent_code,
    y = ~videos,
    color = ~data_type,
    type = "bar",
    hovertemplate = "%{x}<br>%{fullData.name}: %{y:,}<extra></extra>"
  ) |>
    plotly::layout(
      barmode = "group",
      xaxis = list(title = "Talent"),
      yaxis = list(title = "Distinct videos"),
      legend = list(orientation = "h"),
      margin = list(l = 65, r = 20, t = 10, b = 75)
    )
})

output$relation_inventory <- renderDT({
  data <- raw_admin_snapshot()$relations |>
    transmute(
      Domain = .data$domain,
      Relation = .data$relation,
      Type = .data$table_type,
      Rows = .data$row_count,
      Columns = .data$column_count,
      `Recency field` = .data$recency_column,
      Earliest = .data$earliest_value,
      Latest = .data$latest_value,
      Description = .data$description
    )
  raw_admin_table(data, page_length = 20L)
})

output$health_checks <- renderDT({
  checks <- raw_admin_snapshot()$health_checks |>
    transmute(
      Status = .data$status,
      Severity = .data$severity,
      Check = .data$check_name,
      `Affected rows` = .data$affected_rows,
      Relation = .data$relation,
      Details = .data$details
    )
  raw_admin_table(checks, page_length = 20L) |>
    DT::formatStyle(
      "Status",
      color = DT::styleEqual(
        c("Critical", "Review", "Unavailable", "Pass"),
        c("#842029", "#664d03", "#41464b", "#0f5132")
      ),
      backgroundColor = DT::styleEqual(
        c("Critical", "Review", "Unavailable", "Pass"),
        c("#f8d7da", "#fff3cd", "#e2e3e5", "#d1e7dd")
      ),
      fontWeight = "600"
    )
})

output$selected_relation_name <- renderUI({
  state <- preview_state()
  raw_admin_value_box(
    "Loaded relation",
    if (is.null(state)) "Not loaded" else state$metadata$relation
  )
})

output$selected_relation_rows <- renderUI({
  state <- preview_state()
  raw_admin_value_box(
    "Relation rows",
    if (is.null(state)) "—" else scales::comma(state$metadata$row_count)
  )
})

output$selected_relation_columns <- renderUI({
  state <- preview_state()
  raw_admin_value_box(
    "Relation columns",
    if (is.null(state)) "—" else state$metadata$column_count
  )
})

output$relation_preview <- renderDT({
  state <- preview_state()
  if (is.null(state)) {
    return(raw_admin_table(
      data.frame(message = "Choose preview controls, then select Load preview."),
      page_length = 25L,
      filter = "none"
    ))
  }
  raw_admin_table(state$data, page_length = 25L)
})

output$preview_load_status <- renderText({
  state <- preview_state()
  if (is.null(state)) {
    return("Load a preview before exporting data.")
  }
  if (preview_controls_changed()) {
    "Controls have changed. Load the preview again before exporting the new selection."
  } else {
    "The export matches the loaded relation, filters, and row limit."
  }
})

output$preview_download <- renderUI({
  state <- preview_state()
  if (is.null(state) || preview_controls_changed()) {
    return(raw_admin_disabled_input(actionButton(
      "download_preview_disabled",
      "Download preview CSV"
    )))
  }
  downloadButton("download_preview", "Download preview CSV")
})

output$download_preview <- downloadHandler(
  filename = function() {
    state <- preview_state()
    req(!is.null(state))
    paste0(gsub("[.]", "_", state$metadata$relation[[1]]), "_preview.csv")
  },
  content = function(file) {
    state <- preview_state()
    req(!is.null(state))
    utils::write.csv(state$data, file, row.names = FALSE, na = "")
  }
)

output$profiled_relation <- renderText({
  state <- profile_state()
  if (is.null(state)) {
    "No relation has been profiled in this session."
  } else {
    paste("Current profile:", state$relation)
  }
})

output$column_profile <- renderDT({
  state <- profile_state()
  if (is.null(state)) {
    return(raw_admin_table(
      data.frame(message = "Choose a relation and select Profile selected relation."),
      page_length = 25L,
      filter = "none"
    ))
  }
  raw_admin_table(state$profile$columns, page_length = 25L)
})

output$numeric_profile <- renderDT({
  state <- profile_state()
  if (is.null(state)) {
    return(raw_admin_table(
      data.frame(message = "Choose a relation and select Profile selected relation."),
      page_length = 25L,
      filter = "none"
    ))
  }
  raw_admin_table(state$profile$numeric, page_length = 25L)
})

output$talent_coverage_plot <- renderPlotly({
  coverage <- raw_admin_snapshot()$talent_coverage
  columns <- intersect(
    c("videos_with_analytics", "videos_with_subtitles", "videos_with_chat"),
    names(coverage)
  )
  if (nrow(coverage) == 0L || length(columns) == 0L) {
    return(raw_admin_empty_plot("No talent coverage data available."))
  }
  long <- coverage |>
    select("talent_code", all_of(columns)) |>
    pivot_longer(-all_of("talent_code"), names_to = "data_type", values_to = "videos") |>
    mutate(
      data_type = dplyr::recode(
        .data$data_type,
        videos_with_analytics = "Analytics",
        videos_with_subtitles = "Subtitles",
        videos_with_chat = "Chat"
      )
    )
  plotly::plot_ly(
    long,
    x = ~talent_code,
    y = ~videos,
    color = ~data_type,
    type = "bar",
    hovertemplate = "%{x}<br>%{fullData.name}: %{y:,}<extra></extra>"
  ) |>
    plotly::layout(
      barmode = "group",
      xaxis = list(title = "Talent"),
      yaxis = list(title = "Distinct videos"),
      legend = list(orientation = "h")
    )
})

output$talent_coverage <- renderDT({
  coverage <- raw_admin_snapshot()$talent_coverage
  names(coverage) <- tools::toTitleCase(
    gsub("_", " ", names(coverage), fixed = TRUE)
  )
  raw_admin_table(coverage, page_length = 25L)
})

output$recent_runs <- renderDT({
  runs <- raw_admin_snapshot()$recent_runs
  if (nrow(runs) > 0L) {
    runs <- runs |>
      mutate(
        started_at = raw_admin_times(.data$started_at),
        completed_at = raw_admin_times(.data$completed_at)
      )
  }
  names(runs) <- tools::toTitleCase(
    gsub("_", " ", names(runs), fixed = TRUE)
  )
  raw_admin_table(runs, page_length = 15L)
})

output$recent_events <- renderDT({
  events <- raw_admin_snapshot()$recent_events
  if (nrow(events) > 0L) {
    events <- events |>
      mutate(event_at = raw_admin_times(.data$event_at))
  }
  names(events) <- tools::toTitleCase(
    gsub("_", " ", names(events), fixed = TRUE)
  )
  raw_admin_table(events, page_length = 15L)
})

admin_snapshot <- reactive({
  input$refresh_dashboard
  withProgress(message = "Refreshing classification operations", value = 0, {
    incProgress(0.2, detail = "Reading run manifests")
    snapshot <- classification_admin_load_snapshot(
      database_path = admin_database_path,
      run_root = admin_run_root
    )
    incProgress(0.8, detail = "Preparing dashboard data")
    snapshot
  })
})

latest_run <- reactive({
  runs <- admin_snapshot()$runs
  if (nrow(runs) == 0L) return(NULL)
  runs[1, , drop = FALSE]
})

output$run_selector <- renderUI({
  runs <- admin_snapshot()$runs
  if (nrow(runs) == 0L) return(helpText("No traceable runs were found."))
  choices <- stats::setNames(
    runs$run_id,
    paste(
      format(runs$created_at, "%Y-%m-%d %H:%M UTC", tz = "UTC"),
      runs$status,
      runs$run_id,
      sep = " • "
    )
  )
  selected <- isolate(input$selected_run)
  if (is.null(selected) || !selected %in% runs$run_id) selected <- runs$run_id[[1]]
  selectInput("selected_run", "Inspect run", choices, selected = selected)
})

selected_run <- reactive({
  runs <- admin_snapshot()$runs
  req(nrow(runs) > 0L)
  run_id <- input$selected_run
  if (is.null(run_id) || !run_id %in% runs$run_id) run_id <- runs$run_id[[1]]
  runs[runs$run_id == run_id, , drop = FALSE]
})

selected_run_results <- reactive({
  run <- selected_run()
  admin_snapshot()$results |>
    filter(.data$pipeline_run_id == run$pipeline_run_id[[1]])
})

selected_run_candidates <- reactive({
  run <- selected_run()
  admin_snapshot()$candidates |>
    filter(.data$run_id == run$run_id[[1]])
})

selected_run_combined <- reactive({
  candidates <- selected_run_candidates()
  results <- selected_run_results() |>
    select(
      pipeline_run_id,
      video_id,
      result_title = title,
      topic,
      language,
      tags,
      primary_reference,
      referenced_entities,
      confidence,
      model,
      profile_id,
      classification_status,
      collaborative_energy,
      community_milestones,
      interactive_entertainment,
      meme_viral,
      monetization,
      narrative_serialization,
      performance_artistry,
      personality_conversation
    )
  candidates |>
    left_join(results, by = c("pipeline_run_id", "video_id")) |>
    select(-all_of("result_title"))
})

output$latest_status <- renderUI({
  run <- latest_run()
  admin_value_box("Latest run status", if (is.null(run)) NA else run$status)
})

output$latest_titles <- renderUI({
  run <- latest_run()
  admin_value_box("Titles in run", if (is.null(run)) NA else scales::comma(run$title_count))
})

output$current_pending <- renderUI({
  pending <- sum(!admin_snapshot()$current_status$is_classified, na.rm = TRUE)
  admin_value_box("Current pending titles", scales::comma(pending))
})

output$latest_checked <- renderUI({
  run <- latest_run()
  checked <- if (is.null(run) || is.na(run$last_checked_at[[1]])) {
    NA_character_
  } else {
    format(run$last_checked_at[[1]], "%b %d, %H:%M UTC", tz = "UTC")
  }
  admin_value_box("Last checked", checked)
})

output$latest_talent_plot <- renderPlotly({
  run <- latest_run()
  if (is.null(run)) return(admin_empty_plot("No run data are available."))
  counts <- admin_snapshot()$candidates |>
    filter(.data$run_id == run$run_id[[1]]) |>
    count(.data$talent_code, name = "titles")
  admin_bar_plot(counts, "talent_code", "titles")
})

output$classification_coverage_plot <- renderPlotly({
  counts <- admin_snapshot()$current_status |>
    count(.data$classification_status, name = "titles") |>
    mutate(
      classification_status = tools::toTitleCase(
        gsub("_", " ", .data$classification_status, fixed = TRUE)
      )
    )
  admin_bar_plot(counts, "classification_status", "titles")
})

output$run_history <- renderDT({
  admin_datatable(admin_display_runs(admin_snapshot()$runs), page_length = 10L)
})

output$selected_run_summary <- renderDT({
  run <- selected_run()
  summary <- data.frame(
    metric = c(
      "Status", "Created", "Model", "Title version", "Titles", "Talents",
      "API requests", "Results applied", "Unique tags", "Failed responses"
    ),
    value = c(
      run$status, admin_format_time(run$created_at), run$model,
      run$title_version_id, scales::comma(run$title_count), run$talent_count,
      scales::comma(run$request_count), scales::comma(run$result_count),
      run$tag_count, run$failed_count
    )
  )
  admin_datatable(summary, page_length = 15L, filter = "none")
})

output$selected_run_talents <- renderPlotly({
  counts <- selected_run_candidates() |>
    count(.data$talent_code, name = "titles")
  admin_bar_plot(counts, "talent_code", "titles")
})

output$selected_run_tags <- renderPlotly({
  tags <- classification_admin_tag_rows(selected_run_results()) |>
    count(.data$tag, name = "titles", sort = TRUE) |>
    slice_head(n = 20L)
  if (nrow(tags) == 0L) {
    return(admin_empty_plot("Tags appear after this run is applied."))
  }
  admin_bar_plot(tags, "tag", "titles")
})

output$selected_run_titles <- renderDT({
  data <- selected_run_combined() |>
    select(
      video_id,
      talent_code,
      title = title_raw,
      content_type,
      published_at,
      topic,
      tags,
      confidence,
      personality_conversation,
      classification_status,
      model
    )
  admin_datatable(data, page_length = 15L)
})

output$classification_filters <- renderUI({
  results <- admin_snapshot()$results
  choice_values <- function(values) {
    values <- as.character(values)
    sort(unique(values[!is.na(values) & nzchar(values)]))
  }
  fluidRow(
    column(3, selectizeInput("data_talents", "Talent", choice_values(results$talent_code), multiple = TRUE)),
    column(3, selectizeInput("data_versions", "Title version", choice_values(results$title_version_id), multiple = TRUE)),
    column(3, selectizeInput("data_topics", "Topic", choice_values(results$topic), multiple = TRUE)),
    column(
      3,
      selectizeInput("data_tags", "Tags (match all selected)", choices = NULL, multiple = TRUE)
    )
  )
})

observe({
  results <- admin_snapshot()$results
  updateSelectizeInput(
    session,
    "data_tags",
    choices = sort(unique(unlist(results$tag_values, use.names = FALSE))),
    server = TRUE
  )
})

filtered_results <- reactive({
  results <- admin_snapshot()$results
  if (length(input$data_talents) > 0L) results <- results |> filter(.data$talent_code %in% input$data_talents)
  if (length(input$data_versions) > 0L) results <- results |> filter(.data$title_version_id %in% input$data_versions)
  if (length(input$data_topics) > 0L) results <- results |> filter(.data$topic %in% input$data_topics)
  if (length(input$data_tags) > 0L) {
    keep <- vapply(results$tag_values, function(values) all(input$data_tags %in% values), logical(1))
    results <- results[keep, , drop = FALSE]
  }
  results
})

filtered_results_export <- reactive({
  filtered_results() |>
    mutate(
      run = ifelse(
        is.na(.data$pipeline_run_id),
        paste0("legacy-untracked/", .data$title_version_id),
        .data$pipeline_run_id
    )
    ) |>
    select(
      run,
      video_id,
      talent_code,
      talent_name,
      title,
      title_version_id,
      model,
      topic,
      language,
      tags,
      primary_reference,
      referenced_entities,
      confidence,
      classification_status,
      profile_id,
      collaborative_energy,
      community_milestones,
      interactive_entertainment,
      meme_viral,
      monetization,
      narrative_serialization,
      performance_artistry,
      personality_conversation,
      created_at
    )
})

topic_inventory <- reactive({
  admin_snapshot()$results |>
    filter(!is.na(.data$topic), nzchar(.data$topic)) |>
    group_by(.data$topic) |>
    summarise(
      uses = dplyr::n(), unique_titles = n_distinct(.data$video_id),
      talents = n_distinct(.data$talent_code),
      title_versions = n_distinct(.data$title_version_id), .groups = "drop"
    ) |>
    arrange(desc(.data$unique_titles), .data$topic)
})

tag_inventory <- reactive({
  admin_snapshot()$tags |>
    filter(!is.na(.data$tag), nzchar(.data$tag)) |>
    group_by(.data$tag) |>
    summarise(
      uses = dplyr::n(), unique_titles = n_distinct(.data$video_id),
      talents = n_distinct(.data$talent_code),
      title_versions = n_distinct(.data$title_version_id), .groups = "drop"
    ) |>
    arrange(desc(.data$unique_titles), .data$tag)
})

output$filtered_count <- renderUI({
  admin_value_box("Filtered classification rows", scales::comma(nrow(filtered_results())))
})

output$classification_results <- renderDT({
  data <- filtered_results_export() |>
    select(
      video_id,
      talent_code,
      title,
      title_version_id,
      model,
      topic,
      tags,
      confidence,
      personality_conversation,
      classification_status
    )
  admin_datatable(data, page_length = 15L)
})

output$topic_inventory_count <- renderUI({
  admin_value_box("Distinct topics", scales::comma(nrow(topic_inventory())))
})

output$tag_inventory_count <- renderUI({
  admin_value_box("Distinct tags", scales::comma(nrow(tag_inventory())))
})

output$topic_inventory <- renderDT({
  admin_datatable(topic_inventory(), page_length = 15L)
})

output$tag_inventory <- renderDT({
  admin_datatable(tag_inventory(), page_length = 15L)
})

output$download_selected_run <- downloadHandler(
  filename = function() paste0(selected_run()$run_id[[1]], "_titles.csv"),
  content = function(path) {
    write.csv(
      selected_run_combined() |> select(-dplyr::any_of("tag_values")),
      path, row.names = FALSE, na = "", fileEncoding = "UTF-8"
    )
  }
)

output$download_filtered_results <- downloadHandler(
  filename = function() paste0("title_classifications_", format(Sys.Date(), "%Y%m%d"), ".csv"),
  content = function(path) {
    write.csv(filtered_results_export(), path, row.names = FALSE, na = "", fileEncoding = "UTF-8")
  }
)
```
