---
title: "Title Classification Operations"
format:
  dashboard:
    orientation: rows
server: shiny
execute:
  echo: false
  warning: false
  message: false
---

<style>
.admin-path {
  overflow-wrap: anywhere;
  font-family: var(--bs-font-monospace);
  font-size: 0.78rem;
}

.admin-note {
  color: var(--bs-secondary-color);
  font-size: 0.86rem;
}

.dataTables_wrapper {
  font-size: 0.82rem;
}

@media (max-width: 768px) {
  .dashboard-page .card,
  .dashboard-page .card:not(.bslib-value-box) {
    height: auto !important;
    min-height: 0 !important;
  }

  .bslib-value-box .value-box-value {
    font-size: 1.45rem;
  }

  .bslib-value-box .value-box-title {
    font-size: 0.78rem;
  }

  .js-plotly-plot {
    min-height: 17rem;
  }

  .dataTables_wrapper {
    font-size: 0.74rem;
  }

}
</style>

```{r}
#| label: setup
#| context: setup
#| include: false

knitr::opts_knit$set(
  root.dir = normalizePath(getwd(), winslash = "/", mustWork = TRUE)
)

dashboard_machine_library <- file.path(
  path.expand("~/R"),
  paste0(R.version$platform, "-library"),
  paste(R.version$major, sub("\\..*$", "", R.version$minor), sep = ".")
)
if (dir.exists(dashboard_machine_library)) {
  .libPaths(unique(c(.libPaths(), dashboard_machine_library)))
}

suppressPackageStartupMessages({
  library(here)
  library(shiny)
  library(dplyr)
  library(DT)
  library(plotly)
  library(bslib)
  library(scales)
})

source(here::here("r_scripts", "lib", "utils", "repo_env.R"))
source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "duckdb", "db_connect.R"))
source(
  here::here(
    "r_scripts",
    "lib",
    "dashboard",
    "data",
    "classification_admin.R"
  )
)

load_repo_env()
admin_database_path <- talent_lakehouse_db_path()
admin_run_root <- classification_admin_resolve_run_root()

admin_format_time <- function(value) {
  if (length(value) == 0L) return("Not available")
  value <- value[[1]]
  if (is.na(value)) return("Not available")
  if (!inherits(value, "POSIXt")) {
    value <- classification_admin_parse_time(value)
  }
  if (is.na(value)) return("Not available")
  format(value, "%Y-%m-%d %H:%M:%S UTC", tz = "UTC")
}

admin_format_times <- function(values) {
  parsed <- classification_admin_parse_time(values)
  formatted <- format(parsed, "%Y-%m-%d %H:%M:%S UTC", tz = "UTC")
  formatted[is.na(parsed)] <- "Not available"
  formatted
}

admin_value <- function(value, fallback = "—") {
  if (length(value) == 0L || is.na(value[[1]]) || !nzchar(as.character(value[[1]]))) {
    return(fallback)
  }
  as.character(value[[1]])
}

admin_value_box <- function(title, value) {
  bslib::value_box(title = title, value = admin_value(value))
}

admin_empty_plot <- function(message) {
  plotly::plot_ly() |>
    plotly::layout(
      xaxis = list(visible = FALSE),
      yaxis = list(visible = FALSE),
      annotations = list(list(
        text = message,
        x = 0.5,
        y = 0.5,
        xref = "paper",
        yref = "paper",
        showarrow = FALSE
      ))
    )
}

admin_bar_plot <- function(data, label, value, x_title = "Titles") {
  if (nrow(data) == 0L) return(admin_empty_plot("No data are available."))
  data <- data[order(data[[value]], decreasing = FALSE), , drop = FALSE]
  plotly::plot_ly(
    data,
    x = data[[value]],
    y = stats::reorder(data[[label]], data[[value]]),
    type = "bar",
    orientation = "h",
    text = data[[value]],
    textposition = "auto",
    hovertemplate = paste0(
      "%{y}<br>",
      x_title,
      ": %{x:,}<extra></extra>"
    )
  ) |>
    plotly::layout(
      xaxis = list(title = x_title),
      yaxis = list(title = ""),
      margin = list(l = 100, r = 20, t = 10, b = 45)
    )
}

admin_datatable <- function(
    data,
    page_length = 10L,
    filter = "top",
    scroll_x = TRUE
) {
  if (nrow(data) == 0L) {
    data <- data.frame(message = "No rows matched the current selection.")
    filter <- "none"
  }
  DT::datatable(
    data,
    rownames = FALSE,
    filter = filter,
    options = list(
      pageLength = page_length,
      scrollX = scroll_x,
      autoWidth = TRUE,
      dom = "tip"
    )
  )
}

admin_display_runs <- function(runs) {
  if (nrow(runs) == 0L) return(data.frame())
  runs |>
    transmute(
      run_id = .data$run_id,
      status = .data$status,
      created_utc = admin_format_times(.data$created_at),
      titles = .data$title_count,
      talents = .data$talents,
      model = .data$model,
      results_applied = .data$result_count,
      unique_tags = .data$tag_count,
      failed = .data$failed_count
    )
}
```

# {.sidebar}

```{r}
actionButton(
  inputId = "refresh_data",
  label = "Refresh now",
  class = "btn-primary"
)

checkboxInput(
  inputId = "auto_refresh",
  label = "Refresh every five minutes",
  value = TRUE
)

uiOutput("data_freshness")
hr()
uiOutput("run_selector")
downloadButton("download_selected_run", "Download selected run")
hr()
helpText(
  "Run selection controls Run Details. This dashboard is read-only."
)
```

# Overview

The overview reports the newest traceable Batch run and current active-version
coverage. Counts refresh from DuckDB and the DataLake run manifests. Remote
batch status reflects the scheduler's most recent check; this dashboard does
not poll OpenAI directly.

## Row {height=18%}

```{r}
#| title: "Current Run"
uiOutput("latest_status")
```

```{r}
#| title: "Titles in Run"
uiOutput("latest_titles")
```

```{r}
#| title: "Current Pending Titles"
uiOutput("current_pending")
```

```{r}
#| title: "Last Checked"
uiOutput("latest_checked")
```

## Row {height=38%}

```{r}
#| title: "Titles by Talent in Latest Run"
plotlyOutput("latest_talent_plot", height = "100%")
```

```{r}
#| title: "Current Active-Version Coverage"
plotlyOutput("coverage_plot", height = "100%")
```

## Row {height=44%}

```{r}
#| title: "Recent Runs"
DTOutput("run_history")
```

# Run Details

Select a run in the sidebar to inspect its essential metrics, talents, tags,
and titles.

## Row {height=36%}

```{r}
#| title: "Selected Run Summary"
DTOutput("selected_run_summary")
```

```{r}
#| title: "Talent Membership"
plotlyOutput("selected_run_talents", height = "100%")
```

```{r}
#| title: "Tag Frequency"
plotlyOutput("selected_run_tags", height = "100%")
```

## Row {height=64%}

```{r}
#| title: "Titles in Selected Run"
DTOutput("selected_run_titles")
```

# Browse Data

This page exposes all classification rows, including older migrated versions.
Use the table's column filters or the download button for a full filtered
extract. Older rows without a recoverable run ID
remain available here and are labeled `legacy-untracked` in downloads.

## Row {height=28%}

```{r}
#| title: "Data Filters"
uiOutput("classification_filters")
```

```{r}
#| title: "Filtered Rows"
uiOutput("filtered_count")
```

```{r}
#| title: "Filtered Export"
div(
  class = "p-3",
  downloadButton("download_filtered_results", "Download filtered data"),
  tags$p(
    class = "admin-note mt-3",
    "The download includes all classification fields and lineage identifiers."
  )
)
```

## Row {height=72%}

```{r}
#| title: "All Classification Results"
DTOutput("classification_results")
```

# Topics & Tags

This page provides a complete searchable inventory of the topics and tags in
the classification data. Counts include every retained title version, not only
the active version or the most recent run.

## Row {height=18%}

```{r}
#| title: "Topics"
uiOutput("topic_inventory_count")
```

```{r}
#| title: "Tags"
uiOutput("tag_inventory_count")
```

## Row {height=41%}

```{r}
#| title: "All Topics"
DTOutput("topic_inventory")
```

## Row {height=41%}

```{r}
#| title: "All Tags"
DTOutput("tag_inventory")
```

```{r}
#| label: server
#| context: server
#| include: false

admin_snapshot <- reactive({
  input$refresh_data
  if (isTRUE(input$auto_refresh)) {
    invalidateLater(5 * 60 * 1000, session)
  }
  withProgress(message = "Refreshing classification operations", value = 0, {
    incProgress(0.2, detail = "Reading run manifests")
    snapshot <- classification_admin_load_snapshot(
      database_path = admin_database_path,
      run_root = admin_run_root
    )
    incProgress(0.8, detail = "Preparing dashboard data")
    snapshot
  })
})

latest_run <- reactive({
  runs <- admin_snapshot()$runs
  if (nrow(runs) == 0L) return(NULL)
  runs[1, , drop = FALSE]
})

output$data_freshness <- renderUI({
  snapshot <- admin_snapshot()
  htmltools::tagList(
    tags$small(
      class = "text-muted",
      paste("Dashboard refreshed", admin_format_time(snapshot$refreshed_at))
    ),
    tags$br(),
    tags$small(
      class = "text-muted",
      paste("DuckDB modified", admin_format_time(snapshot$database_modified_at))
    )
  )
})

output$run_selector <- renderUI({
  runs <- admin_snapshot()$runs
  if (nrow(runs) == 0L) return(helpText("No traceable runs were found."))
  choices <- stats::setNames(
    runs$run_id,
    paste(
      format(runs$created_at, "%Y-%m-%d %H:%M UTC", tz = "UTC"),
      runs$status,
      runs$run_id,
      sep = " • "
    )
  )
  selected <- isolate(input$selected_run)
  if (is.null(selected) || !selected %in% runs$run_id) selected <- runs$run_id[[1]]
  selectInput("selected_run", "Inspect run", choices, selected = selected)
})

selected_run <- reactive({
  runs <- admin_snapshot()$runs
  req(nrow(runs) > 0L)
  run_id <- input$selected_run
  if (is.null(run_id) || !run_id %in% runs$run_id) run_id <- runs$run_id[[1]]
  runs[runs$run_id == run_id, , drop = FALSE]
})

selected_run_results <- reactive({
  run <- selected_run()
  admin_snapshot()$results |>
    filter(.data$pipeline_run_id == run$pipeline_run_id[[1]])
})

selected_run_candidates <- reactive({
  run <- selected_run()
  admin_snapshot()$candidates |>
    filter(.data$run_id == run$run_id[[1]])
})

selected_run_combined <- reactive({
  candidates <- selected_run_candidates()
  results <- selected_run_results() |>
    select(
      .data$pipeline_run_id,
      .data$video_id,
      result_title = .data$title,
      .data$topic,
      .data$language,
      .data$tags,
      .data$primary_reference,
      .data$referenced_entities,
      .data$confidence,
      .data$model,
      .data$profile_id,
      .data$classification_status,
      .data$collaborative_energy,
      .data$community_milestones,
      .data$interactive_entertainment,
      .data$meme_viral,
      .data$monetization,
      .data$narrative_serialization,
      .data$performance_artistry,
      .data$personality_conversation
    )
  candidates |>
    left_join(results, by = c("pipeline_run_id", "video_id")) |>
    select(-.data$result_title)
})

output$latest_status <- renderUI({
  run <- latest_run()
  admin_value_box("Latest run status", if (is.null(run)) NA else run$status)
})
output$latest_titles <- renderUI({
  run <- latest_run()
  admin_value_box(
    "Titles in run",
    if (is.null(run)) NA else scales::comma(run$title_count)
  )
})
output$current_pending <- renderUI({
  pending <- sum(!admin_snapshot()$current_status$is_classified, na.rm = TRUE)
  admin_value_box("Current pending titles", scales::comma(pending))
})
output$latest_checked <- renderUI({
  run <- latest_run()
  checked <- if (is.null(run) || is.na(run$last_checked_at[[1]])) {
    NA_character_
  } else {
    format(run$last_checked_at[[1]], "%b %d, %H:%M UTC", tz = "UTC")
  }
  admin_value_box("Last checked", checked)
})

output$latest_talent_plot <- renderPlotly({
  run <- latest_run()
  if (is.null(run)) return(admin_empty_plot("No run data are available."))
  counts <- admin_snapshot()$candidates |>
    filter(.data$run_id == run$run_id[[1]]) |>
    count(.data$talent_code, name = "titles")
  admin_bar_plot(counts, "talent_code", "titles")
})

output$coverage_plot <- renderPlotly({
  counts <- admin_snapshot()$current_status |>
    count(.data$classification_status, name = "titles")
  admin_bar_plot(counts, "classification_status", "titles")
})

output$run_history <- renderDT({
  admin_datatable(admin_display_runs(admin_snapshot()$runs), page_length = 10L)
})

output$selected_run_summary <- renderDT({
  run <- selected_run()
  summary <- data.frame(
    metric = c(
      "Status", "Created", "Model", "Title version", "Titles", "Talents",
      "API requests", "Results applied", "Unique tags", "Failed responses"
    ),
    value = c(
      run$status,
      admin_format_time(run$created_at),
      run$model,
      run$title_version_id,
      scales::comma(run$title_count),
      run$talent_count,
      scales::comma(run$request_count),
      scales::comma(run$result_count),
      run$tag_count,
      run$failed_count
    )
  )
  admin_datatable(summary, page_length = 15L, filter = "none")
})

output$selected_run_talents <- renderPlotly({
  candidates <- selected_run_candidates()
  counts <- candidates |>
    count(.data$talent_code, name = "titles")
  admin_bar_plot(counts, "talent_code", "titles")
})

output$selected_run_tags <- renderPlotly({
  results <- selected_run_results()
  tags <- classification_admin_tag_rows(results) |>
    count(.data$tag, name = "titles", sort = TRUE) |>
    slice_head(n = 20L)
  if (nrow(tags) == 0L) {
    return(admin_empty_plot("Tags appear after this run is applied."))
  }
  admin_bar_plot(tags, "tag", "titles")
})

output$selected_run_titles <- renderDT({
  data <- selected_run_combined() |>
    select(
      .data$video_id,
      .data$talent_code,
      title = .data$title_raw,
      .data$content_type,
      .data$published_at,
      .data$topic,
      .data$tags,
      .data$confidence,
      .data$personality_conversation,
      .data$classification_status,
      .data$model
    )
  admin_datatable(data, page_length = 15L)
})

output$classification_filters <- renderUI({
  results <- admin_snapshot()$results
  tag_choices <- sort(unique(unlist(results$tag_values, use.names = FALSE)))
  choice_values <- function(values) {
    values <- as.character(values)
    sort(unique(values[!is.na(values) & nzchar(values)]))
  }
  fluidRow(
    column(
      3,
      selectizeInput(
        "data_talents",
        "Talent",
        choice_values(results$talent_code),
        multiple = TRUE
      )
    ),
    column(
      3,
      selectizeInput(
        "data_versions",
        "Title version",
        choice_values(results$title_version_id),
        multiple = TRUE
      )
    ),
    column(
      3,
      selectizeInput(
        "data_topics",
        "Topic",
        choice_values(results$topic),
        multiple = TRUE
      )
    ),
    column(
      3,
      selectizeInput(
        "data_tags",
        "Tag",
        tag_choices,
        multiple = TRUE
      )
    )
  )
})

filtered_results <- reactive({
  results <- admin_snapshot()$results
  if (length(input$data_talents) > 0L) {
    results <- results |> filter(.data$talent_code %in% input$data_talents)
  }
  if (length(input$data_versions) > 0L) {
    results <- results |>
      filter(.data$title_version_id %in% input$data_versions)
  }
  if (length(input$data_topics) > 0L) {
    results <- results |> filter(.data$topic %in% input$data_topics)
  }
  if (length(input$data_tags) > 0L) {
    keep <- vapply(results$tag_values, function(values) {
      all(input$data_tags %in% values)
    }, logical(1))
    results <- results[keep, , drop = FALSE]
  }
  results
})

filtered_results_export <- reactive({
  filtered_results() |>
    mutate(
      run = ifelse(
        is.na(.data$pipeline_run_id),
        paste0("legacy-untracked/", .data$title_version_id),
        .data$pipeline_run_id
      )
    ) |>
    select(
      .data$run,
      .data$video_id,
      .data$talent_code,
      .data$talent_name,
      .data$title,
      .data$title_version_id,
      .data$model,
      .data$topic,
      .data$language,
      .data$tags,
      .data$primary_reference,
      .data$referenced_entities,
      .data$confidence,
      .data$classification_status,
      .data$profile_id,
      .data$collaborative_energy,
      .data$community_milestones,
      .data$interactive_entertainment,
      .data$meme_viral,
      .data$monetization,
      .data$narrative_serialization,
      .data$performance_artistry,
      .data$personality_conversation,
      .data$created_at
    )
})

topic_inventory <- reactive({
  admin_snapshot()$results |>
    filter(!is.na(.data$topic), nzchar(.data$topic)) |>
    group_by(.data$topic) |>
    summarise(
      uses = dplyr::n(),
      unique_titles = n_distinct(.data$video_id),
      talents = n_distinct(.data$talent_code),
      title_versions = n_distinct(.data$title_version_id),
      .groups = "drop"
    ) |>
    arrange(desc(.data$unique_titles), .data$topic)
})

tag_inventory <- reactive({
  admin_snapshot()$tags |>
    filter(!is.na(.data$tag), nzchar(.data$tag)) |>
    group_by(.data$tag) |>
    summarise(
      uses = dplyr::n(),
      unique_titles = n_distinct(.data$video_id),
      talents = n_distinct(.data$talent_code),
      title_versions = n_distinct(.data$title_version_id),
      .groups = "drop"
    ) |>
    arrange(desc(.data$unique_titles), .data$tag)
})

output$filtered_count <- renderUI({
  admin_value_box("Filtered classification rows", scales::comma(nrow(filtered_results())))
})

output$classification_results <- renderDT({
  data <- filtered_results_export() |>
    select(
      .data$video_id,
      .data$talent_code,
      .data$title,
      .data$title_version_id,
      .data$model,
      .data$topic,
      .data$tags,
      .data$confidence,
      .data$personality_conversation,
      .data$classification_status
    )
  admin_datatable(data, page_length = 15L)
})

output$topic_inventory_count <- renderUI({
  admin_value_box(
    "Distinct topics",
    scales::comma(nrow(topic_inventory()))
  )
})

output$tag_inventory_count <- renderUI({
  admin_value_box(
    "Distinct tags",
    scales::comma(nrow(tag_inventory()))
  )
})

output$topic_inventory <- renderDT({
  admin_datatable(topic_inventory(), page_length = 15L)
})

output$tag_inventory <- renderDT({
  admin_datatable(tag_inventory(), page_length = 15L)
})

output$download_selected_run <- downloadHandler(
  filename = function() paste0(selected_run()$run_id[[1]], "_titles.csv"),
  content = function(path) {
    write.csv(
      selected_run_combined() |> select(-dplyr::any_of("tag_values")),
      path,
      row.names = FALSE,
      na = "",
      fileEncoding = "UTF-8"
    )
  }
)

output$download_filtered_results <- downloadHandler(
  filename = function() {
    paste0("title_classifications_", format(Sys.Date(), "%Y%m%d"), ".csv")
  },
  content = function(path) {
    write.csv(
      filtered_results_export(),
      path,
      row.names = FALSE,
      na = "",
      fileEncoding = "UTF-8"
    )
  }
)
```
