---
title: "Individual Video Performance"
format:
  dashboard:
    orientation: rows
server: shiny
execute:
  echo: false
  warning: false
  message: false
---

<style>
@media (min-width: 769px) {
  body.dashboard-sidebar .bslib-sidebar-layout {
    --bslib-sidebar-width: 340px;
  }
}

#snapshot_dates .input-daterange {
  flex-wrap: nowrap;
}

#snapshot_dates .input-daterange .form-control {
  min-width: 0;
  font-variant-numeric: tabular-nums;
}

.individual-video-context {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(12rem, 1fr));
  gap: 0.65rem 1rem;
  padding: 0.8rem 1rem;
}

.individual-video-context-label {
  color: var(--bs-secondary-color, #666);
  font-size: 0.72rem;
  letter-spacing: 0.04em;
  text-transform: uppercase;
}

.individual-video-context-value {
  font-size: 0.92rem;
  font-weight: 600;
  overflow-wrap: anywhere;
}

.performance-selection {
  align-items: start;
  display: grid;
  grid-template-columns: minmax(14rem, 20%) minmax(0, 1fr);
}

.performance-metric-control {
  padding: 0.8rem 0 0.8rem 1rem;
}

.performance-metric-control .shiny-input-container {
  margin-bottom: 0;
  width: 100% !important;
}

#video_transcript table.dataTable td:nth-child(1),
#video_transcript table.dataTable td:nth-child(2) {
  vertical-align: top;
  white-space: nowrap;
}

#video_transcript table.dataTable td:nth-child(3) {
  min-width: 30rem;
  vertical-align: top;
  white-space: normal;
}

.plot-builder-statistics {
  border-top: 1px solid rgba(0, 0, 0, 0.14);
  margin-top: 1rem;
  padding-top: 0.9rem;
}

.plot-builder-controls {
  display: flex;
  flex-direction: column;
  gap: 0.75rem;
}

.plot-builder-controls .shiny-input-container {
  margin-bottom: 0;
  width: 100% !important;
}

.plot-builder-definition {
  background: rgba(69, 128, 230, 0.08);
  border-left: 3px solid #4580E6;
  border-radius: 0.25rem;
  padding: 0.55rem 0.65rem;
}

.plot-builder-definition-label {
  color: #2A5DAE;
  font-size: 0.68rem;
  font-weight: 700;
  letter-spacing: 0.04em;
  margin-bottom: 0.2rem;
  text-transform: uppercase;
}

.plot-builder-definition p {
  font-size: 0.76rem;
  line-height: 1.35;
  margin-bottom: 0.3rem;
}

.plot-builder-definition .plot-builder-definition-note {
  color: var(--bs-secondary-color, #666);
  font-size: 0.7rem;
  margin-bottom: 0;
}

.plot-builder-statistics h5,
.plot-builder-statistics h6 {
  margin-bottom: 0.35rem;
}

.plot-builder-stat-note {
  color: var(--bs-secondary-color, #666);
  font-size: 0.76rem;
  line-height: 1.3;
  margin-bottom: 0.8rem;
}

.plot-builder-stat-section {
  margin-bottom: 0.9rem;
}

.plot-builder-stat-grid {
  display: grid;
  gap: 0.45rem 0.65rem;
  grid-template-columns: repeat(2, minmax(0, 1fr));
}

.plot-builder-stat-item {
  min-width: 0;
}

.plot-builder-stat-label {
  color: var(--bs-secondary-color, #666);
  font-size: 0.68rem;
  line-height: 1.2;
}

.plot-builder-stat-value {
  font-size: 0.88rem;
  font-variant-numeric: tabular-nums;
  font-weight: 600;
  overflow-wrap: anywhere;
}

.plot-builder-relationship {
  background: rgba(69, 128, 230, 0.08);
  border-radius: 0.4rem;
  padding: 0.65rem;
}

@media (max-width: 768px) {
  .performance-selection {
    grid-template-columns: 1fr;
  }

  .performance-metric-control {
    padding-right: 1rem;
  }

  .card:not(.bslib-value-box) {
    min-height: 23rem;
  }

  .js-plotly-plot {
    min-height: 19rem;
  }

  .dataTables_wrapper {
    font-size: 0.78rem;
  }
}
</style>

```{r}
#| label: setup
#| context: setup
#| include: false

knitr::opts_knit$set(
  root.dir = normalizePath(getwd(), winslash = "/", mustWork = TRUE)
)

dashboard_machine_library <- file.path(
  path.expand("~/R"),
  paste0(R.version$platform, "-library"),
  paste(R.version$major, sub("\\..*$", "", R.version$minor), sep = ".")
)
if (dir.exists(dashboard_machine_library)) {
  .libPaths(unique(c(.libPaths(), dashboard_machine_library)))
}

library(here)
library(shiny)

source(here::here("r_scripts", "lib", "dashboard", "load.R"))

dashboard_database_path <- dashboard_resolve_database_path()
dashboard_startup_talents <- dashboard_unified_talent_catalog(
  dashboard_database_path
)
dashboard_global_min_date <- min(
  dashboard_startup_talents$earliest_analytics_snapshot_date,
  na.rm = TRUE
)
dashboard_global_max_date <- max(
  dashboard_startup_talents$latest_analytics_snapshot_date,
  na.rm = TRUE
)
if (!is.finite(dashboard_global_min_date)) {
  dashboard_global_min_date <- Sys.Date()
}
if (!is.finite(dashboard_global_max_date)) {
  dashboard_global_max_date <- Sys.Date()
}

individual_video_metric_definitions <- dashboard_individual_video_metric_definitions()
individual_video_metric_choices <- stats::setNames(
  individual_video_metric_definitions$metric,
  individual_video_metric_definitions$label
)

individual_video_optional_date <- function(date_range, index) {
  if (is.null(date_range) || length(date_range) < index ||
      is.na(date_range[[index]])) {
    return(NULL)
  }
  as.Date(date_range[[index]])
}

individual_video_context_item <- function(label, value) {
  htmltools::div(
    htmltools::div(class = "individual-video-context-label", label),
    htmltools::div(class = "individual-video-context-value", value)
  )
}
```

# {.sidebar}

```{r}
uiOutput("dashboard_identity")

selectInput(
  inputId = "talent",
  label = "Talent",
  choices = c("Loading authorized talents..." = ""),
  selected = ""
)

uiOutput("video_selector")

dateRangeInput(
  inputId = "snapshot_dates",
  label = "Analytics snapshots between",
  start = dashboard_global_min_date,
  end = dashboard_global_max_date,
  min = dashboard_global_min_date,
  max = dashboard_global_max_date,
  format = "yyyy-mm-dd",
  separator = " to "
)

uiOutput("video_data_freshness")

helpText(
  "Talent and video options are permission-scoped. The date range selects analytics snapshots, not publication dates."
)
```

# Performance

This page follows one selected metric across the video's observed analytics history.

## Row {height=16%}

```{r}
#| title: "Performance Selection"
htmltools::div(
  class = "performance-selection",
  htmltools::div(
    class = "performance-metric-control",
    selectInput(
      inputId = "metric",
      label = "Metric",
      choices = individual_video_metric_choices,
      selected = "views",
      width = "100%",
      selectize = FALSE
    )
  ),
  uiOutput("video_context")
)
```

## Row {height=20%}

```{r}
#| title: "Latest Observed Value"
uiOutput("metric_latest")
```

```{r}
#| title: "Change in Selected Window"
uiOutput("metric_change")
```

```{r}
#| title: "Average Change per Day"
uiOutput("metric_daily_change")
```

```{r}
#| title: "Snapshot Coverage"
uiOutput("metric_coverage")
```

## Row {height=48%}

```{r}
#| title: "Metric by Analytics Snapshot"
plotlyOutput("metric_trend", height = "100%")
```

```{r}
#| title: "Average Daily Change Between Snapshots"
plotlyOutput("metric_change_plot", height = "100%")
```

# Plot Builder

Choose two available metrics for the selected video. The muted path shows the
full relationship across the active date window; use the snapshot slider below
the chart to move the highlighted point through time.

## Row

### Column {width=25%}

```{r}
#| title: "Variables"
htmltools::div(
  class = "plot-builder-controls",
  selectInput(
    inputId = "plot_x_metric",
    label = "Horizontal (X) variable",
    choices = individual_video_metric_choices,
    selected = "views",
    width = "100%"
  ),
  uiOutput("plot_x_definition"),
  selectInput(
    inputId = "plot_y_metric",
    label = "Vertical (Y) variable",
    choices = individual_video_metric_choices,
    selected = "average_view_percentage",
    width = "100%"
  ),
  uiOutput("plot_y_definition"),
  helpText(
    "Choose two different variables. Use the slider below the plot to move through snapshots."
  ),
  uiOutput("plot_builder_statistics")
)
```

### Column {width=75%}

```{r}
#| title: "Animated Snapshot Scatter Plot"
plotlyOutput("plot_builder_scatter", height = "100%")
```

# Snapshot Detail

The interval fields compare each row with the prior visible snapshot. A gap of
several days is normalized by the actual elapsed days.

## Row {height=72%}

```{r}
#| title: "Selected Metric History"
DT::dataTableOutput("snapshot_table")
```

## Row {height=28%}

```{r}
#| title: "How to Read This Metric"
uiOutput("metric_method")
```

# Transcript

This is the full available transcript for the selected video. For live videos,
streamer subtitles and chat messages are merged by their video timestamp. The
analytics snapshot date range does not filter this page.

## Row

```{r}
#| title: "Full Video Transcript"
DT::dataTableOutput("video_transcript")
```

```{r}
#| label: server
#| context: server
#| include: false

dashboard_talents <- dashboard_unified_talent_catalog(dashboard_database_path)
dashboard_session_access <- dashboard_access_context(
  session$request,
  dashboard_talents$talent_code
)
dashboard_allowed_talent_choices <- dashboard_authorized_talent_choices(
  dashboard_talents,
  dashboard_session_access
)

output$dashboard_identity <- renderUI({
  if (!dashboard_session_access$authorized) {
    return(
      htmltools::div(
        class = "alert alert-danger",
        "No active talent permissions were found for this account."
      )
    )
  }
  htmltools::tags$small(
    class = "text-muted",
    paste("Signed in as", dashboard_session_access$verified_email)
  )
})

session$onFlushed(function() {
  if (length(dashboard_allowed_talent_choices) == 0) {
    updateSelectInput(
      session,
      inputId = "talent",
      choices = c("No authorized talents" = ""),
      selected = ""
    )
    return()
  }

  selected_code <- isolate(input$talent)
  if (!dashboard_talent_is_authorized(selected_code, dashboard_session_access)) {
    selected_code <- unname(dashboard_allowed_talent_choices[[1]])
  }
  updateSelectInput(
    session,
    inputId = "talent",
    choices = dashboard_allowed_talent_choices,
    selected = selected_code
  )
}, once = TRUE)

authorized_video_catalog <- reactive({
  req(dashboard_session_access$authorized)
  req(dashboard_talent_is_authorized(input$talent, dashboard_session_access))
  dashboard_individual_video_catalog(
    database_path = dashboard_database_path,
    talent_code = input$talent
  )
})

output$video_selector <- renderUI({
  if (!dashboard_session_access$authorized) {
    return(
      selectInput(
        inputId = "video",
        label = "Video",
        choices = c("No authorized videos" = ""),
        selected = ""
      )
    )
  }

  catalog <- authorized_video_catalog()
  choices <- dashboard_individual_video_choices(catalog)
  if (length(choices) == 0) {
    return(
      selectInput(
        inputId = "video",
        label = "Video",
        choices = c("No videos found" = ""),
        selected = ""
      )
    )
  }

  selectizeInput(
    inputId = "video",
    label = "Video",
    choices = choices,
    selected = unname(choices[[1]]),
    multiple = FALSE,
    options = list(
      create = FALSE,
      placeholder = "Search video titles"
    )
  )
})

selected_video_row <- reactive({
  catalog <- authorized_video_catalog()
  req(input$video)
  selected <- catalog %>%
    dplyr::filter(.data$video_id == input$video) %>%
    dplyr::slice_head(n = 1)
  validate(need(nrow(selected) == 1, "Select an authorized video."))
  selected
})

observeEvent(
  list(input$talent, input$video),
  {
    selected <- selected_video_row()
    req(
      !is.na(selected$first_snapshot_date[[1]]),
      !is.na(selected$latest_snapshot_date[[1]])
    )
    updateDateRangeInput(
      session,
      inputId = "snapshot_dates",
      start = selected$first_snapshot_date[[1]],
      end = selected$latest_snapshot_date[[1]],
      min = selected$first_snapshot_date[[1]],
      max = selected$latest_snapshot_date[[1]]
    )
  },
  ignoreInit = TRUE
)

video_history_raw <- reactive({
  req(dashboard_session_access$authorized)
  req(dashboard_talent_is_authorized(input$talent, dashboard_session_access))
  selected <- selected_video_row()
  req(identical(selected$video_id[[1]], input$video))

  dashboard_load_individual_video_history(
    database_path = dashboard_database_path,
    talent_code = input$talent,
    video_id = input$video
  )
})

video_transcript <- reactive({
  req(dashboard_session_access$authorized)
  req(dashboard_talent_is_authorized(input$talent, dashboard_session_access))
  selected <- selected_video_row()
  req(identical(selected$video_id[[1]], input$video))

  dashboard_load_individual_video_transcript(
    database_path = dashboard_database_path,
    talent_code = input$talent,
    video_id = input$video
  )
})

observe({
  history <- video_history_raw()
  available_metrics <- individual_video_metric_definitions$metric[
    vapply(
      individual_video_metric_definitions$metric,
      function(metric) {
        metric %in% names(history) &&
          any(is.finite(suppressWarnings(as.numeric(history[[metric]]))))
      },
      logical(1)
    )
  ]
  if (all(c("subscribers_gained", "subscribers_lost") %in% names(history)) &&
      any(is.finite(history$subscribers_gained - history$subscribers_lost))) {
    available_metrics <- unique(c(available_metrics, "net_subscribers"))
  }
  choices <- individual_video_metric_choices[
    unname(individual_video_metric_choices) %in% available_metrics
  ]
  req(length(choices) > 0)
  selected_metric <- isolate(input$metric)
  if (is.null(selected_metric) || !selected_metric %in% unname(choices)) {
    selected_metric <- unname(choices[[1]])
  }
  updateSelectInput(
    session,
    inputId = "metric",
    choices = choices,
    selected = selected_metric
  )

  selected_x <- isolate(input$plot_x_metric)
  if (is.null(selected_x) || !selected_x %in% unname(choices)) {
    selected_x <- unname(choices[[1]])
  }
  remaining_y <- setdiff(unname(choices), selected_x)
  selected_y <- isolate(input$plot_y_metric)
  if (is.null(selected_y) || !selected_y %in% remaining_y) {
    selected_y <- if (length(remaining_y) > 0) remaining_y[[1]] else selected_x
  }
  updateSelectInput(
    session,
    inputId = "plot_x_metric",
    choices = choices,
    selected = selected_x
  )
  updateSelectInput(
    session,
    inputId = "plot_y_metric",
    choices = choices,
    selected = selected_y
  )
})

selected_metric <- reactive({
  req(input$metric)
  validate(
    need(
      input$metric %in% individual_video_metric_definitions$metric,
      "Select a supported metric."
    )
  )
  input$metric
})

plot_builder_metrics <- reactive({
  choices <- unname(individual_video_metric_choices)
  req(input$plot_x_metric, input$plot_y_metric)
  validate(
    need(input$plot_x_metric %in% choices, "Select a supported X variable."),
    need(input$plot_y_metric %in% choices, "Select a supported Y variable."),
    need(
      !identical(input$plot_x_metric, input$plot_y_metric),
      "Choose two different variables."
    )
  )
  list(x = input$plot_x_metric, y = input$plot_y_metric)
})

output$plot_x_definition <- renderUI({
  req(input$plot_x_metric)
  validate(
    need(
      input$plot_x_metric %in% individual_video_metric_definitions$metric,
      "Select a supported X variable."
    )
  )
  dashboard_individual_video_metric_definition(input$plot_x_metric)
})

output$plot_y_definition <- renderUI({
  req(input$plot_y_metric)
  validate(
    need(
      input$plot_y_metric %in% individual_video_metric_definitions$metric,
      "Select a supported Y variable."
    )
  )
  dashboard_individual_video_metric_definition(input$plot_y_metric)
})

video_history <- reactive({
  history <- video_history_raw()
  history <- dashboard_apply_snapshot_window(
    history,
    start_date = individual_video_optional_date(input$snapshot_dates, 1),
    end_date = individual_video_optional_date(input$snapshot_dates, 2)
  )
  prepared <- dashboard_individual_video_prepare(history)
  validate(need(nrow(prepared) > 0, "No snapshots are available in the selected date range."))
  prepared
})

metric_summary <- reactive({
  summary <- dashboard_individual_video_summary(video_history(), selected_metric())
  validate(need(!is.null(summary), "The selected metric has no observations in this date range."))
  summary
})

output$video_data_freshness <- renderUI({
  selected <- selected_video_row()
  if (is.na(selected$latest_snapshot_date[[1]])) {
    return(
      htmltools::div(
        class = "alert alert-warning py-2 px-3",
        "This video does not have an analytics snapshot yet."
      )
    )
  }
  htmltools::div(
    class = "alert alert-info py-2 px-3",
    htmltools::tags$strong(
      paste(
        "Analytics available through",
        format(selected$latest_snapshot_date[[1]], "%Y-%m-%d")
      )
    ),
    htmltools::tags$br(),
    htmltools::tags$small(
      paste(scales::comma(selected$snapshot_count[[1]]), "daily snapshots available")
    )
  )
})

output$video_context <- renderUI({
  selected <- selected_video_row()
  htmltools::div(
    class = "individual-video-context",
    individual_video_context_item("Title", selected$title[[1]]),
    individual_video_context_item(
      "Published",
      if (is.na(selected$published_at[[1]])) {
        "Unavailable"
      } else {
        format(as.Date(selected$published_at[[1]]), "%Y-%m-%d")
      }
    ),
    individual_video_context_item(
      "Content type",
      tools::toTitleCase(as.character(selected$content_type[[1]]))
    ),
    individual_video_context_item(
      "Video",
      htmltools::tags$a(
        href = paste0("https://www.youtube.com/watch?v=", selected$video_id[[1]]),
        target = "_blank",
        rel = "noopener noreferrer",
        selected$video_id[[1]]
      )
    )
  )
})

output$metric_latest <- renderUI({
  summary <- metric_summary()
  dashboard_individual_video_value_box(
    summary$metric_info$label[[1]],
    dashboard_individual_video_format_value(
      summary$latest_value,
      summary$metric_info$format[[1]]
    ),
    note = paste("at", format(summary$latest_snapshot_date, "%Y-%m-%d"))
  )
})

output$metric_change <- renderUI({
  summary <- metric_summary()
  dashboard_individual_video_value_box(
    "Observed change",
    dashboard_individual_video_format_value(
      summary$total_change,
      summary$metric_info$format[[1]]
    ),
    note = "latest minus first visible snapshot"
  )
})

output$metric_daily_change <- renderUI({
  summary <- metric_summary()
  dashboard_individual_video_value_box(
    "Average per day",
    dashboard_individual_video_format_value(
      summary$average_change_per_day,
      summary$metric_info$format[[1]]
    ),
    note = "observed change divided by elapsed days"
  )
})

output$metric_coverage <- renderUI({
  summary <- metric_summary()
  dashboard_individual_video_value_box(
    "Metric observations",
    scales::comma(summary$snapshot_count),
    note = paste(scales::comma(summary$span_days), "days from first to latest")
  )
})

output$metric_trend <- plotly::renderPlotly({
  plot <- dashboard_individual_video_trend_plot(video_history(), selected_metric())
  validate(need(inherits(plot, "plotly"), "No trend is available for this metric."))
  plot
})

output$metric_change_plot <- plotly::renderPlotly({
  plot <- dashboard_individual_video_change_plot(video_history(), selected_metric())
  validate(need(inherits(plot, "plotly"), "At least two snapshots are required for interval change."))
  plot
})

output$plot_builder_scatter <- plotly::renderPlotly({
  metrics <- plot_builder_metrics()
  plot <- dashboard_individual_video_scatter_plot(
    video_history(),
    x_metric = metrics$x,
    y_metric = metrics$y
  )
  validate(
    need(
      inherits(plot, "plotly"),
      "No paired observations are available for these variables."
    )
  )
  plot
})

output$plot_builder_statistics <- renderUI({
  metrics <- plot_builder_metrics()
  panel <- dashboard_individual_video_statistics_panel(
    video_history(),
    c(metrics$x, metrics$y)
  )
  validate(
    need(
      !is.null(panel),
      "Descriptive statistics are unavailable for these variables."
    )
  )
  panel
})

output$snapshot_table <- DT::renderDataTable({
  table <- dashboard_individual_video_snapshot_table(video_history(), selected_metric())
  dashboard_datatable(table, page_length = 20, scroll_x = TRUE)
})

output$video_transcript <- DT::renderDataTable({
  transcript <- dashboard_individual_video_transcript_table(video_transcript())
  validate(
    need(
      nrow(transcript) > 0,
      "No subtitle or chat transcript is available for this video."
    )
  )
  DTSettings(
    transcript,
    class = "display stripe hover compact",
    scroll_x = FALSE,
    filter = "none",
    options = list(
      pageLength = 50,
      autoWidth = FALSE,
      columnDefs = list(
        list(targets = 0, width = "15%"),
        list(targets = 1, width = "10%"),
        list(targets = 2, width = "75%")
      )
    ),
    rownames = FALSE
  )
}, server = TRUE)

output$metric_method <- renderUI({
  info <- dashboard_individual_video_metric_info(selected_metric())
  semantics <- if (identical(info$metric_kind[[1]], "cumulative")) {
    "This is a cumulative snapshot metric. The trend shows its recorded total; interval change is the difference from the prior visible snapshot divided by elapsed days."
  } else {
    "This is a snapshot-level average or rate. The trend shows the recorded level; interval change is the change in that level divided by elapsed days."
  }
  htmltools::div(
    style = "padding:0.8rem 1rem;",
    htmltools::tags$p(semantics),
    htmltools::tags$p(
      class = "text-muted mb-0",
      "The first available observation may occur after publication, and changes between snapshots do not reveal within-interval timing."
    )
  )
})
```
