---
title: "Day of the week"
format:
  html:
    code-tools: false
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
---

```{r libraries_and_utils}
library(here)
knitr::opts_knit$set(root.dir = here::here())

library(readr)
library(dplyr)
library(purrr)
library(rENA)
library(DT)

source(here::here("r_scripts", "lib", "utils", "source_dir.r"))
source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "utils", "talent_select.R"))
source(here::here("r_scripts", "lib", "import_data", "talent_files.R"))
source(here::here("r_scripts", "lib", "clean_data", "CleanData.R"))
source_dir("r_scripts", "lib", "ENA_prep", "analysis_helpers")
source(here::here("r_scripts", "lib", "clean_data", "title_classification_join.R"))
source(here::here("r_scripts", "lib", "transcript_analysis", "money_stream_selection.R"))
source(here::here("r_scripts", "lib", "plots", "PlottingThemes.R"))
source(here::here("r_scripts", "lib", "utils", "detect_decimals.R"))
source(here::here("r_scripts", "lib", "linear_regression", "day_of_week", "weekday_transform.R"))

weekday_datatable <- function(df, caption, page_length = 10) {
  DT::datatable(
    df,
    rownames = FALSE,
    caption = caption,
    options = list(
      dom = "tip",
      pageLength = page_length,
      scrollX = TRUE
    )
  )
}

weekday_summary_datatable <- function(df, caption) {
  weekday_datatable(df, caption, page_length = 7) %>%
    DT::formatRound(
      columns = c(
        "mean_views",
        "median_views",
        "sd_views",
        "se_views",
        "ci_low",
        "ci_high",
        "min_views",
        "max_views"
      ),
      digits = 0,
      mark = ","
    )
}

model_coefficient_table <- function(model) {
  stats::coef(summary(model)) %>%
    as.data.frame() %>%
    tibble::rownames_to_column("term") %>%
    dplyr::rename(
      estimate = "Estimate",
      std_error = "Std. Error",
      statistic = "t value",
      p_value = "Pr(>|t|)"
    )
}

model_anova_table <- function(model) {
  stats::anova(model) %>%
    as.data.frame() %>%
    tibble::rownames_to_column("term") %>%
    dplyr::rename(
      df = "Df",
      sum_sq = "Sum Sq",
      mean_sq = "Mean Sq",
      f_value = "F value",
      p_value = "Pr(>F)"
    )
}

model_fit_table <- function(model) {
  model_summary <- summary(model)
  f_statistic <- model_summary$fstatistic
  model_p_value <- stats::pf(
    f_statistic[[1]],
    f_statistic[[2]],
    f_statistic[[3]],
    lower.tail = FALSE
  )

  tibble::tibble(
    metric = c(
      "R-squared",
      "Adjusted R-squared",
      "Residual standard error",
      "F-statistic",
      "Model p-value"
    ),
    value = c(
      model_summary$r.squared,
      model_summary$adj.r.squared,
      model_summary$sigma,
      f_statistic[[1]],
      model_p_value
    )
  )
}

model_coefficient_datatable <- function(model, caption) {
  weekday_datatable(model_coefficient_table(model), caption) %>%
    DT::formatRound(
      columns = c("estimate", "std_error", "statistic"),
      digits = 3
    ) %>%
    DT::formatSignif(columns = "p_value", digits = 3)
}

model_anova_datatable <- function(model, caption) {
  weekday_datatable(model_anova_table(model), caption, page_length = 5) %>%
    DT::formatRound(
      columns = c("sum_sq", "mean_sq", "f_value"),
      digits = 3
    ) %>%
    DT::formatSignif(columns = "p_value", digits = 3)
}

model_fit_datatable <- function(model, caption) {
  weekday_datatable(model_fit_table(model), caption, page_length = 5) %>%
    DT::formatSignif(columns = "value", digits = 4)
}

log_effects_datatable <- function(df, caption) {
  weekday_datatable(df, caption) %>%
    DT::formatRound(
      columns = c("estimate", "approx_percent_change_from_reference"),
      digits = 2
    )
}

```

```{r import_stream_data}
talent_name <- "ava"

talent_root <- get_datalake_root()
talent_path <- select_talent(talent_name, root = talent_root)
talent_folder <- basename(talent_path)

title_classifications <- load_title_classifications(talent = talent_folder)
talent_files <- TalentFiles(talent_path)[[1]]

required_video_types <- c(
  "video_analytics",
  "video_monetary",
  "video_demographics",
  "video_geography"
)

missing_video_exports <- setdiff(required_video_types, names(talent_files))
if (length(missing_video_exports) > 0L) {
  stop(
    "Missing required video export(s) for ",
    talent_folder,
    ": ",
    paste(missing_video_exports, collapse = ", ")
  )
}

stream_data <- video_preps_with_titles(
  files = talent_files,
  titles = title_classifications,
  talent = talent_folder,
  dedupe = TRUE
)

stream_analytics <- stream_data$analytics %>%
  dplyr::mutate(talent_name = talent_folder)

stream_monetary <- stream_data$monetary %>%
  dplyr::mutate(talent_name = talent_folder)

stream_demographics <- stream_data$demo %>%
  dplyr::mutate(talent_name = talent_folder)

stream_geography <- stream_data$geo %>%
  dplyr::mutate(talent_name = talent_folder)

stream_all_long <- dplyr::bind_rows(
  analytics = stream_analytics,
  monetary = stream_monetary,
  demographics = stream_demographics,
  geography = stream_geography,
  .id = "data_source"
)

stream_video_level <- stream_analytics %>%
  dplyr::select(-dplyr::any_of(c("Estimated Revenue", "CPM"))) %>%
  dplyr::left_join(
    stream_monetary %>%
      dplyr::select(
        dplyr::all_of("Video ID"),
        dplyr::any_of(c(
          "Estimated Revenue",
          "CPM"
        ))
      ),
    by = "Video ID"
  )

type <- unique(stream_video_level$`Content Type`)
content <- lapply(type, function(type){
    stream_video_level %>%
        dplyr::filter(`Content Type` == type)
})

content <- setNames(content, type)

```



```{r}
# Overview of Data
glimpse(stream_video_level)
weekday_datatable(
  head(stream_video_level, 25),
  "Stream video-level preview",
  page_length = 10
)

tibble::tibble(content_type = names(content))
```

# Live Content

```{r live_weekday_setup}
live_df <- content$live

#class(live_df$publish_wday)
#is.ordered(live_df$publish_wday)
#levels(live_df$publish_wday)

live_weekday_df <- dow_prep(
  live_df,
  reference_day = "Monday"
)

#is.ordered(live_weekday_df$publish_wday)
#contrasts(live_weekday_df$publish_wday)

live_weekday_summary <- dow_summary(live_weekday_df)
live_weekday_summary_by_median <- live_weekday_summary %>%
  dplyr::arrange(dplyr::desc(.data$median_views))

live_weekday_models <- dow_fit(live_weekday_df)
live_weekday_plots <- dow_plot(live_weekday_df, live_weekday_summary)
```

## Live Weekday Summary

This table describes live stream performance for each publish weekday. Use `n` to judge how much evidence there is for each day, compare `mean_views` and `median_views` for typical performance, and use the confidence interval columns as a rough guide to uncertainty around the mean.

```{r live_weekday_summary_table}
weekday_summary_datatable(
  live_weekday_summary,
  "Live streams: weekday summary"
)
```

## Live Weekdays Ranked By Median Views

This is the same weekday summary, sorted by `median_views` from highest to lowest. Median views are useful when a few unusually large or unusually small streams might distort the mean.

```{r live_weekday_median_rank_table}
weekday_summary_datatable(
  live_weekday_summary_by_median,
  "Live streams: weekday summary ranked by median views"
)
```

## Raw Views Model Fit

This table summarizes the linear model that predicts raw view counts from publish weekday. Higher R-squared values mean weekday explains more of the variation in views, while the model p-value tests whether the weekday model improves on a no-weekday baseline.

```{r live_raw_model_fit_table}
model_fit_datatable(
  live_weekday_models$raw,
  "Live streams: raw views model fit"
)
```

## Raw Views Coefficients

This table shows how each weekday compares with the reference weekday, Monday. The intercept is the estimated Monday view count; each weekday coefficient is the estimated raw-view difference from Monday, with the p-value indicating whether that difference is clearly distinguishable from zero in this model.

```{r live_raw_model_coefficients_table}
model_coefficient_datatable(
  live_weekday_models$raw,
  "Live streams: raw views model coefficients"
)
```

## Raw Views ANOVA

This table tests the overall weekday term for the raw-views model. The weekday row asks whether publish weekday, as a group of categories, explains a meaningful amount of raw-view variation.

```{r live_raw_model_anova_table}
model_anova_datatable(
  live_weekday_models$raw,
  "Live streams: raw views ANOVA"
)
```

## Log Views Model Fit

This table summarizes the model using log-transformed views, which reduces the influence of unusually large streams. Use this model when view counts are skewed and percentage-style differences are easier to interpret than raw count differences.

```{r live_log_model_fit_table}
model_fit_datatable(
  live_weekday_models$log,
  "Live streams: log views model fit"
)
```

## Log Views Coefficients

This table shows weekday differences on the log-view scale relative to Monday. Positive estimates suggest higher expected views than Monday; negative estimates suggest lower expected views, with p-values showing how strong the evidence is for each difference.

```{r live_log_model_coefficients_table}
model_coefficient_datatable(
  live_weekday_models$log,
  "Live streams: log views model coefficients"
)
```

## Log Views ANOVA

This table tests the overall weekday term for the log-views model. If the weekday p-value is small, weekday appears to explain differences in viewership after reducing the impact of extreme view counts.

```{r live_log_model_anova_table}
model_anova_datatable(
  live_weekday_models$log,
  "Live streams: log views ANOVA"
)
```

## Approximate Percent Change From Monday

This table converts the log-model coefficients into approximate percent changes from the reference weekday. Positive values indicate higher expected views than Monday, and negative values indicate lower expected views than Monday.

```{r live_log_effects_table}
log_effects_datatable(
  live_weekday_models$log_effects,
  "Live streams: approximate percent change from reference weekday"
)
```

## Raw Views By Weekday

This boxplot shows the distribution of live stream views for each publish weekday. Compare the median line and the spread within each box; wide boxes or long whiskers mean performance varies more on that day.

```{r live_raw_views_boxplot}
live_weekday_plots$boxplot_views
```

## Mean Views With Confidence Intervals

This plot compares average live stream views by publish weekday. The vertical bars show 95% confidence intervals; overlapping intervals suggest the weekday averages may not be clearly different.

```{r live_mean_ci_plot}
live_weekday_plots$mean_ci_views
```

## Log Views By Weekday

This boxplot shows the same weekday pattern on a log scale, which makes extreme high-view streams less dominant. Use it to compare typical performance when raw views are heavily skewed.

```{r live_log_views_boxplot}
live_weekday_plots$boxplot_log_views
```

# Video Content

```{r video_weekday_setup}
video_df <- if ("videos" %in% names(content)) {
  content$videos
} else {
  content$video
}

#class(video_df$publish_wday)
#is.ordered(video_df$publish_wday)
#levels(video_df$publish_wday)

video_weekday_df <- dow_prep(
  video_df,
  reference_day = "Monday"
)

#is.ordered(video_weekday_df$publish_wday)
#contrasts(video_weekday_df$publish_wday)

video_weekday_summary <- dow_summary(video_weekday_df)
video_weekday_summary_by_median <- video_weekday_summary %>%
  dplyr::arrange(dplyr::desc(.data$median_views))

video_weekday_models <- dow_fit(video_weekday_df)
video_weekday_plots <- dow_plot(video_weekday_df, video_weekday_summary)
```

## Video Weekday Summary

This table describes video performance for each publish weekday. Use `n` to judge how many videos support each weekday estimate, compare `mean_views` and `median_views` for typical performance, and read the confidence interval columns as uncertainty around the mean.

```{r video_weekday_summary_table}
weekday_summary_datatable(
  video_weekday_summary,
  "Videos: weekday summary"
)
```

## Video Weekdays Ranked By Median Views

This is the same video weekday summary, sorted by `median_views` from highest to lowest. Median views are useful for ranking days when a small number of unusually strong or weak videos could pull the mean away from typical performance.

```{r video_weekday_median_rank_table}
weekday_summary_datatable(
  video_weekday_summary_by_median,
  "Videos: weekday summary ranked by median views"
)
```

## Video Raw Views Model Fit

This table summarizes the linear model that predicts raw video view counts from publish weekday. Higher R-squared values mean weekday explains more of the variation in views, while the model p-value tests whether the weekday model improves on a no-weekday baseline.

```{r video_raw_model_fit_table}
model_fit_datatable(
  video_weekday_models$raw,
  "Videos: raw views model fit"
)
```

## Video Raw Views Coefficients

This table shows how each weekday compares with the reference weekday, Monday. The intercept is the estimated Monday view count; each weekday coefficient is the estimated raw-view difference from Monday, with the p-value indicating whether that difference is clearly distinguishable from zero in this model.

```{r video_raw_model_coefficients_table}
model_coefficient_datatable(
  video_weekday_models$raw,
  "Videos: raw views model coefficients"
)
```

## Video Raw Views ANOVA

This table tests the overall weekday term for the raw-views model. The weekday row asks whether publish weekday, as a group of categories, explains a meaningful amount of raw-view variation.

```{r video_raw_model_anova_table}
model_anova_datatable(
  video_weekday_models$raw,
  "Videos: raw views ANOVA"
)
```

## Video Log Views Model Fit

This table summarizes the model using log-transformed views, which reduces the influence of unusually large videos. Use this model when view counts are skewed and percentage-style differences are easier to interpret than raw count differences.

```{r video_log_model_fit_table}
model_fit_datatable(
  video_weekday_models$log,
  "Videos: log views model fit"
)
```

## Video Log Views Coefficients

This table shows weekday differences on the log-view scale relative to Monday. Positive estimates suggest higher expected views than Monday; negative estimates suggest lower expected views, with p-values showing how strong the evidence is for each difference.

```{r video_log_model_coefficients_table}
model_coefficient_datatable(
  video_weekday_models$log,
  "Videos: log views model coefficients"
)
```

## Video Log Views ANOVA

This table tests the overall weekday term for the log-views model. If the weekday p-value is small, weekday appears to explain differences in viewership after reducing the impact of extreme view counts.

```{r video_log_model_anova_table}
model_anova_datatable(
  video_weekday_models$log,
  "Videos: log views ANOVA"
)
```

## Video Approximate Percent Change From Monday

This table converts the log-model coefficients into approximate percent changes from the reference weekday. Positive values indicate higher expected views than Monday, and negative values indicate lower expected views than Monday.

```{r video_log_effects_table}
log_effects_datatable(
  video_weekday_models$log_effects,
  "Videos: approximate percent change from reference weekday"
)
```

## Video Raw Views By Weekday

This boxplot shows the distribution of video views for each publish weekday. Compare the median line and the spread within each box; wide boxes or long whiskers mean performance varies more on that day.

```{r video_raw_views_boxplot}
video_weekday_plots$boxplot_views
```

## Video Mean Views With Confidence Intervals

This plot compares average video views by publish weekday. The vertical bars show 95% confidence intervals; overlapping intervals suggest the weekday averages may not be clearly different.

```{r video_mean_ci_plot}
video_weekday_plots$mean_ci_views
```

## Video Log Views By Weekday

This boxplot shows the same video weekday pattern on a log scale, which makes extreme high-view videos less dominant. Use it to compare typical performance when raw views are heavily skewed.

```{r video_log_views_boxplot}
video_weekday_plots$boxplot_log_views
```

# Short Content

```{r short_weekday_setup}
short_df <- if ("shorts" %in% names(content)) {
  content$shorts
} else {
  content$short
}

#class(short_df$publish_wday)
#is.ordered(short_df$publish_wday)
#levels(short_df$publish_wday)

short_weekday_df <- dow_prep(
  short_df,
  reference_day = "Monday"
)

#is.ordered(short_weekday_df$publish_wday)
#contrasts(short_weekday_df$publish_wday)

short_weekday_summary <- dow_summary(short_weekday_df)
short_weekday_summary_by_median <- short_weekday_summary %>%
  dplyr::arrange(dplyr::desc(.data$median_views))

short_weekday_models <- dow_fit(short_weekday_df)
short_weekday_plots <- dow_plot(short_weekday_df, short_weekday_summary)
```

## Shorts Weekday Summary

This table describes Shorts performance for each publish weekday. Use `n` to judge how many Shorts support each weekday estimate, compare `mean_views` and `median_views` for typical performance, and read the confidence interval columns as uncertainty around the mean.

```{r short_weekday_summary_table}
weekday_summary_datatable(
  short_weekday_summary,
  "Shorts: weekday summary"
)
```

## Shorts Weekdays Ranked By Median Views

This is the same Shorts weekday summary, sorted by `median_views` from highest to lowest. Median views are useful for ranking days when a small number of unusually strong or weak Shorts could pull the mean away from typical performance.

```{r short_weekday_median_rank_table}
weekday_summary_datatable(
  short_weekday_summary_by_median,
  "Shorts: weekday summary ranked by median views"
)
```

## Shorts Raw Views Model Fit

This table summarizes the linear model that predicts raw Shorts view counts from publish weekday. Higher R-squared values mean weekday explains more of the variation in views, while the model p-value tests whether the weekday model improves on a no-weekday baseline.

```{r short_raw_model_fit_table}
model_fit_datatable(
  short_weekday_models$raw,
  "Shorts: raw views model fit"
)
```

## Shorts Raw Views Coefficients

This table shows how each weekday compares with the reference weekday, Monday. The intercept is the estimated Monday view count; each weekday coefficient is the estimated raw-view difference from Monday, with the p-value indicating whether that difference is clearly distinguishable from zero in this model.

```{r short_raw_model_coefficients_table}
model_coefficient_datatable(
  short_weekday_models$raw,
  "Shorts: raw views model coefficients"
)
```

## Shorts Raw Views ANOVA

This table tests the overall weekday term for the raw-views model. The weekday row asks whether publish weekday, as a group of categories, explains a meaningful amount of raw-view variation.

```{r short_raw_model_anova_table}
model_anova_datatable(
  short_weekday_models$raw,
  "Shorts: raw views ANOVA"
)
```

## Shorts Log Views Model Fit

This table summarizes the model using log-transformed views, which reduces the influence of unusually large Shorts. Use this model when view counts are skewed and percentage-style differences are easier to interpret than raw count differences.

```{r short_log_model_fit_table}
model_fit_datatable(
  short_weekday_models$log,
  "Shorts: log views model fit"
)
```

## Shorts Log Views Coefficients

This table shows weekday differences on the log-view scale relative to Monday. Positive estimates suggest higher expected views than Monday; negative estimates suggest lower expected views, with p-values showing how strong the evidence is for each difference.

```{r short_log_model_coefficients_table}
model_coefficient_datatable(
  short_weekday_models$log,
  "Shorts: log views model coefficients"
)
```

## Shorts Log Views ANOVA

This table tests the overall weekday term for the log-views model. If the weekday p-value is small, weekday appears to explain differences in viewership after reducing the impact of extreme view counts.

```{r short_log_model_anova_table}
model_anova_datatable(
  short_weekday_models$log,
  "Shorts: log views ANOVA"
)
```

## Shorts Approximate Percent Change From Monday

This table converts the log-model coefficients into approximate percent changes from the reference weekday. Positive values indicate higher expected views than Monday, and negative values indicate lower expected views than Monday.

```{r short_log_effects_table}
log_effects_datatable(
  short_weekday_models$log_effects,
  "Shorts: approximate percent change from reference weekday"
)
```

## Shorts Raw Views By Weekday

This boxplot shows the distribution of Shorts views for each publish weekday. Compare the median line and the spread within each box; wide boxes or long whiskers mean performance varies more on that day.

```{r short_raw_views_boxplot}
short_weekday_plots$boxplot_views
```

## Shorts Mean Views With Confidence Intervals

This plot compares average Shorts views by publish weekday. The vertical bars show 95% confidence intervals; overlapping intervals suggest the weekday averages may not be clearly different.

```{r short_mean_ci_plot}
short_weekday_plots$mean_ci_views
```

## Shorts Log Views By Weekday

This boxplot shows the same Shorts weekday pattern on a log scale, which makes extreme high-view Shorts less dominant. Use it to compare typical performance when raw views are heavily skewed.

```{r short_log_views_boxplot}
short_weekday_plots$boxplot_log_views
```
