---
title: "Creator Analytics Dashboard"
format:
  dashboard:
    orientation: rows
server: shiny
execute:
  echo: false
  warning: false
  message: false
---

<style>
@media (max-width: 768px) {
  .card:not(.bslib-value-box) {
    min-height: 24rem;
  }

  .js-plotly-plot {
    min-height: 20rem;
  }

  .js-plotly-plot .xtick text,
  .js-plotly-plot .ytick text,
  .js-plotly-plot .legendtext {
    font-size: 9px !important;
  }

  .js-plotly-plot .xtitle,
  .js-plotly-plot .ytitle,
  .js-plotly-plot .gtitle {
    font-size: 11px !important;
  }

  .dataTables_wrapper {
    font-size: 0.78rem;
  }

  .dashboard-recommendation-grid {
    grid-template-columns: 1fr !important;
  }
}

@media (max-width: 480px) {
  .js-plotly-plot .xtick text,
  .js-plotly-plot .ytick text,
  .js-plotly-plot .legendtext {
    font-size: 8px !important;
  }
}
</style>

```{r}
#| label: setup
#| context: setup
#| include: false

knitr::opts_knit$set(root.dir = normalizePath(getwd(), winslash = "/", mustWork = TRUE))

dashboard_machine_library <- file.path(
  path.expand("~/R"),
  paste0(R.version$platform, "-library"),
  paste(R.version$major, sub("\\..*$", "", R.version$minor), sep = ".")
)
if (dir.exists(dashboard_machine_library)) {
  .libPaths(unique(c(.libPaths(), dashboard_machine_library)))
}

library(here)
library(shiny)

source(here::here("r_scripts", "lib", "dashboard", "load.R"))

dashboard_database_path <- dashboard_resolve_database_path()
dashboard_talents <- dashboard_unified_talent_catalog(dashboard_database_path)

dashboard_default_talent_index <- grep(
  "^Avaritia",
  dashboard_talents$talent_name,
  ignore.case = TRUE
)[1]
if (is.na(dashboard_default_talent_index)) {
  dashboard_default_talent_index <- 1
}
dashboard_default_talent <- dashboard_talents[dashboard_default_talent_index, , drop = FALSE]
dashboard_talent_choices <- stats::setNames(
  dashboard_talents$talent_code,
  gsub("_", " ", dashboard_talents$talent_name, fixed = TRUE)
)

dashboard_global_min_date <- min(dashboard_talents$earliest_publish_date, na.rm = TRUE)
dashboard_global_max_date <- max(dashboard_talents$latest_publish_date, na.rm = TRUE)
if (!is.finite(dashboard_global_min_date)) {
  dashboard_global_min_date <- Sys.Date()
}
if (!is.finite(dashboard_global_max_date)) {
  dashboard_global_max_date <- Sys.Date()
}

dashboard_default_start_date <- dashboard_default_talent$earliest_publish_date[[1]]
dashboard_default_end_date <- dashboard_default_talent$latest_publish_date[[1]]
if (is.na(dashboard_default_start_date)) {
  dashboard_default_start_date <- dashboard_global_min_date
}
if (is.na(dashboard_default_end_date)) {
  dashboard_default_end_date <- dashboard_global_max_date
}

dashboard_render_ui <- function(value_fn, empty_message = "No data are available for the active filters.") {
  shiny::renderUI({
    value <- value_fn()
    if (is.null(value)) {
      return(dashboard_empty_state(empty_message))
    }
    if (inherits(value, "ggplot")) {
      value <- dashboard_ggplotly(value)
    }
    htmltools::as.tags(value)
  })
}

dashboard_talent_label <- function(data) {
  data$overview$value[data$overview$metric == "Talent"][[1]]
}

dashboard_optional_input_date <- function(date_range, index) {
  if (is.null(date_range) || length(date_range) < index || is.na(date_range[[index]])) {
    return(NULL)
  }
  as.Date(date_range[[index]])
}
```

# {.sidebar}

```{r}
selectInput(
  inputId = "talent",
  label = "Talent",
  choices = dashboard_talent_choices,
  selected = dashboard_default_talent$talent_code[[1]]
)

dateRangeInput(
  inputId = "publish_dates",
  label = "Published between",
  start = dashboard_default_start_date,
  end = dashboard_default_end_date,
  min = dashboard_global_min_date,
  max = dashboard_global_max_date,
  format = "yyyy-mm-dd",
  separator = " to "
)

actionButton(
  inputId = "apply_filters",
  label = "Apply filters",
  class = "btn-primary"
)

helpText("Date filters use each video's publication date. Clear both dates to use the talent's entire lifespan. Applying a new selection can take a minute while lifecycle and audience summaries rebuild.")
```

# Overview

This page summarizes the selected creator, publication window, source data, and top-performing videos.

## Row {height=22%}

```{r}
#| title: "Total Views"
uiOutput("overview_total_views")
```

```{r}
#| title: "Total Revenue"
uiOutput("overview_total_revenue")
```

```{r}
#| title: "Videos / Streams"
uiOutput("overview_total_videos")
```

```{r}
#| title: "Average Views"
uiOutput("overview_average_views")
```

## Row {height=55%}

```{r}
#| title: "Performance Over Time"
uiOutput("overview_performance_over_time")
```

```{r}
#| title: "Average View % by Content Type"
uiOutput("overview_engagement_distribution")
```

## Row {height=33%}

```{r}
#| title: "Top Videos"
uiOutput("overview_top_videos")
```

# Creator Performance

This page summarizes lifecycle performance for the active talent and publication window.

## Row {height=45%}

```{r}
#| title: "Latest Views vs Video Age"
uiOutput("creator_latest_views_age")
```

```{r}
#| title: "Recent Momentum vs Lifetime Rate"
uiOutput("creator_recent_vs_lifetime")
```

```{r}
#| title: "Lifecycle Classification Guide"
uiOutput("creator_lifecycle_guide")
```

## Row {height=45%}

```{r}
#| title: "Shorts"
uiOutput("creator_short_lifecycle")
```

```{r}
#| title: "Videos"
uiOutput("creator_video_lifecycle")
```

```{r}
#| title: "Live Streams"
uiOutput("creator_live_lifecycle")
```

# Content Strategy

This page focuses on topic, tag, and collaboration patterns that can guide future content planning.

## Row {height=50%}

### Column {width=33%}

```{r}
#| title: "Topic Performance"
uiOutput("strategy_topic_performance")
```

### Column {width=33%}

```{r}
#| title: "Tag Performance"
uiOutput("strategy_tag_performance")
```

### Column {width=34%}

```{r}
#| title: "Topic Longevity by Video Type"
uiOutput("strategy_topic_longevity")
```

## Row {height=50%}

### Column {width=33%}

```{r}
#| title: "Topic Table"
uiOutput("strategy_topic_table")
```

### Column {width=33%}

```{r}
#| title: "Tag Table"
uiOutput("strategy_tag_table")
```

### Column {width=34%}

```{r}
#| title: "Collaboration Performance"
uiOutput("strategy_collaboration_performance")
```

# Publishing Schedule

This page evaluates timing patterns for the active talent and publication window.

## Row {height=50%}

```{r}
#| title: "Day-of-Week Deviation from Average"
uiOutput("schedule_day_of_week_deviation")
```

```{r}
#| title: "Weekend vs Weekday Distribution"
uiOutput("schedule_weekend_weekday_distribution")
```

```{r}
#| title: "Topic-Weekday Heatmap"
uiOutput("schedule_topic_heatmap")
```

## Row {height=50%}

```{r}
#| title: "Day-of-Week Performance"
uiOutput("schedule_day_of_week_performance")
```

```{r}
#| title: "Weekday Summary"
uiOutput("schedule_weekday_summary")
```

# Audience

This page summarizes audience composition and audience geography where data are available.

## Row

```{r}
#| title: "Audience Age and Gender Trends"
uiOutput("audience_trends")
```

```{r}
#| title: "Audience Geography"
uiOutput("audience_geography_map")
```

## Row {height=34%}

```{r}
#| title: "Audience Summary"
uiOutput("audience_summary")
```

# Recommendations

These recommendations are generated from the active talent/publication window and should be read as descriptive signals, not causal claims.

## Row {height=42%}

```{r}
#| title: "Highest-Priority Recommendations"
uiOutput("recommendations_top")
```

## Row {height=42%}

```{r}
#| title: "Publishing Strategy"
uiOutput("recommendations_publishing")
```

```{r}
#| title: "Content Strategy"
uiOutput("recommendations_content")
```

## Row {height=42%}

```{r}
#| title: "Audience Strategy"
uiOutput("recommendations_audience")
```

```{r}
#| title: "Performance Strategy"
uiOutput("recommendations_performance")
```

## Row {height=26%}

```{r}
#| title: "Caveats and Data Limits"
uiOutput("recommendations_caveats")
```

# Method Notes

Use this dashboard as a descriptive operating view. Model-informed recommendations are planning signals, not proof of causality.

## Row

```{r}
#| title: "Active Filters"
uiOutput("method_filters")
```

```{r}
#| title: "Interpretation Notes"
#| results: asis

cat(
  "- The date range filters videos by publication date, not by analytics snapshot date.\n",
  "- Content type filters limit topic-weekday modeling and lifecycle displays to the requested formats.\n",
  "- Descriptive statistics can be affected by outliers, posting volume, and missing data.\n",
  "- Model-based recommendations are planning signals, not guarantees.\n",
  "- Correlation is not causation: timing, topic, collaboration, title, format, and external context can move together.\n",
  sep = ""
)
```

```{r}
#| label: server
#| context: server
#| include: false

observeEvent(input$talent, {
  selected <- dashboard_talents %>%
    dplyr::filter(.data$talent_code == input$talent) %>%
    dplyr::slice_head(n = 1)
  if (nrow(selected) == 1 &&
      !is.na(selected$earliest_publish_date[[1]]) &&
      !is.na(selected$latest_publish_date[[1]])) {
    updateDateRangeInput(
      session,
      inputId = "publish_dates",
      start = selected$earliest_publish_date[[1]],
      end = selected$latest_publish_date[[1]],
      min = selected$earliest_publish_date[[1]],
      max = selected$latest_publish_date[[1]]
    )
  }
}, ignoreInit = TRUE)

dashboard_data_reactive <- eventReactive(
  input$apply_filters,
  {
    req(input$talent)

    start_date <- dashboard_optional_input_date(input$publish_dates, 1)
    end_date <- dashboard_optional_input_date(input$publish_dates, 2)

    withProgress(message = "Building dashboard", value = 0, {
      incProgress(0.15, detail = "Loading unified database data")
      data <- build_creator_dashboard_data(
        talent = input$talent,
        data_source = "unified_db",
        database_path = dashboard_database_path,
        start_date = start_date,
        end_date = end_date,
        content_types = c("live", "video", "short"),
        reference_day = "Monday"
      )
      incProgress(0.85, detail = "Preparing dashboard components")
      data
    })
  },
  ignoreNULL = FALSE
)

dashboard_filter_summary_reactive <- reactive({
  data <- dashboard_data_reactive()
  start_date <- dashboard_optional_input_date(input$publish_dates, 1)
  end_date <- dashboard_optional_input_date(input$publish_dates, 2)
  tibble::tibble(
    setting = c(
      "Talent",
      "Data source",
      "Published from",
      "Published through"
    ),
    value = c(
      dashboard_talent_label(data),
      "Unified DuckDB",
      if (is.null(start_date)) "All available" else as.character(start_date),
      if (is.null(end_date)) "All available" else as.character(end_date)
    )
  )
})

output$overview_total_views <- dashboard_render_ui(function() {
  dashboard_metric_card(dashboard_data_reactive(), "total_views")
})
output$overview_total_revenue <- dashboard_render_ui(function() {
  dashboard_metric_card(dashboard_data_reactive(), "total_revenue")
})
output$overview_total_videos <- dashboard_render_ui(function() {
  dashboard_metric_card(dashboard_data_reactive(), "video_count")
})
output$overview_average_views <- dashboard_render_ui(function() {
  dashboard_metric_card(dashboard_data_reactive(), "average_views")
})
output$overview_performance_over_time <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_monthly_performance_plot(data, dashboard_talent_label(data))
})
output$overview_engagement_distribution <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_content_engagement_plot(data, dashboard_talent_label(data))
})
output$overview_top_videos <- dashboard_render_ui(function() {
  dashboard_top_videos_table(dashboard_data_reactive())
})

output$creator_latest_views_age <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_lifecycle_latest_views_age_plot(data, dashboard_talent_label(data))
})
output$creator_recent_vs_lifetime <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_lifecycle_recent_vs_lifetime_plot(data, dashboard_talent_label(data))
})
output$creator_lifecycle_guide <- dashboard_render_ui(dashboard_lifecycle_classification_guide)
output$creator_short_lifecycle <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_lifecycle_type_age_curve_plot(data, dashboard_talent_label(data), "short")
})
output$creator_video_lifecycle <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_lifecycle_type_age_curve_plot(data, dashboard_talent_label(data), "video")
})
output$creator_live_lifecycle <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_lifecycle_type_age_curve_plot(data, dashboard_talent_label(data), "live")
})

output$strategy_topic_performance <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_topic_performance_plot(data, dashboard_talent_label(data))
})
output$strategy_tag_performance <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_tag_performance_plot(data, dashboard_talent_label(data))
})
output$strategy_topic_longevity <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_lifecycle_topic_longevity_plot(data, dashboard_talent_label(data))
})
output$strategy_topic_table <- dashboard_render_ui(function() {
  dashboard_topic_performance_table(dashboard_data_reactive(), page_length = 10)
})
output$strategy_tag_table <- dashboard_render_ui(function() {
  dashboard_tag_performance_table(dashboard_data_reactive(), page_length = 15)
})
output$strategy_collaboration_performance <- dashboard_render_ui(function() {
  dashboard_collaboration_performance_compact_plot(dashboard_data_reactive())
})

output$schedule_day_of_week_deviation <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_day_of_week_deviation_plot(data, dashboard_talent_label(data))
})
output$schedule_weekend_weekday_distribution <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_weekend_weekday_distribution_plot(data, dashboard_talent_label(data))
})
output$schedule_topic_heatmap <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  available_types <- names(data$topic_weekday_summary)[
    purrr::map_lgl(data$topic_weekday_summary, function(result) {
      !is.null(result) && !is.null(result$topic_weekday) && nrow(result$topic_weekday) > 0
    })
  ]
  if (length(available_types) == 0) {
    return(dashboard_empty_state("Topic-weekday heatmap is unavailable for the active filters."))
  }
  content_type <- available_types[[1]]
  dashboard_topic_weekday_heatmap(
    data,
    content_type = content_type,
    content_label = dow_report_content_label(content_type)
  )
})
output$schedule_day_of_week_performance <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_weekday_plot(data, dashboard_talent_label(data))
})
output$schedule_weekday_summary <- dashboard_render_ui(function() {
  dashboard_weekday_table(dashboard_data_reactive())
})

output$audience_trends <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_audience_plot(data, dashboard_talent_label(data))
})
output$audience_geography_map <- dashboard_render_ui(function() {
  data <- dashboard_data_reactive()
  dashboard_audience_geography_map(data, dashboard_talent_label(data))
})
output$audience_summary <- dashboard_render_ui(function() {
  dashboard_datatable(dashboard_data_reactive()$audience_summary, page_length = 15)
})

output$recommendations_top <- dashboard_render_ui(function() {
  dashboard_recommendation_cards(dashboard_data_reactive()$recommendations$story$top)
})
output$recommendations_publishing <- dashboard_render_ui(function() {
  dashboard_recommendation_cards(
    dashboard_data_reactive()$recommendations$story,
    domain = "publishing"
  )
})
output$recommendations_content <- dashboard_render_ui(function() {
  dashboard_recommendation_cards(
    dashboard_data_reactive()$recommendations$story,
    domain = "content"
  )
})
output$recommendations_audience <- dashboard_render_ui(function() {
  dashboard_recommendation_cards(
    dashboard_data_reactive()$recommendations$story,
    domain = "audience"
  )
})
output$recommendations_performance <- dashboard_render_ui(function() {
  dashboard_recommendation_cards(
    dashboard_data_reactive()$recommendations$story,
    domain = "performance"
  )
})
output$recommendations_caveats <- dashboard_render_ui(function() {
  dashboard_recommendation_caveat_cards(dashboard_data_reactive()$recommendations$story)
})

output$method_filters <- dashboard_render_ui(function() {
  dashboard_filter_context_card(dashboard_filter_summary_reactive())
})
```
