---
title: "Creator Analytics Dashboard"
format:
  dashboard:
    embed-resources: true
    orientation: rows
execute:
  echo: false
  warning: false
  message: false
  keep-md: true
params:
  talent: "Ava"
  data_source: "datalake"
  data_root: null
  start_date: null
  end_date: null
  content_types: ["live", "video", "short"]
  reference_day: "Monday"
---

```{r}
#| label: setup
#| include: false

knitr::opts_knit$set(root.dir = normalizePath(getwd(), winslash = "/", mustWork = TRUE))
dashboard_render_dir <- normalizePath(getwd(), winslash = "/", mustWork = TRUE)

source("../../../r_scripts/lib/dashboard/dashboard_dependencies.R")
source("../../../r_scripts/lib/dashboard/dashboard_data.R")
source("../../../r_scripts/lib/dashboard/dashboard_sections.R")

dashboard_data <- build_creator_dashboard_data(
  talent = params$talent,
  data_source = params$data_source,
  data_root = params$data_root,
  start_date = params$start_date,
  end_date = params$end_date,
  content_types = params$content_types,
  reference_day = params$reference_day
)

dashboard_talent_label <- dashboard_data$overview$value[
  dashboard_data$overview$metric == "Talent"
][[1]]
dashboard_content_types <- names(dashboard_data$topic_weekday_summary)
dashboard_topic_weekday_types <- dashboard_content_types[
  purrr::map_lgl(dashboard_data$topic_weekday_summary, function(x) {
    !is.null(x) && !is.null(x$topic_weekday) && nrow(x$topic_weekday) > 0
  })
]
dashboard_primary_content_type <- if (length(dashboard_topic_weekday_types) > 0) {
  dashboard_topic_weekday_types[[1]]
} else {
  NA_character_
}

dashboard_filter_summary <- tibble::tibble(
  setting = c(
    "Talent parameter",
    "Data source",
    "Start date",
    "End date",
    "Content type filters",
    "Reference weekday"
  ),
  value = c(
    as.character(params$talent),
    as.character(params$data_source),
    if (is.null(params$start_date) || is.na(params$start_date)) "All available" else as.character(params$start_date),
    if (is.null(params$end_date) || is.na(params$end_date)) "All available" else as.character(params$end_date),
    paste(params$content_types, collapse = ", "),
    as.character(params$reference_day)
  )
)

dashboard_lifecycle_note <- paste(
  "Lifecycle summaries are now built from Bundle E panel data for the active talent and date window.",
  "Use the Creator Performance tab for the primary lifecycle view."
)
```

# Overview

This page summarizes the selected creator, reporting window, source data, and top-performing videos.

## Row {height=22%}

```{r}
#| label: overview-total-views
#| title: "Total Views"

dashboard_metric_card(dashboard_data, metric = "total_views")
```

```{r}
#| label: overview-total-revenue
#| title: "Total Revenue"

dashboard_metric_card(dashboard_data, metric = "total_revenue")
```

```{r}
#| label: overview-total-videos
#| title: "Videos / Streams"

dashboard_metric_card(dashboard_data, metric = "video_count")
```

```{r}
#| label: overview-average-views
#| title: "Average Views"

dashboard_metric_card(dashboard_data, metric = "average_views")
```

## Row {height=55%}

```{r}
#| label: overview-performance-over-time
#| title: "Performance Over Time"

dashboard_monthly_performance_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| label: overview-revenue-by-content-type
#| title: "Total Revenue by Content Type"

dashboard_revenue_content_type_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| label: overview-engagement-distribution
#| title: "Average View % by Content Type"

dashboard_content_engagement_plot(dashboard_data, talent = dashboard_talent_label)
```

## Row {height=33%}

```{r}
#| label: overview-top-videos
#| title: "Top Videos"

dashboard_top_videos_table(dashboard_data)
```

# Creator Performance

This page summarizes lifecycle performance for the active talent and date window.

## Row {height=45%}

```{r}
#| label: creator-latest-views-age
#| title: "Latest Views vs Video Age"

dashboard_lifecycle_latest_views_age_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| label: creator-recent-vs-lifetime
#| title: "Recent Momentum vs Lifetime Rate"

dashboard_lifecycle_recent_vs_lifetime_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| label: creator-lifecycle-classification-guide
#| title: "Lifecycle Classification Guide"

dashboard_lifecycle_classification_guide()
```

## Row {height=45%}

```{r}
#| label: creator-short-lifecycle
#| title: "Shorts"

dashboard_lifecycle_type_age_curve_plot(
  dashboard_data,
  talent = dashboard_talent_label,
  content_type = "short"
)
```

```{r}
#| label: creator-video-lifecycle
#| title: "Videos"

dashboard_lifecycle_type_age_curve_plot(
  dashboard_data,
  talent = dashboard_talent_label,
  content_type = "video"
)
```

```{r}
#| label: creator-live-lifecycle
#| title: "Live Streams"

dashboard_lifecycle_type_age_curve_plot(
  dashboard_data,
  talent = dashboard_talent_label,
  content_type = "live"
)
```

# Content Strategy

This page focuses on topic, tag, and collaboration patterns that can guide future content planning.

## Row {height=50%}

### Column {width=33%}

```{r}
#| label: strategy-topic-performance
#| title: "Topic Performance"

dashboard_topic_performance_plot(dashboard_data, talent = dashboard_talent_label)
```

### Column {width=33%}

```{r}
#| label: strategy-tag-performance
#| title: "Tag Performance"

dashboard_tag_performance_plot(dashboard_data, talent = dashboard_talent_label)
```

### Column {width=34%}

```{r}
#| label: strategy-topic-longevity
#| title: "Topic Longevity by Video Type"

dashboard_lifecycle_topic_longevity_plot(dashboard_data, talent = dashboard_talent_label)
```

## Row {height=50%}

### Column {width=33%}

```{r}
#| label: strategy-topic-table
#| title: "Topic Table"

dashboard_topic_performance_table(dashboard_data, page_length = 10)
```

### Column {width=33%}

```{r}
#| label: strategy-tag-table
#| title: "Tag Table"

dashboard_tag_performance_table(dashboard_data, page_length = 15)
```

### Column {width=34%}

```{r}
#| label: strategy-collaboration-performance
#| title: "Collaboration Performance"

dashboard_collaboration_performance_compact_plot(dashboard_data)
```

# Publishing Schedule

This page evaluates timing patterns for the active talent and date window.

## Row {height=50%}

```{r}
#| label: schedule-day-of-week-deviation
#| title: "Day-of-Week Deviation from Average"
#| fig-height: 4.8
#| fig-width: 5.2

dashboard_day_of_week_deviation_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| label: schedule-weekend-weekday-distribution
#| title: "Weekend vs Weekday Distribution"
#| fig-height: 4.8
#| fig-width: 5.2

dashboard_weekend_weekday_distribution_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| label: schedule-topic-heatmap
#| title: "Topic-Weekday Heatmap"
#| fig-height: 4.8
#| fig-width: 5.2

if (!is.na(dashboard_primary_content_type)) {
  dashboard_topic_weekday_heatmap(
    dashboard_data,
    content_type = dashboard_primary_content_type,
    content_label = dow_report_content_label(dashboard_primary_content_type)
  )
} else {
  dashboard_empty_state("Topic-weekday heatmap is unavailable for the active filters.")
}
```

## Row {height=50%}

```{r}
#| label: schedule-day-of-week-performance
#| title: "Day-of-Week Performance"
#| fig-height: 3.5
#| fig-width: 7

dashboard_weekday_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| label: schedule-weekday-summary
#| title: "Weekday Summary"

dashboard_weekday_table(dashboard_data)
```

# Audience

This page summarizes audience composition and audience geography where exports are available.

## Row

```{r}
#| label: audience-trends
#| title: "Audience Age and Gender Trends"

dashboard_audience_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| label: audience-geography-map
#| title: "Audience Geography"

dashboard_audience_geography_map(dashboard_data, talent = dashboard_talent_label)
```

## Row {height=34%}

```{r}
#| label: audience-summary
#| title: "Audience Summary"

dashboard_datatable(dashboard_data$audience_summary, page_length = 15)
```

# Recommendations

These recommendations are generated from the active talent/date window and should be read as descriptive signals, not causal claims.

## Row {height=42%}

```{r}
#| label: recommendations-top
#| title: "Highest-Priority Recommendations"

dashboard_recommendation_cards(dashboard_data$recommendations$story$top)
```

## Row {height=42%}

```{r}
#| label: recommendations-publishing
#| title: "Publishing Strategy"

dashboard_recommendation_cards(dashboard_data$recommendations$story, domain = "publishing")
```

```{r}
#| label: recommendations-content
#| title: "Content Strategy"

dashboard_recommendation_cards(dashboard_data$recommendations$story, domain = "content")
```

## Row {height=42%}

```{r}
#| label: recommendations-audience
#| title: "Audience Strategy"

dashboard_recommendation_cards(dashboard_data$recommendations$story, domain = "audience")
```

```{r}
#| label: recommendations-performance
#| title: "Performance Strategy"

dashboard_recommendation_cards(dashboard_data$recommendations$story, domain = "performance")
```

## Row {height=26%}

```{r}
#| label: recommendations-caveats
#| title: "Caveats and Data Limits"

dashboard_recommendation_caveat_cards(dashboard_data$recommendations$story)
```

# Method Notes

Use this dashboard as a descriptive operating view. Model-informed recommendations are planning signals, not proof of causality.

## Row

```{r}
#| label: method-filters
#| title: "Filters"

dashboard_datatable(dashboard_filter_summary, page_length = 6)
```

```{r}
#| label: method-interpretation-notes
#| title: "Interpretation Notes"
#| results: asis

cat(
  "- Reporting period follows the selected `start_date` and `end_date`; when both are empty, all available rows are used.\n",
  "- Content type filters limit topic-weekday modeling to the requested formats that exist in the prepared data.\n",
  "- Descriptive statistics summarize observed performance and can be affected by outliers, posting volume, and missing exports.\n",
  "- Model-based recommendations estimate expected logged views by weekday/topic patterns; they are planning signals, not guarantees.\n",
  "- Correlation is not causation: timing, topic, collaboration, title, format, and external context can move together.\n",
  "- Creator Performance uses Bundle E lifecycle panel summaries for age, momentum, topic longevity, and per-format curve comparisons.\n",
  sep = ""
)
```

```{r}
#| label: method-recommendation-rules
#| title: "Recommendation Rules"
#| results: asis

cat(
  "- Recommendations are generated by deterministic rule functions, not freeform AI prose.\n",
  "- Recommendations are descriptive signals from the active talent/date window, not causal claims.\n",
  "- Per-video metrics are preferred over total-volume metrics when making action recommendations.\n",
  "- Sample-size thresholds affect confidence labels; small samples produce weak or insufficient recommendations.\n",
  "- Views and revenue signals are evaluated separately when those fields are available.\n",
  "- Audience percentages are treated as shares, not raw audience counts.\n",
  "- Missing or sparse data produces fallback/data-limit messages instead of forced recommendations.\n",
  sep = ""
)
```

```{r}
#| label: method-lifecycle-classification
#| title: "Lifecycle Classification Rules"
#| results: asis

cat(
  "- `Re-accelerating`: recent 7-day average views per day are at least 1.5x the prior 7-day average.\n",
  "- `Evergreen`: the upload is at least 90 days old and its recent 30-day average views per day are at least 25% of its lifetime average views per day.\n",
  "- `Front-loaded`: the 30-day launch window is observed and recent 30-day average views per day have fallen to 10% or less of the first-30-days average pace.\n",
  "- `Other`: the upload does not meet the re-accelerating, evergreen, or front-loaded rules.\n",
  "- When more than one rule could apply in the momentum plot, Bundle E labels the video in this order: Re-accelerating, then Evergreen, then Front-loaded, then Other.\n",
  sep = ""
)
```

```{r}
#| label: restore-render-dir
#| include: false

setwd(dashboard_render_dir)
```
