---
title: "Bundle F: Day-of-Week Performance"
format:
  html:
    code-fold: false
    df-print: paged
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
params:
  talent: "Ava"
  data_source: "datalake"
  data_root: null
  render_generated_at: null
  included_date_range: "All available dates"
  render_cli: ""
  render_output_dir: null
  render_output_prefix: "Bundle_F"
  window_days: null
  start_date: null
  end_date: null
  reference_day: "Monday"
  content_types:
    - live
    - video
    - short
---

```{r}
#| label: setup
#| include: false

knitr::opts_knit$set(root.dir = normalizePath(file.path(getwd()), winslash = "/", mustWork = FALSE))

library(here)
library(readr)
library(dplyr)
library(purrr)
library(DT)

`%||%` <- function(x, y) {
  if (is.null(x) || length(x) == 0 || (length(x) == 1 && !nzchar(x))) y else x
}

source(here::here("r_scripts", "lib", "utils", "source_dir.r"))
source(here::here("r_scripts", "lib", "utils", "staging_root.R"))
source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "utils", "talent_select.R"))
source(here::here("r_scripts", "lib", "import_data", "talent_files.R"))
source(here::here("r_scripts", "lib", "clean_data", "CleanData.R"))
source(here::here("r_scripts", "lib", "clean_data", "title_classification_join.R"))
source(here::here("r_scripts", "lib", "plots", "PlottingThemes.R"))
source(here::here("r_scripts", "lib", "utils", "content_type_utils.R"))
source(here::here("r_scripts", "lib", "linear_regression", "day_of_week", "weekday_transform.R"))
source(here::here("r_scripts", "lib", "linear_regression", "day_of_week", "report_helpers.R"))

resolve_bundle_f_data_root <- function(data_source, data_root) {
  if (!is.null(data_root) && nzchar(trimws(data_root))) {
    return(normalizePath(data_root, winslash = "/", mustWork = FALSE))
  }
  if (identical(tolower(data_source), "datalake")) {
    return(normalizePath(get_datalake_root(), winslash = "/", mustWork = FALSE))
  }
  normalizePath(get_staging_root(), winslash = "/", mustWork = FALSE)
}

apply_bundle_f_publish_window <- function(df, start_date, end_date) {
  if (!("publish_date" %in% names(df))) {
    return(df)
  }
  if (!is.null(start_date) && nzchar(start_date)) {
    df <- df %>% dplyr::filter(.data$publish_date >= as.Date(start_date))
  }
  if (!is.null(end_date) && nzchar(end_date)) {
    df <- df %>% dplyr::filter(.data$publish_date <= as.Date(end_date))
  }
  df
}

canonical_bundle_f_content_types <- function(x) {
  if (is.null(x) || length(x) == 0) {
    return(c("live", "video", "short"))
  }
  x <- tolower(trimws(as.character(unlist(x))))
  x <- x[nzchar(x)]
  x <- dplyr::recode(
    x,
    videos = "video",
    shorts = "short",
    all = "all",
    .default = x
  )
  if ("all" %in% x) {
    return(c("live", "video", "short"))
  }
  unique(x)
}

data_root <- resolve_bundle_f_data_root(params$data_source, params$data_root)
talent_path <- select_talent(params$talent, root = data_root)
talent_folder <- basename(talent_path)
title_classifications <- load_title_classifications(talent = talent_folder)
talent_files <- TalentFiles(talent_path)[[1]]

required_video_types <- c(
  "video_analytics",
  "video_monetary",
  "video_demographics",
  "video_geography"
)
missing_video_exports <- setdiff(required_video_types, names(talent_files))
if (length(missing_video_exports) > 0L) {
  stop(
    "Missing required video export(s) for ",
    talent_folder,
    ": ",
    paste(missing_video_exports, collapse = ", ")
  )
}

stream_data <- video_preps_with_titles(
  files = talent_files,
  titles = title_classifications,
  talent = talent_folder,
  dedupe = TRUE
)

stream_video_level <- stream_data$analytics %>%
  dplyr::select(-dplyr::any_of(c("Estimated Revenue", "CPM"))) %>%
  dplyr::left_join(
    stream_data$monetary %>%
      dplyr::select(
        dplyr::all_of("Video ID"),
        dplyr::any_of(c("Estimated Revenue", "CPM"))
      ),
    by = "Video ID"
  ) %>%
  dplyr::mutate(talent_name = talent_folder) %>%
  apply_bundle_f_publish_window(params$start_date, params$end_date)

content_types <- canonical_bundle_f_content_types(params$content_types)
available_content_types <- sort(unique(tolower(trimws(as.character(stream_video_level$`Content Type`)))))
content_types <- intersect(content_types, available_content_types)
if (length(content_types) == 0L) {
  stop("No requested content types are available after filtering.")
}

content <- purrr::map(
  content_types,
  ~ stream_video_level %>%
    dplyr::filter(tolower(trimws(as.character(.data$`Content Type`))) == .x)
)
names(content) <- content_types
```

## Report Scope

```{r report_scope}
dow_report_datatable(
  tibble::tibble(
    field = c(
      "Talent",
      "Data source",
      "Data root",
      "Included publish date range",
      "Reference weekday",
      "Content types",
      "Generated"
    ),
    value = c(
      talent_folder,
      params$data_source,
      data_root,
      params$included_date_range,
      params$reference_day,
      paste(dow_report_content_label(content_types), collapse = ", "),
      params$render_generated_at %||% as.character(Sys.time())
    )
  ),
  "Bundle F render scope",
  page_length = 7
)
```

```{r content_type_overview}
stream_video_level %>%
  dplyr::count(`Content Type`, name = "videos") %>%
  dplyr::arrange(`Content Type`) %>%
  dow_report_datatable("Available content by type", page_length = 10)
```

```{r content_sections, results='asis'}
bundle_f_content_child <- function(content_type) {
  key <- gsub("[^a-z0-9]+", "_", tolower(content_type))
  key <- gsub("^_+|_+$", "", key)
  title <- dow_report_content_title(content_type)
  label <- dow_report_content_label(content_type)

  paste0(
    "\n# ", title, "\n\n",
    "```{r ", key, "_weekday_setup, include=FALSE}\n",
    "content_type <- \"", content_type, "\"\n",
    "content_df <- content[[content_type]]\n",
    "content_label <- dow_report_content_label(content_type)\n",
    "if (nrow(content_df) == 0L) {\n",
    "  stop(\"No rows are available for \", content_label, \" after filtering.\")\n",
    "}\n",
    "weekday_df <- dow_prep(content_df, reference_day = params$reference_day)\n",
    "weekday_summary <- dow_summary(weekday_df)\n",
    "weekday_summary_by_median <- weekday_summary %>%\n",
    "  dplyr::arrange(dplyr::desc(.data$median_views))\n",
    "weekday_models <- dow_fit(weekday_df)\n",
    "weekday_plots <- dow_plot(weekday_df, weekday_summary)\n",
    "```\n\n",
    "## Weekday Summary\n\n",
    "This table describes ", label, " performance for each publish weekday. Use `n` to judge how much evidence there is for each day, compare `mean_views` and `median_views` for typical performance, and use the confidence interval columns as a rough guide to uncertainty around the mean.\n\n",
    "```{r ", key, "_weekday_summary_table}\n",
    "dow_report_summary_datatable(weekday_summary, paste0(content_label, \": weekday summary\"))\n",
    "```\n\n",
    "## Weekdays Ranked By Median Views\n\n",
    "This is the same weekday summary, sorted by `median_views` from highest to lowest. Median views are useful when a few unusually large or unusually small uploads might distort the mean.\n\n",
    "```{r ", key, "_weekday_median_rank_table}\n",
    "dow_report_summary_datatable(\n",
    "  weekday_summary_by_median,\n",
    "  paste0(content_label, \": weekday summary ranked by median views\")\n",
    ")\n",
    "```\n\n",
    "## Raw Views Model Fit\n\n",
    "This table summarizes the linear model that predicts raw view counts from publish weekday. Higher R-squared values mean weekday explains more of the variation in views, while the model p-value tests whether the weekday model improves on a no-weekday baseline.\n\n",
    "```{r ", key, "_raw_model_fit_table}\n",
    "dow_report_model_fit_datatable(weekday_models$raw, paste0(content_label, \": raw views model fit\"))\n",
    "```\n\n",
    "## Raw Views Coefficients\n\n",
    "This table shows how each weekday compares with the reference weekday. The intercept is the estimated reference-day view count; each weekday coefficient is the estimated raw-view difference from that reference weekday.\n\n",
    "```{r ", key, "_raw_model_coefficients_table}\n",
    "dow_report_model_coefficient_datatable(\n",
    "  weekday_models$raw,\n",
    "  paste0(content_label, \": raw views model coefficients\")\n",
    ")\n",
    "```\n\n",
    "## Raw Views ANOVA\n\n",
    "This table tests the overall weekday term for the raw-views model. The weekday row asks whether publish weekday, as a group of categories, explains a meaningful amount of raw-view variation.\n\n",
    "```{r ", key, "_raw_model_anova_table}\n",
    "dow_report_model_anova_datatable(weekday_models$raw, paste0(content_label, \": raw views ANOVA\"))\n",
    "```\n\n",
    "## Log Views Model Fit\n\n",
    "This table summarizes the model using log-transformed views, which reduces the influence of unusually large uploads. Use this model when view counts are skewed and percentage-style differences are easier to interpret than raw count differences.\n\n",
    "```{r ", key, "_log_model_fit_table}\n",
    "dow_report_model_fit_datatable(weekday_models$log, paste0(content_label, \": log views model fit\"))\n",
    "```\n\n",
    "## Log Views Coefficients\n\n",
    "This table shows weekday differences on the log-view scale relative to the reference weekday. Positive estimates suggest higher expected views than the reference day; negative estimates suggest lower expected views.\n\n",
    "```{r ", key, "_log_model_coefficients_table}\n",
    "dow_report_model_coefficient_datatable(\n",
    "  weekday_models$log,\n",
    "  paste0(content_label, \": log views model coefficients\")\n",
    ")\n",
    "```\n\n",
    "## Log Views ANOVA\n\n",
    "This table tests the overall weekday term for the log-views model. If the weekday p-value is small, weekday appears to explain differences in viewership after reducing the impact of extreme view counts.\n\n",
    "```{r ", key, "_log_model_anova_table}\n",
    "dow_report_model_anova_datatable(weekday_models$log, paste0(content_label, \": log views ANOVA\"))\n",
    "```\n\n",
    "## Approximate Percent Change From Reference Weekday\n\n",
    "This table converts the log-model coefficients into approximate percent changes from the reference weekday. Positive values indicate higher expected views than the reference day, and negative values indicate lower expected views.\n\n",
    "```{r ", key, "_log_effects_table}\n",
    "dow_report_log_effects_datatable(\n",
    "  weekday_models$log_effects,\n",
    "  paste0(content_label, \": approximate percent change from reference weekday\")\n",
    ")\n",
    "```\n\n",
    "## Raw Views By Weekday\n\n",
    "This boxplot shows the distribution of views for each publish weekday. Compare the median line and the spread within each box; wide boxes or long whiskers mean performance varies more on that day.\n\n",
    "```{r ", key, "_raw_views_boxplot, fig.width=9, fig.height=5}\n",
    "weekday_plots$boxplot_views\n",
    "```\n\n",
    "## Mean Views With Confidence Intervals\n\n",
    "This plot compares average views by publish weekday. The vertical bars show 95% confidence intervals; overlapping intervals suggest the weekday averages may not be clearly different.\n\n",
    "```{r ", key, "_mean_ci_plot, fig.width=9, fig.height=5}\n",
    "weekday_plots$mean_ci_views\n",
    "```\n\n",
    "## Log Views By Weekday\n\n",
    "This boxplot shows the same weekday pattern on a log scale, which makes extreme high-view uploads less dominant. Use it to compare typical performance when raw views are heavily skewed.\n\n",
    "```{r ", key, "_log_views_boxplot, fig.width=9, fig.height=5}\n",
    "weekday_plots$boxplot_log_views\n",
    "```\n\n"
  )
}

child_text <- paste(vapply(names(content), bundle_f_content_child, character(1)), collapse = "\n")
cat(knitr::knit_child(text = child_text, quiet = TRUE))
```
