---
title: "Company Performance Dashboard"
format:
  dashboard:
    orientation: rows
server: shiny
execute:
  echo: false
  warning: false
  message: false
---

<style>
@media (min-width: 769px) {
  body.dashboard-sidebar .bslib-sidebar-layout {
    --bslib-sidebar-width: 330px;
  }
}

#snapshot_dates .input-daterange {
  flex-wrap: nowrap;
}

#snapshot_dates .input-daterange .form-control {
  min-width: 0;
  font-variant-numeric: tabular-nums;
}

.card-body:has(.company-dashboard-plot) {
  overflow: hidden;
}

.company-dashboard-plot {
  display: flex;
  width: 100%;
  height: 100%;
  min-width: 0;
  min-height: 0;
  overflow: hidden;
}

.company-dashboard-plot > .html-widget {
  flex: 1 1 auto;
  min-width: 0;
  min-height: 0;
}

.company-downloads {
  display: flex;
  flex-wrap: wrap;
  gap: 0.6rem;
  padding: 0.75rem 0;
}

.company-fun-stat-grid {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(12rem, 1fr));
  gap: 0.75rem;
}

.company-fun-stat {
  border: 1px solid rgba(0, 0, 0, 0.12);
  border-radius: 0.5rem;
  padding: 0.8rem;
  background: var(--bs-body-bg, #fff);
}

.company-fun-stat-value {
  font-size: 1.35rem;
  font-weight: 700;
}

.company-fun-stat-label {
  color: var(--bs-secondary-color, #666);
  font-size: 0.82rem;
}

.company-value-note {
  display: block;
  margin-top: 0.3rem;
  color: var(--bs-secondary-color, #666);
  font-size: 0.75rem;
  font-weight: 400;
  line-height: 1.25;
}

@media (max-width: 768px) {
  .card:not(.bslib-value-box) {
    min-height: 24rem;
  }

  .js-plotly-plot {
    min-height: 20rem;
  }

  .dataTables_wrapper {
    font-size: 0.78rem;
  }
}
</style>

```{r}
#| label: setup
#| context: setup
#| include: false

knitr::opts_knit$set(
  root.dir = normalizePath(getwd(), winslash = "/", mustWork = TRUE)
)

dashboard_machine_library <- file.path(
  path.expand("~/R"),
  paste0(R.version$platform, "-library"),
  paste(R.version$major, sub("\\..*$", "", R.version$minor), sep = ".")
)
if (dir.exists(dashboard_machine_library)) {
  .libPaths(unique(c(.libPaths(), dashboard_machine_library)))
}

library(here)
library(shiny)

source(here::here("r_scripts", "lib", "dashboard", "load.R"))

dashboard_database_path <- dashboard_resolve_database_path()
dashboard_startup_talents <- dashboard_unified_talent_catalog(
  dashboard_database_path
)
dashboard_startup_companies <- dashboard_company_memberships(
  dashboard_startup_talents
)

dashboard_global_min_date <- min(
  dashboard_startup_companies$earliest_analytics_snapshot_date,
  na.rm = TRUE
)
dashboard_global_max_date <- max(
  dashboard_startup_companies$latest_analytics_snapshot_date,
  na.rm = TRUE
)
if (!is.finite(dashboard_global_min_date)) {
  dashboard_global_min_date <- Sys.Date()
}
if (!is.finite(dashboard_global_max_date)) {
  dashboard_global_max_date <- Sys.Date()
}

company_display_name <- function(x) {
  gsub("_", " ", as.character(x), fixed = TRUE)
}

company_optional_input_date <- function(date_range, index) {
  if (is.null(date_range) || length(date_range) < index ||
      is.na(date_range[[index]])) {
    return(NULL)
  }
  as.Date(date_range[[index]])
}

company_render_ui <- function(
  value_fn,
  empty_message = "No data are available for the active filters."
) {
  shiny::renderUI({
    value <- value_fn()
    if (is.null(value)) {
      return(dashboard_empty_state(empty_message))
    }
    if (inherits(value, "ggplot")) {
      value <- dashboard_ggplotly(value)
    }
    if (inherits(value, "plotly")) {
      return(
        htmltools::div(
          class = "company-dashboard-plot",
          htmltools::as.tags(value)
        )
      )
    }
    htmltools::as.tags(value)
  })
}

company_value_box <- function(title, value, note = NULL) {
  displayed_value <- if (is.null(note)) {
    value
  } else {
    htmltools::tagList(
      htmltools::tags$span(value),
      htmltools::tags$small(class = "company-value-note", note)
    )
  }
  if (requireNamespace("bslib", quietly = TRUE)) {
    return(bslib::value_box(title = title, value = displayed_value))
  }
  htmltools::div(
    class = "dashboard-metric-card",
    htmltools::tags$div(class = "dashboard-metric-label", title),
    htmltools::tags$div(class = "dashboard-metric-value", displayed_value)
  )
}

company_number <- function(value, accuracy = 1) {
  if (length(value) == 0 || !is.finite(value[[1]])) {
    return("N/A")
  }
  scales::comma(value[[1]], accuracy = accuracy)
}

company_percent <- function(value, accuracy = 0.1) {
  if (length(value) == 0 || !is.finite(value[[1]])) {
    return("N/A")
  }
  scales::percent(value[[1]], accuracy = accuracy)
}

company_seconds <- function(value) {
  if (length(value) == 0 || !is.finite(value[[1]])) {
    return("N/A")
  }
  paste0(scales::number(value[[1]] / 60, accuracy = 0.1), " min")
}

company_searchable_datatable <- function(data, page_length = 25) {
  if (is.null(data) || nrow(data) == 0) {
    return(NULL)
  }
  DT::datatable(
    data,
    rownames = FALSE,
    filter = "top",
    class = "display stripe hover",
    options = list(
      pageLength = page_length,
      scrollX = TRUE,
      autoWidth = TRUE
    )
  )
}

company_fun_stat_cards <- function(data) {
  if (is.null(data) || nrow(data) == 0) {
    return(NULL)
  }
  htmltools::div(
    class = "company-fun-stat-grid",
    lapply(seq_len(nrow(data)), function(index) {
      htmltools::div(
        class = "company-fun-stat",
        htmltools::div(
          class = "company-fun-stat-value",
          data$value[[index]]
        ),
        htmltools::div(
          class = "company-fun-stat-label",
          data$statistic[[index]]
        )
      )
    })
  )
}

company_month_plot <- function(data, value_col, y_label) {
  if (is.null(data) || nrow(data) == 0) {
    return(NULL)
  }
  ggplot2::ggplot(
    data,
    ggplot2::aes(
      x = .data$publish_month,
      y = .data[[value_col]],
      text = paste0(
        format(.data$publish_month, "%Y-%m"),
        "<br>", y_label, ": ", scales::comma(.data[[value_col]])
      )
    )
  ) +
    ggplot2::geom_col(fill = "#2c7fb8") +
    ggplot2::scale_x_date(date_labels = "%Y-%m", date_breaks = "3 months") +
    ggplot2::labs(x = "Publication month", y = y_label) +
    ggplot2::theme_minimal(base_size = 11)
}

company_talent_weekday_plot <- function(data) {
  if (is.null(data) || nrow(data) == 0) {
    return(NULL)
  }
  data <- data %>%
    dplyr::mutate(talent_label = company_display_name(.data$talent_name))
  weekday_totals <- data %>%
    dplyr::group_by(.data$publish_wday) %>%
    dplyr::summarise(
      total_releases = sum(.data$`Content Releases`),
      .groups = "drop"
    )
  ggplot2::ggplot(
    data,
    ggplot2::aes(
      x = .data$publish_wday,
      y = .data$`Content Releases`,
      fill = .data$talent_label,
      text = paste0(
        .data$talent_label,
        "<br>Day: ", .data$publish_wday,
        "<br>Content releases: ", scales::comma(.data$`Content Releases`)
      )
    )
  ) +
    ggplot2::geom_col(position = "stack", width = 0.75) +
    ggplot2::geom_text(
      data = weekday_totals,
      ggplot2::aes(
        x = .data$publish_wday,
        y = .data$total_releases,
        label = scales::comma(.data$total_releases)
      ),
      inherit.aes = FALSE,
      vjust = -0.4,
      fontface = "bold",
      size = 3.5
    ) +
    ggplot2::scale_y_continuous(
      expand = ggplot2::expansion(mult = c(0, 0.12))
    ) +
    ggplot2::labs(x = NULL, y = "Content releases", fill = "Talent") +
    ggplot2::theme_minimal(base_size = 11) +
    ggplot2::theme(legend.position = "bottom")
}

company_portfolio_share_plot <- function(data) {
  if (is.null(data) || nrow(data) == 0) {
    return(NULL)
  }
  metric_levels <- c(
    "Releases",
    "Cumulative views",
    "Audience watch hours",
    "Video-page subscriptions"
  )
  plot_data <- dplyr::bind_rows(
    data %>%
      dplyr::transmute(
        Talent = company_display_name(.data$talent_name),
        Metric = "Releases",
        Value = as.numeric(.data$`Videos / Streams`),
        Share = .data$`Release Share`
      ),
    data %>%
      dplyr::transmute(
        Talent = company_display_name(.data$talent_name),
        Metric = "Cumulative views",
        Value = .data$`Total Views`,
        Share = .data$`View Share`
      ),
    data %>%
      dplyr::transmute(
        Talent = company_display_name(.data$talent_name),
        Metric = "Audience watch hours",
        Value = .data$`Watch Hours`,
        Share = .data$`Watch-time Share`
      ),
    data %>%
      dplyr::transmute(
        Talent = company_display_name(.data$talent_name),
        Metric = "Video-page subscriptions",
        Value = .data$`Video-Page Subscriptions`,
        Share = .data$`Video-Page Subscription Share`
      )
  ) %>%
    dplyr::group_by(.data$Metric) %>%
    dplyr::mutate(
      Total = sum(.data$Value, na.rm = TRUE),
      `Contribution Value` = dplyr::if_else(
        .data$Metric == "Audience watch hours",
        scales::comma(.data$Value, accuracy = 0.1),
        scales::comma(round(.data$Value))
      ),
      `Company Total` = dplyr::if_else(
        .data$Metric == "Audience watch hours",
        scales::comma(.data$Total, accuracy = 0.1),
        scales::comma(round(.data$Total))
      ),
      `Share Label` = scales::percent(.data$Share, accuracy = 0.1),
      Metric = factor(.data$Metric, levels = rev(metric_levels))
    ) %>%
    dplyr::ungroup()

  ggplot2::ggplot(
    plot_data,
      ggplot2::aes(
        x = .data$Share,
        y = .data$Metric,
        fill = .data$Talent,
        text = paste0(
          .data$Talent,
          "<br>",
          .data$Metric,
          "<br>Contribution: ",
          .data$`Contribution Value`,
          " of ",
          .data$`Company Total`,
          "<br>Share: ",
          .data$`Share Label`
        )
      )
    ) +
    ggplot2::geom_col(position = "stack", width = 0.7) +
    ggplot2::geom_text(
      ggplot2::aes(label = .data$`Share Label`),
      position = ggplot2::position_stack(vjust = 0.5),
      color = "white",
      fontface = "bold",
      size = 3.2,
      show.legend = FALSE
    ) +
    ggplot2::scale_x_continuous(
      labels = scales::label_percent(),
      limits = c(0, 1),
      expand = c(0, 0)
    ) +
    ggplot2::guides(fill = ggplot2::guide_legend(reverse = TRUE)) +
    ggplot2::labs(
      x = "Talent share of the selected-company total",
      y = NULL,
      fill = "Talent",
      subtitle = paste(
        "Each bar represents 100% of one metric across the selected talents.",
        "Colored segments show each talent's contribution."
      ),
      caption = paste(
        "Values use each talent's latest analytics snapshot inside the active",
        "date window. Hover for exact contribution and total values."
      )
    ) +
    ggplot2::theme_minimal(base_size = 11) +
    ggplot2::theme(
      legend.position = "bottom",
      panel.grid.major.y = ggplot2::element_blank(),
      plot.subtitle = ggplot2::element_text(color = "#555555"),
      plot.caption = ggplot2::element_text(hjust = 0, color = "#666666")
    )
}
```

# {.sidebar}

```{r}
uiOutput("dashboard_identity")
uiOutput("company_selector")
uiOutput("talent_selector")
uiOutput("dashboard_data_freshness")

dateRangeInput(
  inputId = "snapshot_dates",
  label = "Analytics snapshots between",
  start = dashboard_global_min_date,
  end = dashboard_global_max_date,
  min = dashboard_global_min_date,
  max = dashboard_global_max_date,
  format = "yyyy-mm-dd",
  separator = " to "
)

helpText(
  "All authorized company talents are selected by default. Remove talents to compare a subset. ",
  "The date range selects daily analytics snapshots, matching the creator dashboard; ",
  "each talent contributes its latest available snapshot inside the window."
)
```

# Overview

Company totals aggregate the latest selected snapshot for each selected talent.
Each video is counted once, so cumulative analytics are not summed across days.

## Row {height=22%}

```{r}
#| title: "Total Views"
uiOutput("total_views")
```

```{r}
#| title: "Videos / Streams"
uiOutput("video_count")
```

```{r}
#| title: "Total Content Hours"
uiOutput("content_hours")
```

```{r}
#| title: "Video-Page Subscriptions"
uiOutput("video_page_subscriptions")
```

## Row {height=22%}

```{r}
#| title: "Average Views per Release"
uiOutput("average_views")
```

```{r}
#| title: "Median Views per Release"
uiOutput("median_views")
```

```{r}
#| title: "Average Video-Page Subscriptions"
uiOutput("subscriptions_per_release")
```

```{r}
#| title: "Collaboration-Tagged Releases"
uiOutput("collaboration_releases")
```

## Row {height=48%}

```{r}
#| title: "Talent Breakdown"
uiOutput("talent_summary")
```

```{r}
#| title: "Content Releases by Month"
uiOutput("content_month_plot")
```

# Performance & Attention

Attention metrics use cumulative analytics from each talent's selected
snapshot. They describe observed channel performance, not unique audience reach
or predicted campaign results.

## Row {height=24%}

```{r}
#| title: "Watch Hours"
uiOutput("watch_hours")
```

```{r}
#| title: "Average View Duration"
uiOutput("average_view_duration")
```

```{r}
#| title: "Views-weighted Average View %"
uiOutput("weighted_view_percentage")
```

```{r}
#| title: "Views per Content Hour"
uiOutput("views_per_content_hour")
```

```{r}
#| title: "Video-Page Subscriptions per 1,000 Views"
uiOutput("subscriptions_per_thousand_views")
```

## Row {height=68%}

```{r}
#| title: "Performance by Content Type"
uiOutput("content_type_performance")
```

```{r}
#| title: "Performance by Topic"
uiOutput("topic_performance")
```

# Talent Portfolio

Each contribution bar represents 100% of one metric across the active talent
selection. The colored segments show how much each talent contributes to that
total; they do not show growth or performance against a target.

## Row {height=48%}

```{r}
#| title: "How Talents Contribute to Company Totals"
uiOutput("portfolio_share_plot")
```

```{r}
#| title: "Talent Portfolio Summary"
uiOutput("portfolio_table")
```

## Row {height=44%}

```{r}
#| title: "Content Mix by Talent"
uiOutput("content_type_mix")
```

# Publishing Activity

These panels group the selected videos by publication timing. The sidebar dates
still select analytics snapshots, not video publication dates.

## Row {height=48%}

```{r}
#| title: "Release Day Frequency"
uiOutput("weekday_plot")
```

```{r}
#| title: "Collaborations by Month"
uiOutput("collaboration_plot")
```

## Row {height=44%}

```{r}
#| title: "Monthly Release Table"
uiOutput("month_table")
```

```{r}
#| title: "Weekday Release Table"
uiOutput("weekday_table")
```

# Content Mix

Topic and reference values come from the same latest title-classification rows
used by the creator dashboard.

## Row {height=46%}

```{r}
#| title: "Content Hours by Topic"
uiOutput("topic_plot")
```

```{r}
#| title: "Topic Summary"
uiOutput("topic_table")
```

## Row {height=48%}

```{r}
#| title: "Topic and Included Reference"
uiOutput("reference_table")
```

## Row {height=48%}

```{r}
#| title: "Collaboration Performance"
uiOutput("collaboration_performance")
```

```{r}
#| title: "Representative Content"
uiOutput("representative_content")
```

# Video Explorer & Data Extraction

The explorer contains one row per selected video at the applicable talent
snapshot. Search and column filters support evidence review; downloads preserve
the active company, talent, and snapshot selections.

## Row {height=18%}

```{r}
htmltools::div(
  class = "company-downloads",
  downloadButton("download_company_summary", "Company summary CSV"),
  downloadButton("download_talent_portfolio", "Talent portfolio CSV"),
  downloadButton("download_content_summary", "Content summary CSV"),
  downloadButton("download_video_data", "Video-level CSV")
)
```

## Row {height=72%}

```{r}
#| title: "Searchable Video Explorer"
uiOutput("video_explorer")
```

# Fun Statistics

These are reproducible, graphic-friendly observations from the active
selection. They are descriptive statistics rather than promotional claims.

## Row {height=75%}

```{r}
uiOutput("fun_statistics")
```

# Method Notes

## Row {height=38%}

```{r}
#| title: "Active Filters"
uiOutput("method_filters")
```

```{r}
#| title: "Snapshot Coverage"
uiOutput("snapshot_coverage")
```

## Row {height=34%}

```{r}
#| title: "Metric Coverage"
uiOutput("metric_coverage")
```

```{r}
#| title: "Audience Data Availability"
uiOutput("audience_availability")
```

## Row {height=50%}

```{r}
#| title: "Metric Definitions"
uiOutput("metric_definitions")
```

```{r}
#| title: "Calculation Notes"
#| results: asis

cat(
  "- Date filters apply to analytics snapshot dates, matching the creator dashboard.\n",
  "- Each talent contributes only its latest snapshot within the selected range.\n",
  "- Total views and video-page subscription events are cumulative values at those snapshots.\n",
  "- Total content hours sum the catalogued duration of each distinct video or stream; the displayed day conversion is a scale reference, not elapsed calendar time or audience watch time.\n",
  "- Watch hours use cumulative estimated minutes watched from YouTube Analytics.\n",
  "- Average view duration is aggregate watch seconds divided by total views.\n",
  "- Average view percentage is weighted by views rather than averaged equally across releases.\n",
  "- Monthly and weekday panels group those distinct videos by publication date.\n",
  "- Representative content is selected reproducibly as the top three releases by cumulative views for each selected talent.\n",
  "- Total views are not unique viewers or unique reach. Unsupported audience fields remain explicitly unavailable.\n",
  "- Company membership is maintained in `config/dashboard/company_talents.csv`.\n",
  sep = ""
)
```

```{r}
#| label: server
#| context: server
#| include: false

dashboard_talents <- dashboard_unified_talent_catalog(dashboard_database_path)
dashboard_companies <- dashboard_company_memberships(dashboard_talents)
dashboard_session_access <- dashboard_access_context(
  session$request,
  dashboard_talents$talent_code
)
dashboard_allowed_companies <- dashboard_companies %>%
  dplyr::filter(
    .data$talent_code %in% dashboard_session_access$allowed_talent_codes
  )

dashboard_live_talents <- reactive({
  invalidateLater(60 * 1000, session)
  tryCatch(
    dashboard_unified_talent_catalog(dashboard_database_path),
    error = function(e) dashboard_talents
  )
})

output$dashboard_identity <- renderUI({
  if (!dashboard_session_access$authorized ||
      nrow(dashboard_allowed_companies) == 0) {
    return(
      htmltools::div(
        class = "alert alert-danger",
        "No company dashboard permissions were found for this account."
      )
    )
  }

  htmltools::tags$small(
    class = "text-muted",
    paste("Signed in as", dashboard_session_access$verified_email)
  )
})

output$company_selector <- renderUI({
  if (!dashboard_session_access$authorized ||
      nrow(dashboard_allowed_companies) == 0) {
    return(NULL)
  }

  choices <- dashboard_allowed_companies %>%
    dplyr::distinct(.data$company_code, .data$company_name) %>%
    dplyr::arrange(.data$company_name)
  selectInput(
    inputId = "company",
    label = "Company",
    choices = stats::setNames(choices$company_code, choices$company_name),
    selected = choices$company_code[[1]]
  )
})

output$talent_selector <- renderUI({
  req(input$company)
  choices <- dashboard_allowed_companies %>%
    dplyr::filter(.data$company_code == input$company) %>%
    dplyr::arrange(.data$talent_name)
  if (nrow(choices) == 0) {
    return(NULL)
  }

  htmltools::tagList(
    selectizeInput(
      inputId = "talents",
      label = "Talents",
      choices = stats::setNames(
        choices$talent_code,
        company_display_name(choices$talent_name)
      ),
      selected = choices$talent_code,
      multiple = TRUE,
      options = list(plugins = list("remove_button"))
    ),
    actionLink(
      inputId = "select_all_talents",
      label = "Select all company talents"
    )
  )
})

selected_company_memberships <- reactive({
  req(input$company)
  dashboard_allowed_companies %>%
    dplyr::filter(.data$company_code == input$company)
})

observeEvent(input$select_all_talents, {
  choices <- selected_company_memberships() %>%
    dplyr::arrange(.data$talent_name)
  updateSelectizeInput(
    session,
    inputId = "talents",
    choices = stats::setNames(
      choices$talent_code,
      company_display_name(choices$talent_name)
    ),
    selected = choices$talent_code,
    server = FALSE
  )
})

selected_talent_codes <- reactive({
  req(length(input$talents) > 0)
  allowed <- selected_company_memberships()$talent_code
  selected <- intersect(as.character(input$talents), allowed)
  req(length(selected) > 0)
  selected
})

dashboard_snapshot_bounds <- reactiveVal(NULL)

observe({
  selected_codes <- selected_talent_codes()
  selected <- dashboard_live_talents() %>%
    dplyr::filter(.data$talent_code %in% selected_codes)
  req(nrow(selected) > 0)

  min_date <- min(selected$earliest_analytics_snapshot_date, na.rm = TRUE)
  max_date <- max(selected$latest_analytics_snapshot_date, na.rm = TRUE)
  req(is.finite(min_date), is.finite(max_date))

  new_bounds <- list(
    talent_codes = sort(selected_codes),
    min = min_date,
    max = max_date
  )
  old_bounds <- isolate(dashboard_snapshot_bounds())
  if (!is.null(old_bounds) && identical(old_bounds, new_bounds)) {
    return()
  }

  current_dates <- isolate(input$snapshot_dates)
  talents_changed <- is.null(old_bounds) ||
    !identical(old_bounds$talent_codes, new_bounds$talent_codes)
  if (talents_changed || is.null(current_dates) || length(current_dates) < 2) {
    selected_start <- new_bounds$min
    selected_end <- new_bounds$max
  } else {
    selected_start <- max(as.Date(current_dates[[1]]), new_bounds$min, na.rm = TRUE)
    current_end <- as.Date(current_dates[[2]])
    selected_end <- if (is.na(current_end) || identical(current_end, old_bounds$max)) {
      new_bounds$max
    } else {
      min(current_end, new_bounds$max)
    }
  }

  updateDateRangeInput(
    session,
    inputId = "snapshot_dates",
    start = selected_start,
    end = selected_end,
    min = new_bounds$min,
    max = new_bounds$max
  )
  dashboard_snapshot_bounds(new_bounds)
})

output$dashboard_data_freshness <- renderUI({
  selected_codes <- selected_talent_codes()
  selected <- dashboard_live_talents() %>%
    dplyr::filter(.data$talent_code %in% selected_codes)
  req(nrow(selected) > 0)

  latest_dates <- selected$latest_analytics_snapshot_date
  latest_dates <- latest_dates[!is.na(latest_dates)]
  if (length(latest_dates) == 0) {
    return(NULL)
  }

  htmltools::div(
    class = "alert alert-info py-2 px-3",
    htmltools::tags$strong(
      paste(
        "Latest talent snapshots:",
        format(min(latest_dates), "%Y-%m-%d"),
        "to",
        format(max(latest_dates), "%Y-%m-%d")
      )
    ),
    htmltools::tags$br(),
    htmltools::tags$small(
      paste(length(selected_codes), "talent(s) selected")
    )
  )
})

dashboard_filters <- shiny::debounce(
  reactive({
    req(dashboard_session_access$authorized)
    company <- selected_company_memberships() %>% dplyr::slice_head(n = 1)
    list(
      company_code = company$company_code[[1]],
      company_name = company$company_name[[1]],
      talent_codes = selected_talent_codes(),
      start_date = company_optional_input_date(input$snapshot_dates, 1),
      end_date = company_optional_input_date(input$snapshot_dates, 2)
    )
  }),
  millis = 400
)

company_data_reactive <- reactive({
  filters <- dashboard_filters()
  withProgress(message = "Building company dashboard", value = 0, {
    incProgress(0.2, detail = "Loading latest selected snapshots")
    data <- dashboard_load_company_analytics(
      database_path = dashboard_database_path,
      talent_codes = filters$talent_codes,
      start_date = filters$start_date,
      end_date = filters$end_date
    )
    incProgress(0.8, detail = "Preparing company summaries")
    data
  })
})

company_analytics_reactive <- reactive({
  company_data_reactive()$analytics
})

company_totals_reactive <- reactive({
  dashboard_company_totals(company_analytics_reactive())
})

company_month_reactive <- reactive({
  dashboard_company_month_summary(company_analytics_reactive())
})

company_weekday_reactive <- reactive({
  dashboard_company_weekday_summary(company_analytics_reactive())
})

company_topic_reactive <- reactive({
  dashboard_company_topic_summary(company_analytics_reactive())
})

company_performance_reactive <- reactive({
  dashboard_company_performance_summary(company_analytics_reactive())
})

company_attention_reactive <- reactive({
  dashboard_company_attention_summary(company_analytics_reactive())
})

company_portfolio_reactive <- reactive({
  dashboard_company_portfolio_summary(company_analytics_reactive())
})

company_content_type_reactive <- reactive({
  dashboard_company_content_type_summary(company_analytics_reactive())
})

company_topic_performance_reactive <- reactive({
  dashboard_company_performance_summary(
    company_analytics_reactive(),
    group_columns = "topic"
  ) %>%
    dplyr::arrange(dplyr::desc(.data$`Total Views`))
})

company_collaboration_performance_reactive <- reactive({
  company_analytics_reactive() %>%
    dplyr::mutate(
      Collaboration = dplyr::if_else(.data$is_collab, "Yes", "No")
    ) %>%
    dashboard_company_performance_summary(group_columns = "Collaboration")
})

company_video_reactive <- reactive({
  dashboard_company_video_explorer(company_analytics_reactive())
})

company_representative_reactive <- reactive({
  dashboard_company_representative_content(company_analytics_reactive())
})

company_fun_statistics_reactive <- reactive({
  dashboard_company_fun_statistics(company_analytics_reactive())
})

company_metric_coverage_reactive <- reactive({
  dashboard_company_data_quality(company_analytics_reactive())
})

output$total_views <- company_render_ui(function() {
  company_value_box(
    "Total Views",
    scales::comma(round(company_totals_reactive()$total_views[[1]]))
  )
})

output$video_count <- company_render_ui(function() {
  company_value_box(
    "Videos / Streams",
    scales::comma(company_totals_reactive()$video_count[[1]])
  )
})

output$content_hours <- company_render_ui(function() {
  total_hours <- company_totals_reactive()$total_hours[[1]]
  company_value_box(
    "Total Content Hours",
    scales::comma(total_hours, accuracy = 0.1),
    paste0(
      "Equivalent to ",
      scales::comma(total_hours / 24, accuracy = 0.1),
      " continuous 24-hour days of content"
    )
  )
})

output$video_page_subscriptions <- company_render_ui(function() {
  company_value_box(
    "Video-Page Subscriptions",
    scales::comma(
      round(company_totals_reactive()$video_page_subscriptions[[1]])
    ),
    "Cumulative watch-page events; not current subscriber total"
  )
})

output$average_views <- company_render_ui(function() {
  company_value_box(
    "Average Views per Release",
    company_number(company_performance_reactive()$`Average Views`, accuracy = 1)
  )
})

output$median_views <- company_render_ui(function() {
  company_value_box(
    "Median Views per Release",
    company_number(company_performance_reactive()$`Median Views`, accuracy = 1)
  )
})

output$subscriptions_per_release <- company_render_ui(function() {
  performance <- company_performance_reactive()
  company_value_box(
    "Average Video-Page Subscriptions",
    company_number(
      performance$`Video-Page Subscriptions per Release`,
      accuracy = 0.1
    ),
    paste0(
      scales::comma(round(performance$`Video-Page Subscriptions`[[1]])),
      " events across ",
      scales::comma(performance$`Videos / Streams`[[1]]),
      " releases"
    )
  )
})

output$collaboration_releases <- company_render_ui(function() {
  performance <- company_performance_reactive()
  collaboration_count <- performance$`Collaboration-Tagged Releases`[[1]]
  release_count <- performance$`Videos / Streams`[[1]]
  company_value_box(
    "Collaboration-Tagged Releases",
    paste0(
      scales::comma(collaboration_count),
      " of ",
      scales::comma(release_count)
    ),
    paste0(
      company_percent(
        performance$`Collaboration-Tagged Share`,
        accuracy = 0.1
      ),
      " of selected releases"
    )
  )
})

output$watch_hours <- company_render_ui(function() {
  company_value_box(
    "Watch Hours",
    company_number(company_attention_reactive()$`Watch Hours`, accuracy = 0.1)
  )
})

output$average_view_duration <- company_render_ui(function() {
  company_value_box(
    "Average View Duration",
    company_seconds(
      company_attention_reactive()$`Average View Duration (sec)`
    )
  )
})

output$weighted_view_percentage <- company_render_ui(function() {
  value <- company_attention_reactive()$`Views-weighted Average View %`
  company_value_box(
    "Views-weighted Average View %",
    if (length(value) == 0 || !is.finite(value[[1]])) {
      "N/A"
    } else {
      paste0(company_number(value, accuracy = 0.1), "%")
    }
  )
})

output$views_per_content_hour <- company_render_ui(function() {
  company_value_box(
    "Views per Content Hour",
    company_number(
      company_attention_reactive()$`Views per Content Hour`,
      accuracy = 0.1
    )
  )
})

output$subscriptions_per_thousand_views <- company_render_ui(function() {
  company_value_box(
    "Video-Page Subscriptions per 1,000 Views",
    company_number(
      company_attention_reactive()$`Video-Page Subscriptions per 1,000 Views`,
      accuracy = 0.01
    )
  )
})

output$talent_summary <- company_render_ui(function() {
  dashboard_company_talent_summary(company_analytics_reactive()) %>%
    dplyr::mutate(
      Talent = company_display_name(.data$talent_name),
      `Content Hours` = round(.data$`Content Hours`, 1)
    ) %>%
    dplyr::select(dplyr::all_of(c(
      "Talent",
      "Videos / Streams",
      "Content Hours",
      "Total Views",
      "Video-Page Subscriptions",
      "Snapshot Date"
    ))) %>%
    dashboard_datatable(page_length = 10)
})

output$content_type_performance <- company_render_ui(function() {
  dashboard_company_performance_summary(
    company_analytics_reactive(),
    group_columns = "Content Type"
  ) %>%
    dplyr::mutate(
      `Content Type` = stringr::str_to_title(.data$`Content Type`),
      dplyr::across(
        dplyr::all_of(c(
          "Average Views",
          "Median Views",
          "Watch Hours",
          "Average View Duration (sec)",
          "Views-weighted Average View %",
          "Video-Page Subscriptions per Release"
        )),
        ~ round(.x, 1)
      )
    ) %>%
    dplyr::select(dplyr::all_of(c(
      "Content Type",
      "Videos / Streams",
      "Average Views",
      "Median Views",
      "Watch Hours",
      "Average View Duration (sec)",
      "Views-weighted Average View %",
      "Video-Page Subscriptions per Release"
    ))) %>%
    dashboard_datatable(page_length = 10)
})

output$topic_performance <- company_render_ui(function() {
  company_topic_performance_reactive() %>%
    dplyr::mutate(
      dplyr::across(
        dplyr::all_of(c(
          "Average Views",
          "Median Views",
          "Watch Hours",
          "Video-Page Subscriptions per Release"
        )),
        ~ round(.x, 1)
      )
    ) %>%
    dplyr::select(dplyr::all_of(c(
      "topic",
      "Videos / Streams",
      "Average Views",
      "Median Views",
      "Watch Hours",
      "Video-Page Subscriptions per Release"
    ))) %>%
    dplyr::rename(Topic = "topic") %>%
    dashboard_datatable(page_length = 15)
})

output$portfolio_share_plot <- company_render_ui(function() {
  company_portfolio_share_plot(company_portfolio_reactive())
})

output$portfolio_table <- company_render_ui(function() {
  company_portfolio_reactive() %>%
    dplyr::mutate(
      Talent = company_display_name(.data$talent_name),
      dplyr::across(
        dplyr::all_of(c(
          "Release Share",
          "View Share",
          "Watch-time Share",
          "Video-Page Subscription Share",
          "Collaboration-Tagged Share"
        )),
        ~ scales::percent(.x, accuracy = 0.1)
      ),
      `Median Views` = round(.data$`Median Views`),
      `Watch Hours` = round(.data$`Watch Hours`, 1)
    ) %>%
    dplyr::select(dplyr::all_of(c(
      "Talent",
      "Videos / Streams",
      "Release Share",
      "View Share",
      "Watch-time Share",
      "Video-Page Subscription Share",
      "Median Views",
      "Collaboration-Tagged Share",
      "Topic Breadth"
    ))) %>%
    dashboard_datatable(page_length = 10)
})

output$content_type_mix <- company_render_ui(function() {
  company_content_type_reactive() %>%
    dplyr::mutate(
      Talent = company_display_name(.data$talent_name),
      `Content Type` = stringr::str_to_title(.data$`Content Type`),
      `Talent Release Share` = scales::percent(
        .data$`Talent Release Share`,
        accuracy = 0.1
      ),
      `Median Views` = round(.data$`Median Views`),
      `Watch Hours` = round(.data$`Watch Hours`, 1),
      `Collaboration-Tagged Share` = scales::percent(
        .data$`Collaboration-Tagged Share`,
        accuracy = 0.1
      )
    ) %>%
    dplyr::select(dplyr::all_of(c(
      "Talent",
      "Content Type",
      "Videos / Streams",
      "Talent Release Share",
      "Median Views",
      "Watch Hours",
      "Collaboration-Tagged Share",
      "Topic Breadth"
    ))) %>%
    dashboard_datatable(page_length = 15)
})

output$content_month_plot <- company_render_ui(function() {
  company_month_plot(
    company_month_reactive(),
    "Content Releases",
    "Content releases"
  )
})

output$weekday_plot <- company_render_ui(function() {
  company_talent_weekday_plot(company_weekday_reactive())
})

output$collaboration_plot <- company_render_ui(function() {
  company_month_plot(
    dashboard_company_collaboration_summary(company_analytics_reactive()),
    "Collaborations",
    "Collaborations"
  )
})

output$month_table <- company_render_ui(function() {
  company_month_reactive() %>%
    dplyr::mutate(Month = format(.data$publish_month, "%Y-%m")) %>%
    dplyr::select(dplyr::all_of(c("Month", "Content Releases"))) %>%
    dplyr::arrange(dplyr::desc(.data$Month)) %>%
    dashboard_datatable(page_length = 12)
})

output$weekday_table <- company_render_ui(function() {
  company_weekday_reactive() %>%
    dplyr::mutate(Talent = company_display_name(.data$talent_name)) %>%
    dplyr::rename(`Day of Week` = "publish_wday") %>%
    dplyr::select(dplyr::all_of(c(
      "Talent",
      "Day of Week",
      "Content Releases"
    ))) %>%
    dashboard_datatable(page_length = 25)
})

output$topic_plot <- company_render_ui(function() {
  company_topic_reactive() %>%
    dplyr::slice_max(.data$`Content Hours`, n = 12, with_ties = FALSE) %>%
    dplyr::mutate(topic = stats::reorder(.data$topic, .data$`Content Hours`)) %>%
    ggplot2::ggplot(
      ggplot2::aes(
        x = .data$topic,
        y = .data$`Content Hours`,
        text = paste0(
          .data$topic,
          "<br>Content hours: ",
          scales::comma(.data$`Content Hours`, accuracy = 0.1)
        )
      )
    ) +
    ggplot2::geom_col(fill = "#2c7fb8") +
    ggplot2::coord_flip() +
    ggplot2::labs(x = NULL, y = "Content hours") +
    ggplot2::theme_minimal(base_size = 11)
})

output$topic_table <- company_render_ui(function() {
  company_topic_reactive() %>%
    dplyr::mutate(`Content Hours` = round(.data$`Content Hours`, 1)) %>%
    dplyr::rename(Topic = "topic") %>%
    dashboard_datatable(page_length = 12)
})

output$reference_table <- company_render_ui(function() {
  dashboard_company_reference_summary(company_analytics_reactive()) %>%
    dplyr::mutate(`Content Hours` = round(.data$`Content Hours`, 1)) %>%
    dplyr::rename(
      Topic = "topic",
      `Reference / Tags` = "content_reference"
    ) %>%
    dashboard_datatable(page_length = 15)
})

output$collaboration_performance <- company_render_ui(function() {
  company_collaboration_performance_reactive() %>%
    dplyr::mutate(
      `Average Views` = round(.data$`Average Views`),
      `Median Views` = round(.data$`Median Views`),
      `Watch Hours` = round(.data$`Watch Hours`, 1),
      `Video-Page Subscriptions per Release` = round(
        .data$`Video-Page Subscriptions per Release`,
        2
      )
    ) %>%
    dplyr::select(dplyr::all_of(c(
      "Collaboration",
      "Videos / Streams",
      "Average Views",
      "Median Views",
      "Watch Hours",
      "Video-Page Subscriptions per Release"
    ))) %>%
    dashboard_datatable(page_length = 10)
})

output$representative_content <- company_render_ui(function() {
  company_representative_reactive() %>%
    dplyr::mutate(
      Talent = company_display_name(.data$Talent),
      `Watch Hours` = round(.data$`Watch Hours`, 1)
    ) %>%
    dashboard_datatable(page_length = 10)
})

output$video_explorer <- company_render_ui(function() {
  company_video_reactive() %>%
    dplyr::mutate(
      Talent = company_display_name(.data$Talent),
      `Watch Hours` = round(.data$`Watch Hours`, 1),
      `Average View Duration (sec)` = round(
        .data$`Average View Duration (sec)`,
        1
      ),
      `Average View %` = round(.data$`Average View %`, 1)
    ) %>%
    company_searchable_datatable(page_length = 25)
})

output$fun_statistics <- company_render_ui(function() {
  company_fun_stat_cards(company_fun_statistics_reactive())
})

output$method_filters <- company_render_ui(function() {
  filters <- dashboard_filters()
  selected_names <- selected_company_memberships() %>%
    dplyr::filter(.data$talent_code %in% filters$talent_codes) %>%
    dplyr::pull("talent_name") %>%
    company_display_name()
  dashboard_filter_context_card(
    tibble::tibble(
      setting = c(
        "Company",
        "Talents",
        "Data source",
        "Snapshots from",
        "Snapshots through"
      ),
      value = c(
        filters$company_name,
        paste(selected_names, collapse = ", "),
        "Unified DuckDB",
        if (is.null(filters$start_date)) {
          "All available"
        } else {
          as.character(filters$start_date)
        },
        if (is.null(filters$end_date)) {
          "All available"
        } else {
          as.character(filters$end_date)
        }
      )
    )
  )
})

output$snapshot_coverage <- company_render_ui(function() {
  company_data_reactive()$coverage %>%
    dplyr::transmute(
      Talent = company_display_name(.data$talent_name),
      `Talent Code` = .data$talent_code,
      `Snapshot Used` = .data$snapshot_date
    ) %>%
    dashboard_datatable(page_length = 10)
})

output$metric_coverage <- company_render_ui(function() {
  company_metric_coverage_reactive() %>%
    dplyr::mutate(`Coverage %` = round(.data$`Coverage %`, 1)) %>%
    dashboard_datatable(page_length = 12)
})

output$audience_availability <- company_render_ui(function() {
  htmltools::div(
    class = "alert alert-info",
    htmltools::tags$strong("Available in this iteration"),
    htmltools::tags$ul(
      htmltools::tags$li("Total views and cumulative watch hours"),
      htmltools::tags$li("Average view duration and average view percentage"),
      htmltools::tags$li("Video-page subscription events and release-level performance")
    ),
    htmltools::tags$strong("Not available in the current source"),
    htmltools::tags$ul(
      htmltools::tags$li("Unique viewers or unique reach"),
      htmltools::tags$li("Geography, age, and gender"),
      htmltools::tags$li("Average concurrent livestream viewers")
    ),
    htmltools::tags$small(
      "Total views must not be described as unique audience reach. Missing ",
      "audience fields are not estimated."
    )
  )
})

output$metric_definitions <- company_render_ui(function() {
  tibble::tribble(
    ~Metric, ~Definition,
    "Latest selected snapshot",
    "Maximum available analytics snapshot date per selected talent inside the sidebar window.",
    "Total views",
    "Sum of cumulative video views at each talent's latest selected snapshot.",
    "Average / median views",
    "Unweighted distribution of cumulative views across distinct selected releases.",
    "Total content hours",
    "Sum of catalogued video or stream durations; this is content duration, not elapsed days or watch time.",
    "Watch hours",
    "Sum of cumulative estimated minutes watched divided by 60.",
    "Average view duration",
    "Total cumulative watch seconds divided by total cumulative views.",
    "Views-weighted average view %",
    "Average video view percentage weighted by cumulative views.",
    "Views per content hour",
    "Total cumulative views divided by catalogued content hours.",
    "Video-page subscriptions",
    "Cumulative subscription events attributed by YouTube Analytics to the selected videos' watch pages; not current or net channel subscribers.",
    "Average video-page subscriptions",
    "Video-page subscription events divided by distinct selected releases.",
    "Collaboration-tagged releases",
    "Count and share of distinct releases whose latest title classification has collaborative energy.",
    "Representative content",
    "Top three releases by cumulative views for each selected talent."
  ) %>%
    dashboard_datatable(page_length = 12)
})

company_export_filename <- function(suffix) {
  company_code <- dashboard_filters()$company_code
  safe_company_code <- gsub("[^A-Za-z0-9_-]", "_", company_code)
  paste0(
    tolower(safe_company_code),
    "_",
    suffix,
    "_",
    format(Sys.Date(), "%Y-%m-%d"),
    ".csv"
  )
}

output$download_company_summary <- downloadHandler(
  filename = function() company_export_filename("company_summary"),
  content = function(file) {
    utils::write.csv(company_performance_reactive(), file, row.names = FALSE)
  }
)

output$download_talent_portfolio <- downloadHandler(
  filename = function() company_export_filename("talent_portfolio"),
  content = function(file) {
    utils::write.csv(company_portfolio_reactive(), file, row.names = FALSE)
  }
)

output$download_content_summary <- downloadHandler(
  filename = function() company_export_filename("content_summary"),
  content = function(file) {
    utils::write.csv(company_topic_performance_reactive(), file, row.names = FALSE)
  }
)

output$download_video_data <- downloadHandler(
  filename = function() company_export_filename("video_data"),
  content = function(file) {
    utils::write.csv(company_video_reactive(), file, row.names = FALSE)
  }
)
```
