---
title: "Company Performance Dashboard"
format:
  dashboard:
    orientation: rows
server: shiny
execute:
  echo: false
  warning: false
  message: false
---

<style>
@media (min-width: 769px) {
  body.dashboard-sidebar .bslib-sidebar-layout {
    --bslib-sidebar-width: 330px;
  }
}

#snapshot_dates .input-daterange {
  flex-wrap: nowrap;
}

#snapshot_dates .input-daterange .form-control {
  min-width: 0;
  font-variant-numeric: tabular-nums;
}

.card-body:has(.company-dashboard-plot) {
  overflow: hidden;
}

.company-dashboard-plot {
  display: flex;
  width: 100%;
  height: 100%;
  min-width: 0;
  min-height: 0;
  overflow: hidden;
}

.company-dashboard-plot > .html-widget {
  flex: 1 1 auto;
  min-width: 0;
  min-height: 0;
}

@media (max-width: 768px) {
  .card:not(.bslib-value-box) {
    min-height: 24rem;
  }

  .js-plotly-plot {
    min-height: 20rem;
  }

  .dataTables_wrapper {
    font-size: 0.78rem;
  }
}
</style>

```{r}
#| label: setup
#| context: setup
#| include: false

knitr::opts_knit$set(
  root.dir = normalizePath(getwd(), winslash = "/", mustWork = TRUE)
)

dashboard_machine_library <- file.path(
  path.expand("~/R"),
  paste0(R.version$platform, "-library"),
  paste(R.version$major, sub("\\..*$", "", R.version$minor), sep = ".")
)
if (dir.exists(dashboard_machine_library)) {
  .libPaths(unique(c(.libPaths(), dashboard_machine_library)))
}

library(here)
library(shiny)

source(here::here("r_scripts", "lib", "dashboard", "load.R"))

dashboard_database_path <- dashboard_resolve_database_path()
dashboard_startup_talents <- dashboard_unified_talent_catalog(
  dashboard_database_path
)
dashboard_startup_companies <- dashboard_company_memberships(
  dashboard_startup_talents
)

dashboard_global_min_date <- min(
  dashboard_startup_companies$earliest_analytics_snapshot_date,
  na.rm = TRUE
)
dashboard_global_max_date <- max(
  dashboard_startup_companies$latest_analytics_snapshot_date,
  na.rm = TRUE
)
if (!is.finite(dashboard_global_min_date)) {
  dashboard_global_min_date <- Sys.Date()
}
if (!is.finite(dashboard_global_max_date)) {
  dashboard_global_max_date <- Sys.Date()
}

company_display_name <- function(x) {
  gsub("_", " ", as.character(x), fixed = TRUE)
}

company_optional_input_date <- function(date_range, index) {
  if (is.null(date_range) || length(date_range) < index ||
      is.na(date_range[[index]])) {
    return(NULL)
  }
  as.Date(date_range[[index]])
}

company_render_ui <- function(
  value_fn,
  empty_message = "No data are available for the active filters."
) {
  shiny::renderUI({
    value <- value_fn()
    if (is.null(value)) {
      return(dashboard_empty_state(empty_message))
    }
    if (inherits(value, "ggplot")) {
      value <- dashboard_ggplotly(value)
    }
    if (inherits(value, "plotly")) {
      return(
        htmltools::div(
          class = "company-dashboard-plot",
          htmltools::as.tags(value)
        )
      )
    }
    htmltools::as.tags(value)
  })
}

company_value_box <- function(title, value) {
  if (requireNamespace("bslib", quietly = TRUE)) {
    return(bslib::value_box(title = title, value = value))
  }
  htmltools::div(
    class = "dashboard-metric-card",
    htmltools::tags$div(class = "dashboard-metric-label", title),
    htmltools::tags$div(class = "dashboard-metric-value", value)
  )
}

company_month_plot <- function(data, value_col, y_label) {
  if (is.null(data) || nrow(data) == 0) {
    return(NULL)
  }
  ggplot2::ggplot(
    data,
    ggplot2::aes(
      x = .data$publish_month,
      y = .data[[value_col]],
      text = paste0(
        format(.data$publish_month, "%Y-%m"),
        "<br>", y_label, ": ", scales::comma(.data[[value_col]])
      )
    )
  ) +
    ggplot2::geom_col(fill = "#2c7fb8") +
    ggplot2::scale_x_date(date_labels = "%Y-%m", date_breaks = "3 months") +
    ggplot2::labs(x = "Publication month", y = y_label) +
    ggplot2::theme_minimal(base_size = 11)
}

company_talent_weekday_plot <- function(data) {
  if (is.null(data) || nrow(data) == 0) {
    return(NULL)
  }
  data <- data %>%
    dplyr::mutate(talent_label = company_display_name(.data$talent_name))
  weekday_totals <- data %>%
    dplyr::group_by(.data$publish_wday) %>%
    dplyr::summarise(
      total_releases = sum(.data$`Content Releases`),
      .groups = "drop"
    )
  ggplot2::ggplot(
    data,
    ggplot2::aes(
      x = .data$publish_wday,
      y = .data$`Content Releases`,
      fill = .data$talent_label,
      text = paste0(
        .data$talent_label,
        "<br>Day: ", .data$publish_wday,
        "<br>Content releases: ", scales::comma(.data$`Content Releases`)
      )
    )
  ) +
    ggplot2::geom_col(position = "stack", width = 0.75) +
    ggplot2::geom_text(
      data = weekday_totals,
      ggplot2::aes(
        x = .data$publish_wday,
        y = .data$total_releases,
        label = scales::comma(.data$total_releases)
      ),
      inherit.aes = FALSE,
      vjust = -0.4,
      fontface = "bold",
      size = 3.5
    ) +
    ggplot2::scale_y_continuous(
      expand = ggplot2::expansion(mult = c(0, 0.12))
    ) +
    ggplot2::labs(x = NULL, y = "Content releases", fill = "Talent") +
    ggplot2::theme_minimal(base_size = 11) +
    ggplot2::theme(legend.position = "bottom")
}
```

# {.sidebar}

```{r}
uiOutput("dashboard_identity")
uiOutput("company_selector")
uiOutput("talent_selector")
uiOutput("dashboard_data_freshness")

dateRangeInput(
  inputId = "snapshot_dates",
  label = "Analytics snapshots between",
  start = dashboard_global_min_date,
  end = dashboard_global_max_date,
  min = dashboard_global_min_date,
  max = dashboard_global_max_date,
  format = "yyyy-mm-dd",
  separator = " to "
)

helpText(
  "All authorized company talents are selected by default. Remove talents to compare a subset. ",
  "The date range selects daily analytics snapshots, matching the creator dashboard; ",
  "each talent contributes its latest available snapshot inside the window."
)
```

# Overview

Company totals aggregate the latest selected snapshot for each selected talent.
Each video is counted once, so cumulative analytics are not summed across days.

## Row {height=22%}

```{r}
#| title: "Total Views"
uiOutput("total_views")
```

```{r}
#| title: "Videos / Streams"
uiOutput("video_count")
```

```{r}
#| title: "Streamed Hours"
uiOutput("streamed_hours")
```

```{r}
#| title: "Streamed Days"
uiOutput("streamed_days")
```

```{r}
#| title: "Subscribers Gained"
uiOutput("subscribers_gained")
```

## Row {height=58%}

```{r}
#| title: "Talent Breakdown"
uiOutput("talent_summary")
```

```{r}
#| title: "Content Releases by Month"
uiOutput("content_month_plot")
```

# Publishing Activity

These panels group the selected videos by publication timing. The sidebar dates
still select analytics snapshots, not video publication dates.

## Row {height=48%}

```{r}
#| title: "Release Day Frequency"
uiOutput("weekday_plot")
```

```{r}
#| title: "Collaborations by Month"
uiOutput("collaboration_plot")
```

## Row {height=44%}

```{r}
#| title: "Monthly Release Table"
uiOutput("month_table")
```

```{r}
#| title: "Weekday Release Table"
uiOutput("weekday_table")
```

# Content Mix

Topic and reference values come from the same latest title-classification rows
used by the creator dashboard.

## Row {height=46%}

```{r}
#| title: "Streamed Hours by Topic"
uiOutput("topic_plot")
```

```{r}
#| title: "Topic Summary"
uiOutput("topic_table")
```

## Row {height=48%}

```{r}
#| title: "Topic and Included Reference"
uiOutput("reference_table")
```

# Method Notes

## Row {height=45%}

```{r}
#| title: "Active Filters"
uiOutput("method_filters")
```

```{r}
#| title: "Snapshot Coverage"
uiOutput("snapshot_coverage")
```

## Row {height=35%}

```{r}
#| title: "Calculation Notes"
#| results: asis

cat(
  "- Date filters apply to analytics snapshot dates, matching the creator dashboard.\n",
  "- Each talent contributes only its latest snapshot within the selected range.\n",
  "- Total views and subscriber gains are cumulative values at those snapshots.\n",
  "- Streamed hours use the catalogued duration of each distinct video or stream.\n",
  "- Monthly and weekday panels group those distinct videos by publication date.\n",
  "- Company membership is maintained in `config/dashboard/company_talents.csv`.\n",
  sep = ""
)
```

```{r}
#| label: server
#| context: server
#| include: false

dashboard_talents <- dashboard_unified_talent_catalog(dashboard_database_path)
dashboard_companies <- dashboard_company_memberships(dashboard_talents)
dashboard_session_access <- dashboard_access_context(
  session$request,
  dashboard_talents$talent_code
)
dashboard_allowed_companies <- dashboard_companies %>%
  dplyr::filter(
    .data$talent_code %in% dashboard_session_access$allowed_talent_codes
  )

dashboard_live_talents <- reactive({
  invalidateLater(60 * 1000, session)
  tryCatch(
    dashboard_unified_talent_catalog(dashboard_database_path),
    error = function(e) dashboard_talents
  )
})

output$dashboard_identity <- renderUI({
  if (!dashboard_session_access$authorized ||
      nrow(dashboard_allowed_companies) == 0) {
    return(
      htmltools::div(
        class = "alert alert-danger",
        "No company dashboard permissions were found for this account."
      )
    )
  }

  htmltools::tags$small(
    class = "text-muted",
    paste("Signed in as", dashboard_session_access$verified_email)
  )
})

output$company_selector <- renderUI({
  if (!dashboard_session_access$authorized ||
      nrow(dashboard_allowed_companies) == 0) {
    return(NULL)
  }

  choices <- dashboard_allowed_companies %>%
    dplyr::distinct(.data$company_code, .data$company_name) %>%
    dplyr::arrange(.data$company_name)
  selectInput(
    inputId = "company",
    label = "Company",
    choices = stats::setNames(choices$company_code, choices$company_name),
    selected = choices$company_code[[1]]
  )
})

output$talent_selector <- renderUI({
  req(input$company)
  choices <- dashboard_allowed_companies %>%
    dplyr::filter(.data$company_code == input$company) %>%
    dplyr::arrange(.data$talent_name)
  if (nrow(choices) == 0) {
    return(NULL)
  }

  htmltools::tagList(
    selectizeInput(
      inputId = "talents",
      label = "Talents",
      choices = stats::setNames(
        choices$talent_code,
        company_display_name(choices$talent_name)
      ),
      selected = choices$talent_code,
      multiple = TRUE,
      options = list(plugins = list("remove_button"))
    ),
    actionLink(
      inputId = "select_all_talents",
      label = "Select all company talents"
    )
  )
})

selected_company_memberships <- reactive({
  req(input$company)
  dashboard_allowed_companies %>%
    dplyr::filter(.data$company_code == input$company)
})

observeEvent(input$select_all_talents, {
  choices <- selected_company_memberships() %>%
    dplyr::arrange(.data$talent_name)
  updateSelectizeInput(
    session,
    inputId = "talents",
    choices = stats::setNames(
      choices$talent_code,
      company_display_name(choices$talent_name)
    ),
    selected = choices$talent_code,
    server = FALSE
  )
})

selected_talent_codes <- reactive({
  req(length(input$talents) > 0)
  allowed <- selected_company_memberships()$talent_code
  selected <- intersect(as.character(input$talents), allowed)
  req(length(selected) > 0)
  selected
})

dashboard_snapshot_bounds <- reactiveVal(NULL)

observe({
  selected_codes <- selected_talent_codes()
  selected <- dashboard_live_talents() %>%
    dplyr::filter(.data$talent_code %in% selected_codes)
  req(nrow(selected) > 0)

  min_date <- min(selected$earliest_analytics_snapshot_date, na.rm = TRUE)
  max_date <- max(selected$latest_analytics_snapshot_date, na.rm = TRUE)
  req(is.finite(min_date), is.finite(max_date))

  new_bounds <- list(
    talent_codes = sort(selected_codes),
    min = min_date,
    max = max_date
  )
  old_bounds <- isolate(dashboard_snapshot_bounds())
  if (!is.null(old_bounds) && identical(old_bounds, new_bounds)) {
    return()
  }

  current_dates <- isolate(input$snapshot_dates)
  talents_changed <- is.null(old_bounds) ||
    !identical(old_bounds$talent_codes, new_bounds$talent_codes)
  if (talents_changed || is.null(current_dates) || length(current_dates) < 2) {
    selected_start <- new_bounds$min
    selected_end <- new_bounds$max
  } else {
    selected_start <- max(as.Date(current_dates[[1]]), new_bounds$min, na.rm = TRUE)
    current_end <- as.Date(current_dates[[2]])
    selected_end <- if (is.na(current_end) || identical(current_end, old_bounds$max)) {
      new_bounds$max
    } else {
      min(current_end, new_bounds$max)
    }
  }

  updateDateRangeInput(
    session,
    inputId = "snapshot_dates",
    start = selected_start,
    end = selected_end,
    min = new_bounds$min,
    max = new_bounds$max
  )
  dashboard_snapshot_bounds(new_bounds)
})

output$dashboard_data_freshness <- renderUI({
  selected_codes <- selected_talent_codes()
  selected <- dashboard_live_talents() %>%
    dplyr::filter(.data$talent_code %in% selected_codes)
  req(nrow(selected) > 0)

  latest_dates <- selected$latest_analytics_snapshot_date
  latest_dates <- latest_dates[!is.na(latest_dates)]
  if (length(latest_dates) == 0) {
    return(NULL)
  }

  htmltools::div(
    class = "alert alert-info py-2 px-3",
    htmltools::tags$strong(
      paste(
        "Latest talent snapshots:",
        format(min(latest_dates), "%Y-%m-%d"),
        "to",
        format(max(latest_dates), "%Y-%m-%d")
      )
    ),
    htmltools::tags$br(),
    htmltools::tags$small(
      paste(length(selected_codes), "talent(s) selected")
    )
  )
})

dashboard_filters <- shiny::debounce(
  reactive({
    req(dashboard_session_access$authorized)
    company <- selected_company_memberships() %>% dplyr::slice_head(n = 1)
    list(
      company_code = company$company_code[[1]],
      company_name = company$company_name[[1]],
      talent_codes = selected_talent_codes(),
      start_date = company_optional_input_date(input$snapshot_dates, 1),
      end_date = company_optional_input_date(input$snapshot_dates, 2)
    )
  }),
  millis = 400
)

company_data_reactive <- reactive({
  filters <- dashboard_filters()
  withProgress(message = "Building company dashboard", value = 0, {
    incProgress(0.2, detail = "Loading latest selected snapshots")
    data <- dashboard_load_company_analytics(
      database_path = dashboard_database_path,
      talent_codes = filters$talent_codes,
      start_date = filters$start_date,
      end_date = filters$end_date
    )
    incProgress(0.8, detail = "Preparing company summaries")
    data
  })
})

company_analytics_reactive <- reactive({
  company_data_reactive()$analytics
})

company_totals_reactive <- reactive({
  dashboard_company_totals(company_analytics_reactive())
})

company_month_reactive <- reactive({
  dashboard_company_month_summary(company_analytics_reactive())
})

company_weekday_reactive <- reactive({
  dashboard_company_weekday_summary(company_analytics_reactive())
})

company_topic_reactive <- reactive({
  dashboard_company_topic_summary(company_analytics_reactive())
})

output$total_views <- company_render_ui(function() {
  company_value_box(
    "Total Views",
    scales::comma(round(company_totals_reactive()$total_views[[1]]))
  )
})

output$video_count <- company_render_ui(function() {
  company_value_box(
    "Videos / Streams",
    scales::comma(company_totals_reactive()$video_count[[1]])
  )
})

output$streamed_hours <- company_render_ui(function() {
  company_value_box(
    "Streamed Hours",
    scales::comma(company_totals_reactive()$total_hours[[1]], accuracy = 0.1)
  )
})

output$streamed_days <- company_render_ui(function() {
  company_value_box(
    "Streamed Days",
    scales::comma(company_totals_reactive()$total_days[[1]], accuracy = 0.1)
  )
})

output$subscribers_gained <- company_render_ui(function() {
  company_value_box(
    "Subscribers Gained",
    scales::comma(round(company_totals_reactive()$subscribers_gained[[1]]))
  )
})

output$talent_summary <- company_render_ui(function() {
  dashboard_company_talent_summary(company_analytics_reactive()) %>%
    dplyr::mutate(
      Talent = company_display_name(.data$talent_name),
      `Streamed Hours` = round(.data$`Streamed Hours`, 1)
    ) %>%
    dplyr::select(dplyr::all_of(c(
      "Talent",
      "Videos / Streams",
      "Streamed Hours",
      "Total Views",
      "Subscribers Gained",
      "Snapshot Date"
    ))) %>%
    dashboard_datatable(page_length = 10)
})

output$content_month_plot <- company_render_ui(function() {
  company_month_plot(
    company_month_reactive(),
    "Content Releases",
    "Content releases"
  )
})

output$weekday_plot <- company_render_ui(function() {
  company_talent_weekday_plot(company_weekday_reactive())
})

output$collaboration_plot <- company_render_ui(function() {
  company_month_plot(
    dashboard_company_collaboration_summary(company_analytics_reactive()),
    "Collaborations",
    "Collaborations"
  )
})

output$month_table <- company_render_ui(function() {
  company_month_reactive() %>%
    dplyr::mutate(Month = format(.data$publish_month, "%Y-%m")) %>%
    dplyr::select(dplyr::all_of(c("Month", "Content Releases"))) %>%
    dplyr::arrange(dplyr::desc(.data$Month)) %>%
    dashboard_datatable(page_length = 12)
})

output$weekday_table <- company_render_ui(function() {
  company_weekday_reactive() %>%
    dplyr::mutate(Talent = company_display_name(.data$talent_name)) %>%
    dplyr::rename(`Day of Week` = "publish_wday") %>%
    dplyr::select(dplyr::all_of(c(
      "Talent",
      "Day of Week",
      "Content Releases"
    ))) %>%
    dashboard_datatable(page_length = 25)
})

output$topic_plot <- company_render_ui(function() {
  company_topic_reactive() %>%
    dplyr::slice_max(.data$`Streamed Hours`, n = 12, with_ties = FALSE) %>%
    dplyr::mutate(topic = stats::reorder(.data$topic, .data$`Streamed Hours`)) %>%
    ggplot2::ggplot(
      ggplot2::aes(
        x = .data$topic,
        y = .data$`Streamed Hours`,
        text = paste0(
          .data$topic,
          "<br>Streamed hours: ",
          scales::comma(.data$`Streamed Hours`, accuracy = 0.1)
        )
      )
    ) +
    ggplot2::geom_col(fill = "#2c7fb8") +
    ggplot2::coord_flip() +
    ggplot2::labs(x = NULL, y = "Streamed hours") +
    ggplot2::theme_minimal(base_size = 11)
})

output$topic_table <- company_render_ui(function() {
  company_topic_reactive() %>%
    dplyr::mutate(`Streamed Hours` = round(.data$`Streamed Hours`, 1)) %>%
    dplyr::rename(Topic = "topic") %>%
    dashboard_datatable(page_length = 12)
})

output$reference_table <- company_render_ui(function() {
  dashboard_company_reference_summary(company_analytics_reactive()) %>%
    dplyr::mutate(`Streamed Hours` = round(.data$`Streamed Hours`, 1)) %>%
    dplyr::rename(
      Topic = "topic",
      `Reference / Tags` = "content_reference"
    ) %>%
    dashboard_datatable(page_length = 15)
})

output$method_filters <- company_render_ui(function() {
  filters <- dashboard_filters()
  selected_names <- selected_company_memberships() %>%
    dplyr::filter(.data$talent_code %in% filters$talent_codes) %>%
    dplyr::pull("talent_name") %>%
    company_display_name()
  dashboard_filter_context_card(
    tibble::tibble(
      setting = c(
        "Company",
        "Talents",
        "Data source",
        "Snapshots from",
        "Snapshots through"
      ),
      value = c(
        filters$company_name,
        paste(selected_names, collapse = ", "),
        "Unified DuckDB",
        if (is.null(filters$start_date)) {
          "All available"
        } else {
          as.character(filters$start_date)
        },
        if (is.null(filters$end_date)) {
          "All available"
        } else {
          as.character(filters$end_date)
        }
      )
    )
  )
})

output$snapshot_coverage <- company_render_ui(function() {
  company_data_reactive()$coverage %>%
    dplyr::transmute(
      Talent = company_display_name(.data$talent_name),
      `Talent Code` = .data$talent_code,
      `Snapshot Used` = .data$snapshot_date
    ) %>%
    dashboard_datatable(page_length = 10)
})
```
