---
title: "Creator Analytics Dashboard"
format:
  dashboard:
    embed-resources: true
    orientation: rows
execute:
  echo: false
  warning: false
  message: false
params:
  talent: "Ava"
  data_source: "datalake"
  data_root: null
  start_date: null
  end_date: null
  content_types: ["live", "video", "short"]
  reference_day: "Monday"
---

```{r}
#| label: setup
#| include: false

source("../../../r_scripts/lib/dashboard/dashboard_dependencies.R")
source("../../../r_scripts/lib/dashboard/dashboard_data.R")
source("../../../r_scripts/lib/dashboard/dashboard_sections.R")

dashboard_data <- build_creator_dashboard_data(
  talent = params$talent,
  data_source = params$data_source,
  data_root = params$data_root,
  start_date = params$start_date,
  end_date = params$end_date,
  content_types = params$content_types,
  reference_day = params$reference_day
)

dashboard_talent_label <- dashboard_data$overview$value[
  dashboard_data$overview$metric == "Talent"
][[1]]
dashboard_content_types <- names(dashboard_data$topic_weekday_summary)
dashboard_primary_content_type <- if (length(dashboard_content_types) > 0) {
  dashboard_content_types[[1]]
} else {
  NA_character_
}
```

# Overview

This page summarizes the selected creator, reporting window, source data, and top-performing videos.

## Row

```{r}
#| title: "Overview Metrics"

dashboard_overview_table(dashboard_data)
```

```{r}
#| title: "Top Videos"

dashboard_top_videos_table(dashboard_data)
```

## Row

```{r}
#| title: "Performance Over Time"

dashboard_monthly_performance_plot(dashboard_data, talent = dashboard_talent_label)
```

# Creator Performance

This page shows performance by time and content format, including views, revenue-adjacent context, engagement, and high-performing uploads.

## Row

```{r}
#| title: "Monthly Views and Revenue"

dashboard_monthly_performance_plot(dashboard_data, talent = dashboard_talent_label)
```

## Row

```{r}
#| title: "Content Type Views"

dashboard_content_views_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| title: "Top Videos"

dashboard_top_videos_table(dashboard_data, page_length = 12)
```

# Content Strategy

This page compares content type performance and engagement patterns so recurring formats can be prioritized with evidence.

## Row

```{r}
#| title: "Views by Content Type"

dashboard_content_views_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| title: "Content Summary"

dashboard_datatable(dashboard_data$content_summary$total_views, page_length = 10)
```

## Row

```{r}
#| title: "Engagement by Content Type"

dashboard_content_engagement_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| title: "Engagement Summary"

dashboard_datatable(dashboard_data$content_summary$engagement, page_length = 10)
```

# Publishing Schedule

This page evaluates timing patterns, including weekday performance and topic-by-weekday recommendations.

## Row

```{r}
#| title: "Weekday Performance"

dashboard_weekday_plot(dashboard_data, talent = dashboard_talent_label, as_share = FALSE)
```

```{r}
#| title: "Weekday Summary"

dashboard_weekday_table(dashboard_data)
```

## Row

```{r}
#| title: "Topic-Weekday Heatmap"

if (!is.na(dashboard_primary_content_type)) {
  dashboard_topic_weekday_heatmap(
    dashboard_data,
    content_type = dashboard_primary_content_type,
    content_label = dow_report_content_label(dashboard_primary_content_type)
  )
}
```

```{r}
#| title: "Topic-Weekday Recommendations"

if (!is.na(dashboard_primary_content_type)) {
  dashboard_topic_weekday_recommendation_table(
    dashboard_data,
    content_type = dashboard_primary_content_type,
    page_length = 15
  )
}
```

# Audience

This page summarizes audience composition and audience-share trends where demographic exports are available.

## Row

```{r}
#| title: "Audience Age and Gender Trends"

dashboard_audience_plot(dashboard_data, talent = dashboard_talent_label)
```

```{r}
#| title: "Audience Summary"

dashboard_datatable(dashboard_data$audience_summary, page_length = 15)
```

# Recommendations

This page converts descriptive and model-informed dashboard outputs into practical planning tables.

## Row

```{r}
#| title: "Weekday Recommendations"

dashboard_datatable(dashboard_data$recommendations$weekday, page_length = 7)
```

## Row

```{r}
#| title: "Topic-Weekday Recommendations"

if (!is.na(dashboard_primary_content_type)) {
  dashboard_topic_weekday_recommendation_table(
    dashboard_data,
    content_type = dashboard_primary_content_type,
    page_length = 20
  )
}
```

```{r}
#| title: "Lifecycle Recommendations"
#| results: asis

cat(
  "Lifecycle recommendations are not wired into the dashboard yet. ",
  "Bundle E lifecycle outputs still depend on artifact CSV loading that should be extracted into a reusable dashboard loader before this card is populated."
)
```

# Method Notes

Use this dashboard as a descriptive operating view, not as a causal proof system.

## Row

```{r}
#| title: "Dashboard Scope"

dashboard_overview_table(dashboard_data)
```

```{r}
#| title: "Filters"

tibble::tibble(
  setting = c(
    "Talent parameter",
    "Data source",
    "Start date",
    "End date",
    "Content type filters",
    "Reference weekday"
  ),
  value = c(
    as.character(params$talent),
    as.character(params$data_source),
    if (is.null(params$start_date) || is.na(params$start_date)) "All available" else as.character(params$start_date),
    if (is.null(params$end_date) || is.na(params$end_date)) "All available" else as.character(params$end_date),
    paste(params$content_types, collapse = ", "),
    as.character(params$reference_day)
  )
) |>
  dashboard_datatable(page_length = 6)
```

## Row

```{r}
#| title: "Interpretation Notes"
#| results: asis

cat(
  "- Reporting period follows the selected `start_date` and `end_date`; when both are empty, all available rows are used.\n",
  "- Content type filters limit topic-weekday modeling to the requested formats that exist in the prepared data.\n",
  "- Descriptive statistics summarize observed performance and can be affected by outliers, posting volume, and missing exports.\n",
  "- Model-based recommendations estimate expected logged views by weekday/topic patterns; they are planning signals, not guarantees.\n",
  "- Correlation is not causation: timing, topic, collaboration, title, format, and external context can move together.\n",
  "- Lifecycle recommendations are pending a reusable Bundle E artifact loader extraction.\n",
  sep = ""
)
```
