---
title: "`r { t <- params$talent; if (!(length(t) == 1 && !is.na(t) && nzchar(trimws(as.character(t))))) t <- 'Talent'; t <- trimws(as.character(t)); t_clean <- trimws(gsub('\\s*[\\[【].*$', '', t)); paste0('Video Lifecycle and Library Growth Report: ', t_clean) }`"
subtitle: "`r { r <- params$included_date_range; if (!(length(r) == 1 && !is.na(r) && nzchar(trimws(as.character(r))))) r <- 'All available dates'; paste0('Data Range: ', as.character(r)) }`"
author: "Author: Zhuni Excel & Jonathon Sun"
date: "`r { x <- params$render_generated_at; if (length(x) == 1 && !is.na(x) && nzchar(trimws(as.character(x)))) { x <- trimws(as.character(x)); x_date <- sub('^([0-9]{4}-[0-9]{2}-[0-9]{2}).*$', '\\\\1', x); if (grepl('^[0-9]{4}-[0-9]{2}-[0-9]{2}$', x_date)) paste0('Report Date: ', x_date) else paste0('Report Date: ', format(Sys.Date(), '%Y-%m-%d')) } else paste0('Report Date: ', format(Sys.Date(), '%Y-%m-%d')) }`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float: true
    toc_depth: 3
params:
  talent: "Leia Memoria【Variance Project】"
  data_source: "datalake"
  data_root: null
  artifact_root: null
  render_generated_at: null
  included_date_range: null
  render_cli: null
  render_output_dir: null
  render_output_prefix: null
  window_days: null
  start_date: null
  end_date: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)

plot_w_std <- 10
plot_h_std <- 6
plot_w_facet <- 11
plot_h_facet <- 8

knitr::opts_knit$set(root.dir = here::here())

if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(
    fig.width = 14,
    fig.height = 8,
    out.width = "0.8\\linewidth"
  )
} else {
  knitr::opts_chunk$set(
    fig.width = plot_w_std,
    fig.height = plot_h_std,
    out.width = "100%"
  )
}
```

```{r libraries, include=FALSE}
library(tidyverse)
library(purrr)
library(here)
library(ggplot2)
library(DT)
library(plotly)
```

```{r report_layout_style, echo=FALSE, results='asis'}
cat(
  "<style>
  .main-container {
    max-width: 1200px !important;
  }
  .section.level1,
  .section.level2,
  .section.level3 {
    max-width: 100%;
    overflow-x: hidden;
  }
  .html-widget,
  .plotly.html-widget,
  .js-plotly-plot,
  .plot-container,
  .svg-container {
    max-width: 100% !important;
  }
  .plotly.html-widget {
    width: 100% !important;
  }
  .dataTables_wrapper {
    width: 100%;
    max-width: 100%;
  }
  .dataTables_wrapper .dataTables_scroll {
    overflow-x: auto;
  }
  table.dataTable {
    width: 100% !important;
  }
  .dataTables_wrapper table.dataTable thead th,
  .dataTables_wrapper table.dataTable thead td {
    white-space: normal !important;
    line-height: 1.2;
    vertical-align: bottom;
  }
  </style>"
)
```

```{r plotly_helpers, include=FALSE}
bundle_e_ggplotly <- function(plot_obj, tooltip = NULL, rotate_y_axis_title = TRUE, height = NULL) {
  p <- if (is.null(tooltip)) {
    plotly::ggplotly(plot_obj)
  } else {
    plotly::ggplotly(plot_obj, tooltip = tooltip)
  }

  if (!inherits(plot_obj, "ggplot")) {
    return(p)
  }

  title_txt <- plot_obj$labels$title
  subtitle_txt <- plot_obj$labels$subtitle

  wrap_for_plotly <- function(x, width = 80) {
    txt <- trimws(as.character(x))
    if (!nzchar(txt)) {
      return("")
    }
    txt <- gsub("\\s+", " ", txt)
    paste(strwrap(txt, width = width), collapse = "\n")
  }

  title_txt <- if (is.null(title_txt) || !nzchar(trimws(as.character(title_txt)))) {
    ""
  } else {
    as.character(title_txt[[1]])
  }
  subtitle_txt <- if (is.null(subtitle_txt) || !nzchar(trimws(as.character(subtitle_txt)))) {
    ""
  } else {
    as.character(subtitle_txt[[1]])
  }

  title_plain <- wrap_for_plotly(title_txt, width = 54)
  subtitle_plain <- wrap_for_plotly(subtitle_txt, width = 88)

  title_txt <- gsub("\n", "<br>", htmltools::htmlEscape(title_plain), fixed = TRUE)
  subtitle_txt <- gsub("\n", "<br>", htmltools::htmlEscape(subtitle_plain), fixed = TRUE)

  title_lines <- max(1L, length(strsplit(title_plain, "\n", fixed = TRUE)[[1]]))
  subtitle_lines <- if (nzchar(subtitle_plain)) {
    length(strsplit(subtitle_plain, "\n", fixed = TRUE)[[1]])
  } else {
    0L
  }

  current_top <- p$x$layout$margin$t
  if (is.null(current_top) || !is.finite(current_top)) {
    current_top <- 60
  }
  needed_top <- 68 + (title_lines * 24) + (subtitle_lines * 20) + 14
  top_margin <- max(as.numeric(current_top), as.numeric(needed_top))
  attr_height <- attr(plot_obj, "bundle_e_plotly_height", exact = TRUE)
  if (is.null(height) && !is.null(attr_height) && is.finite(attr_height)) {
    height <- as.numeric(attr_height)
  }

  combined_title <- if (nzchar(subtitle_txt)) {
    paste0(
      "<b>", title_txt, "</b>",
      "<br><span style='font-size:0.78em;'>", subtitle_txt, "</span>"
    )
  } else {
    paste0("<b>", title_txt, "</b>")
  }

  if (isTRUE(rotate_y_axis_title) && length(p$x$layout$annotations) > 0) {
    anns <- p$x$layout$annotations
    for (i in seq_along(anns)) {
      ann <- anns[[i]]
      ann_x <- if (is.null(ann$x)) NA_real_ else suppressWarnings(as.numeric(ann$x))
      ann_y <- if (is.null(ann$y)) NA_real_ else suppressWarnings(as.numeric(ann$y))
      is_axis_annot <- identical(ann$annotationType, "axis")
      is_y_axis_title <- isTRUE(is_axis_annot) &&
        is.finite(ann_x) && is.finite(ann_y) &&
        abs(ann_x - 0) < 1e-9 &&
        abs(ann_y - 0.5) < 1e-9

      if (is_y_axis_title) {
        anns[[i]]$textangle <- -90
        anns[[i]]$xanchor <- "center"
        anns[[i]]$yanchor <- "middle"
        anns[[i]]$xshift <- -58
      }
    }
    p$x$layout$annotations <- anns
  }

  current_bottom <- p$x$layout$margin$b
  if (is.null(current_bottom) || !is.finite(current_bottom)) {
    current_bottom <- 60
  }
  attr_margin_l <- attr(plot_obj, "bundle_e_plotly_margin_l", exact = TRUE)
  attr_margin_b <- attr(plot_obj, "bundle_e_plotly_margin_b", exact = TRUE)
  margin_cfg <- list(
    t = top_margin,
    b = max(
      as.numeric(current_bottom),
      96,
      if (is.null(attr_margin_b) || !is.finite(attr_margin_b)) 0 else as.numeric(attr_margin_b)
    )
  )
  if (isTRUE(rotate_y_axis_title)) {
    current_left <- p$x$layout$margin$l
    if (is.null(current_left) || !is.finite(current_left)) {
      current_left <- 80
    }
    margin_cfg$l <- max(
      as.numeric(current_left),
      132,
      if (is.null(attr_margin_l) || !is.finite(attr_margin_l)) 0 else as.numeric(attr_margin_l)
    )
  }

  layout_args <- list(
    title = list(
      text = combined_title,
      x = 0,
      xanchor = "left",
      y = 0.98,
      yanchor = "top",
      pad = list(t = 10, b = 12)
    ),
    margin = margin_cfg,
    autosize = TRUE
  )
  if (!is.null(height) && is.finite(height)) {
    layout_args$height <- as.numeric(height)
  }

  p %>%
    do.call(plotly::layout, c(list(.), layout_args)) %>%
    plotly::config(responsive = TRUE)
}
```

```{r modules, include=FALSE}
source("r_scripts/lib/utils/staging_root.R")
source("r_scripts/lib/utils/datalake_root.r")

bundle_e_plot_dir <- here("r_scripts", "lib", "plots", "report", "bundle_e")
if (dir.exists(bundle_e_plot_dir)) {
  list.files(bundle_e_plot_dir, full.names = TRUE) %>%
    walk(source)
}

list.files(here("r_scripts", "lib", "plots", "report", "bundle_A"), full.names = TRUE) %>%
  walk(source)
list.files(here("r_scripts", "lib", "utils"), full.names = TRUE) %>%
  walk(source)
source(here("r_scripts", "lib", "plots", "PlottingThemes.R"))
```

```{r load_data, include=FALSE}
data_source <- tolower(trimws(as.character(params$data_source)))
if (!nzchar(data_source)) {
  data_source <- "datalake"
}
if (!(data_source %in% c("staging", "datalake"))) {
  stop("`params$data_source` must be one of: 'staging', 'datalake'.")
}

Talent <- as.character(params$talent)
if (length(Talent) != 1 || is.na(Talent) || !nzchar(trimws(Talent))) {
  stop("`params$talent` must be a single non-empty talent name.")
}
Talent <- trimws(Talent)

artifact_root_param <- if (is.null(params$artifact_root) || (length(params$artifact_root) == 1 && is.na(params$artifact_root))) {
  ""
} else {
  trimws(as.character(params$artifact_root[[1]]))
}

artifact_root <- if (nzchar(artifact_root_param)) {
  normalizePath(artifact_root_param, winslash = "/", mustWork = FALSE)
} else {
  artifact_talent_root <- select_talent(Talent, root = get_datalake_root())
  normalizePath(
    file.path(get_datalake_root(), basename(artifact_talent_root), "reports", "bundle_e", "artifacts"),
    winslash = "/",
    mustWork = FALSE
  )
}

tables_dir <- file.path(artifact_root, "tables")
if (!dir.exists(tables_dir)) {
  stop(
    "Bundle E artifact tables not found: ", tables_dir, ". ",
    "Run `r_scripts/run/bundle_e/import_data.R` first."
  )
}

bundle_e_read_table <- function(name) {
  path <- file.path(tables_dir, paste0(name, ".csv"))
  if (!file.exists(path)) {
    return(tibble::tibble())
  }
  readr::read_csv(path, show_col_types = FALSE, progress = FALSE)
}

dataset_sizes <- bundle_e_read_table("dataset_sizes")
metadata_tbl <- bundle_e_read_table("metadata")
panel_coverage_summary <- bundle_e_read_table("panel_coverage_summary")
library_growth_snapshot <- bundle_e_read_table("library_growth_snapshot")
back_catalog_vs_recent_contribution <- bundle_e_read_table("back_catalog_vs_recent_contribution")
video_lifecycle_summary <- bundle_e_read_table("video_lifecycle_summary")
publish_cohort_performance <- bundle_e_read_table("publish_cohort_performance")
publish_cohort_performance_by_type <- bundle_e_read_table("publish_cohort_performance_by_type")
video_type_longevity <- bundle_e_read_table("video_type_longevity")
short_window_diagnostics <- bundle_e_read_table("short_window_diagnostics")
short_window_selection <- bundle_e_read_table("short_window_selection")
short_window_video_scores <- bundle_e_read_table("short_window_video_scores")
video_type_highest_overall_performing <- bundle_e_read_table("video_type_highest_overall_performing")
video_type_newest_five_videos <- bundle_e_read_table("video_type_newest_five_videos")
video_type_top_performing_videos <- bundle_e_read_table("video_type_top_performing_videos")
live_top_vs_newest_age_curve_comparison <- bundle_e_read_table("live_top_vs_newest_age_curve_comparison")
video_highest_vs_newest_age_curve_comparison <- bundle_e_read_table("video_highest_vs_newest_age_curve_comparison")
short_highest_vs_newest_age_curve_comparison <- bundle_e_read_table("short_highest_vs_newest_age_curve_comparison")
evergreen_video_leaders <- bundle_e_read_table("evergreen_video_leaders")
sleeper_reacceleration_candidates <- bundle_e_read_table("sleeper_reacceleration_candidates")
topic_longevity <- bundle_e_read_table("topic_longevity")
tag_longevity <- bundle_e_read_table("tag_longevity")

bundle_e_interp_root <- {
  out_dir <- params$render_output_dir
  if (is.null(out_dir) || length(out_dir) == 0 || is.na(out_dir[[1]]) || !nzchar(trimws(as.character(out_dir[[1]])))) {
    NULL
  } else {
    file.path(trimws(as.character(out_dir[[1]])), "interpretations")
  }
}

bundle_e_read_interpretation <- function(rel_dir) {
  if (is.null(bundle_e_interp_root) || !nzchar(bundle_e_interp_root)) {
    return("")
  }
  interp_path <- file.path(bundle_e_interp_root, rel_dir, "output.md")
  if (!file.exists(interp_path)) {
    return("")
  }
  txt <- paste(readLines(interp_path, warn = FALSE, encoding = "UTF-8"), collapse = "\n")
  txt <- trimws(txt)
  if (!nzchar(txt)) {
    return("")
  }
  txt
}

bundle_e_emit_interpretation <- function(rel_dir) {
  txt <- bundle_e_read_interpretation(rel_dir)
  if (!nzchar(txt)) {
    return(invisible(NULL))
  }
  cat(txt, "\n\n")
}
```

```{r bundle-e-prep, include=FALSE}
bundle_e_title_case <- function(x) {
  out <- trimws(as.character(x))
  out[!nzchar(out)] <- NA_character_
  stringr::str_to_title(out)
}

bundle_e_metric_value <- function(key) {
  hit <- metadata_tbl %>%
    dplyr::filter(.data$key == key) %>%
    dplyr::pull(.data$value)
  if (length(hit) == 0) {
    return(NA_character_)
  }
  hit[[1]]
}

bundle_e_first_non_missing <- function(x) {
  x <- x[!is.na(x)]
  if (length(x) == 0) {
    return(NA)
  }
  x[[1]]
}

bundle_e_type_slice <- function(df, type_name, column = "Content Type") {
  if (nrow(df) == 0 || !(column %in% names(df))) {
    return(df[0, , drop = FALSE])
  }
  df %>%
    dplyr::filter(tolower(trimws(as.character(.data[[column]]))) == tolower(type_name))
}

bundle_e_render_note <- function(text) {
  cat(paste0("**Note:** ", text, "\n\n"))
}

bundle_e_type_table <- function(df, empty_text = "No data available for this video type yet.") {
  if (nrow(df) == 0) {
    bundle_e_render_note(empty_text)
    return(invisible(NULL))
  }

  display_df <- df %>%
    dplyr::select(
      -dplyr::any_of(c(
        "evergreen_flag",
        "front_loaded_flag",
        "sleeper_flag",
        "reacceleration_flag"
      ))
    )

  DTSettings(display_df, class = "display stripe hover", scroll_x = TRUE)
}

bundle_e_age_curve_comparison_table <- function(curve_df) {
  if (nrow(curve_df) == 0) {
    return(curve_df)
  }

  curve_df %>%
    dplyr::group_by(.data$`Video ID`) %>%
    dplyr::slice_max(order_by = .data$video_age_days, n = 1, with_ties = FALSE) %>%
    dplyr::ungroup() %>%
    dplyr::transmute(
      `Comparison Group` = .data$comparison_role,
      Title = .data$Title,
      `Publish Date` = .data$publish_date,
      `Latest Age Days` = .data$video_age_days,
      `Latest Views` = .data$views_cumulative
    ) %>%
    dplyr::arrange(.data$`Comparison Group`, dplyr::desc(.data$`Latest Views`), .data$Title)
}

bundle_e_attribute_summary_table <- function(df, group_col, group_label, top_n = 12) {
  if (nrow(df) == 0 || !(group_col %in% names(df))) {
    return(df[0, , drop = FALSE])
  }

  df %>%
    dplyr::slice_head(n = top_n) %>%
    dplyr::transmute(
      !!group_label := .data[[group_col]],
      `Video Count` = .data$video_count,
      `Median Latest Views` = .data$median_latest_views,
      `Median Lifetime Avg Views/Day` = .data$median_lifetime_avg_views_per_day,
      `Median Recent 30-Day Avg Views/Day` = .data$median_recent_30d_avg_views_per_day
    )
}

bundle_e_topic_video_type_table <- function(video_summary, top_n = 12, min_videos = 2) {
  if (nrow(video_summary) == 0 || !"topic" %in% names(video_summary)) {
    return(tibble::tibble())
  }

  out <- video_summary %>%
    dplyr::mutate(
      Topic = trimws(as.character(.data$topic)),
      `Content Type` = dplyr::case_when(
        .data$`Content Type` == "live" ~ "Stream",
        .data$`Content Type` == "short" ~ "Short",
        .data$`Content Type` == "video" ~ "Video",
        TRUE ~ bundle_e_title_case(.data$`Content Type`)
      )
    ) %>%
    dplyr::filter(
      !is.na(.data$Topic),
      nzchar(.data$Topic),
      !is.na(.data$recent_30d_avg_views_per_day),
      is.finite(.data$recent_30d_avg_views_per_day)
    ) %>%
    dplyr::group_by(.data$Topic, .data$`Content Type`) %>%
    dplyr::summarise(
      `Video Count` = dplyr::n_distinct(.data$`Video ID`),
      `Median Recent 30-Day Avg Views/Day` = stats::median(.data$recent_30d_avg_views_per_day, na.rm = TRUE),
      `Median Latest Views` = stats::median(.data$latest_views, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    dplyr::filter(.data$`Video Count` >= min_videos) %>%
    dplyr::arrange(dplyr::desc(.data$`Median Recent 30-Day Avg Views/Day`), dplyr::desc(.data$`Video Count`))

  out %>%
    dplyr::slice_head(n = top_n)
}

bundle_e_abbrev_leader_table <- function(df, classification) {
  if (nrow(df) == 0) {
    return(df)
  }

  if (identical(classification, "evergreen")) {
    out <- df %>%
      dplyr::transmute(
        Title = .data$Title,
        `Publish Date` = .data$publish_date,
        `Content Type` = bundle_e_title_case(.data$`Content Type`),
        Classification = "Evergreen"
      )
    return(out)
  }

  df %>%
    dplyr::transmute(
      Title = .data$Title,
      `Publish Date` = .data$publish_date,
      `Content Type` = bundle_e_title_case(.data$`Content Type`),
      Classification = dplyr::case_when(
        .data$sleeper_flag & .data$reacceleration_flag ~ "Sleeper + Re-accelerating",
        .data$reacceleration_flag ~ "Re-accelerating",
        .data$sleeper_flag ~ "Sleeper",
        TRUE ~ "Other"
      )
    )
}

bundle_e_combined_leader_table <- function(evergreen_df, sleeper_df) {
  evergreen_tbl <- bundle_e_abbrev_leader_table(evergreen_df, "evergreen")
  sleeper_tbl <- bundle_e_abbrev_leader_table(sleeper_df, "sleeper")

  combined <- dplyr::bind_rows(evergreen_tbl, sleeper_tbl) %>%
    dplyr::arrange(.data$Classification, dplyr::desc(.data$`Publish Date`), .data$Title)

  combined
}

bundle_e_classification_guide <- tibble::tibble(
  Classification = c(
    "Evergreen",
    "Front-loaded",
    "Re-accelerating",
    "Sleeper",
    "Sleeper + Re-accelerating"
  ),
  `Plain-language meaning` = c(
    "The video is still pulling a meaningful amount of views well after release.",
    "The video got most of its traction early and has cooled off a lot since launch.",
    "The video is gaining momentum again after an earlier slower period.",
    "The video did not stand out early, but is now showing stronger recent performance.",
    "The video started quietly and is now picking up again in a noticeable way."
  ),
  `What it usually suggests` = c(
    "This content has longer-tail value and may keep contributing to the library over time.",
    "This content depended more on launch energy than on long-run durability.",
    "Something may have renewed interest, such as search, recommendations, clips, or a new audience fit.",
    "The video may have hidden long-tail potential that was not obvious at launch.",
    "This is a stronger late-bloomer signal and is often worth a closer look for repeatable patterns."
  )
)

latest_library_row <- library_growth_snapshot %>%
  dplyr::arrange(dplyr::desc(.data$snapshot_date)) %>%
  dplyr::slice_head(n = 1)

overall_summary <- tibble::tibble(
  Metric = c(
    "Included date range",
    "Latest snapshot date",
    "Observed snapshots",
    "Unique videos in lifecycle summary",
    "Latest observed library views",
    "Panel rows in window"
  ),
  Value = c(
    if (is.null(params$included_date_range) || is.na(params$included_date_range)) "All available dates" else as.character(params$included_date_range),
    if (nrow(latest_library_row) == 0) NA_character_ else as.character(latest_library_row$snapshot_date[[1]]),
    nrow(library_growth_snapshot),
    if (nrow(video_lifecycle_summary) == 0) 0 else dplyr::n_distinct(video_lifecycle_summary$`Video ID`),
    if (nrow(latest_library_row) == 0) NA_character_ else scales::comma(bundle_e_first_non_missing(latest_library_row$total_library_views)),
    if (nrow(dataset_sizes) == 0) NA_character_ else as.character(bundle_e_first_non_missing(dataset_sizes$rows[dataset_sizes$dataset == "panel_window"]))
  )
)

video_type_longevity_display <- video_type_longevity %>%
  dplyr::mutate(group_value = bundle_e_title_case(.data$group_value))
```

# How This Report Supports Video Lifecycle Decisions

This report is the longitudinal view of the library. It focuses on how videos compound over time, whether the library is increasingly driven by fresh uploads or the back catalog, and how growth patterns differ across `live`, `video`, and `short` uploads.

```{r bundle-e-intro-synthesis, results='asis'}
bundle_e_emit_interpretation("00_how_this_report_supports_video_lifecycle_decisions/00_section_synthesis")
```

# Executive Summary

```{r bundle-e-executive-summary, results='asis'}
bundle_e_emit_interpretation("05_report_bookends/01_executive_summary")
```

# Overall Library Snapshot

This section establishes the overall state of the library before breaking performance out by video type.

```{r bundle-e-overall-synthesis, results='asis'}
bundle_e_emit_interpretation("01_overall_library_snapshot/00_section_synthesis")
```

## Overall Summary Table

```{r bundle-e-overall-summary-table}
DTSettings(overall_summary, class = "display stripe hover", scroll_x = TRUE, filter = "none")
```

## Back Catalog vs Recent Contribution

**What this chart shows:** At each snapshot date, this compares how much of total library views came from recent videos (`0-30 days old`) versus older videos in the back catalog (`31+ days old`).  
**Why it matters:** This helps show whether overall performance is being driven mostly by new releases or by older videos continuing to pull views over time.  
**How to read it:** If the back-catalog panel is higher, older videos are driving more of total library views. If the recent panel is higher, newer uploads are contributing more of the total.

```{r bundle-e-back-catalog-share}
bundle_e_ggplotly(
  plot_bundle_e_back_catalog_share(back_catalog_vs_recent_contribution, Talent),
  tooltip = "text"
)
```

```{r bundle-e-back-catalog-text, results='asis'}
bundle_e_emit_interpretation("01_overall_library_snapshot/02_back_catalog_vs_recent_contribution")
```

## Publish Cohort Performance

**What this chart shows:** Publish cohorts group videos by the month they were released. This chart compares the overall recent viewing pace of those monthly upload waves.  
**Why it matters:** It helps show whether stronger current performance is concentrated in newer or older upload waves at the overall library level.  
**How to read it:** Higher bars mean that cohort is driving a stronger recent viewing pace overall. Use this as the combined picture first, then compare it with the video-type breakout below.

```{r bundle-e-publish-cohort}
bundle_e_ggplotly(
  plot_bundle_e_publish_cohort(publish_cohort_performance, Talent),
  tooltip = "text"
)
```

## Publish Cohort Performance by Video Type

**What this chart shows:** The same publish-cohort view, broken out separately for Shorts, Videos, and Streams.  
**Why it matters:** This helps show whether the overall cohort pattern is being driven by one format more than the others.  
**How to read it:** Compare cohorts within each video type first, then compare across panels to see whether Shorts, Videos, or Streams are shaping the overall result.

```{r bundle-e-publish-cohort-by-type}
bundle_e_ggplotly(
  plot_bundle_e_publish_cohort_by_type(publish_cohort_performance_by_type, Talent),
  tooltip = "text"
)
```

```{r bundle-e-publish-cohort-text, results='asis'}
bundle_e_emit_interpretation("01_overall_library_snapshot/03_publish_cohort_performance")
```

# Video Lifecycle Behavior

This section looks at video-level patterns rather than library totals, with attention to durability, momentum, and sleeper behavior.

```{r bundle-e-lifecycle-synthesis, results='asis'}
bundle_e_emit_interpretation("02_video_lifecycle_behavior/00_section_synthesis")
```

## Latest Views vs Video Age

**What this chart shows:** Current observed views plotted against video age, split by video type so each format can be read on its own scale. A simple trend line is included in each panel to show the average direction.  
**How to read it:** Use the points to see individual videos and the trend line to see the typical pattern within each format. This helps separate “older because it had more time” from “older and still exceptional” without forcing all formats onto one shared scale.

```{r bundle-e-latest-views-vs-age}
bundle_e_ggplotly(
  plot_bundle_e_latest_views_vs_age(video_lifecycle_summary, Talent),
  tooltip = "text"
)
```

```{r bundle-e-latest-views-vs-age-text, results='asis'}
bundle_e_emit_interpretation("02_video_lifecycle_behavior/01_latest_views_vs_video_age")
```

## Recent Momentum vs Lifetime Rate

**What this chart shows:** Recent 30-day pace compared with each video's lifetime average pace.  
**How to read it:** Each facet shows one lifecycle profile. Videos above their long-run pace are still showing momentum; videos below it are likely cooling.

**Classification guide:** Use the quick reference below before reading the chart and table.

```{r bundle-e-classification-guide}
DTSettings(
  bundle_e_classification_guide,
  class = "display stripe hover",
  scroll_x = TRUE,
  filter = "none",
  options = list(dom = "t", paging = FALSE)
)
```

```{r bundle-e-recent-vs-lifetime}
bundle_e_ggplotly(
  plot_bundle_e_recent_vs_lifetime_rate(video_lifecycle_summary, Talent),
  tooltip = "text"
)
```

```{r bundle-e-recent-vs-lifetime-text, results='asis'}
bundle_e_emit_interpretation("02_video_lifecycle_behavior/02_recent_momentum_vs_lifetime_rate")
```

```{r bundle-e-classification-leaders}
bundle_e_type_table(
  bundle_e_combined_leader_table(
    evergreen_video_leaders,
    sleeper_reacceleration_candidates
  ),
  empty_text = "No lifecycle classification leaders were exported for the current filters."
)
```

# Video Type Deep Dive

This section is where Bundle E becomes intentionally different from Bundles A and B. It separates `live`, `video`, and `short` uploads because each type can have very different longevity, launch shape, and library contribution patterns.

```{r bundle-e-video-type-synthesis, results='asis'}
bundle_e_emit_interpretation("03_video_type_deep_dive/00_section_synthesis")
```

## Topic Longevity by Video Type

**What this chart shows:** Median recent 30-day pace by topic, split by Shorts, Videos, and Streams.  
**How to read it:** Use this to see which topics still have current momentum, and whether that momentum is coming more from Shorts, Videos, or Streams.

```{r bundle-e-video-type-longevity}
bundle_e_ggplotly(
  plot_bundle_e_topic_video_type_longevity(video_lifecycle_summary, Talent),
  tooltip = "text"
)
```

```{r bundle-e-video-type-longevity-table}
bundle_e_type_table(
  bundle_e_topic_video_type_table(video_lifecycle_summary),
  empty_text = "No topic by video-type longevity table was exported for the current filters."
)
```

## Live Uploads

```{r bundle-e-live-text, results='asis'}
bundle_e_emit_interpretation("03_video_type_deep_dive/01_live_uploads")
```

### Age-Normalized Live Comparison

**What this chart shows:** Top-performing live uploads, defined as the top 10% within the format with at least five where available, plotted against the newest live uploads on the same age-normalized timeline.  
**How to read it:** Use the top-performing benchmark group to see the pace stronger live uploads tend to follow, then compare whether the newest uploads are tracking above, near, or below that pace at the same stage of life.

```{r bundle-e-live-age-curve}
bundle_e_ggplotly(
  plot_bundle_e_type_age_curve_comparison(
    live_top_vs_newest_age_curve_comparison,
    Talent,
    content_type_label = "Live uploads"
  ),
  tooltip = "text"
)
```

### Live Uploads Included in Comparison

```{r bundle-e-live-top}
bundle_e_type_table(
  bundle_e_age_curve_comparison_table(live_top_vs_newest_age_curve_comparison),
  empty_text = "No live uploads were exported for the current comparison."
)
```

## Video Uploads

```{r bundle-e-video-text, results='asis'}
bundle_e_emit_interpretation("03_video_type_deep_dive/02_video_uploads")
```

### Age-Normalized Video Comparison

**What this chart shows:** Top-performing video uploads, defined as the top 10% within the format with at least five where available, plotted against the newest video uploads on the same age-normalized timeline.  
**How to read it:** Use the top-performing benchmark group to see the pace stronger videos tend to follow, then compare whether the newest uploads are tracking above, near, or below that pace at the same stage of life.

```{r bundle-e-video-age-curve}
bundle_e_ggplotly(
  plot_bundle_e_type_age_curve_comparison(
    video_highest_vs_newest_age_curve_comparison,
    Talent,
    content_type_label = "Video uploads"
  ),
  tooltip = "text"
)
```

### Video Uploads Included in Comparison

```{r bundle-e-video-top}
bundle_e_type_table(
  bundle_e_age_curve_comparison_table(video_highest_vs_newest_age_curve_comparison),
  empty_text = "No video uploads were exported for the current comparison."
)
```

## Shorts

```{r bundle-e-short-text, results='asis'}
bundle_e_emit_interpretation("03_video_type_deep_dive/03_shorts")
```

### Age-Normalized Short Comparison

**What this chart shows:** Top-performing Shorts, defined as the top 10% within the format with at least five where available, plotted against the newest Shorts on the same age-normalized timeline.  
**How to read it:** Use the top-performing benchmark group to see the pace stronger Shorts tend to follow, then compare whether the newest shorts are tracking above, near, or below that pace at the same stage of life.

```{r bundle-e-short-age-curve}
bundle_e_ggplotly(
  plot_bundle_e_type_age_curve_comparison(
    short_highest_vs_newest_age_curve_comparison,
    Talent,
    content_type_label = "Short uploads"
  ),
  tooltip = "text"
)
```

### Shorts Included in Comparison

```{r bundle-e-short-top}
bundle_e_type_table(
  bundle_e_age_curve_comparison_table(short_highest_vs_newest_age_curve_comparison),
  empty_text = "No shorts were exported for the current comparison."
)
```

### Short Stability Window

**What this chart shows:** Candidate early-read windows for Shorts, evaluated by how much view share is typically still left after that day.  
**How to read it:** Lower is better. The first day where both lines have settled enough is the most practical talent-specific Shorts window.

```{r bundle-e-short-window-plot}
bundle_e_ggplotly(
  plot_bundle_e_short_window_diagnostics(short_window_diagnostics, Talent),
  tooltip = c("x", "y", "colour")
)
```

### Top Shorts Within Selected Window

**What this chart shows:** The highest-performing Shorts measured at the selected early-read window rather than at full lifetime.  
**How to read it:** This is the apples-to-apples launch leaderboard for Shorts at the talent-specific window selected above.

```{r bundle-e-short-window-leaders}
bundle_e_ggplotly(
  plot_bundle_e_short_window_leaders(short_window_video_scores, Talent),
  tooltip = "text"
)
```

```{r bundle-e-short-window-leaders-table}
bundle_e_type_table(
  short_window_video_scores %>%
    dplyr::select(
      Title,
      window_days,
      views_at_window,
      views_at_window_percentile,
      early_performance_bucket,
      standout_within_window
    ),
  empty_text = "No short-window leader table was exported for the current filters."
)
```

# Topic and Tag Longevity

This section keeps the classifier-enriched view in Bundle E, but frames it through a longitudinal lens rather than a one-period performance lens.

```{r bundle-e-attribute-synthesis, results='asis'}
bundle_e_emit_interpretation("04_topic_and_tag_longevity/00_section_synthesis")
```

## Topic Longevity

**What this chart shows:** Each panel is a topic. Each point is one video, comparing its long-run average pace with its recent 30-day pace.  
**How to read it:** Higher points have stronger recent momentum; points farther right have stronger long-run pace. Shape and color show whether the point is a Short, Video, or Stream. Hover over a point to see its observed date window and view gain.

```{r bundle-e-topic-momentum-by-type, fig.width=12, fig.height=10}
bundle_e_ggplotly(
  plot_bundle_e_attribute_momentum_by_type(
    video_lifecycle_summary,
    Talent,
    attribute = "topic",
    top_n = 6,
    min_videos = 3
  ),
  tooltip = "text"
)
```

```{r bundle-e-topic-longevity}
bundle_e_type_table(
  bundle_e_attribute_summary_table(topic_longevity, "group_value", "Topic"),
  empty_text = "No topic longevity table was exported for the current filters."
)
```

## Tag Longevity

**What this chart shows:** Each panel is a tag. Each point is one video, comparing its long-run average pace with its recent 30-day pace.  
**How to read it:** Higher points have stronger recent momentum; points farther right have stronger long-run pace. Shape and color show whether the tag is being carried by Shorts, Videos, or Streams. Hover over a point to see its observed date window and view gain.

```{r bundle-e-tag-momentum-by-type, fig.width=12, fig.height=12}
bundle_e_ggplotly(
  plot_bundle_e_attribute_momentum_by_type(
    video_lifecycle_summary,
    Talent,
    attribute = "tag",
    top_n = 8,
    min_videos = 3
  ),
  tooltip = "text"
)
```

```{r bundle-e-tag-longevity}
bundle_e_type_table(
  bundle_e_attribute_summary_table(tag_longevity, "tag_group", "Tag", top_n = 15),
  empty_text = "No tag longevity table was exported for the current filters."
)
```

# Wrap-up and Conclusion

```{r bundle-e-conclusion, results='asis'}
bundle_e_emit_interpretation("05_report_bookends/02_conclusion")
```

## Active Analysis Window

```{r bundle-e-analysis-window-summary}
window_setting <- dplyr::case_when(
  !is.null(params$start_date) || !is.null(params$end_date) ~ "Explicit date range",
  !is.null(params$window_days) ~ paste0("Last ", params$window_days, " days"),
  TRUE ~ "All available dates"
)

window_summary <- tibble::tibble(
  Metric = c(
    "Window setting",
    "Included date range",
    "Artifact root",
    "Latest snapshot date",
    "Snapshot count",
    "Unique videos",
    "Median observations per video"
  ),
  Value = c(
    window_setting,
    if (is.null(params$included_date_range) || is.na(params$included_date_range)) "All available dates" else as.character(params$included_date_range),
    artifact_root,
    if (nrow(latest_library_row) == 0) NA_character_ else as.character(latest_library_row$snapshot_date[[1]]),
    nrow(library_growth_snapshot),
    if (nrow(video_lifecycle_summary) == 0) 0 else dplyr::n_distinct(video_lifecycle_summary$`Video ID`),
    if (nrow(panel_coverage_summary) == 0 || !("median_observations_per_video" %in% names(panel_coverage_summary))) {
      NA_character_
    } else {
      as.character(bundle_e_first_non_missing(panel_coverage_summary$median_observations_per_video))
    }
  )
)

DTSettings(window_summary, class = "display stripe hover", scroll_x = TRUE, filter = "none")
```
