---
title: "BundleB"
author: "Jonathon Sun"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)

knitr::opts_knit$set(root.dir = here::here())

if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(
    fig.width = 14,
    fig.height = 7,
    out.width = "0.8\\linewidth"
  )
} else {
  knitr::opts_chunk$set(
    fig.width = 10,
    fig.height = 5
  )
}
```

```{r libraries, include=FALSE}
library(tidyverse)
library(purrr)
library(here)
library(ggplot2)
library(DT)
library(plotly)
```

```{r modules, include=FALSE}
source("scripts/lib/utils/staging_root.R")

bundle_b_plot_dir <- here("scripts", "lib", "plots", "report", "bundle_B")
if (dir.exists(bundle_b_plot_dir)) {
  list.files(bundle_b_plot_dir, full.names = TRUE) %>%
    walk(source)
}

list.files(here("scripts", "lib", "plots", "report", "bundle_A"), full.names = TRUE) %>%
  walk(source)
list.files(here("scripts", "lib", "utils"), full.names = TRUE) %>%
  walk(source)
list.files(here("scripts", "lib", "import_data"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
list.files(here("scripts", "lib", "report_tables"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
source(here("scripts", "lib", "plots", "PlottingThemes.R"))

clean_data_dir <- here::here("scripts", "lib", "clean_data")
source(file.path(clean_data_dir, "analytics_core.R"))
source(file.path(clean_data_dir, "analytics_join.R"))
source(file.path(clean_data_dir, "clean_columns.R"))
source(file.path(clean_data_dir, "video_prep.R"))
source(file.path(clean_data_dir, "title_classification_join.R"))

root <- get_staging_root()
```

```{r load_data, include=FALSE}
talent_root <- list.files(root, full.names = TRUE)

Talent <- c("Ava")

talent_root <- select_talent(Talent)
files <- TalentFiles(talent_root)

titles <- load_title_classifications(talent = Talent)
preps <- video_preps_with_titles(
  files = files,
  titles = titles,
  talent = Talent,
  dedupe = TRUE,
  key_cols = "Video ID",
  sort_cols = c("confidence", "published_at", "Published At"),
  dedupe_sets = c("analytics", "monetary", "demo")
)

analytics <- preps$analytics
monetary <- preps$monetary
demo <- preps$demo

# Backward-compatible alias used by legacy chunks.
df <- analytics
```

```{r bundle-b-prep, include=FALSE}
analytics_eng <- analytics %>%
  mutate(avg_view_prop = averageViewPercentage / 100)

views_by_content <- total_views_content_type_prep(analytics)

revenue_by_content <- total_metric_content_type_prep(
  monetary,
  metric_col = "Estimated Revenue",
  window_months = 1
) %>%
  group_by(`Content Type`) %>%
  summarize(
    Total_Revenue = sum(Total, na.rm = TRUE),
    Revenue_Video_Count = sum(VideoCount, na.rm = TRUE),
    .groups = "drop"
  )

eng_summary <- engagement_summary_content_type_prep(
  analytics_eng,
  metric_col = "avg_view_prop"
)

safe_zscore <- function(x) {
  x_num <- suppressWarnings(as.numeric(x))
  if (length(stats::na.omit(x_num)) <= 1 || isTRUE(all.equal(stats::sd(x_num, na.rm = TRUE), 0))) {
    return(rep(0, length(x_num)))
  }
  as.numeric(scale(x_num))
}

strength_matrix <- views_by_content %>%
  rename(Content_Type = `Content Type`) %>%
  left_join(
    revenue_by_content %>% rename(Content_Type = `Content Type`),
    by = "Content_Type"
  ) %>%
  left_join(
    eng_summary %>%
      transmute(
        Content_Type = as.character(.content),
        Engagement_Video_Count = VideoCount,
        Median_Engagement = Median,
        Mean_Engagement = Mean
      ),
    by = "Content_Type"
  ) %>%
  mutate(
    across(
      c(Total_Views, Total_Revenue, Revenue_Video_Count, Engagement_Video_Count, Median_Engagement, Mean_Engagement),
      ~ tidyr::replace_na(.x, 0)
    ),
    Views_Z = safe_zscore(Total_Views),
    Revenue_Z = safe_zscore(Total_Revenue),
    Engagement_Z = safe_zscore(Median_Engagement),
    Composite_Score = rowMeans(across(c(Views_Z, Revenue_Z, Engagement_Z)), na.rm = TRUE)
  )

high_cut <- stats::quantile(strength_matrix$Composite_Score, probs = 0.67, na.rm = TRUE, names = FALSE)
low_cut <- stats::quantile(strength_matrix$Composite_Score, probs = 0.33, na.rm = TRUE, names = FALSE)

strength_matrix <- strength_matrix %>%
  mutate(
    Performance_Band = case_when(
      Composite_Score >= high_cut ~ "Strength",
      Composite_Score <= low_cut ~ "Weakness / Improve",
      TRUE ~ "Middle"
    )
  ) %>%
  arrange(desc(Composite_Score))
```

# Bundle B: Content Strategy & Optimization

This report is structured to answer the Bundle B questions directly:

- Which formats consistently retain viewer attention?
- Where are performance strengths and weaknesses by category?
- How do specific content attributes affect engagement?

## 1) Format Retention Consistency

### Engagement Distribution by Content Type
What this plot does:
- Shows the full spread of engagement outcomes for each content type so you can evaluate reliability, not just averages.

How to read it:
- Compare each category's center and spread to see which formats are consistently strong versus volatile.

```{r b2-engagement-distribution, fig.width=10, fig.height=8}
ggplotly(
  engagement_distribution_content_type(
    analytics_eng,
    Talent,
    metric_col = "avg_view_prop",
    metric_label = "Average View %",
    y_as_percent = TRUE
  )
)
```

### Median Engagement by Content Type
What this plot does:
- Summarizes typical engagement per format and how tight or wide the middle performance range is.

How to read it:
- Bar height is median engagement; the error range shows the interquartile range (25th to 75th percentile).

```{r b2-engagement-summary-plot, fig.width=10, fig.height=8}
ggplotly(
  engagement_summary_content_type_plot(
    eng_summary,
    Talent,
    metric_label = "Average View %",
    y_as_percent = TRUE
  )
)
```

```{r b2-engagement-summary-table}
eng_summary_table <- eng_summary %>%
  transmute(
    Content_Type = as.character(.content),
    Video_Count = VideoCount,
    Median_Engagement = Median,
    Mean_Engagement = Mean,
    Q25_Engagement = Q25,
    Q75_Engagement = Q75
  )

DTSettings(
  eng_summary_table,
  class = "display stripe hover",
  scroll_x = TRUE,
  percent_cols = c("Median_Engagement", "Mean_Engagement", "Q25_Engagement", "Q75_Engagement")
)
```

## 2) Category Strengths and Weaknesses

### Content-Type Position in Full Distribution
What this plot does:
- Shows the full per-video distribution for views, revenue, and engagement.
- Overlays each content type's median as a vertical marker on that full distribution.

How to read it:
- Grey bars show how many videos fall into each value range for that metric.
- Each vertical line shows where a content type sits relative to the full population.
- If a content type median sits further right, that format is typically stronger on that metric.
- X-axis stays on a linear scale with raw values.

```{r b2-priority-rank, fig.width=10, fig.height=10}
content_position <- bundle_b_content_position_distribution_prep(
  analytics_df = analytics,
  monetary_df = monetary
)

bundle_b_content_position_distribution_plotly(
  content_position,
  Talent
)
```

```{r b2-priority-components-table}
priority_components <- bundle_b_content_position_metric_table(content_position)

DTSettings(
  priority_components,
  class = "display stripe hover",
  scroll_x = TRUE,
  percent_cols = c("MedianPercentile")
)
```

### Combined Opportunity Matrix (Content Types, Tags, and Title Labels)
What this plot does:
- Combines content types, tags, and title labels into one opportunity map.
- Keeps `Strength`, `Middle`, and `Weakness / Improve` as shape categories.

How to read it:
- Each point is a content descriptor (content type, tag, or title label).
- X-axis is median engagement, Y-axis is average revenue per video, and bubble size is video count.
- Point shape indicates performance band.
- Y-axis is linear and shows raw dollar values.

How Strength / Middle / Weakness is calculated:
- Compute three per-attribute metrics: `AvgViewsPerVideo`, `AvgRevenuePerVideo`, and `MedianEngagement`.
- Standardize each metric across all plotted attributes using z-scores.
- `Composite_Score = mean(Views_Z, Revenue_Z, Engagement_Z)`.
- `Strength` = top third (`Composite_Score >= 67th percentile`), `Weakness / Improve` = bottom third (`<= 33rd percentile`), otherwise `Middle`.

```{r b2-opportunity-matrix-interactive, fig.width=12, fig.height=9}
attribute_opportunity <- bundle_b_attribute_opportunity_prep(
  analytics_df = analytics,
  monetary_df = monetary,
  top_n_content = 8,
  top_n_labels = 8,
  top_n_tags = 10,
  min_videos = 2
)

bundle_b_attribute_opportunity_matrix_plotly(
  attribute_opportunity,
  Talent
)
```

```{r b2-attribute-opportunity-table}
attribute_opportunity_table <- bundle_b_attribute_opportunity_table(attribute_opportunity)

DTSettings(
  attribute_opportunity_table,
  class = "display stripe hover",
  scroll_x = TRUE,
  percent_cols = c("MedianEngagement")
)
```

### Revenue Efficiency by Content Type
What this plot does:
- Compares monetization efficiency by format, normalized to views.

How to read it:
- Bar height is estimated revenue per 1,000 views; higher values indicate better revenue conversion per view.

```{r b2-revenue-efficiency, fig.width=10, fig.height=8}
ggplotly(
  bundle_b_revenue_efficiency_plot(
    strength_matrix,
    Talent
  )
)
```

### Distribution-Based Strength/Weakness Summary by Content Type
What this table does:
- Summarizes where each content type lands in the full-video distribution by metric percentile.

How to read it:
- `ViewsMedianPercentile`: percentile position of that content type's median views per video.
- `RevenueMedianPercentile`: percentile position of median revenue per video.
- `EngagementMedianPercentile`: percentile position of median engagement rate.
- `AvgMedianPercentile`: average of the available median percentiles for that content type.
- `Performance_Band` is assigned from `AvgMedianPercentile` across content types:
  - `Strength`: top third (>= 67th percentile)
  - `Weakness / Improve`: bottom third (<= 33rd percentile)
  - `Middle`: all others
- `MetricsCovered` shows how many metrics were available for that content type; if this is below 3, interpret banding with caution.

```{r b2-strength-matrix-table}
strength_matrix_table <- bundle_b_content_position_overall_table(content_position)

DTSettings(
  strength_matrix_table,
  class = "display stripe hover",
  scroll_x = TRUE,
  percent_cols = c(
    "ViewsMedianPercentile",
    "RevenueMedianPercentile",
    "EngagementMedianPercentile",
    "AvgMedianPercentile"
  )
)
```

## 3) Content Attributes and Engagement

### Collaboration Lift vs Non-Collaborative

In this section, **lift** means the relative difference between collaborative and non-collaborative content.

What this plot does:
- Estimates whether collaborative content outperforms or underperforms non-collaborative baseline on per-video views and per-video revenue.

How to read it:
- Bars above zero are positive lift (better than baseline); bars below zero are negative lift (worse than baseline).

This plot estimates two lifts:

`Views lift = (Avg views per collaborative video / Avg views per non-collaborative video) - 1`

`Revenue lift = (Avg revenue per collaborative video / Avg revenue per non-collaborative video) - 1`

How to interpret:

- Positive lift: collaborative content performs better than non-collaborative baseline.
- Negative lift: collaborative content performs worse than non-collaborative baseline.
- `+0.25` means about `+25%` lift; `-0.10` means about `-10%` lift.

Method notes:

- This is a **descriptive estimate**, not a causal effect.
- The baseline is the non-collaborative average in the same dataset.
- Revenue and views can be based on different row counts, so read both metrics together.

```{r b2-collaboration-lift-plot, fig.width=10, fig.height=8}
collab_summary <- collaboration_effectiveness_prep(analytics, monetary)

ggplotly(
  bundle_b_collaboration_lift_plot(
    collab_summary,
    Talent
  )
)
```

```{r b2-collaboration-table}
collab_table <- collab_summary %>%
  select(
    collab_group,
    VideoCountViews,
    VideoCountRevenue,
    TotalViews,
    TotalRevenue,
    AverageViewsPerVideo,
    AverageRevenuePerVideo,
    AvgViewsLiftVsNonCollab,
    AvgRevenueLiftVsNonCollab
  )

DTSettings(
  collab_table,
  class = "display stripe hover",
  scroll_x = TRUE,
  percent_cols = c("AvgViewsLiftVsNonCollab", "AvgRevenueLiftVsNonCollab")
)
```

### Topic View Distribution
What this plot does:
- Shows the distribution of per-video views within top topics, rather than only topic totals.

How to read it:
- Compare medians and spread across topics to distinguish stable performance from outlier-driven performance.

```{r b2-topic-view-distribution-plot, fig.width=12, fig.height=9}
topic_view_dist <- topic_view_distribution_prep(
  analytics,
  top_n = 8,
  min_videos = 2
)

ggplotly(
  topic_view_distribution_plot(
    topic_view_dist,
    Talent
  )
)
```

```{r b2-topic-view-distribution-table}
DTSettings(topic_view_dist$summary, class = "display stripe hover", scroll_x = TRUE)
```

### Tag View Distribution
What this plot does:
- Shows the distribution of per-video views within top tags for finer-grain content attributes.

How to read it:
- Compare medians, quartiles, and range across tags to see which tags are more consistently strong.

```{r b2-tag-view-distribution-plot, fig.width=12, fig.height=9}
tag_view_dist <- tag_view_distribution_prep(
  analytics,
  top_n = 15,
  min_videos = 2,
  min_views_per_video = 10
)

ggplotly(
  tag_view_distribution_plot(
    tag_view_dist,
    Talent
  )
)
```

```{r b2-tag-view-distribution-table}
DTSettings(tag_view_dist$summary, class = "display stripe hover", scroll_x = TRUE)
```

## 4) Scheduling Effects

### Day-of-Week Deviation from Average
What this plot does:
- Shows how far each weekday is above or below the overall weekday average.

How to read it:
- Values above `0` are above-average days.
- Values below `0` are below-average days.
- This is not a z-score.
- Formula: `Deviation = weekday average - overall weekday average`.
- Top panel is views deviation; bottom panel is revenue deviation.

```{r b2-dow-lift-plot, fig.width=10, fig.height=8}
dow_summary <- day_of_week_performance_prep(analytics, monetary)

ggplotly(
  bundle_b_day_of_week_lift_plot(
    dow_summary,
    Talent
  )
)
```

```{r b2-dow-table}
dow_deviation_table <- bundle_b_day_of_week_deviation_table(dow_summary)
DTSettings(dow_deviation_table, class = "display stripe hover", scroll_x = TRUE)
```

### Weekend vs Weekday Summary
```{r b2-weekend-table}
wk_summary <- weekend_vs_weekday_prep(analytics, monetary)
DTSettings(wk_summary, class = "display stripe hover", scroll_x = TRUE)
```

# Wrap-up: What this means

Use the retention and strength/weakness sections to prioritize content types to scale, then use topic/tag/collaboration/scheduling sections to tune execution for higher engagement and monetization efficiency.
