---
title: "BundleB"
author: "Jonathon Sun"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)

knitr::opts_knit$set(root.dir = here::here())

if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(
    fig.width = 14,
    fig.height = 7,
    out.width = "0.8\\linewidth"
  )
} else {
  knitr::opts_chunk$set(
    fig.width = 10,
    fig.height = 5
  )
}
```

```{r libraries, include=FALSE}
library(tidyverse)
library(purrr)
library(here)
library(ggplot2)
library(DT)
library(plotly)
```

```{r modules, include=FALSE}
source("scripts/lib/utils/staging_root.R")

bundle_b_plot_dir <- here("scripts", "lib", "plots", "report", "bundle_B")
if (dir.exists(bundle_b_plot_dir)) {
  list.files(bundle_b_plot_dir, full.names = TRUE) %>%
    walk(source)
}

list.files(here("scripts", "lib", "plots", "report", "bundle_A"), full.names = TRUE) %>%
  walk(source)
list.files(here("scripts", "lib", "utils"), full.names = TRUE) %>%
  walk(source)
list.files(here("scripts", "lib", "import_data"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
list.files(here("scripts", "lib", "report_tables"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
source(here("scripts", "lib", "plots", "PlottingThemes.R"))

clean_data_dir <- here::here("scripts", "lib", "clean_data")
source(file.path(clean_data_dir, "analytics_core.R"))
source(file.path(clean_data_dir, "analytics_join.R"))
source(file.path(clean_data_dir, "clean_columns.R"))
source(file.path(clean_data_dir, "video_prep.R"))
source(file.path(clean_data_dir, "title_classification_join.R"))

if (!exists("DTSettings")) {
  DTSettings <- function(df, class = NULL, scroll_x = FALSE, ...) {
    DT::datatable(
      df,
      class = class,
      options = list(scrollX = isTRUE(scroll_x)),
      ...
    )
  }
}

root <- get_staging_root()
```

```{r load_data, include=FALSE}
talent_root <- list.files(root, full.names = TRUE)

Talent <- c("Ava")

talent_root <- select_talent(Talent)
files <- TalentFiles(talent_root)

titles <- load_title_classifications(talent = Talent)
preps <- video_preps_with_titles(
  files = files,
  titles = titles,
  talent = Talent,
  dedupe = TRUE,
  key_cols = "Video ID",
  sort_cols = c("confidence", "published_at", "Published At"),
  dedupe_sets = c("analytics", "monetary", "demo")
)

analytics <- preps$analytics
monetary <- preps$monetary
demo <- preps$demo

# Backward-compatible alias used by legacy chunks.
df <- analytics
```

```{r bundle-b-prep, include=FALSE}
analytics_eng <- analytics %>%
  mutate(avg_view_prop = averageViewPercentage / 100)

views_by_content <- total_views_content_type_prep(analytics)

revenue_by_content <- total_metric_content_type_prep(
  monetary,
  metric_col = "Estimated Revenue",
  window_months = 1
) %>%
  group_by(`Content Type`) %>%
  summarize(
    Total_Revenue = sum(Total, na.rm = TRUE),
    Revenue_Video_Count = sum(VideoCount, na.rm = TRUE),
    .groups = "drop"
  )

eng_summary <- engagement_summary_content_type_prep(
  analytics_eng,
  metric_col = "avg_view_prop"
)

safe_zscore <- function(x) {
  x_num <- suppressWarnings(as.numeric(x))
  if (length(stats::na.omit(x_num)) <= 1 || isTRUE(all.equal(stats::sd(x_num, na.rm = TRUE), 0))) {
    return(rep(0, length(x_num)))
  }
  as.numeric(scale(x_num))
}

strength_matrix <- views_by_content %>%
  rename(Content_Type = `Content Type`) %>%
  left_join(
    revenue_by_content %>% rename(Content_Type = `Content Type`),
    by = "Content_Type"
  ) %>%
  left_join(
    eng_summary %>%
      transmute(
        Content_Type = as.character(.content),
        Engagement_Video_Count = VideoCount,
        Median_Engagement = Median,
        Mean_Engagement = Mean
      ),
    by = "Content_Type"
  ) %>%
  mutate(
    across(
      c(Total_Views, Total_Revenue, Revenue_Video_Count, Engagement_Video_Count, Median_Engagement, Mean_Engagement),
      ~ tidyr::replace_na(.x, 0)
    ),
    Views_Z = safe_zscore(Total_Views),
    Revenue_Z = safe_zscore(Total_Revenue),
    Engagement_Z = safe_zscore(Median_Engagement),
    Composite_Score = rowMeans(across(c(Views_Z, Revenue_Z, Engagement_Z)), na.rm = TRUE)
  )

high_cut <- stats::quantile(strength_matrix$Composite_Score, probs = 0.67, na.rm = TRUE, names = FALSE)
low_cut <- stats::quantile(strength_matrix$Composite_Score, probs = 0.33, na.rm = TRUE, names = FALSE)

strength_matrix <- strength_matrix %>%
  mutate(
    Performance_Band = case_when(
      Composite_Score >= high_cut ~ "Strength",
      Composite_Score <= low_cut ~ "Weakness / Improve",
      TRUE ~ "Middle"
    )
  ) %>%
  arrange(desc(Composite_Score))
```

# Bundle B: Content Strategy & Optimization

This report is structured to answer the Bundle B questions directly:

- Which formats consistently retain viewer attention?
- Where are performance strengths and weaknesses by category?
- How do specific content attributes affect engagement?

## 1) Format Retention Consistency

### Engagement Distribution by Content Type
```{r b2-engagement-distribution, fig.width=10, fig.height=8}
ggplotly(
  engagement_distribution_content_type(
    analytics_eng,
    Talent,
    metric_col = "avg_view_prop",
    metric_label = "Average View %",
    y_as_percent = TRUE
  )
)
```

### Median Engagement by Content Type
```{r b2-engagement-summary-plot, fig.width=10, fig.height=8}
ggplotly(
  engagement_summary_content_type_plot(
    eng_summary,
    Talent,
    metric_label = "Average View %",
    y_as_percent = TRUE
  )
)
```

```{r b2-engagement-summary-table}
eng_summary_table <- eng_summary %>%
  transmute(
    Content_Type = as.character(.content),
    Video_Count = VideoCount,
    Median_Engagement = Median,
    Mean_Engagement = Mean,
    Q25_Engagement = Q25,
    Q75_Engagement = Q75
  )

DTSettings(eng_summary_table, class = "display stripe hover", scroll_x = TRUE) %>%
  DT::formatPercentage(
    columns = c("Median_Engagement", "Mean_Engagement", "Q25_Engagement", "Q75_Engagement"),
    digits = 1
  )
```

## 2) Category Strengths and Weaknesses

### Total Views by Content Type
```{r b2-total-views, fig.width=10, fig.height=8}
ggplotly(
  total_views_content_type(analytics, Talent) +
    theme_nyt()
)
```

### Total Revenue by Content Type
```{r b2-total-revenue, fig.width=10, fig.height=8}
ggplotly(
  total_metric_content_type(
    monetary,
    Talent,
    metric_col = "Estimated Revenue",
    metric_label = "Revenue",
    window_months = 1,
    bar_position = "stack",
    show_counts = TRUE
  )
)
```

### Strength/Weakness Matrix by Content Type
```{r b2-strength-matrix-table}
strength_matrix_table <- strength_matrix %>%
  select(
    Content_Type,
    Total_Views,
    Total_Revenue,
    Median_Engagement,
    Composite_Score,
    Performance_Band
  )

DTSettings(strength_matrix_table, class = "display stripe hover", scroll_x = TRUE) %>%
  DT::formatRound(columns = c("Total_Views", "Total_Revenue", "Composite_Score"), digits = 2) %>%
  DT::formatPercentage(columns = c("Median_Engagement"), digits = 1)
```

## 3) Content Attributes and Engagement

### Collaboration Effectiveness
```{r b2-collaboration-plot, fig.width=10, fig.height=8}
collab_summary <- collaboration_effectiveness_prep(analytics, monetary)

ggplotly(
  collaboration_effectiveness_plot(
    collab_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r b2-collaboration-table}
collab_table <- collab_summary %>%
  select(
    collab_group,
    VideoCountViews,
    VideoCountRevenue,
    TotalViews,
    TotalRevenue,
    AverageViewsPerVideo,
    AverageRevenuePerVideo,
    AvgViewsLiftVsNonCollab,
    AvgRevenueLiftVsNonCollab
  )

decimal_cols <- detect_decimals(collab_table)
DTSettings(collab_table, class = "display stripe hover", scroll_x = TRUE) %>%
  DT::formatRound(columns = decimal_cols, digits = 3)
```

### Topic Performance
```{r b2-topic-plot, fig.width=10, fig.height=8}
topic_summary <- topic_performance_prep(analytics, monetary, top_n = 8)

ggplotly(
  topic_performance_plot(
    topic_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r b2-topic-table}
decimal_cols <- detect_decimals(topic_summary)
DTSettings(topic_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  DT::formatRound(columns = decimal_cols, digits = 3)
```

### Tag Performance
```{r b2-tag-plot, fig.width=12, fig.height=9}
tag_summary <- tag_performance_prep(
  analytics,
  monetary,
  top_n = 15,
  min_videos = 2
)

ggplotly(
  tag_performance_plot(
    tag_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r b2-tag-table}
decimal_cols <- detect_decimals(tag_summary)
DTSettings(tag_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  DT::formatRound(columns = decimal_cols, digits = 3)
```

### Tag View Distribution
```{r b2-tag-view-distribution-plot, fig.width=12, fig.height=9}
tag_view_dist <- tag_view_distribution_prep(
  analytics,
  top_n = 15,
  min_videos = 2
)

ggplotly(
  tag_view_distribution_plot(
    tag_view_dist,
    Talent
  )
)
```

```{r b2-tag-view-distribution-table}
decimal_cols <- detect_decimals(tag_view_dist$summary)
DTSettings(tag_view_dist$summary, class = "display stripe hover", scroll_x = TRUE) %>%
  DT::formatRound(columns = decimal_cols, digits = 3)
```

## 4) Scheduling Effects

### Weekend vs Weekday
```{r b2-weekend-plot, fig.width=10, fig.height=8}
wk_summary <- weekend_vs_weekday_prep(analytics, monetary)

ggplotly(
  weekend_vs_weekday_plot(
    wk_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r b2-weekend-table}
decimal_cols <- detect_decimals(wk_summary)
DTSettings(wk_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  DT::formatRound(columns = decimal_cols, digits = 3)
```

### Day-of-Week Distribution
```{r b2-dow-plot, fig.width=10, fig.height=8}
dow_summary <- day_of_week_performance_prep(analytics, monetary)

ggplotly(
  day_of_week_performance_plot(
    dow_summary,
    Talent,
    as_share = TRUE
  )
)
```

```{r b2-dow-table}
decimal_cols <- detect_decimals(dow_summary)
DTSettings(dow_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  DT::formatRound(columns = decimal_cols, digits = 3)
```

# Wrap-up: What this means

Use the retention and strength/weakness sections to prioritize content types to scale, then use topic/tag/collaboration/scheduling sections to tune execution for higher engagement and monetization efficiency.
