---
title: "`r { t <- params$talent; if (!(length(t) == 1 && !is.na(t) && nzchar(trimws(as.character(t))))) t <- 'Talent'; t <- trimws(as.character(t)); t_clean <- trimws(gsub('\\s*[\\[【].*$', '', t)); paste0('Content Strategy Optimization Report: ', t_clean) }`"
subtitle: "`r { r <- params$included_date_range; if (!(length(r) == 1 && !is.na(r) && nzchar(trimws(as.character(r))))) r <- 'All available dates'; paste0('Data Range: ', as.character(r)) }`"
author: "Author: Zhuni Excel & Jonathon Sun"
date: "`r { x <- params$render_generated_at; if (length(x) == 1 && !is.na(x) && nzchar(trimws(as.character(x)))) { x <- trimws(as.character(x)); x_date <- sub('^([0-9]{4}-[0-9]{2}-[0-9]{2}).*$', '\\\\1', x); if (grepl('^[0-9]{4}-[0-9]{2}-[0-9]{2}$', x_date)) paste0('Report Date: ', x_date) else paste0('Report Date: ', format(Sys.Date(), '%Y-%m-%d')) } else paste0('Report Date: ', format(Sys.Date(), '%Y-%m-%d')) }`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float: true
    toc_depth: 3
params:
  talent: "Ava"
  data_source: "datalake"
  data_root: null
  render_generated_at: null
  included_date_range: null
  render_cli: null
  render_output_dir: null
  render_output_prefix: null
  window_days: null
  start_date: null
  end_date: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)

knitr::opts_knit$set(root.dir = here::here())

if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(
    fig.width = 14,
    fig.height = 7,
    out.width = "0.8\\linewidth"
  )
} else {
  knitr::opts_chunk$set(
    fig.width = 10,
    fig.height = 5,
    out.width = "100%"
  )
}
```

```{r libraries, include=FALSE}
library(tidyverse)
library(purrr)
library(here)
library(ggplot2)
library(DT)
library(plotly)
```

```{r modules, include=FALSE}
source("r_scripts/lib/utils/staging_root.R")
source("r_scripts/lib/utils/datalake_root.r")

bundle_b_plot_dir <- here("r_scripts", "lib", "plots", "report", "bundle_B")
if (dir.exists(bundle_b_plot_dir)) {
  list.files(bundle_b_plot_dir, full.names = TRUE) %>%
    walk(source)
}

list.files(here("r_scripts", "lib", "plots", "report", "bundle_A"), full.names = TRUE) %>%
  walk(source)
list.files(here("r_scripts", "lib", "utils"), full.names = TRUE) %>%
  walk(source)
list.files(here("r_scripts", "lib", "import_data"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
list.files(here("r_scripts", "lib", "report_tables"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
source(here("r_scripts", "lib", "plots", "PlottingThemes.R"))

clean_data_dir <- here::here("r_scripts", "lib", "clean_data")
source(file.path(clean_data_dir, "analytics_core.R"))
source(file.path(clean_data_dir, "analytics_join.R"))
source(file.path(clean_data_dir, "clean_columns.R"))
source(file.path(clean_data_dir, "video_prep.R"))
source(file.path(clean_data_dir, "title_classification_join.R"))
```

```{r load_data, include=FALSE}
data_source <- tolower(trimws(as.character(params$data_source)))
if (!nzchar(data_source)) {
  data_source <- "datalake"
}
if (!(data_source %in% c("staging", "datalake"))) {
  stop("`params$data_source` must be one of: 'staging', 'datalake'.")
}

data_root_param <- if (is.null(params$data_root) || (length(params$data_root) == 1 && is.na(params$data_root))) {
  ""
} else {
  trimws(as.character(params$data_root[[1]]))
}

root <- if (nzchar(data_root_param)) {
  data_root_param
} else if (identical(data_source, "datalake")) {
  get_datalake_root()
} else {
  get_staging_root()
}

if (!dir.exists(root)) {
  stop("Resolved data root does not exist: ", root)
}

Talent <- as.character(params$talent)
if (length(Talent) != 1 || is.na(Talent) || !nzchar(trimws(Talent))) {
  stop("`params$talent` must be a single non-empty talent name.")
}
Talent <- trimws(Talent)

window_days <- params$window_days
if (is.null(window_days) || (length(window_days) == 1 && is.na(window_days))) {
  window_days <- NA_integer_
} else {
  window_days <- suppressWarnings(as.integer(window_days))
  if (length(window_days) != 1 || is.na(window_days) || window_days <= 0) {
    stop("`params$window_days` must be NULL/NA or a single positive integer.")
  }
}

parse_optional_date <- function(x, label) {
  if (is.null(x) || (length(x) == 1 && is.na(x)) || !nzchar(trimws(as.character(x)))) {
    return(as.Date(NA))
  }
  d <- suppressWarnings(as.Date(as.character(x)))
  if (is.na(d)) {
    stop("`params$", label, "` must be in YYYY-MM-DD format when provided.")
  }
  d
}

start_date_param <- parse_optional_date(params$start_date, "start_date")
end_date_param <- parse_optional_date(params$end_date, "end_date")

if (!is.na(start_date_param) || !is.na(end_date_param)) {
  if (is.na(start_date_param)) {
    start_date_param <- as.Date("1900-01-01")
  }
  if (is.na(end_date_param)) {
    end_date_param <- Sys.Date()
  }
  if (start_date_param > end_date_param) {
    stop("`params$start_date` cannot be after `params$end_date`.")
  }
  window_start_date <- start_date_param
  window_end_date <- end_date_param
  window_mode <- "explicit_range"
} else if (!is.na(window_days)) {
  window_end_date <- Sys.Date()
  window_start_date <- window_end_date - as.integer(window_days) + 1
  window_mode <- "days_back"
} else {
  window_start_date <- as.Date(NA)
  window_end_date <- as.Date(NA)
  window_mode <- "all_data"
}

talent_root <- select_talent(Talent, root = root)
files <- TalentFiles(talent_root)

titles <- load_title_classifications(talent = Talent)
preps <- video_preps_with_titles(
  files = files,
  titles = titles,
  talent = Talent,
  dedupe = TRUE,
  key_cols = "Video ID",
  sort_cols = c("confidence", "published_at", "Published At"),
  dedupe_sets = c("analytics", "monetary", "demo")
)

analytics <- preps$analytics
monetary <- preps$monetary
demo <- preps$demo

apply_days_back_window <- function(df) {
  if (window_mode == "all_data" || nrow(df) == 0) {
    return(df)
  }

  date_col <- bundle_a_optional_col(
    df,
    candidates = c("publish_date", "Published At", "date"),
    label = "analysis window date column"
  )
  if (is.null(date_col)) {
    return(df)
  }

  df %>%
    mutate(.window_date = bundle_a_as_date(.data[[date_col]])) %>%
    filter(
      !is.na(.data$.window_date),
      .data$.window_date >= window_start_date,
      .data$.window_date <= window_end_date
    ) %>%
    select(-.window_date)
}

analytics <- apply_days_back_window(analytics)
monetary <- apply_days_back_window(monetary)
demo <- apply_days_back_window(demo)

if (nrow(analytics) == 0 || nrow(monetary) == 0) {
  stop(
    "No data after applying the selected window. ",
    "At least analytics and monetary data are required. ",
    "Try a larger `window_days` value or set it to NULL for all available data."
  )
}

# Backward-compatible alias used by legacy chunks.
df <- analytics

bundle_b_interp_root <- {
  out_dir <- params$render_output_dir
  if (is.null(out_dir) || length(out_dir) == 0 || is.na(out_dir[[1]]) || !nzchar(trimws(as.character(out_dir[[1]])))) {
    NULL
  } else {
    file.path(trimws(as.character(out_dir[[1]])), "interpretations")
  }
}

bundle_b_read_interpretation <- function(rel_dir) {
  if (is.null(bundle_b_interp_root) || !nzchar(bundle_b_interp_root)) {
    return("")
  }
  interp_path <- file.path(bundle_b_interp_root, rel_dir, "output.md")
  if (!file.exists(interp_path)) {
    return("")
  }
  txt <- paste(readLines(interp_path, warn = FALSE, encoding = "UTF-8"), collapse = "\n")
  txt <- trimws(txt)
  if (!nzchar(txt)) {
    return("")
  }
  txt
}

bundle_b_emit_interpretation <- function(rel_dir) {
  txt <- bundle_b_read_interpretation(rel_dir)
  if (!nzchar(txt)) {
    return(invisible(NULL))
  }
  cat(txt, "\n\n")
}
```

```{r bundle-b-prep, include=FALSE}
analytics_eng <- analytics %>%
  mutate(avg_view_prop = averageViewPercentage / 100)

views_by_content <- total_views_content_type_prep(analytics)

revenue_by_content <- total_metric_content_type_prep(
  monetary,
  metric_col = "Estimated Revenue",
  window_months = 1
) %>%
  group_by(`Content Type`) %>%
  summarize(
    Total_Revenue = sum(Total, na.rm = TRUE),
    Revenue_Video_Count = sum(VideoCount, na.rm = TRUE),
    .groups = "drop"
  )

eng_summary <- engagement_summary_content_type_prep(
  analytics_eng,
  metric_col = "avg_view_prop"
)

eng_dist <- engagement_distribution_content_type_prep(
  analytics_eng,
  metric_col = "avg_view_prop"
)

revenue_eff_dist <- bundle_b_revenue_efficiency_distribution_prep(
  analytics,
  monetary
)

safe_zscore <- function(x) {
  x_num <- suppressWarnings(as.numeric(x))
  if (length(stats::na.omit(x_num)) <= 1 || isTRUE(all.equal(stats::sd(x_num, na.rm = TRUE), 0))) {
    return(rep(0, length(x_num)))
  }
  as.numeric(scale(x_num))
}

strength_matrix <- views_by_content %>%
  rename(Content_Type = `Content Type`) %>%
  left_join(
    revenue_by_content %>% rename(Content_Type = `Content Type`),
    by = "Content_Type"
  ) %>%
  left_join(
    eng_summary %>%
      transmute(
        Content_Type = as.character(.content),
        Engagement_Video_Count = VideoCount,
        Median_Engagement = Median,
        Mean_Engagement = Mean
      ),
    by = "Content_Type"
  ) %>%
  mutate(
    across(
      c(Total_Views, Total_Revenue, Revenue_Video_Count, Engagement_Video_Count, Median_Engagement, Mean_Engagement),
      ~ tidyr::replace_na(.x, 0)
    ),
    Views_Z = safe_zscore(Total_Views),
    Revenue_Z = safe_zscore(Total_Revenue),
    Engagement_Z = safe_zscore(Median_Engagement),
    Composite_Score = rowMeans(across(c(Views_Z, Revenue_Z, Engagement_Z)), na.rm = TRUE)
  )

high_cut <- stats::quantile(strength_matrix$Composite_Score, probs = 0.67, na.rm = TRUE, names = FALSE)
low_cut <- stats::quantile(strength_matrix$Composite_Score, probs = 0.33, na.rm = TRUE, names = FALSE)

strength_matrix <- strength_matrix %>%
  mutate(
    Performance_Band = case_when(
      Composite_Score >= high_cut ~ "Strength",
      Composite_Score <= low_cut ~ "Weakness / Improve",
      TRUE ~ "Middle"
    )
  ) %>%
  arrange(desc(Composite_Score))
```

# How This Report Supports Content Strategy Decisions

This report is structured to support tactical content decisions with transparent, descriptive analysis.
Each primary section answers a practical planning question: where performance is stable, where it is strong or weak, which content attributes move outcomes, and when publishing windows tend to outperform.

**Scope note:** This version of Bundle B depends on monetary data and is optimized for talents with both analytics and revenue coverage. For talents without monetary data, use a non-monetary strategy variant centered on views and engagement diagnostics.

- Which formats consistently retain viewer attention?
- Where are performance strengths and weaknesses by category?
- How do specific content attributes affect engagement?

# Executive Summary

```{r bundle-b-executive-summary, results='asis'}
bundle_b_emit_interpretation("06_report_bookends/01_executive_summary")
```

## Why Format-Level Retention Consistency Matters
This section establishes a quality baseline before optimization.
Retention-focused metrics are used first because they are less sensitive to posting volume than totals and help identify which formats consistently hold viewer attention.

```{r bundle-b-section-01-synthesis, results='asis'}
bundle_b_emit_interpretation("01_format_level_retention_consistency/00_section_synthesis")
```

### Engagement Distribution by Content Type
**What this plot does:**
- Shows the full spread of engagement outcomes for each content type so you can evaluate reliability, not just averages.

**How to read it:**
- Compare each category's center and spread to see which formats are consistently strong versus volatile.

```{r b2-engagement-distribution, fig.width=10, fig.height=8}
bundle_b_ggplotly(
  engagement_distribution_content_type(
    analytics_eng,
    Talent,
    metric_col = "avg_view_prop",
    metric_label = "Average View %",
    y_as_percent = TRUE
  )
)
```

```{r bundle-b-engagement-distribution-text, results='asis'}
bundle_b_emit_interpretation("01_format_level_retention_consistency/01_engagement_distribution_by_content_type")
```

### Median Engagement by Content Type
**What this plot does:**
- Summarizes typical engagement per format and how tight or wide the middle performance range is.

**How to read it:**
- Box shows median and quartiles for each content type; jittered points are individual videos.

```{r b2-engagement-summary-plot, fig.width=10, fig.height=8}
bundle_b_ggplotly(
  bundle_b_engagement_summary_distribution_plot(
    eng_dist,
    Talent,
    metric_label = "Average View %",
    y_as_percent = TRUE
  )
)
```

```{r b2-engagement-summary-table}
eng_summary_table <- eng_summary %>%
  transmute(
    Content_Type = as.character(.content),
    Video_Count = VideoCount,
    Median_Engagement = Median,
    Mean_Engagement = Mean,
    Q25_Engagement = Q25,
    Q75_Engagement = Q75
  )

DTSettings(
  eng_summary_table,
  class = "display stripe hover",
  scroll_x = TRUE,
  percent_cols = c("Median_Engagement", "Mean_Engagement", "Q25_Engagement", "Q75_Engagement")
)
```

```{r bundle-b-median-engagement-text, results='asis'}
bundle_b_emit_interpretation("01_format_level_retention_consistency/02_median_engagement_by_content_type")
```

## Why Category Strengths and Weaknesses Matter for Prioritization
This section translates performance into prioritization signals.
Views, revenue, and engagement are analyzed together so recommendations are balanced across reach, monetization, and audience quality rather than driven by a single metric.

```{r bundle-b-section-02-synthesis, results='asis'}
bundle_b_emit_interpretation("02_category_strengths_and_weaknesses/00_section_synthesis")
```

### Content-Type Position in Full Distribution
**What this plot does:**
- Shows the full per-video distribution for views, revenue, and engagement.
- Overlays each content type's median as a vertical marker on that full distribution.

**How to read it:**
- Grey bars show how many videos fall into each value range for that metric.
- Each vertical line shows where a content type sits relative to the full population.
- If a content type median sits further right, that format is typically stronger on that metric.
- X-axis stays on a linear scale with raw values.

```{r b2-priority-rank, fig.width=10, fig.height=10}
content_position <- bundle_b_content_position_distribution_prep(
  analytics_df = analytics,
  monetary_df = monetary
)

bundle_b_content_position_distribution_plotly(
  content_position,
  Talent
)
```

```{r bundle-b-content-position-text, results='asis'}
bundle_b_emit_interpretation("02_category_strengths_and_weaknesses/01_content_type_position_in_full_distribution")
```

```{r b2-priority-components-table}
priority_components <- bundle_b_content_position_metric_table(content_position)

DTSettings(
  priority_components,
  class = "display stripe hover",
  scroll_x = TRUE,
  percent_cols = c("MedianPercentile")
)
```

### Combined Opportunity Matrix (Content Types, Tags, and Title Labels)
**What this plot does:**
- Combines content types, tags, and title labels into one opportunity map.
- Keeps `Strength`, `Middle`, and `Weakness / Improve` as shape categories.

**How to read it:**
- Each point is a content descriptor (content type, tag, or title label).
- X-axis is median engagement, Y-axis is average revenue per video, and bubble size is video count.
- Point shape indicates performance band.
- Y-axis is linear and shows raw dollar values.

How Strength / Middle / Weakness is calculated:
- Compute three per-attribute metrics: `AvgViewsPerVideo`, `AvgRevenuePerVideo`, and `MedianEngagement`.
- Standardize each metric across all plotted attributes using z-scores.
- `Composite_Score = mean(Views_Z, Revenue_Z, Engagement_Z)`.
- `Strength` = top third (`Composite_Score >= 67th percentile`), `Weakness / Improve` = bottom third (`<= 33rd percentile`), otherwise `Middle`.

```{r b2-opportunity-matrix-interactive, fig.width=12, fig.height=9}
attribute_opportunity <- bundle_b_attribute_opportunity_prep(
  analytics_df = analytics,
  monetary_df = monetary,
  top_n_content = 8,
  top_n_labels = 8,
  top_n_tags = 10,
  min_videos = 2
)

bundle_b_attribute_opportunity_matrix_plotly(
  attribute_opportunity,
  Talent
)
```

```{r bundle-b-opportunity-matrix-text, results='asis'}
bundle_b_emit_interpretation("02_category_strengths_and_weaknesses/02_combined_opportunity_matrix_content_types_tags_and_title_labels")
```

### Combined Opportunity Matrix (Median Engagement vs Average Views)
**What this plot does:**
- Uses the same combined attribute set, but with `Average views per video` on Y for performance scale.

**How to read it:**
- X-axis remains median engagement.
- Y-axis is average views per video (raw values).
- Bubble size is video count and shape is performance band.

```{r b2-opportunity-matrix-engagement-views, fig.width=12, fig.height=9}
bundle_b_attribute_engagement_views_matrix_plotly(
  attribute_opportunity,
  Talent
)
```

```{r bundle-b-engagement-views-matrix-text, results='asis'}
bundle_b_emit_interpretation("02_category_strengths_and_weaknesses/03_combined_opportunity_matrix_median_engagement_vs_average_views")
```

### Combined Opportunity Matrix (Average Views vs Average Revenue)
**What this plot does:**
- Directly compares view scale to monetization scale across the same combined attributes.

**How to read it:**
- X-axis is average views per video.
- Y-axis is average revenue per video.
- Bubble size is video count and shape is performance band.

```{r b2-opportunity-matrix-views-revenue, fig.width=12, fig.height=9}
bundle_b_attribute_views_revenue_matrix_plotly(
  attribute_opportunity,
  Talent
)
```

```{r bundle-b-views-revenue-matrix-text, results='asis'}
bundle_b_emit_interpretation("02_category_strengths_and_weaknesses/04_combined_opportunity_matrix_average_views_vs_average_revenue")
```

```{r b2-attribute-opportunity-table}
attribute_opportunity_table <- bundle_b_attribute_opportunity_table(attribute_opportunity)

DTSettings(
  attribute_opportunity_table,
  class = "display stripe hover",
  scroll_x = TRUE,
  percent_cols = c("MedianEngagement")
)
```

### Revenue Efficiency by Content Type
**What this plot does:**
- Compares monetization efficiency by format, normalized to views.

**How to read it:**
- Box shows median and quartiles of per-video revenue efficiency; jittered points are individual videos.

```{r b2-revenue-efficiency, fig.width=10, fig.height=8}
bundle_b_ggplotly(
  bundle_b_revenue_efficiency_plot(
    revenue_eff_dist,
    Talent
  )
)
```

```{r bundle-b-revenue-efficiency-text, results='asis'}
bundle_b_emit_interpretation("02_category_strengths_and_weaknesses/05_revenue_efficiency_by_content_type")
```

### Distribution-Based Strength/Weakness Summary by Content Type
**What this table does:**
- Summarizes where each content type lands in the full-video distribution by metric percentile.

**How to read it:**
- `ViewsMedianPercentile`: percentile position of that content type's median views per video.
- `RevenueMedianPercentile`: percentile position of median revenue per video.
- `EngagementMedianPercentile`: percentile position of median engagement rate.
- `AvgMedianPercentile`: average of the available median percentiles for that content type.
- `Performance_Band` is assigned from `AvgMedianPercentile` across content types:
  - `Strength`: top third (>= 67th percentile)
  - `Weakness / Improve`: bottom third (<= 33rd percentile)
  - `Middle`: all others
- `MetricsCovered` shows how many metrics were available for that content type; if this is below 3, interpret banding with caution.

```{r b2-strength-matrix-table}
strength_matrix_table <- bundle_b_content_position_overall_table(content_position)

DTSettings(
  strength_matrix_table,
  class = "display stripe hover",
  scroll_x = TRUE,
  percent_cols = c(
    "ViewsMedianPercentile",
    "RevenueMedianPercentile",
    "EngagementMedianPercentile",
    "AvgMedianPercentile"
  )
)
```

```{r bundle-b-strength-summary-text, results='asis'}
bundle_b_emit_interpretation("02_category_strengths_and_weaknesses/06_distribution_based_strength_weakness_summary_by_content_type")
```

## Why Content Attributes Matter for Engagement Outcomes
This section moves from format-level performance to creative levers.
By breaking performance down by collaboration, topic, and tag attributes, the report helps identify what to scale, what to refine, and what to test next.

```{r bundle-b-section-03-synthesis, results='asis'}
bundle_b_emit_interpretation("03_content_attributes_matter_for_engagement_outcomes/00_section_synthesis")
```

### Collaboration Distribution vs Non-Collaborative Baseline

**What this plot does:**
- Shows per-video distributions for collaborative vs non-collaborative uploads (box + whisker + points).
- Shows each group's mean and directly connects those means to make the collaborative delta explicit.

**What this adds vs Bundle A:**
- Bundle A shows absolute collaboration effectiveness levels.
- Bundle B adds a baseline-change lens to support decision framing: *how much does collaboration change outcomes vs non-collab baseline?*

**How to read it:**
- Each point is one video; box shows quartiles/median spread.
- Diamond markers are group means (non-collab vs collaborative).
- Connector line links those two means; center label reports `absolute delta` and `% change` vs non-collab baseline.

**Method notes:**
- This is a **descriptive estimate**, not a causal effect.
- Baseline is non-collaborative average in the same dataset.
- Views and revenue can be based on different row counts, so read both metrics together.

```{r b2-collaboration-lift-plot, fig.width=11, fig.height=9}
collab_summary <- collaboration_effectiveness_prep(analytics, monetary)
collab_dist <- bundle_b_collaboration_distribution_prep(analytics, monetary)

bundle_b_ggplotly(
  bundle_b_collaboration_lift_plot(
    collab_dist,
    Talent
  )
) %>%
  bundle_b_plotly_layout(margin_l = 170, margin_r = 35)
```

```{r b2-collaboration-table}
base_views <- collab_summary$AverageViewsPerVideo[collab_summary$collab_group == "Non-collaborative"][1]
base_revenue <- collab_summary$AverageRevenuePerVideo[collab_summary$collab_group == "Non-collaborative"][1]

collab_table <- collab_summary %>%
  mutate(
    ViewsDeltaVsNonCollab = AverageViewsPerVideo - base_views,
    RevenueDeltaVsNonCollab = AverageRevenuePerVideo - base_revenue
  ) %>%
  select(
    collab_group,
    VideoCountViews,
    VideoCountRevenue,
    TotalViews,
    TotalRevenue,
    AverageViewsPerVideo,
    AverageRevenuePerVideo,
    ViewsDeltaVsNonCollab,
    RevenueDeltaVsNonCollab,
    AvgViewsLiftVsNonCollab,
    AvgRevenueLiftVsNonCollab
  )

DTSettings(
  collab_table,
  class = "display stripe hover",
  scroll_x = TRUE,
  percent_cols = c("AvgViewsLiftVsNonCollab", "AvgRevenueLiftVsNonCollab")
)
```

```{r bundle-b-collaboration-text, results='asis'}
bundle_b_emit_interpretation("03_content_attributes_matter_for_engagement_outcomes/01_collaboration_distribution_vs_non_collaborative_baseline")
```

### Topic View Distribution
**What this plot does:**
- Shows the distribution of per-video views within top topics, rather than only topic totals.

**How to read it:**
- Compare medians and spread across topics to distinguish stable performance from outlier-driven performance.

```{r b2-topic-view-distribution-plot, fig.width=12, fig.height=9}
topic_view_dist <- topic_view_distribution_prep(
  analytics,
  top_n = 8,
  min_videos = 2
)

bundle_b_ggplotly(
  bundle_b_topic_view_distribution_plot(
    topic_view_dist,
    Talent
  )
)
```

```{r b2-topic-view-distribution-table}
DTSettings(topic_view_dist$summary, class = "display stripe hover", scroll_x = TRUE)
```

```{r bundle-b-topic-text, results='asis'}
bundle_b_emit_interpretation("03_content_attributes_matter_for_engagement_outcomes/02_topic_view_distribution")
```

### Tag View Distribution
**What this plot does:**
- Shows the distribution of per-video views within top tags for finer-grain content attributes.

**How to read it:**
- Compare medians, quartiles, and range across tags to see which tags are more consistently strong.

```{r b2-tag-view-distribution-plot, fig.width=12, fig.height=9}
tag_view_dist <- tag_view_distribution_prep(
  analytics,
  top_n = 15,
  min_videos = 2,
  min_views_per_video = 10
)

bundle_b_ggplotly(
  bundle_b_tag_view_distribution_plot(
    tag_view_dist,
    Talent
  )
)
```

```{r b2-tag-view-distribution-table}
DTSettings(tag_view_dist$summary, class = "display stripe hover", scroll_x = TRUE)
```

```{r bundle-b-tag-text, results='asis'}
bundle_b_emit_interpretation("03_content_attributes_matter_for_engagement_outcomes/03_tag_view_distribution")
```

## Why Scheduling Effects Matter for Publishing Decisions
This section isolates timing effects so publishing cadence can be tuned with evidence.
The goal is to show whether weekday patterns and weekend/weekday differences create meaningful upside or downside on a per-video basis.

```{r bundle-b-section-04-synthesis, results='asis'}
bundle_b_emit_interpretation("04_scheduling_effects_matter_for_publishing_decisions/00_section_synthesis")
```

### Day-of-Week Deviation from Average
**What this plot does:**
- Shows how far each weekday is above or below the overall weekday average.

**How to read it:**
- Values above `0` are above-average days.
- Values below `0` are below-average days.
- This is not a z-score.
- Formula: `Deviation = weekday average - overall weekday average`.
- Top panel is views deviation; bottom panel is revenue deviation.

```{r b2-dow-lift-plot, fig.width=10, fig.height=8}
dow_summary <- day_of_week_performance_prep(analytics, monetary)

bundle_b_ggplotly(
  bundle_b_day_of_week_lift_plot(
    dow_summary,
    Talent
  )
)
```

**Day-of-week table calculation notes:**
- `AverageViewsPerVideo` = average per-video views for that weekday.
- `AverageRevenuePerVideo` = average per-video revenue for that weekday.
- `ViewsDeviation` = `AverageViewsPerVideo - OverallAverageViewsPerVideo`.
- `RevenueDeviation` = `AverageRevenuePerVideo - OverallAverageRevenuePerVideo`.
- The overall baseline columns are used for calculation but intentionally hidden from this display table.

```{r b2-dow-table}
dow_deviation_table <- bundle_b_day_of_week_deviation_table(dow_summary)
dow_deviation_display <- dow_deviation_table %>%
  dplyr::transmute(
    day_of_week = .data$day_of_week,
    AverageViewsPerVideo = .data$AverageViewsPerVideo,
    ViewsDeviation = .data$ViewsDeviation,
    AverageRevenuePerVideo = .data$AverageRevenuePerVideo,
    RevenueDeviation = .data$RevenueDeviation
  )

DTSettings(dow_deviation_display, class = "display stripe hover", scroll_x = TRUE)
```

```{r bundle-b-day-of-week-text, results='asis'}
bundle_b_emit_interpretation("04_scheduling_effects_matter_for_publishing_decisions/01_day_of_week_deviation_from_average")
```

### Weekend vs Weekday Summary
**What this plot does:**
- Shows per-video distributions for weekday vs weekend uploads (box + whisker + points).
- Shows each group's mean and directly connects those means to make the weekend delta explicit.

**How to read it:**
- Each point is one video; box shows quartiles/median spread.
- Diamond markers are group means (weekday vs weekend).
- Connector line links those two means; center label reports `absolute delta` and `% change` vs weekday baseline.

**Method notes:**
- This is a **descriptive estimate**, not a causal effect.
- Baseline is weekday average in the same dataset.
- Views and revenue can be based on different row counts, so read both metrics together.

```{r b2-weekend-weekday-distribution-plot, fig.width=11, fig.height=9}
wk_dist <- weekend_vs_weekday_distribution_prep(analytics, monetary)

bundle_b_ggplotly(
  bundle_b_weekend_weekday_distribution_plot(
    wk_dist,
    Talent
  )
) %>%
  bundle_b_plotly_layout(margin_l = 170, margin_r = 35)
```

```{r b2-weekend-table}
wk_summary <- weekend_vs_weekday_prep(analytics, monetary)
DTSettings(wk_summary, class = "display stripe hover", scroll_x = TRUE)
```

```{r bundle-b-weekend-text, results='asis'}
bundle_b_emit_interpretation("04_scheduling_effects_matter_for_publishing_decisions/02_weekend_vs_weekday_summary")
```

# How to Turn These Findings into Action

Use the retention and strength/weakness sections to prioritize content types to scale, then use topic/tag/collaboration/scheduling sections to tune execution for higher engagement and monetization efficiency.

```{r bundle-b-action-synthesis, results='asis'}
bundle_b_emit_interpretation("05_turn_findings_into_action/00_section_synthesis")
```

# Wrap-up and Conclusion

```{r bundle-b-conclusion, results='asis'}
bundle_b_emit_interpretation("06_report_bookends/02_conclusion")
```
