---
title: "Bundle G: Topic-by-Weekday Recommendations"
format:
  html:
    code-fold: false
    df-print: paged
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
params:
  talent: "Ava"
  data_source: "datalake"
  data_root: null
  render_generated_at: null
  included_date_range: "All available dates"
  render_cli: ""
  render_output_dir: null
  render_output_prefix: "Bundle_G"
  window_days: null
  start_date: null
  end_date: null
  reference_day: "Monday"
  content_types:
    - live
    - video
    - short
---

```{r}
#| label: setup
#| include: false

knitr::opts_knit$set(root.dir = normalizePath(file.path(getwd()), winslash = "/", mustWork = FALSE))

library(here)
library(dplyr)
library(DT)
library(ggplot2)
library(purrr)

`%||%` <- function(x, y) {
  if (is.null(x) || length(x) == 0 || (length(x) == 1 && !nzchar(x))) y else x
}

source(here::here("r_scripts", "lib", "utils", "source_dir.r"))
source(here::here("r_scripts", "lib", "utils", "staging_root.R"))
source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "utils", "talent_select.R"))
source(here::here("r_scripts", "lib", "import_data", "talent_files.R"))
source(here::here("r_scripts", "lib", "clean_data", "CleanData.R"))
source(here::here("r_scripts", "lib", "clean_data", "title_classification_join.R"))
source(here::here("r_scripts", "lib", "plots", "PlottingThemes.R"))
source(here::here("r_scripts", "lib", "utils", "content_type_utils.R"))
source(here::here("r_scripts", "lib", "linear_regression", "day_of_week", "weekday_transform.R"))
source(here::here("r_scripts", "lib", "linear_regression", "day_of_week", "report_helpers.R"))
source(here::here("r_scripts", "lib", "linear_regression", "day_of_week", "topic_weekday_recommendations.R"))

bundle_g_datatable <- function(df, caption, page_length = 10) {
  DT::datatable(
    df,
    rownames = FALSE,
    caption = caption,
    options = list(
      dom = "tip",
      pageLength = page_length,
      scrollX = TRUE
    )
  )
}

bundle_g_summary_datatable <- function(df, caption, page_length = 20) {
  bundle_g_datatable(df, caption, page_length = page_length) %>%
    DT::formatRound(
      columns = intersect(
        c(
          "mean_views",
          "median_views",
          "median_log_views",
          "min_views",
          "max_views",
          "predicted_views",
          "second_best_predicted_views",
          "predicted_view_gap"
        ),
        names(df)
      ),
      digits = 2,
      mark = ","
    )
}

bundle_g_topic_heatmap <- function(summary_df, content_label) {
  plot_theme <- if (exists("theme_nyt", mode = "function")) {
    theme_nyt()
  } else {
    ggplot2::theme_minimal()
  }

  ggplot2::ggplot(
    summary_df,
    ggplot2::aes(
      x = .data$publish_wday,
      y = .data$topic_lumped,
      fill = .data$median_views
    )
  ) +
    ggplot2::geom_tile(color = "white") +
    ggplot2::geom_text(ggplot2::aes(label = .data$streams), size = 3) +
    ggplot2::scale_fill_viridis_c(option = "C", labels = scales::comma) +
    ggplot2::labs(
      x = "Publish weekday",
      y = "Topic",
      fill = "Median views",
      title = paste("Observed median views by", tolower(content_label), "topic and weekday"),
      subtitle = "Tile color is observed median views; labels are stream counts."
    ) +
    plot_theme +
    ggplot2::theme(
      axis.text.x = ggplot2::element_text(angle = 45, hjust = 1, vjust = 1)
    )
}

resolve_bundle_g_data_root <- function(data_source, data_root) {
  if (!is.null(data_root) && nzchar(trimws(data_root))) {
    return(normalizePath(data_root, winslash = "/", mustWork = FALSE))
  }
  if (identical(tolower(data_source), "datalake")) {
    return(normalizePath(get_datalake_root(), winslash = "/", mustWork = FALSE))
  }
  normalizePath(get_staging_root(), winslash = "/", mustWork = FALSE)
}

apply_bundle_g_publish_window <- function(df, start_date, end_date) {
  if (!("publish_date" %in% names(df))) {
    return(df)
  }
  if (!is.null(start_date) && nzchar(start_date)) {
    df <- df %>% dplyr::filter(.data$publish_date >= as.Date(start_date))
  }
  if (!is.null(end_date) && nzchar(end_date)) {
    df <- df %>% dplyr::filter(.data$publish_date <= as.Date(end_date))
  }
  df
}

canonical_bundle_g_content_types <- function(x) {
  if (is.null(x) || length(x) == 0) {
    return(c("live", "video", "short"))
  }
  x <- tolower(trimws(as.character(unlist(x))))
  x <- x[nzchar(x)]
  x <- dplyr::recode(
    x,
    videos = "video",
    shorts = "short",
    all = "all",
    .default = x
  )
  if ("all" %in% x) {
    return(c("live", "video", "short"))
  }
  unique(x)
}

build_bundle_g_content_results <- function(content_df, reference_day = "Monday") {
  topic_df <- content_df %>%
    dow_prep(reference_day = reference_day) %>%
    topic_clean(min_topic_n = 3)

  topic_counts <- topic_df %>%
    dplyr::count(.data$topic_lumped, sort = TRUE, name = "streams")

  topic_weekday <- topic_weekday_summary(topic_df)
  observed_best <- observed_best_weekday_by_topic(topic_weekday, min_streams = 2)
  models <- fit_topic_day_models(topic_df)
  model_check <- model_comparison(models)
  recommendations <- model_recommend_weekday_by_topic(topic_df, models)

  recommendation_summary <- recommendations %>%
    dplyr::transmute(
      topic = .data$topic_lumped,
      recommended_day = .data$recommended_weekday,
      predicted_views = round(.data$predicted_views, 0),
      second_best_day = .data$second_best_weekday,
      second_best_predicted_views = round(.data$second_best_predicted_views, 0),
      predicted_view_gap = round(.data$predicted_view_gap, 0),
      observed_streams_for_topic_day = .data$observed_streams_for_topic_day,
      total_topic_streams = .data$total_topic_streams,
      recommendation_strength = .data$recommendation_strength,
      recommendation_note = .data$recommendation_note
    )

  schedule_by_day <- recommendations %>%
    dplyr::transmute(
      weekday = .data$recommended_weekday,
      topic = .data$topic_lumped,
      predicted_views = round(.data$predicted_views, 0),
      recommendation_strength = .data$recommendation_strength,
      recommendation_note = .data$recommendation_note
    ) %>%
    dplyr::arrange(.data$weekday, dplyr::desc(.data$predicted_views))

  list(
    topic_df = topic_df,
    topic_counts = topic_counts,
    topic_weekday = topic_weekday,
    observed_best = observed_best,
    models = models,
    model_check = model_check,
    recommendations = recommendations,
    recommendation_summary = recommendation_summary,
    schedule_by_day = schedule_by_day
  )
}

data_root <- resolve_bundle_g_data_root(params$data_source, params$data_root)
talent_path <- select_talent(params$talent, root = data_root)
talent_folder <- basename(talent_path)
title_classifications <- load_title_classifications(talent = talent_folder)
talent_files <- TalentFiles(talent_path)[[1]]

required_video_types <- c("video_analytics", "video_monetary")
missing_video_exports <- setdiff(required_video_types, names(talent_files))
if (length(missing_video_exports) > 0L) {
  stop(
    "Missing required video export(s) for ",
    talent_folder,
    ": ",
    paste(missing_video_exports, collapse = ", ")
  )
}

stream_data <- video_preps_with_titles(
  files = talent_files,
  titles = title_classifications,
  talent = talent_folder,
  dedupe = TRUE
)

stream_video_level <- stream_data$analytics %>%
  dplyr::select(-dplyr::any_of(c("Estimated Revenue", "CPM"))) %>%
  dplyr::left_join(
    stream_data$monetary %>%
      dplyr::select(
        dplyr::all_of("Video ID"),
        dplyr::any_of(c("Estimated Revenue", "CPM"))
      ),
    by = "Video ID"
  ) %>%
  dplyr::mutate(talent_name = talent_folder) %>%
  apply_bundle_g_publish_window(params$start_date, params$end_date)

content_types <- canonical_bundle_g_content_types(params$content_types)
available_content_types <- sort(unique(tolower(trimws(as.character(stream_video_level$`Content Type`)))))
content_types <- intersect(content_types, available_content_types)
if (length(content_types) == 0L) {
  stop("No requested content types are available after filtering.")
}

content <- purrr::map(
  content_types,
  ~ stream_video_level %>%
    dplyr::filter(tolower(trimws(as.character(.data$`Content Type`))) == .x)
)
names(content) <- content_types
```

```{r report_layout_style, results='asis'}
cat(
  "<style>
  .main-container {
    max-width: 1200px !important;
  }
  .dataTables_wrapper {
    width: 100%;
    max-width: 100%;
  }
  .dataTables_wrapper .dataTables_scroll {
    overflow-x: auto;
  }
  table.dataTable {
    width: 100% !important;
  }
  </style>"
)
```

## Report Scope

Bundle G extends Bundle F's weekday analysis by asking a more specific scheduling question: **which topics appear most promising on which weekdays?** Each requested content type is analyzed separately. The report combines descriptive historical topic-day performance with a simple model of logged views, then translates the model predictions into topic-day recommendations with evidence-strength labels.

```{r report_scope}
bundle_g_datatable(
  tibble::tibble(
    field = c(
      "Talent",
      "Data source",
      "Data root",
      "Included publish date range",
      "Reference weekday",
      "Content types",
      "Generated"
    ),
    value = c(
      talent_folder,
      params$data_source,
      data_root,
      params$included_date_range,
      params$reference_day,
      paste(dow_report_content_label(content_types), collapse = ", "),
      params$render_generated_at %||% as.character(Sys.time())
    )
  ),
  "Bundle G render scope",
  page_length = 7
)
```

```{r content_type_overview}
stream_video_level %>%
  dplyr::count(`Content Type`, name = "videos") %>%
  dplyr::arrange(`Content Type`) %>%
  bundle_g_datatable("Available content by type", page_length = 10)
```

## Method Overview

The outcome is `log_views`, created as `log1p(views)`, or `log(views + 1)`. Logged views are used because stream view counts are usually skewed: a few unusually large streams can dominate averages on the raw view scale. Modeling logged views reduces the influence of extreme streams while still allowing the final predictions to be back-transformed into approximate view counts for planning.

The report uses linear regression rather than a standalone ANOVA because the goal is not only to test whether groups differ. Bundle G needs predicted values for every topic-weekday combination so it can rank possible scheduling choices. ANOVA with categorical predictors is mathematically part of the same linear-model family; the regression form makes it easier to include multiple categorical predictors, hold other predictors steady, and generate recommendation tables.

Categorical variables such as publish weekday and topic enter the model as indicator variables. One level becomes the reference category, and the model estimates each other level as a difference from that reference while the other predictors are held constant. The additive model, `log_views ~ publish_wday + topic_lumped`, estimates generally stronger weekdays and generally stronger topics. The interaction model, `log_views ~ publish_wday * topic_lumped`, estimates whether specific topics perform differently on specific weekdays. When the interaction model is too sparse or unstable, the recommendation system falls back to a simpler model and labels the recommendations more cautiously.

```{r content_sections, results='asis'}
for (content_type in names(content)) {
  content_df <- content[[content_type]]
  content_label <- dow_report_content_label(content_type)

  if (nrow(content_df) == 0L) {
    next
  }

  content_results <- build_bundle_g_content_results(
    content_df,
    reference_day = params$reference_day
  )

  cat("\n\n# ", dow_report_content_title(content_type), "\n\n", sep = "")
  cat(
    "This section analyzes ",
    tolower(content_label),
    " only. It first documents topic coverage and observed historical topic-day performance, ",
    "then shows model diagnostics, and finally presents the model-informed scheduling recommendations.\n\n",
    sep = ""
  )

  cat("\n\n## Topic Coverage\n\n")
  print(bundle_g_datatable(
    content_results$topic_counts,
    paste0(content_label, ": topic coverage"),
    page_length = 15
  ))

  cat("\n\n## Observed Historical Best Days\n\n")
  cat(
    "This table is descriptive. It selects the highest observed median-view weekday for each topic ",
    "among topic/day cells with at least two streams. The final recommendation table below is model-informed ",
    "and should be treated as the primary scheduling output.\n\n",
    sep = ""
  )
  print(bundle_g_summary_datatable(
    content_results$observed_best,
    paste0(content_label, ": observed historical best weekdays by topic"),
    page_length = 15
  ))

  cat("\n\n## Weekday By Topic Detail\n\n")
  print(bundle_g_summary_datatable(
    content_results$topic_weekday,
    paste0(content_label, ": weekday by topic detail"),
    page_length = 20
  ))

  cat("\n\n## Quick Model Check\n\n")
  cat(
    "Lower AIC indicates better relative fit among the models compared, while adjusted R-squared gives a rough ",
    "sense of explanatory power after accounting for model size. This check helps decide whether topic adds signal ",
    "beyond weekday alone. The final recommendation model is selected by stability and recommendation usefulness, ",
    "not by AIC alone.\n\n",
    sep = ""
  )
  print(bundle_g_datatable(
    content_results$model_check,
    paste0(content_label, ": day-only vs topic-aware model comparison"),
    page_length = 10
  ) %>%
    DT::formatRound(
      columns = c("adj_r_squared", "aic", "residual_standard_error"),
      digits = 3
    ))

  cat("\n\n## Topic-Day Heatmap\n\n")
  print(bundle_g_topic_heatmap(content_results$topic_weekday, content_label))

  cat("\n\n## Final Topic-Day Recommendations\n\n")
  cat(
    "This table is the primary scheduling output. Each row gives the recommended weekday for a topic. ",
    "Predicted views come from the selected log-view model and have been back-transformed into the original ",
    "view-count scale. Recommendation strength indicates whether the recommendation is strong, tentative, ",
    "exploratory, or not topic-specific.\n\n",
    sep = ""
  )
  print(bundle_g_datatable(
    content_results$recommendation_summary,
    paste0(content_label, ": simplified topic-day recommendations"),
    page_length = 20
  ))

  cat("\n\n## Recommended Topics By Weekday\n\n")
  cat(
    "This table answers the planning question: if a stream is happening on a given weekday, ",
    "which topics look most promising?\n\n",
    sep = ""
  )
  print(bundle_g_datatable(
    content_results$schedule_by_day,
    paste0(content_label, ": recommended topics by weekday"),
    page_length = 20
  ))

  cat("\n\n## Detailed Model-Informed Recommendation Diagnostics\n\n")
  print(bundle_g_summary_datatable(
    content_results$recommendations,
    paste0(content_label, ": detailed model-informed recommendation diagnostics"),
    page_length = 20
  ))

  cat(
    "\n\nThe recommendation table should be read as a scheduling guide, not as proof that a weekday causes higher viewership. ",
    "The model estimates expected logged views for each topic-weekday combination and then ranks weekdays within each topic. ",
    "Strong recommendations are based on repeated historical observations and a meaningful predicted gap over the second-best weekday. ",
    "Tentative or exploratory recommendations should be treated as hypotheses to test in future streams rather than firm conclusions.\n\n",
    sep = ""
  )
}
```
