---
title: "Subtitle Speaker-Change Feasibility Test"
subtitle: "PALACE PURGE and DeBERTa NLI"
format:
  html:
    toc: true
    code-fold: show
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

## Question

Can the existing `MoritzLaurer/DeBERTa-v3-base-mnli-fever-anli` model infer
whether the speaker changed between two adjacent reconstructed subtitle
sentences?

This is a small, read-only feasibility test. It does not create a dataset,
publish results, or modify subtitle reconstruction.

## Read the source sentences

The test reads the published `subtitle_sentence_v2` rows for PALACE PURGE
(`rp34cYzfLic`) and closes DuckDB immediately. The selected boundaries include
two explicit `>>` transitions, four likely missing transitions, and two
same-speaker controls.

```{r}
library(DBI)
library(here)
library(knitr)

source(here::here("r_scripts", "lib", "utils", "repo_env.R"))
source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "duckdb", "db_connect.R"))

load_repo_env(repo_root = here::here())
con <- duckdb_connect(db_path = talent_lakehouse_db_path(), read_only = TRUE)

sentences <- DBI::dbGetQuery(
  con,
  paste(
    "SELECT sentence_number, speaker_turn_id, speaker_change, sentence_text",
    "FROM text.subtitle_sentence_units",
    "WHERE video_id = 'rp34cYzfLic'",
    "AND pipeline_version = 'subtitle_sentence_v2'",
    "AND sentence_number IN (1, 2, 5, 6, 7, 14, 15, 25, 26, 33, 34, 42, 43, 48, 49)",
    "ORDER BY sentence_number"
  )
)

DBI::dbDisconnect(con, shutdown = TRUE)
rm(con)

knitr::kable(sentences)
```

## Test cases

Each pair was scored with one sentence of context before and after it. A pair
was classified only when the winning entailment score was at least 0.60 and
exceeded the competing entailment score by at least 0.20. Otherwise the result
was `uncertain`.

```{r}
results <- data.frame(
  boundary = c("42→43", "48→49", "5→6", "6→7", "14→15", "25→26", "1→2", "33→34"),
  evidence = c(
    "known >>", "known >>",
    "likely missing", "likely missing", "likely missing", "likely missing",
    "same-speaker control", "same-speaker control"
  ),
  expected = c(
    rep("speaker_change", 6),
    rep("same_speaker", 2)
  ),
  same_entailment = c(0.9863, 0.9731, 0.9561, 0.9785, 0.9790, 0.9653, 0.9839, 0.9790),
  same_neutral = c(0.0019, 0.0034, 0.0049, 0.0034, 0.0025, 0.0088, 0.0014, 0.0046),
  same_contradiction = c(0.0117, 0.0235, 0.0388, 0.0179, 0.0185, 0.0258, 0.0147, 0.0166),
  change_entailment = c(0.9780, 0.9683, 0.9834, 0.9785, 0.9604, 0.8960, 0.9756, 0.9780),
  change_neutral = c(0.0145, 0.0230, 0.0082, 0.0113, 0.0209, 0.0961, 0.0129, 0.0155),
  change_contradiction = c(0.0072, 0.0086, 0.0082, 0.0100, 0.0185, 0.0082, 0.0114, 0.0062)
)

results$entailment_margin <- abs(
  results$same_entailment - results$change_entailment
)
results$derived <- ifelse(
  pmax(results$same_entailment, results$change_entailment) >= 0.60 &
    results$entailment_margin >= 0.20,
  ifelse(
    results$same_entailment > results$change_entailment,
    "same_speaker",
    "speaker_change"
  ),
  "uncertain"
)

display_results <- results
numeric_columns <- vapply(display_results, is.numeric, logical(1))
display_results[numeric_columns] <- lapply(
  display_results[numeric_columns],
  round,
  digits = 4
)
knitr::kable(display_results)
```

The hypotheses were:

- `The same person is speaking in Sentence A and Sentence B.`
- `A different person is speaking in Sentence B.`

The model ran from the existing pinned snapshot through the deployed
`ModelManager` on `cuda:0`. Loading took 3.28 seconds. Scoring the 16 hypothesis
pairs for these eight boundaries in one batch took 0.36 seconds.

## What the test shows

The model did not reliably recognize known speaker changes. Both explicit
`>>` examples were `uncertain`, and their raw entailment ranking slightly
favored `same_speaker`, which is wrong.

It also did not reliably identify the likely missing changes. The clearest
positive example was sentence 5→6:

> **A:** I might as well ask: Do I look [music] like her keeper?<br>
> **B:** I thought that was your job, Hawthorne.

The change hypothesis ranked higher, but only by 0.0273, far below a useful
decision margin. Sentence 6→7 produced identical entailment scores for both
hypotheses. Sentences 14→15 and 25→26 incorrectly favored `same_speaker`.

The two same-speaker controls ranked `same_speaker` slightly higher, so those
rankings were directionally correct. Their margins were only 0.0083 and
0.0010, however, and cannot support confident decisions.

Neutral scores do **not** dominate. The problem is more serious: entailment is
above 0.89 for both mutually exclusive hypotheses in every displayed case.
The model responds to the fluent meta-statements as entailed even when the
subtitle text does not establish who spoke either sentence.

## Recommendation

This formulation is not promising enough to add to production. DeBERTa's raw
scores are not calibrated evidence for subtitle speaker changes, and lowering
the threshold would create arbitrary changes from tiny score differences.

The other small models already in the inference stack are trained for entity
extraction, embeddings, sentiment, question answering, summarization,
punctuation, or search reranking. None is a better direct speaker-change
classifier. In particular, the MiniLM reranker measures relevance rather than
dialogue identity. The next experiment should use a model that can explicitly
reason over dialogue turns; swapping to another existing small task model is
unlikely to improve this test.

No production code, DuckDB data, schemas, or publication logic was changed.
