---
title: "Qwen 3B Subtitle Speaker-Change Feasibility Test"
subtitle: "Comparison with the Qwen 1.5B few-shot baseline"
format:
  html:
    toc: true
    code-fold: show
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

## Question

Does `Qwen/Qwen2.5-3B-Instruct` improve on the 6/8 Qwen 1.5B few-shot
baseline when both models use the same prompt and PALACE PURGE boundaries?

This test uses deterministic text generation rather than label scoring. It is
read-only and does not publish speaker changes.

## Source sentences

The test reads the same eight reconstructed boundaries used by
`qwen_feasibility.qmd` and closes DuckDB immediately.

```{r}
library(DBI)
library(here)
library(knitr)

source(here::here("r_scripts", "lib", "utils", "repo_env.R"))
source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "duckdb", "db_connect.R"))

load_repo_env(repo_root = here::here())
con <- duckdb_connect(db_path = talent_lakehouse_db_path(), read_only = TRUE)
sentences <- DBI::dbGetQuery(
  con,
  paste(
    "SELECT sentence_number, speaker_turn_id, speaker_change, sentence_text",
    "FROM text.subtitle_sentence_units",
    "WHERE video_id = 'rp34cYzfLic'",
    "AND pipeline_version = 'subtitle_sentence_v2'",
    "AND sentence_number IN (1, 2, 5, 6, 7, 14, 15, 25, 26, 33, 34, 42, 43, 48, 49)",
    "ORDER BY sentence_number"
  )
)
DBI::dbDisconnect(con, shutdown = TRUE)
rm(con)

knitr::kable(sentences)
```

## Method

Qwen 3B received the same previous context, Sentence A, Sentence B, following
context, label definitions, and two few-shot examples as the 1.5B generation
test. Generation used `temperature = 0`, `max_new_tokens = 8`, and accepted
only these exact outputs:

- `same_speaker`
- `speaker_change`
- `uncertain`

The model was loaded from pinned local revision
`aa8e72537993ba99e69dfaafa59ed015b17504d1`. No score-based classification was
used.

## Results

```{r}
results <- data.frame(
  boundary = c("42→43", "48→49", "5→6", "6→7", "14→15", "25→26", "1→2", "33→34"),
  evidence = c(
    "known >>", "known >>",
    rep("likely missing", 4),
    rep("same-speaker control", 2)
  ),
  expected = c(rep("speaker_change", 6), rep("same_speaker", 2)),
  qwen_1_5b = c(
    "speaker_change", "speaker_change", "speaker_change", "same_speaker",
    "same_speaker", "speaker_change", "same_speaker", "same_speaker"
  ),
  qwen_3b = c(
    "speaker_change", "speaker_change", "speaker_change", "speaker_change",
    "same_speaker", "speaker_change", "same_speaker", "same_speaker"
  ),
  inference_seconds_3b = c(
    15.4548, 2.2615, 2.2901, 2.2456,
    2.8952, 2.2534, 2.9255, 2.8416
  )
)
results$matched_1_5b <- results$expected == results$qwen_1_5b
results$matched_3b <- results$expected == results$qwen_3b

knitr::kable(results, digits = 4)
```

```{r}
accuracy <- aggregate(
  cbind(matched_1_5b, matched_3b) ~ evidence,
  data = results,
  FUN = sum
)
counts <- table(results$evidence)
accuracy$total <- as.integer(counts[accuracy$evidence])
accuracy$qwen_1_5b <- sprintf(
  "%d/%d (%.0f%%)",
  accuracy$matched_1_5b,
  accuracy$total,
  100 * accuracy$matched_1_5b / accuracy$total
)
accuracy$qwen_3b <- sprintf(
  "%d/%d (%.0f%%)",
  accuracy$matched_3b,
  accuracy$total,
  100 * accuracy$matched_3b / accuracy$total
)
overall <- data.frame(
  evidence = "overall",
  qwen_1_5b = "6/8 (75%)",
  qwen_3b = "7/8 (88%)"
)

knitr::kable(rbind(
  accuracy[, c("evidence", "qwen_1_5b", "qwen_3b")],
  overall
))
```

## Runtime and GPU memory

| Measurement | Qwen 3B |
|---|---:|
| Cold model load | 21.04 seconds |
| Mean across all eight generations | 4.15 seconds |
| Mean after first-generation warm-up | 2.53 seconds |
| GPU memory before load | 3 MiB |
| GPU memory after load | 1,849 MiB |
| Peak sampled GPU memory | 1,967 MiB |

The first generation took 15.45 seconds because it included one-time runtime
warm-up after the measured model load. Qwen 3B used FP16 with part of the model
offloaded to system RAM to fit the 3 GiB GPU.

## Assessment

Qwen 3B improves overall accuracy from 6/8 to 7/8. It preserves both known
changes and both same-speaker controls while improving likely missing changes
from 2/4 to 3/4.

The improvement is boundary 6→7, which 1.5B classified as `same_speaker` and
3B correctly classified as `speaker_change`. Boundary 14→15 remains the only
error: both models classify it as `same_speaker`.

This small result favors Qwen 3B, although eight boundaries are insufficient
for a production decision. No subtitle pipeline, DuckDB data, schemas, or
publication logic was changed.
