---
title: "Qwen Subtitle Speaker-Change Few-Shot Test"
subtitle: "PALACE PURGE comparison with the initial Qwen prompt"
format:
  html:
    toc: true
    code-fold: show
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

## Question

Does one clear example of each class remove Qwen's initial
`speaker_change` bias on the same eight PALACE PURGE boundaries?

This is a read-only experiment. It does not publish speaker changes or alter
subtitle reconstruction.

## Source sentences

The notebook reads the same reconstructed sentences used in
`deberta_feasibility.qmd` and closes DuckDB immediately.

```{r}
library(DBI)
library(here)
library(knitr)

source(here::here("r_scripts", "lib", "utils", "repo_env.R"))
source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "duckdb", "db_connect.R"))

load_repo_env(repo_root = here::here())
con <- duckdb_connect(db_path = talent_lakehouse_db_path(), read_only = TRUE)

sentences <- DBI::dbGetQuery(
  con,
  paste(
    "SELECT sentence_number, speaker_turn_id, speaker_change, sentence_text",
    "FROM text.subtitle_sentence_units",
    "WHERE video_id = 'rp34cYzfLic'",
    "AND pipeline_version = 'subtitle_sentence_v2'",
    "AND sentence_number IN (1, 2, 5, 6, 7, 14, 15, 25, 26, 33, 34, 42, 43, 48, 49)",
    "ORDER BY sentence_number"
  )
)

DBI::dbDisconnect(con, shutdown = TRUE)
rm(con)

knitr::kable(sentences)
```

## API behavior

`POST /v1/subtitle-speaker-change` is unchanged. It accepts
`previous_context`, `sentence_a`, `sentence_b`, and `following_context`. The
fixed internal instruction now defines all three labels and gives one
`same_speaker` and one `speaker_change` example:

```text
same_speaker: Sentence B continues the same person's thought, explanation,
story, or statement.

speaker_change: Sentence B is a response, interruption, question/answer
reversal, direct reply, or otherwise appears to come from another participant.

uncertain: There is not enough textual evidence to decide.

Example:
A: I'm sure you're wondering where I've been.
B: Don't worry, I'm safe.
Answer: same_speaker

Example:
A: I thought that was your job, Hawthorne.
B: Yes, that is my job.
Answer: speaker_change
```

The endpoint now scores those three exact label continuations. It takes the
mean token log probability for each label, then normalizes the three values
into relative probabilities. This avoids favoring `uncertain` merely because
it contains fewer tokens. The response `result` is exactly one of:

- `same_speaker`
- `speaker_change`
- `uncertain`

The highest-scoring label is returned when its lead over the second label is
at least `min_margin`. Otherwise the result is `uncertain`. This run uses the
default `min_margin = 0.10`; callers can configure it from 0 to 1.

## Results

```{r}
results <- data.frame(
  boundary = c("42→43", "48→49", "5→6", "6→7", "14→15", "25→26", "1→2", "33→34"),
  evidence = c(
    "known >>", "known >>",
    rep("likely missing", 4),
    rep("same-speaker control", 2)
  ),
  expected = c(rep("speaker_change", 6), rep("same_speaker", 2)),
  initial_result = rep("speaker_change", 8),
  few_shot_result = c(
    "speaker_change", "speaker_change", "speaker_change", "same_speaker",
    "same_speaker", "speaker_change", "same_speaker", "same_speaker"
  ),
  same_score = c(
    0.6597, 0.5225, 0.4280, 0.6128,
    0.9282, 0.4194, 0.6860, 0.5254
  ),
  change_score = c(
    0.3188, 0.4202, 0.5601, 0.3757,
    0.0656, 0.4773, 0.2391, 0.4229
  ),
  uncertain_score = c(
    0.0217, 0.0573, 0.0120, 0.0112,
    0.0062, 0.1032, 0.0746, 0.0517
  ),
  score_margin = c(
    0.3408, 0.1023, 0.1321, 0.2371,
    0.8627, 0.0579, 0.4469, 0.1025
  ),
  score_result = c(
    "same_speaker", "same_speaker", "speaker_change", "same_speaker",
    "same_speaker", "uncertain", "same_speaker", "same_speaker"
  )
)
results$initial_matched <- results$expected == results$initial_result
results$few_shot_matched <- results$expected == results$few_shot_result
results$score_matched <- results$expected == results$score_result

comparison <- results[, c(
  "boundary", "evidence", "expected", "initial_result", "few_shot_result",
  "score_result", "score_matched"
)]
knitr::kable(comparison)
```

### Relative label scores

```{r}
score_details <- results[, c(
  "boundary", "same_score", "change_score", "uncertain_score", "score_margin"
)]
knitr::kable(score_details, digits = 4)
```

The first score-based request, including the cold model load, took **5.28
seconds**. The following seven requests averaged **1.44 seconds per boundary**.

```{r}
accuracy <- aggregate(
  cbind(initial_matched, few_shot_matched, score_matched) ~ evidence,
  data = results,
  FUN = sum
)
counts <- table(results$evidence)
accuracy$total <- as.integer(counts[accuracy$evidence])
accuracy$initial_accuracy <- sprintf(
  "%d/%d (%.0f%%)",
  accuracy$initial_matched,
  accuracy$total,
  100 * accuracy$initial_matched / accuracy$total
)
accuracy$few_shot_accuracy <- sprintf(
  "%d/%d (%.0f%%)",
  accuracy$few_shot_matched,
  accuracy$total,
  100 * accuracy$few_shot_matched / accuracy$total
)
accuracy$score_accuracy <- sprintf(
  "%d/%d (%.0f%%)",
  accuracy$score_matched,
  accuracy$total,
  100 * accuracy$score_matched / accuracy$total
)
overall <- data.frame(
  evidence = "overall",
  initial_accuracy = sprintf(
    "%d/%d (%.0f%%)",
    sum(results$initial_matched),
    nrow(results),
    100 * mean(results$initial_matched)
  ),
  few_shot_accuracy = sprintf(
    "%d/%d (%.0f%%)",
    sum(results$few_shot_matched),
    nrow(results),
    100 * mean(results$few_shot_matched)
  ),
  score_accuracy = sprintf(
    "%d/%d (%.0f%%)",
    sum(results$score_matched),
    nrow(results),
    100 * mean(results$score_matched)
  )
)

knitr::kable(rbind(
  accuracy[, c(
    "evidence", "initial_accuracy", "few_shot_accuracy", "score_accuracy"
  )],
  overall
))
```

## Assessment

Few-shot prompting removed the always-change behavior. Both same-speaker
controls improved from 0/2 to 2/2, while the known `>>` changes remained 2/2.

The improvement came at a cost: likely missing changes fell from 4/4 to 2/4.
Boundaries 6→7 and 14→15 changed from correct `speaker_change` predictions to
incorrect `same_speaker` predictions. Overall accuracy therefore remained 6/8.
The model still did not use `uncertain`.

With score-based classification and a 0.10 margin, accuracy falls to 3/8. Both
same-speaker controls remain correct, but the known changes fall to 0/2 and the
likely missing changes fall to 1/4. Boundary 25→26 becomes `uncertain` because
its top-two margin is only 0.0579; this removes a previously correct prediction.

Score-based uncertainty does not fix the two requested problem cases. Boundary
6→7 favors `same_speaker` by 0.2371. Boundary 14→15 favors `same_speaker` by
0.8627. Both margins exceed the threshold, so neither becomes `uncertain`.

Changing the margin cannot turn an incorrectly ranked label into the correct
label. A threshold above 0.2371 would suppress the 6→7 error, but would also
suppress correct change and same-speaker cases with smaller margins. The very
confident 14→15 error would remain. Score-based uncertainty therefore does not
improve overall classification on these eight boundaries.

No production subtitle code, DuckDB data, schemas, or publication logic was
changed.
