---
title: "Bundle F: Day-of-Week Performance"
format:
  html:
    code-fold: false
    df-print: paged
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
params:
  talent: "Ava"
  data_source: "datalake"
  data_root: null
  render_generated_at: null
  included_date_range: "All available dates"
  render_cli: ""
  render_output_dir: null
  render_output_prefix: "Bundle_F"
  window_days: null
  start_date: null
  end_date: null
  reference_day: "Monday"
  content_types:
    - live
    - video
    - short
---

```{r}
#| label: setup
#| include: false

knitr::opts_knit$set(root.dir = normalizePath(file.path(getwd()), winslash = "/", mustWork = FALSE))

library(here)
library(readr)
library(dplyr)
library(purrr)
library(DT)
library(plotly)

`%||%` <- function(x, y) {
  if (is.null(x) || length(x) == 0 || (length(x) == 1 && !nzchar(x))) y else x
}

source(here::here("r_scripts", "lib", "utils", "source_dir.r"))
source(here::here("r_scripts", "lib", "utils", "staging_root.R"))
source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "utils", "talent_select.R"))
source(here::here("r_scripts", "lib", "import_data", "talent_files.R"))
source(here::here("r_scripts", "lib", "clean_data", "CleanData.R"))
source(here::here("r_scripts", "lib", "clean_data", "title_classification_join.R"))
source(here::here("r_scripts", "lib", "plots", "PlottingThemes.R"))
source(here::here("r_scripts", "lib", "utils", "content_type_utils.R"))
source(here::here("r_scripts", "lib", "linear_regression", "day_of_week", "weekday_transform.R"))
source(here::here("r_scripts", "lib", "linear_regression", "day_of_week", "report_helpers.R"))

bundle_f_plotly_layout <- function(
  plot_obj,
  margin_l = 120,
  margin_r = 30,
  margin_b = 95,
  margin_t = 88
) {
  layout_args <- list(
    margin = list(l = margin_l, r = margin_r, b = margin_b, t = margin_t),
    xaxis = list(automargin = TRUE, tickangle = -45),
    yaxis = list(automargin = TRUE),
    autosize = TRUE,
    title = list(x = 0.01, xanchor = "left")
  )

  plot_obj <- do.call(plotly::layout, c(list(p = plot_obj), layout_args))

  axis_keys <- names(plot_obj$x$layout)[grepl("^(x|y)axis[0-9]*$", names(plot_obj$x$layout))]
  for (axis_key in axis_keys) {
    if (is.null(plot_obj$x$layout[[axis_key]])) {
      plot_obj$x$layout[[axis_key]] <- list()
    }
    plot_obj$x$layout[[axis_key]]$automargin <- TRUE
    if (grepl("^xaxis[0-9]*$", axis_key)) {
      plot_obj$x$layout[[axis_key]]$tickangle <- -45
    }
  }

  plotly::config(plot_obj, responsive = TRUE, displaylogo = FALSE)
}

bundle_f_ggplotly <- function(plot_obj, tooltip = c("x", "y"), height = 720) {
  plot_obj <- plot_obj +
    ggplot2::theme(
      axis.text.x = ggplot2::element_text(angle = 45, hjust = 1, vjust = 1)
    )
  bundle_f_plotly_layout(plotly::ggplotly(plot_obj, tooltip = tooltip, height = height))
}

resolve_bundle_f_data_root <- function(data_source, data_root) {
  if (!is.null(data_root) && nzchar(trimws(data_root))) {
    return(normalizePath(data_root, winslash = "/", mustWork = FALSE))
  }
  if (identical(tolower(data_source), "datalake")) {
    return(normalizePath(get_datalake_root(), winslash = "/", mustWork = FALSE))
  }
  normalizePath(get_staging_root(), winslash = "/", mustWork = FALSE)
}

apply_bundle_f_publish_window <- function(df, start_date, end_date) {
  if (!("publish_date" %in% names(df))) {
    return(df)
  }
  if (!is.null(start_date) && nzchar(start_date)) {
    df <- df %>% dplyr::filter(.data$publish_date >= as.Date(start_date))
  }
  if (!is.null(end_date) && nzchar(end_date)) {
    df <- df %>% dplyr::filter(.data$publish_date <= as.Date(end_date))
  }
  df
}

canonical_bundle_f_content_types <- function(x) {
  if (is.null(x) || length(x) == 0) {
    return(c("live", "video", "short"))
  }
  x <- tolower(trimws(as.character(unlist(x))))
  x <- x[nzchar(x)]
  x <- dplyr::recode(
    x,
    videos = "video",
    shorts = "short",
    all = "all",
    .default = x
  )
  if ("all" %in% x) {
    return(c("live", "video", "short"))
  }
  unique(x)
}

data_root <- resolve_bundle_f_data_root(params$data_source, params$data_root)
talent_path <- select_talent(params$talent, root = data_root)
talent_folder <- basename(talent_path)
title_classifications <- load_title_classifications(talent = talent_folder)
talent_files <- TalentFiles(talent_path)[[1]]

required_video_types <- c(
  "video_analytics",
  "video_monetary",
  "video_demographics",
  "video_geography"
)
missing_video_exports <- setdiff(required_video_types, names(talent_files))
if (length(missing_video_exports) > 0L) {
  stop(
    "Missing required video export(s) for ",
    talent_folder,
    ": ",
    paste(missing_video_exports, collapse = ", ")
  )
}

stream_data <- video_preps_with_titles(
  files = talent_files,
  titles = title_classifications,
  talent = talent_folder,
  dedupe = TRUE
)

stream_video_level <- stream_data$analytics %>%
  dplyr::select(-dplyr::any_of(c("Estimated Revenue", "CPM"))) %>%
  dplyr::left_join(
    stream_data$monetary %>%
      dplyr::select(
        dplyr::all_of("Video ID"),
        dplyr::any_of(c("Estimated Revenue", "CPM"))
      ),
    by = "Video ID"
  ) %>%
  dplyr::mutate(talent_name = talent_folder) %>%
  apply_bundle_f_publish_window(params$start_date, params$end_date)

content_types <- canonical_bundle_f_content_types(params$content_types)
available_content_types <- sort(unique(tolower(trimws(as.character(stream_video_level$`Content Type`)))))
content_types <- intersect(content_types, available_content_types)
if (length(content_types) == 0L) {
  stop("No requested content types are available after filtering.")
}

content <- purrr::map(
  content_types,
  ~ stream_video_level %>%
    dplyr::filter(tolower(trimws(as.character(.data$`Content Type`))) == .x)
)
names(content) <- content_types
```

```{r report_layout_style, results='asis'}
cat(
  "<style>
  .main-container {
    max-width: 1200px !important;
  }
  .html-widget,
  .plotly.html-widget,
  .js-plotly-plot,
  .plot-container,
  .svg-container {
    max-width: 100% !important;
  }
  .plotly.html-widget {
    width: 100% !important;
    height: 720px !important;
    overflow: visible !important;
  }
  .plotly.html-widget .plot-container,
  .plotly.html-widget .svg-container {
    height: 720px !important;
    overflow: visible !important;
  }
  .dataTables_wrapper {
    width: 100%;
    max-width: 100%;
  }
  .dataTables_wrapper .dataTables_scroll {
    overflow-x: auto;
  }
  table.dataTable {
    width: 100% !important;
  }
  </style>"
)
```

## Report Scope

This report is designed to identify the best general day to stream for the selected talent, date range, and content types. Each included content type is analyzed separately, with weekday rankings, typical-view summaries, log-view models, estimated percent differences from the reference weekday, and supporting plots. The tables below document the exact render inputs and the available content counts used for this run.

```{r report_scope}
dow_report_datatable(
  tibble::tibble(
    field = c(
      "Talent",
      "Data source",
      "Data root",
      "Included publish date range",
      "Reference weekday",
      "Content types",
      "Generated"
    ),
    value = c(
      talent_folder,
      params$data_source,
      data_root,
      params$included_date_range,
      params$reference_day,
      paste(dow_report_content_label(content_types), collapse = ", "),
      params$render_generated_at %||% as.character(Sys.time())
    )
  ),
  "Bundle F render scope",
  page_length = 7
)
```

```{r content_type_overview}
stream_video_level %>%
  dplyr::count(`Content Type`, name = "videos") %>%
  dplyr::arrange(`Content Type`) %>%
  dow_report_datatable("Available content by type", page_length = 10)
```

```{r content_sections, results='asis'}
content_section_path <- here::here("r_scripts", "notebooks", "reports", "bundle_f", "_content_section.qmd")

for (content_type in names(content)) {
  content_env <- new.env(parent = knitr::knit_global())
  content_env$content_type <- content_type

  cat(
    knitr::knit_child(
      content_section_path,
      envir = content_env,
      quiet = TRUE
    ),
    sep = "\n"
  )
}
```
