---
title: "Variance Project: TMA Monetary Axis"
format:
  html:
    code-tools: false
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
---

```{r libraries_and_utils}
library(here)
knitr::opts_knit$set(root.dir = here::here())

library(dplyr)
library(tma)

source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "duckdb", "db_connect.R"))
source(here::here("r_scripts", "lib", "import_data", "qualitative_transcripts.R"))
source(here::here("r_scripts", "lib", "transcript_analysis", "qualitative_codes.R"))
source(here::here("r_scripts", "lib", "transcript_analysis", "money_stream_selection.R"))
source(here::here("r_scripts", "lib", "utils", "dt_utils.R"))
```





## Introduction
Live streamers and content creators have become a more common occurence.

```{r import_paths}
qualitative_dataset_id <- "chat_monetary_growth_variance_30_video"
qualitative_codebook_id <- "chat_monetary_growth_v1"
qualitative_db_path <- talent_lakehouse_db_path()

variance_talent_labels <- c(
  AVA1 = "Ava",
  KAT2 = "Katya",
  LEI3 = "Leia"
)

variance_streamer_handles <- c(
  AVA1 = "@AvaritiaHawthorne",
  KAT2 = "@KatyaSable",
  LEI3 = "@LeiaMemoria"
)
```

```{r importing_qualitative_data}
import_data <- load_qualitative_transcripts_wide(
  codebook_id = qualitative_codebook_id,
  dataset_id = qualitative_dataset_id,
  pipeline_run_id = "latest",
  response_status = NULL,
  db_path = qualitative_db_path
) %>%
  dplyr::mutate(
    talent_name = dplyr::recode(
      .data$talent_code,
      !!!variance_talent_labels
    ),
    row_number = .data$line_number
  ) %>%
  dplyr::select(
    source_file,
    talent_code,
    talent_name,
    video_id,
    row_number,
    timecode,
    source,
    speaker,
    paid_amount_text,
    paid_amount_value,
    paid_currency,
    message_type,
    text,
    starts_with("code_")
  )
```



## Clean transcript speaker labels

The `source` value remains `subtitle` because it identifies the TMA modality.
For subtitle rows, placeholder speaker values such as `STREAM` and `subtitle`
are replaced with the corresponding streamer's handle. The original value is
retained in `speaker_raw` for auditing.

```{r clean_transcript_speakers}
placeholder_streamer_speakers <- c("STREAM", "SUBTITLE")

import_data <- import_data %>%
  dplyr::mutate(
    speaker_raw = .data$speaker,
    speaker_key = toupper(trimws(dplyr::coalesce(.data$speaker, ""))),
    streamer_handle = unname(
      variance_streamer_handles[.data$talent_code]
    ),
    speaker = dplyr::if_else(
      .data$source == "subtitle" &
        .data$speaker_key %in% placeholder_streamer_speakers &
        !is.na(.data$streamer_handle),
      .data$streamer_handle,
      .data$speaker
    )
  ) %>%
  dplyr::select(-speaker_key, -streamer_handle)

unmapped_streamer_speakers <- import_data %>%
  dplyr::filter(
    .data$source == "subtitle",
    toupper(trimws(dplyr::coalesce(.data$speaker, ""))) %in%
      placeholder_streamer_speakers
  )

if (nrow(unmapped_streamer_speakers) > 0L) {
  stop(
    "Some subtitle rows still have placeholder speaker labels. ",
    "Add their talent codes and handles to variance_streamer_handles.",
    call. = FALSE
  )
}

subtitle_speaker_cleaning_summary <- import_data %>%
  dplyr::filter(.data$source == "subtitle") %>%
  dplyr::count(
    .data$talent_name,
    .data$speaker_raw,
    .data$speaker,
    name = "transcript_rows"
  ) %>%
  dplyr::arrange(.data$talent_name)

DTSettings(
  subtitle_speaker_cleaning_summary,
  options = list(pageLength = 10)
)
```








## Introduction
There are two issues with the original ENA model
1. I set an ininfite stanza window, which is an issue because I lose a lot of granularity and control across my dataset. WHile it is fair to assume that conversations from the beginning of the stream are related to the end of the stream, the general scope is just too large to be able to support any kind of analysis.
1. ENA doesn't handle this multimodal data as well, I do have my data split by streamer and chat. But I got some suggestions that ...
    1. I should just have chat as one massive entity. While chat data is available I'm not particularly interested in the
    1. While I originally made this model to simply quantify the qualitative qualities from the stream
1. Also another issue, I need to update my chat data so that the streamers sentences are all put together as full sentences rather than as segmented chunks. It's very unnatural and it will mess up the any network analysis.

## Qualitative Codebook

```{r qualitative_codebook}
codebook_data <- load_qualitative_codebook(
  codebook_id = qualitative_codebook_id,
  db_path = qualitative_db_path
)

codebook_display <- codebook_data %>%
  dplyr::mutate(
    code_id = dplyr::if_else(
      is.na(.data[["Secondary Code ID"]]) | !nzchar(trimws(.data[["Secondary Code ID"]])),
      .data[["Primary Code ID"]],
      .data[["Secondary Code ID"]]
    ),
    code_label = dplyr::if_else(
      is.na(.data[["Secondary Code"]]) | !nzchar(trimws(.data[["Secondary Code"]])),
      .data[["Primary Code"]],
      .data[["Secondary Code"]]
    )
  ) %>%
  dplyr::transmute(
    code_id,
    code_label,
    definition = .data[["Definition"]]
  ) %>%
  dplyr::arrange(.data$code_id)

DTSettings(
  codebook_display,
  scroll_x = TRUE,
  options = list(pageLength = 10)
)
```







## Prepare data for TMA
Note I need to fix the data. Streamer text data because it's disjointed. I also have events that are happening simultaneously and technically in two modalities the stream and the chat. There are times where the stream and the chat engage with one another and there are times they do not.

```{r prepare_tma_data}
code_window_size_back <- 4L
selected_code_cols <- select_frequent_code_pairs(
  data = import_data,
  codebook = codebook_data,
  n = 8L,
  window_size_back = code_window_size_back,
  prefer = "secondary"
)$selected_code_cols

removed_low_frequency_code_col <- selected_code_cols[[length(selected_code_cols)]]
selected_code_cols <- c(
  selected_code_cols[-length(selected_code_cols)],
  "gave_money"
)

tma_input_data <- import_data %>%
  normalize_text_playback_paid_amounts() %>%
  dplyr::mutate(
    paid_amount_value = .data$paid_amount_native,
    paid_currency = .data$paid_currency_norm,
    gave_money = !is.na(.data$paid_amount_value) & .data$paid_amount_value > 0
  ) %>%
  dplyr::select(
    source_file,
    talent_name,
    video_id,
    row_number,
    timecode,
    source,
    speaker,
    message_type,
    text,
    paid_amount_text,
    paid_amount_value,
    paid_currency,
    paid_amount_usd,
    dplyr::all_of(selected_code_cols)
  )
```



The model retains eight nodes. `gave_money` replaces
`r removed_low_frequency_code_col`, the lowest-ranked member of the previous
eight qualitative codes based on windowed pair participation.

### TMA input data structure

The table below presents the main fields that organize the TMA model:

- `talent_name` and `video_id` jointly define the unit of analysis and keep the
  horizon inside a single talent-stream combination.
- `source` identifies the chat or subtitle modality.
- `row_number` and `timecode` locate the event in the stream. The current model
  applies its four-row window using event order; `timecode` is retained for
  interpretation.
- `speaker` and `text` identify the actor and the coded event.
- `paid_amount_usd` is retained for the later monetary rotation.
- The final eight logical columns are the codes accumulated into network
  connections.

To keep the rendered notebook responsive, the display includes up to the first
10 events from each modality in each talent-video unit. The model continues to
use every row in `tma_input_data`.

```{r display_tma_input_structure}
tma_input_code_labels <- codebook_display$code_label[
  match(
    sub("^code_", "", selected_code_cols),
    codebook_display$code_id
  )
]
tma_input_code_labels[selected_code_cols == "gave_money"] <- "Gave Money"

if (any(is.na(tma_input_code_labels))) {
  stop(
    "Every displayed TMA code must have a readable label.",
    call. = FALSE
  )
}

tma_input_preview <- tma_input_data %>%
  dplyr::arrange(
    .data$talent_name,
    .data$video_id,
    .data$row_number
  ) %>%
  dplyr::group_by(
    .data$talent_name,
    .data$video_id,
    .data$source
  ) %>%
  dplyr::slice_head(n = 10L) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(
    .data$talent_name,
    .data$video_id,
    .data$row_number
  ) %>%
  dplyr::select(
    talent_name,
    video_id,
    row_number,
    timecode,
    source,
    speaker,
    text,
    paid_amount_usd,
    dplyr::all_of(selected_code_cols)
  )

tma_input_column_labels <- c(
  "Unit: Talent",
  "Unit / Horizon: Video ID",
  "Event Order",
  "Timecode",
  "Modality",
  "Speaker",
  "Coded Text",
  "USD Payment",
  paste0("Code: ", tma_input_code_labels)
)

DTSettings(
  tma_input_preview,
  scroll_x = TRUE,
  currency_cols = "paid_amount_usd",
  options = list(pageLength = 10),
  colnames = tma_input_column_labels
)
```





## TMA Setup

Chat and subtitle rows are modeled as separate modalities. Each talent-stream
combination is a unit of analysis. The flexible horizon below makes the
observation boundary modality-specific while keeping both modalities within the
unit's own stream:

- Chat contributes the collective chat activity for the talent-video unit.
- Subtitles contribute the streamer's speech for the same talent-video unit.
- Events from other talents or videos remain outside the unit's horizon.

```{r tma_setup}
flexible_horizon_rules <- tma::rules(
  source == "chat" &
    talent_name %in% UNIT$talent_name &
    video_id %in% UNIT$video_id,
  source == "subtitle" &
    talent_name %in% UNIT$talent_name &
    video_id %in% UNIT$video_id
)

context_model <- tma::contexts(
  x = tma_input_data,
  units_by = c("talent_name", "video_id"),
  hoo_rules = flexible_horizon_rules
)

context_window_tensor <- tma::context_tensor(
  df = tma_input_data,
  mode_column = "source",
  default_window = 4,
  default_weight = 1
)

# context_window_tensor["chat", "window"] <- 4
# context_window_tensor["subtitle", "window"] <- 1
```




The horizon rules determine which events a unit can observe. The tensor
determines how far an observed event can influence connections. The current
model uses a four-row window for both chat and subtitles. The commented
assignments show where modality-specific windows can be restored if the
substantive model changes. Because every row is already assigned to a
talent-video unit, these horizon rules formalize the stream boundary but do not
expand it.


## Visualize the TMA

Accumulate the code connections using the modality-specific windows above, then
project the resulting unit networks into a two-dimensional ENA space.

```{r tma_accumulation}
tma_model <- tma::accumulate(
  context_model = context_model,
  codes = selected_code_cols,
  tensor = context_window_tensor,
  ordered = FALSE,
  binary = TRUE
)

tma_set <- rENA::ena.make.set(tma_model)

tma_unit_display <- tibble::tibble(
  talent_name = as.vector(tma_model$meta.data[["talent_name"]]),
  video_id = as.vector(tma_model$meta.data[["video_id"]])
) %>%
  dplyr::left_join(
    tma_input_data %>%
      dplyr::group_by(.data$talent_name, .data$video_id) %>%
      dplyr::summarise(
        source_file = dplyr::first(.data$source_file),
        source_file_count = dplyr::n_distinct(.data$source_file),
        total_paid_amount_usd = sum(.data$paid_amount_usd, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("talent_name", "video_id")
  )

if (
  any(tma_unit_display$source_file_count != 1L) ||
    any(is.na(tma_unit_display$source_file)) ||
    any(!is.finite(tma_unit_display$total_paid_amount_usd))
) {
  stop(
    "Each TMA unit must have one source file and one finite USD total.",
    call. = FALSE
  )
}

tma_unit_display <- tma_unit_display %>%
  dplyr::mutate(
    source_file_label = tools::file_path_sans_ext(
      basename(.data$source_file)
    ),
    stream_name = dplyr::if_else(
      endsWith(
        .data$source_file_label,
        paste0("_", .data$video_id)
      ),
      substr(
        .data$source_file_label,
        1L,
        nchar(.data$source_file_label) - nchar(.data$video_id) - 1L
      ),
      .data$source_file_label
    ),
    stream_name = trimws(gsub("_+", " ", .data$stream_name))
  ) %>%
  dplyr::select(-dplyr::all_of("source_file_count"))

wrap_tooltip_title <- function(title, width = 42L) {
  vapply(
    title,
    function(value) {
      paste(strwrap(value, width = width), collapse = "<br>")
    },
    character(1)
  )
}

node_code_label_lookup <- codebook_display %>%
  dplyr::transmute(
    code_column = paste0("code_", .data$code_id),
    code_label = .data$code_label
  ) %>%
  dplyr::bind_rows(
    tibble::tibble(
      code_column = "gave_money",
      code_label = "Gave Money"
    )
  )

get_tma_node_labels <- function(ena_set, code_label_lookup, width = 18L) {
  node_codes <- as.character(ena_set$rotation$nodes$code)
  node_labels <- code_label_lookup$code_label[
    match(node_codes, code_label_lookup$code_column)
  ]

  if (any(is.na(node_labels))) {
    stop(
      "Every TMA node must have a human-readable codebook label.",
      call. = FALSE
    )
  }

  wrap_tooltip_title(node_labels, width = width)
}

get_tma_node_label_offsets <- function(ena_set) {
  node_positions <- as.matrix(ena_set$rotation$nodes)[, 1:2, drop = FALSE]

  ifelse(
    abs(node_positions[, 1]) >= abs(node_positions[, 2]),
    ifelse(
      node_positions[, 1] >= 0,
      "middle right",
      "middle left"
    ),
    ifelse(
      node_positions[, 2] >= 0,
      "top center",
      "bottom center"
    )
  )
}

move_tma_node_label_with_leader <- function(enaplot,
                                            label,
                                            x_offset = -110,
                                            y_offset = 45) {
  built_plot <- plotly::plotly_build(enaplot$plot)
  matched_trace <- integer()
  matched_label <- integer()

  for (trace_index in seq_along(built_plot$x$data)) {
    trace_text <- as.character(built_plot$x$data[[trace_index]]$text)
    label_index <- which(trace_text == label)

    if (length(label_index) > 0L) {
      matched_trace <- c(matched_trace, rep(trace_index, length(label_index)))
      matched_label <- c(matched_label, label_index)
    }
  }

  if (length(matched_trace) != 1L) {
    stop(
      "The requested TMA node label must match exactly one plotted node.",
      call. = FALSE
    )
  }

  node_trace <- built_plot$x$data[[matched_trace]]
  node_x <- node_trace$x[[matched_label]]
  node_y <- node_trace$y[[matched_label]]
  node_trace$text[[matched_label]] <- ""
  built_plot$x$data[[matched_trace]] <- node_trace

  leader_annotation <- list(
    x = node_x,
    y = node_y,
    xref = "x",
    yref = "y",
    text = label,
    showarrow = TRUE,
    arrowhead = 0,
    arrowsize = 1,
    arrowwidth = 1,
    arrowcolor = "#666666",
    ax = x_offset,
    ay = y_offset,
    align = "center",
    font = list(
      family = "Arial",
      size = 9,
      color = "#000000"
    ),
    bgcolor = "rgba(255,255,255,0.9)",
    borderpad = 2
  )

  existing_annotations <- built_plot$x$layout$annotations
  if (is.null(existing_annotations)) {
    existing_annotations <- list()
  }
  built_plot$x$layout$annotations <- c(
    existing_annotations,
    list(leader_annotation)
  )

  enaplot$plot <- built_plot
  enaplot
}

payment_point_color <- scales::col_numeric(
  palette = c("#440154", "#21908C", "#FDE725"),
  domain = range(tma_unit_display$total_paid_amount_usd)
)

talent_point_shapes <- c(
  Ava = "circle",
  Katya = "square",
  Leia = "diamond"
)

tma_unit_display <- tma_unit_display %>%
  dplyr::mutate(
    tooltip = sprintf(
      "<b>%s</b><br>Streamer: %s<br>Total payment: USD %.2f",
      wrap_tooltip_title(.data$stream_name),
      .data$talent_name,
      .data$total_paid_amount_usd
    ),
    point_color = payment_point_color(.data$total_paid_amount_usd),
    point_shape = unname(talent_point_shapes[.data$talent_name])
  )

if (any(is.na(tma_unit_display$point_shape))) {
  stop(
    "Every talent must have a shape in talent_point_shapes.",
    call. = FALSE
  )
}

set_tma_point_tooltips <- function(enaplot, tooltips) {
  built_plot <- plotly::plotly_build(enaplot$plot)
  point_trace_indices <- which(
    vapply(
      built_plot$x$data,
      function(trace) {
        length(trace$hoverinfo) == 1L &&
          identical(trace$hoverinfo, "x+y+name")
      },
      logical(1)
    )
  )

  if (length(point_trace_indices) != length(tooltips)) {
    stop(
      "The number of TMA point traces does not match the tooltip labels.",
      call. = FALSE
    )
  }

  for (point_index in seq_along(point_trace_indices)) {
    trace_index <- point_trace_indices[[point_index]]
    built_plot$x$data[[trace_index]]$hoverinfo <- "text"
    built_plot$x$data[[trace_index]]$hovertemplate <- paste0(
      tooltips[[point_index]],
      "<extra></extra>"
    )
    built_plot$x$data[[trace_index]]$hoverlabel <- list(align = "left")
  }

  enaplot$plot <- built_plot
  enaplot
}
```





The points represent talent-stream units, while the network summarizes the mean
code connections across all units. Point color follows a continuous payment
gradient from purple for lower totals through teal to yellow for higher totals.
Point shape identifies the talent: Ava is a circle, Katya is a square, and Leia
is a diamond. Tooltips show the readable stream name, streamer, and total USD
payment. Coordinates and `video_id` are hidden from the tooltip, although
`video_id` remains available in `tma_unit_display` as the internal join key.
Edge thickness indicates connection strength.

Network nodes display the full codebook names rather than internal `code_*`
identifiers. Long names wrap across lines, and their label positions are moved
outward from the node to reduce overlap.

```{r tma_visualization}
tma_plot <- rENA::ena.plot(
  tma_set,
  title = "TMA: Chat and Subtitle Code Connections"
  ) |>
  rENA::ena.plot.points(
    points = tma_set$points,
    labels = tma_unit_display$stream_name,
    colors = tma_unit_display$point_color,
    shape = tma_unit_display$point_shape,
    point.size = 8,
    show.legend = FALSE
  ) |>
  rENA::add_network(
    colors = "#0072B2",
    edge.multiplier = 1,
    labels = get_tma_node_labels(
      ena_set = tma_set,
      code_label_lookup = node_code_label_lookup
    ),
    label.offset = get_tma_node_label_offsets(tma_set),
    label.font.size = 9
  )

tma_plot <- set_tma_point_tooltips(
  enaplot = tma_plot,
  tooltips = tma_unit_display$tooltip
)

tma_plot <- move_tma_node_label_with_leader(
  enaplot = tma_plot,
  label = "Collective<br>In-Group Framing"
)

tma_plot
```



## TMA monetary axis

The default `tma_set` uses an SVD rotation, so its first dimension describes
the largest source of variation in the unit networks. To answer the monetary
question directly, the same accumulated `tma_model` can instead be rotated
toward total payment with `rENA::ena.rotate.by.generalized()`.

This requires three steps:

1. Aggregate `paid_amount_usd` to the talent-video level and arrange those
   values in the same order as `tma_model$meta.data`.
2. Create the generalized-rotation ENA set with the payment target as `x_var`.
3. Plot the payment-oriented set.

The rotation changes the orientation of the existing network space. It does not
rebuild the TMA connections or convert the ENA coordinate into dollars.

### 1. Create the payment target

`paid_amount_usd` is used instead of `paid_amount_value` because the latter
contains native-currency amounts. `tma_unit_display` already follows the
model's row order and contains the cleaned `source_file` label, the retained
`video_id` join key, and the stream's USD total.

```{r payment_target}
payment_x_var <- tma_unit_display %>%
  dplyr::select(.data$total_paid_amount_usd) %>%
  as.data.frame()

if (
  nrow(payment_x_var) != nrow(tma_model$meta.data) ||
    any(!is.finite(payment_x_var$total_paid_amount_usd))
) {
  stop(
    "Each TMA unit must have one finite total_paid_amount_usd value.",
    call. = FALSE
  )
}
```


### 2. Apply the generalized rotation

This is the complete monetary-axis model. `payment_x_var` is a one-column data
frame because `ena.rotate.by.generalized()` uses its first column as the
continuous rotation target.

```{r payment_rotation}
tma_money_set <- rENA::ena.make.set(
  enadata = tma_model,
  rotation.by = rENA::ena.rotate.by.generalized,
  rotation.params = list(x_var = payment_x_var)
)
```


The first coordinate now represents the network direction associated with
increasing total payment. The second coordinate is the leading residual SVD
dimension produced by the generalized rotation.

### 3. Plot the payment-oriented TMA

The horizontal coordinate is a normalized network score—not a dollar amount.
The hover label supplies the corresponding unit-level USD total.

```{r payment_plot}
tma_money_plot <- rENA::ena.plot(
  tma_money_set,
  title = "TMA: Payment-Aligned Network",
  dimension.labels = c(
    "Payment-aligned network dimension",
    "Residual SVD dimension"
  )
  ) |>
  rENA::ena.plot.points(
    points = tma_money_set$points,
    labels = tma_unit_display$stream_name,
    colors = tma_unit_display$point_color,
    shape = tma_unit_display$point_shape,
    point.size = 8,
    show.legend = FALSE
  ) |>
  rENA::add_network(
    colors = "#0072B2",
    edge.multiplier = 1,
    labels = get_tma_node_labels(
      ena_set = tma_money_set,
      code_label_lookup = node_code_label_lookup
    ),
    label.offset = get_tma_node_label_offsets(tma_money_set),
    label.font.size = 9
  )

tma_money_plot <- set_tma_point_tooltips(
  enaplot = tma_money_plot,
  tooltips = tma_unit_display$tooltip
)

tma_money_plot <- move_tma_node_label_with_leader(
  enaplot = tma_money_plot,
  label = "Collective<br>In-Group Framing"
)

tma_money_plot
```


### Goodness of fit

`rENA::ena.correlations()` reports the co-registration goodness of fit between
the plotted unit points and their corresponding network centroids. Pearson and
Spearman correlations are reported separately for each plotted dimension.
Values closer to one indicate that the visualization more faithfully
represents the underlying network model.

```{r payment_goodness_of_fit}
tma_money_goodness_of_fit <- rENA::ena.correlations(
  tma_money_set,
  dims = c(1, 2)
)

rownames(tma_money_goodness_of_fit) <- c(
  "Payment-aligned network dimension",
  "Residual SVD dimension"
)

knitr::kable(
  tma_money_goodness_of_fit,
  digits = 3,
  caption = "TMA co-registration goodness of fit"
)
```


These correlations evaluate the fit of the network visualization to the
underlying model. They do not measure how much variance in USD payment is
explained by the monetary axis.

Read points farther to the right as units whose connection patterns are more
strongly associated with higher total payment, and points farther to the left
as units whose patterns are more strongly associated with lower total payment.
This is an associational network gradient; it is not a literal USD axis or a
causal estimate.


## TMA Talent Averages

The plot below replaces the 30 individual stream points with one mean point for
each talent in the payment-oriented ENA space. Color represents the talent's
average stream payment using the same payment gradient, and shape retains the
talent mapping used above.

Each dashed box contains the separate 95% *t* confidence intervals for the
talent's mean horizontal and vertical coordinates. These boxes visualize
uncertainty around each mean. Their overlap is useful descriptively, but it is
not by itself a formal significance test between talents.

```{r talent_average_plot}
talent_average_display <- tma_unit_display %>%
  dplyr::group_by(.data$talent_name) %>%
  dplyr::summarise(
    stream_count = dplyr::n(),
    average_paid_amount_usd = mean(.data$total_paid_amount_usd),
    point_shape = dplyr::first(.data$point_shape),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    point_color = payment_point_color(.data$average_paid_amount_usd),
    tooltip = sprintf(
      "<b>%s</b><br>Streams: %d<br>Average payment: USD %.2f",
      .data$talent_name,
      .data$stream_count,
      .data$average_paid_amount_usd
    )
  )

talent_plot_order <- names(talent_point_shapes)
talent_average_coordinates <- as.matrix(tma_money_set$points)[, 1:2, drop = FALSE]

tma_talent_average_plot <- rENA::ena.plot(
  tma_money_set,
  title = "TMA: Talent Averages on the Payment-Aligned Network",
  dimension.labels = c(
    "Payment-aligned network dimension",
    "Residual SVD dimension"
  )
)

for (talent in talent_plot_order) {
  talent_rows <- tma_unit_display$talent_name == talent
  talent_display_row <- match(
    talent,
    talent_average_display$talent_name
  )

  tma_talent_average_plot <- rENA::ena.plot.group(
    enaplot = tma_talent_average_plot,
    points = talent_average_coordinates[talent_rows, , drop = FALSE],
    labels = talent,
    colors = talent_average_display$point_color[[talent_display_row]],
    shape = talent_average_display$point_shape[[talent_display_row]],
    confidence.interval = "box",
    point.size = 10,
    show.legend = TRUE,
    legend.name = "Talent"
  )
}

tma_talent_average_plot <- tma_talent_average_plot |>
  rENA::add_network(
    colors = "#0072B2",
    edge.multiplier = 1,
    labels = get_tma_node_labels(
      ena_set = tma_money_set,
      code_label_lookup = node_code_label_lookup
    ),
    label.offset = get_tma_node_label_offsets(tma_money_set),
    label.font.size = 9
  )

tma_talent_average_plot <- set_tma_point_tooltips(
  enaplot = tma_talent_average_plot,
  tooltips = talent_average_display$tooltip[
    match(talent_plot_order, talent_average_display$talent_name)
  ]
)

tma_talent_average_plot <- move_tma_node_label_with_leader(
  enaplot = tma_talent_average_plot,
  label = "Collective<br>In-Group Framing"
)

tma_talent_average_plot
```


### Individual talent average networks

The three plots below retain the same payment-oriented axes and global node
positions so that their edge structures remain directly comparable. Within
each plot, the network is the column mean of the normalized line weights from
that talent's streams. The point and dashed box show the talent's mean position
and 95% coordinate confidence intervals; individual video points are omitted.

```{r build_individual_talent_networks}
build_talent_average_network_plot <- function(talent,
                                              ena_set,
                                              unit_display,
                                              title_suffix) {
  unit_line_weights <- as.matrix(ena_set$line.weights)
  unit_coordinates <- as.matrix(ena_set$points)[, 1:2, drop = FALSE]
  talent_rows <- unit_display$talent_name == talent
  talent_display_row <- match(
    talent,
    talent_average_display$talent_name
  )

  if (
    nrow(unit_line_weights) != nrow(unit_display) ||
      nrow(unit_coordinates) != nrow(unit_display)
  ) {
    stop(
      "Talent labels, coordinates, and TMA line weights must share row order.",
      call. = FALSE
    )
  }

  if (sum(talent_rows) < 2L || is.na(talent_display_row)) {
    stop(
      "Each talent plot requires at least two streams and display metadata.",
      call. = FALSE
    )
  }

  talent_color <- talent_average_display$point_color[[talent_display_row]]
  talent_shape <- talent_average_display$point_shape[[talent_display_row]]
  talent_mean_network <- colMeans(
    unit_line_weights[talent_rows, , drop = FALSE]
  )

  talent_plot <- rENA::ena.plot(
    ena_set,
    title = sprintf(
      "TMA: %s<br>%s",
      talent,
      title_suffix
    ),
    dimension.labels = c(
      "Payment-aligned network dimension",
      "Residual SVD dimension"
    )
  )

  talent_plot <- rENA::ena.plot.group(
    enaplot = talent_plot,
    points = unit_coordinates[talent_rows, , drop = FALSE],
    labels = talent,
    colors = talent_color,
    shape = talent_shape,
    confidence.interval = "box",
    point.size = 10,
    show.legend = FALSE
  )

  talent_plot <- rENA::ena.plot.network(
    enaplot = talent_plot,
    network = talent_mean_network,
    colors = talent_color,
    edge.multiplier = 1,
    labels = get_tma_node_labels(
      ena_set = ena_set,
      code_label_lookup = node_code_label_lookup
    ),
    label.offset = get_tma_node_label_offsets(ena_set),
    label.font.size = 9
  )

  talent_plot <- set_tma_point_tooltips(
    enaplot = talent_plot,
    tooltips = talent_average_display$tooltip[[talent_display_row]]
  )

  move_tma_node_label_with_leader(
    enaplot = talent_plot,
    label = "Collective<br>In-Group Framing"
  )
}

tma_talent_network_plots <- stats::setNames(
  lapply(
    talent_plot_order,
    build_talent_average_network_plot,
    ena_set = tma_money_set,
    unit_display = tma_unit_display,
    title_suffix = "Average Payment-Aligned Network"
  ),
  talent_plot_order
)
```


#### Ava average network

```{r ava_average_network}
tma_talent_network_plots$Ava
```


#### Katya average network

```{r katya_average_network}
tma_talent_network_plots$Katya
```


#### Leia average network

```{r leia_average_network}
tma_talent_network_plots$Leia
```


## Talent Chat Networks

The full TMA model accumulates code connections from chat and subtitle events
within each talent-stream unit. Its normalized line weights no longer identify
which modality contributed a connection, so a chat network should not be
created by subsetting the finished `tma_money_set`.

Instead, the model below filters to chat events *before* defining contexts and
accumulating connections. It retains `talent_name` and `video_id` as the unit
and horizon boundary. Therefore, chat messages remain situated within their
own stream, but streamer subtitle events do not contribute codes or
connections.

Because subtitle rows are removed first, the four-row window now means the
current chat event and the preceding chat events in that stream, rather than
four events drawn from both modalities. This is the appropriate interpretation
for a chat-only sequential network.

```{r build_chat_only_tma}
chat_tma_input_data <- tma_input_data %>%
  dplyr::filter(.data$source == "chat")

chat_horizon_rules <- tma::rules(
  source == "chat" &
    talent_name %in% UNIT$talent_name &
    video_id %in% UNIT$video_id
)

chat_context_model <- tma::contexts(
  x = chat_tma_input_data,
  units_by = c("talent_name", "video_id"),
  hoo_rules = chat_horizon_rules
)

chat_context_tensor <- tma::context_tensor(
  df = chat_tma_input_data,
  mode_column = "source",
  default_window = code_window_size_back,
  default_weight = 1
)

chat_tma_model <- tma::accumulate(
  context_model = chat_context_model,
  codes = selected_code_cols,
  tensor = chat_context_tensor,
  ordered = FALSE,
  binary = TRUE
)

chat_tma_set <- rENA::ena.make.set(
  chat_tma_model,
  rotation.by = NULL,
  rotation.set = tma_money_set$rotation
)

chat_unit_display <- tibble::tibble(
  talent_name = as.vector(chat_tma_model$meta.data[["talent_name"]]),
  video_id = as.vector(chat_tma_model$meta.data[["video_id"]])
)
```

`rotation.set = tma_money_set$rotation` places the chat-only networks in the
same payment-aligned coordinate system and uses the same node positions as the
multimodal model. Thus, horizontal location describes how strongly a chat-only
connection pattern expresses the payment gradient learned from the full model.
It does not mean the chat-only set was independently optimized against payment.

The following plots average the normalized chat-only connection weights across
the streams belonging to each talent. Each dashed box is the 95% confidence
interval for that talent's chat-only stream coordinates.

```{r build_talent_chat_networks}
chat_talent_network_plots <- stats::setNames(
  lapply(
    talent_plot_order,
    build_talent_average_network_plot,
    ena_set = chat_tma_set,
    unit_display = chat_unit_display,
    title_suffix = "Average Chat-Only Network"
  ),
  talent_plot_order
)
```

### Ava chat network

```{r ava_chat_network}
chat_talent_network_plots$Ava
```

### Katya chat network

```{r katya_chat_network}
chat_talent_network_plots$Katya
```

### Leia chat network

```{r leia_chat_network}
chat_talent_network_plots$Leia
```

These plots answer what codes chat connects without subtitle contributions.
They do not represent streamer-to-chat engagement, because that relationship
requires retaining both modalities and explicitly modeling cross-modal event
pairs.


## Chat and streamer modal interactions

The models above do not isolate streamer-chat engagement:

- The full multimodal model includes chat-chat, subtitle-subtitle, and
  cross-modal connections in the same line weights.
- The chat-only model removes subtitle events, so it cannot contain a
  streamer-to-chat or chat-to-streamer connection.

To isolate modal interaction, the model below retains both modalities but
assigns zero weight to within-modality event pairs. Only a subtitle event in
the ground followed by a chat response, or a chat event in the ground followed
by a subtitle response, can contribute to the network.

This is an operational definition of engagement: two coded events from
different modalities occur within the specified window. It identifies
cross-modal temporal and epistemic connections, but it does not by itself
prove that one speaker intentionally replied to the other.

```{r build_cross_modal_interaction_tma}
interaction_tma_input_data <- tma_input_data %>%
  dplyr::mutate(interaction_mode = "event")

interaction_context_model <- tma::contexts(
  x = interaction_tma_input_data,
  units_by = c("talent_name", "video_id"),
  hoo_rules = flexible_horizon_rules
)

interaction_context_tensor <- tma::context_tensor(
  df = interaction_tma_input_data,
  sender_cols = "source",
  receiver_cols = "source",
  mode_column = "interaction_mode",
  default_window = code_window_size_back,
  default_weight = 0
)

interaction_context_tensor[
  "subtitle",
  "chat",
  "event",
  "weight"
] <- 1
interaction_context_tensor[
  "chat",
  "subtitle",
  "event",
  "weight"
] <- 1

interaction_tma_model <- tma::accumulate(
  context_model = interaction_context_model,
  codes = selected_code_cols,
  tensor = interaction_context_tensor,
  ordered = FALSE,
  binary = TRUE
)

interaction_tma_set <- rENA::ena.make.set(
  interaction_tma_model,
  rotation.by = NULL,
  rotation.set = tma_money_set$rotation
)
```

The tensor dimensions have a substantive interpretation:

- `sender_cols = "source"` describes the modality of the preceding ground
  event.
- `receiver_cols = "source"` describes the modality of the current response
  event.
- A zero default weight removes chat-chat and subtitle-subtitle contributions.
- The two assignments above retain both cross-modal directions.

The model remains unordered at the code level, so an edge describes which
codes connect across modalities rather than placing an arrow between codes.
Direction is retained in the row-level response events below: a chat response
has subtitle ground (`Streamer -> chat`), while a subtitle response has chat
ground (`Chat -> streamer`).

```{r prepare_cross_modal_interaction_events}
interaction_row_connections <-
  interaction_tma_model$model$row.connection.counts
interaction_connection_cols <- names(interaction_row_connections)[
  vapply(
    interaction_row_connections,
    inherits,
    logical(1),
    what = "ena.co.occurrence"
  )
]

interaction_connection_matrix <- as.matrix(
  interaction_row_connections[
    ,
    interaction_connection_cols,
    with = FALSE
  ]
)

interaction_response_events <- tibble::tibble(
  QEID = as.vector(interaction_row_connections[["QEID"]]),
  talent_name = as.vector(
    interaction_row_connections[["talent_name"]]
  ),
  video_id = as.vector(interaction_row_connections[["video_id"]]),
  cross_modal_connection_weight = rowSums(
    interaction_connection_matrix,
    na.rm = TRUE
  )
) %>%
  dplyr::filter(.data$cross_modal_connection_weight > 0) %>%
  dplyr::left_join(
    tibble::as_tibble(interaction_tma_model$model$raw.input) %>%
      dplyr::transmute(
        QEID = as.vector(.data$QEID),
        timecode = .data$timecode,
        response_source = .data$source,
        response_speaker = .data$speaker,
        response_text = .data$text
      ),
    by = "QEID"
  ) %>%
  dplyr::left_join(
    tma_unit_display %>%
      dplyr::select(
        .data$talent_name,
        .data$video_id,
        .data$stream_name
      ),
    by = c("talent_name", "video_id")
  ) %>%
  dplyr::mutate(
    interaction_direction = dplyr::case_when(
      .data$response_source == "chat" ~ "Streamer -> chat",
      .data$response_source == "subtitle" ~ "Chat -> streamer",
      TRUE ~ NA_character_
    )
  ) %>%
  dplyr::arrange(
    dplyr::desc(.data$cross_modal_connection_weight)
  )

interaction_direction_summary <- interaction_response_events %>%
  dplyr::group_by(
    .data$talent_name,
    .data$interaction_direction
  ) %>%
  dplyr::summarise(
    response_event_count = dplyr::n(),
    total_connection_weight = sum(
      .data$cross_modal_connection_weight
    ),
    .groups = "drop"
  )

DTSettings(
  interaction_direction_summary,
  scroll_x = TRUE,
  options = list(pageLength = 10)
)
```

Each `response_event_count` is a coded response row with at least one
opposite-modality event in its four-event ground window. The
`total_connection_weight` also reflects how many cross-modal code connections
were present, so it should not be interpreted as a count of conversational
turns.

The table below previews the 500 strongest response events. The complete set
remains available in `interaction_response_events` for qualitative inspection.

```{r display_cross_modal_interaction_events}
DTSettings(
  interaction_response_events %>%
    dplyr::select(
      .data$talent_name,
      .data$stream_name,
      .data$timecode,
      .data$interaction_direction,
      .data$response_speaker,
      .data$response_text,
      .data$cross_modal_connection_weight
    ) %>%
    dplyr::slice_head(n = 500L),
  scroll_x = TRUE,
  options = list(pageLength = 10)
)
```

### Cross-modal interaction network

The final plot shows the mean network made only from cross-modal connections.
It uses the full model's payment-oriented rotation, so its node positions and
axes remain comparable with the multimodal and chat-only plots above.

```{r visualize_cross_modal_interaction_tma}
interaction_coordinates <- as.matrix(
  interaction_tma_set$points
)[, 1:2, drop = FALSE]
interaction_mean_network <- colMeans(
  as.matrix(interaction_tma_set$line.weights)
)

interaction_plot <- rENA::ena.plot(
  interaction_tma_set,
  title = "TMA: Chat and Streamer<br>Cross-Modal Interaction Network",
  dimension.labels = c(
    "Payment-aligned network dimension",
    "Residual SVD dimension"
  )
)

interaction_plot <- rENA::ena.plot.group(
  enaplot = interaction_plot,
  points = interaction_coordinates,
  labels = "All talents",
  colors = "#7B2CBF",
  shape = "circle",
  confidence.interval = "box",
  point.size = 10,
  show.legend = FALSE
)

interaction_plot <- rENA::ena.plot.network(
  enaplot = interaction_plot,
  network = interaction_mean_network,
  colors = "#7B2CBF",
  edge.multiplier = 1,
  labels = get_tma_node_labels(
    ena_set = interaction_tma_set,
    code_label_lookup = node_code_label_lookup
  ),
  label.offset = get_tma_node_label_offsets(interaction_tma_set),
  label.font.size = 9
)

interaction_plot <- set_tma_point_tooltips(
  enaplot = interaction_plot,
  tooltips = sprintf(
    paste0(
      "Group: All talents",
      "<br>Streams: %s",
      "<br>Cross-modal response events: %s",
      "<br>Average payment: %s"
    ),
    nrow(interaction_tma_model$meta.data),
    scales::comma(nrow(interaction_response_events)),
    scales::dollar(
      mean(tma_unit_display$total_paid_amount_usd),
      accuracy = 0.01
    )
  )
)

interaction_plot <- move_tma_node_label_with_leader(
  enaplot = interaction_plot,
  label = "Collective<br>In-Group Framing"
)

interaction_plot
```

The strongest edges in this plot answer: **Which coded ideas tend to bridge
streamer speech and chat activity within the selected window?** The direction
summary and response-event table answer: **When, and in which direction, do
those cross-modal windows occur?**
