---
title: "Variance Project: Qualitative Analysis (TMA)"
format:
  html:
    code-tools: false
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
---

```{r libraries_and_utils}
library(here)
knitr::opts_knit$set(root.dir = here::here())

library(dplyr)
library(tma)

source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "duckdb", "db_connect.R"))
source(here::here("r_scripts", "lib", "import_data", "qualitative_transcripts.R"))
source(here::here("r_scripts", "lib", "transcript_analysis", "qualitative_codes.R"))
source(here::here("r_scripts", "lib", "transcript_analysis", "money_stream_selection.R"))
source(here::here("r_scripts", "lib", "utils", "dt_utils.R"))
```




## Introduction
Live streamers and content creators have become a more common occurence. 

```{r import_paths}
qualitative_dataset_id <- "chat_monetary_growth_variance_30_video"
qualitative_codebook_id <- "chat_monetary_growth_v1"
qualitative_db_path <- talent_lakehouse_db_path()

variance_talent_labels <- c(
  AVA1 = "Ava",
  KAT2 = "Katya",
  LEI3 = "Leia"
)

variance_streamer_handles <- c(
  AVA1 = "@AvaritiaHawthorne",
  KAT2 = "@KatyaSable",
  LEI3 = "@LeiaMemoria"
)
```

```{r importing_qualitative_data}
import_data <- load_qualitative_transcripts_wide(
  codebook_id = qualitative_codebook_id,
  dataset_id = qualitative_dataset_id,
  pipeline_run_id = "latest",
  response_status = NULL,
  db_path = qualitative_db_path
) %>%
  dplyr::mutate(
    talent_name = dplyr::recode(
      .data$talent_code,
      !!!variance_talent_labels
    ),
    row_number = .data$line_number
  ) %>%
  dplyr::select(
    source_file,
    talent_code,
    talent_name,
    video_id,
    row_number,
    timecode,
    source,
    speaker,
    paid_amount_text,
    paid_amount_value,
    paid_currency,
    message_type,
    text,
    starts_with("code_")
  )
```


## Clean transcript speaker labels

The `source` value remains `subtitle` because it identifies the TMA modality.
For subtitle rows, placeholder speaker values such as `STREAM` and `subtitle`
are replaced with the corresponding streamer's handle. The original value is
retained in `speaker_raw` for auditing.

```{r clean_transcript_speakers}
placeholder_streamer_speakers <- c("STREAM", "SUBTITLE")

import_data <- import_data %>%
  dplyr::mutate(
    speaker_raw = .data$speaker,
    speaker_key = toupper(trimws(dplyr::coalesce(.data$speaker, ""))),
    streamer_handle = unname(
      variance_streamer_handles[.data$talent_code]
    ),
    speaker = dplyr::if_else(
      .data$source == "subtitle" &
        .data$speaker_key %in% placeholder_streamer_speakers &
        !is.na(.data$streamer_handle),
      .data$streamer_handle,
      .data$speaker
    )
  ) %>%
  dplyr::select(-speaker_key, -streamer_handle)

unmapped_streamer_speakers <- import_data %>%
  dplyr::filter(
    .data$source == "subtitle",
    toupper(trimws(dplyr::coalesce(.data$speaker, ""))) %in%
      placeholder_streamer_speakers
  )

if (nrow(unmapped_streamer_speakers) > 0L) {
  stop(
    "Some subtitle rows still have placeholder speaker labels. ",
    "Add their talent codes and handles to variance_streamer_handles.",
    call. = FALSE
  )
}

subtitle_speaker_cleaning_summary <- import_data %>%
  dplyr::filter(.data$source == "subtitle") %>%
  dplyr::count(
    .data$talent_name,
    .data$speaker_raw,
    .data$speaker,
    name = "transcript_rows"
  ) %>%
  dplyr::arrange(.data$talent_name)

DTSettings(
  subtitle_speaker_cleaning_summary,
  options = list(pageLength = 10)
)
```







## Introduction
There are two issues with the original ENA model
1. I set an ininfite stanza window, which is an issue because I lose a lot of granularity and control across my dataset. WHile it is fair to assume that conversations from the beginning of the stream are related to the end of the stream, the general scope is just too large to be able to support any kind of analysis. 
1. ENA doesn't handle this multimodal data as well, I do have my data split by streamer and chat. But I got some suggestions that ...
    1. I should just have chat as one massive entity. While chat data is available I'm not particularly interested in the  
    1. While I originally made this model to simply quantify the qualitative qualities from the stream
1. Also another issue, I need to update my chat data so that the streamers sentences are all put together as full sentences rather than as segmented chunks. It's very unnatural and it will mess up the any network analysis.

## Qualitative Codebook

```{r qualitative_codebook}
codebook_data <- load_qualitative_codebook(
  codebook_id = qualitative_codebook_id,
  db_path = qualitative_db_path
)

codebook_display <- codebook_data %>%
  dplyr::mutate(
    code_id = dplyr::if_else(
      is.na(.data[["Secondary Code ID"]]) | !nzchar(trimws(.data[["Secondary Code ID"]])),
      .data[["Primary Code ID"]],
      .data[["Secondary Code ID"]]
    ),
    code_label = dplyr::if_else(
      is.na(.data[["Secondary Code"]]) | !nzchar(trimws(.data[["Secondary Code"]])),
      .data[["Primary Code"]],
      .data[["Secondary Code"]]
    )
  ) %>%
  dplyr::transmute(
    code_id,
    code_label,
    definition = .data[["Definition"]]
  ) %>%
  dplyr::arrange(.data$code_id)

DTSettings(
  codebook_display,
  scroll_x = TRUE,
  options = list(pageLength = 10)
)
```






## Prepare data for TMA
Note I need to fix the data. Streamer text data because it's disjointed. I also have events that are happening simultaneously and technically in two modalities the stream and the chat. There are times where the stream and the chat engage with one another and there are times they do not. 

```{r prepare_tma_data}
code_window_size_back <- 4L
selected_code_cols <- select_frequent_code_pairs(
  data = import_data,
  codebook = codebook_data,
  n = 8L,
  window_size_back = code_window_size_back,
  prefer = "secondary"
)$selected_code_cols

removed_low_frequency_code_col <- selected_code_cols[[length(selected_code_cols)]]
selected_code_cols <- c(
  selected_code_cols[-length(selected_code_cols)],
  "gave_money"
)

tma_input_data <- import_data %>%
  normalize_text_playback_paid_amounts() %>%
  dplyr::mutate(
    paid_amount_value = .data$paid_amount_native,
    paid_currency = .data$paid_currency_norm,
    gave_money = !is.na(.data$paid_amount_value) & .data$paid_amount_value > 0
  ) %>%
  dplyr::select(
    source_file,
    talent_name,
    video_id,
    row_number,
    timecode,
    source,
    speaker,
    message_type,
    text,
    paid_amount_text,
    paid_amount_value,
    paid_currency,
    paid_amount_usd,
    dplyr::all_of(selected_code_cols)
  )
```


The model retains eight nodes. `gave_money` replaces
`r removed_low_frequency_code_col`, the lowest-ranked member of the previous
eight qualitative codes based on windowed pair participation.





## TMA Setup

Chat and subtitle rows are modeled as separate modalities. Each talent-stream
combination is a unit of analysis. The flexible horizon below makes the
observation boundary modality-specific while keeping both modalities within the
unit's own stream:

- Chat contributes the collective chat activity for the talent-video unit.
- Subtitles contribute the streamer's speech for the same talent-video unit.
- Events from other talents or videos remain outside the unit's horizon.

```{r tma_setup}
flexible_horizon_rules <- tma::rules(
  source == "chat" &
    talent_name %in% UNIT$talent_name &
    video_id %in% UNIT$video_id,
  source == "subtitle" &
    talent_name %in% UNIT$talent_name &
    video_id %in% UNIT$video_id
)

context_model <- tma::contexts(
  x = tma_input_data,
  units_by = c("talent_name", "video_id"),
  hoo_rules = flexible_horizon_rules
)

context_window_tensor <- tma::context_tensor(
  df = tma_input_data,
  mode_column = "source",
  default_window = 4,
  default_weight = 1
)

# context_window_tensor["chat", "window"] <- 4
# context_window_tensor["subtitle", "window"] <- 1
```



The horizon rules determine which events a unit can observe. The tensor
determines how far an observed event can influence connections: four rows for
chat and one row for subtitles. Because every row is already assigned to a
talent-video unit, these horizon rules formalize the stream boundary but do not
expand it. Reproducing the tutorial's group-versus-individual asymmetry would
require an actor-level unit identifier analogous to its `userID`.


## Visualize the TMA

Accumulate the code connections using the modality-specific windows above, then
project the resulting unit networks into a two-dimensional ENA space.

```{r tma_accumulation}
tma_model <- tma::accumulate(
  context_model = context_model,
  codes = selected_code_cols,
  tensor = context_window_tensor,
  ordered = FALSE,
  binary = TRUE
)

tma_set <- rENA::ena.make.set(tma_model)
```




The points represent talent-stream units, while the network summarizes the mean
code connections across all units. Edge thickness indicates connection strength.

```{r tma_visualization}
tma_plot <- plot(
  tma_set,
  empty = FALSE,
  title = "TMA: Chat and Subtitle Code Connections"
) |>
  rENA::add_network(
    colors = "#0072B2",
    edge.multiplier = 1
  )

tma_plot
```


## TMA X axis change

### How I reached this decision

Each talent-video unit is represented by its complete vector of normalized code
connections, rather than by one value for each code. The default SVD rotation
orients the first dimension toward the largest source of variation among those
network vectors. That direction is useful for describing general network
variation, but it is not guaranteed to have any relationship with payment.

The research question requires a more specific orientation:

> As total stream payment increases, how does the relative configuration of
> connections among chat, subtitle, and payment-related codes change?

The current [`rENA` documentation](https://cran.r-universe.dev/rENA/doc/manual.html)
identifies `rENA::ena.rotate.by.generalized()` as the generalized means rotation
(GMR) method. Its `x_var` parameter is a data frame whose first column is the
target variable. With a numeric target, GMR estimates a direction through
network space associated with increases in that variable. If `y_var` is
omitted, rENA obtains the second dimension from an SVD of the network variation
remaining after the payment-aligned direction is removed.

The rotation changes the viewing direction, not the underlying connection
weights. The original SVD model will therefore remain available as the
descriptive baseline, and a second GMR model will answer the
payment-oriented question.

### X-axis interpretation plan

The new x-axis will represent a gradient from network structures associated
with lower total payment to network structures associated with higher total
payment:

```text
Lower-payment-associated networks  <---->  Higher-payment-associated networks
```

- A point farther right has more of the overall network pattern associated with
  higher total payment.
- A point farther left has more of the network pattern associated with lower
  total payment.
- A point near zero is near the average network configuration on this
  payment-related contrast.

The x-coordinate is still a normalized ENA coordinate. It is not a dollar
amount, and a change of 0.10 on the x-axis has no fixed USD interpretation.
The axis will therefore be labeled **Payment-aligned network dimension**.
Actual `total_paid_amount_usd` values will be represented separately through
point color, labels, tooltips, or an accompanying diagnostic plot.

After rotation, nodes and connections positioned toward the right help
characterize higher-payment-associated networks, while those toward the left
help characterize lower-payment-associated networks. This supports
associational statements about network configuration. It does not establish
that a code or connection caused additional payments.

### Why two payment variables are needed

`gave_money` and `total_paid_amount_usd` have different analytical roles:

```text
gave_money
    -> transcript-level binary code and node inside each network

total_paid_amount_usd
    -> talent-stream-level continuous variable used to orient the x-axis
```

Keeping `gave_money` in the code set allows the network to show how payment
events connect with chat and streamer behavior. Rotating by
`total_paid_amount_usd` asks which complete network configurations distinguish
lower-revenue streams from higher-revenue streams.

### Variables

| Variable | Level | Planned role |
| --- | --- | --- |
| `talent_name`, `video_id` | Talent-stream unit | Join keys matching the unit definition used by `tma::contexts()` |
| `paid_amount_value` | Transcript row | Native-currency amount; excluded as the rotation target because the data contain multiple currencies |
| `paid_amount_usd` | Transcript row | Currency-normalized payment amount used to construct the unit-level target |
| `gave_money` | Transcript row | Binary TMA code retained as a network node in the primary specification |
| `total_paid_amount_usd` | Talent-stream unit | Sum of `paid_amount_usd` within each `talent_name` and `video_id`; primary continuous rotation target |
| `paid_event_count` | Talent-stream unit | Count of positive-payment rows used to audit the aggregation |
| `payment_x_var` | Model-unit order | One-column data frame containing `total_paid_amount_usd`, ordered exactly like `tma_model$meta.data` and supplied as `rotation.params$x_var` |
| `payment_x_coordinate` | Talent-stream unit | Resulting first-dimension ENA coordinate; a network score rather than a USD amount |

The current data contain 30 talent-video units and 499 paid events across 16
currencies. All positive-payment rows have a USD conversion. Unit totals range
from USD 21.02 to USD 264.82, so the primary rotation will use untransformed
`total_paid_amount_usd`.

### Circularity and robustness plan

The same payment events contribute to both the `gave_money` code and
`total_paid_amount_usd`. The primary model may therefore find a payment gradient
partly because higher-payment streams contain more payment-related network
activity. This is substantively appropriate for the primary question:

> How are payment events embedded within the broader interaction structure of
> higher- and lower-revenue streams?

It is less informative about whether non-payment discourse distinguishes stream
revenue. The analysis will therefore include a sensitivity model that removes
`gave_money` from the network while retaining `total_paid_amount_usd` as the
rotation target. Similar substantive patterns across the two specifications
would suggest that the gradient reflects broader interaction structure rather
than only the presence of payment events.

Because there are only 30 units, the analysis will also examine whether a few
high-payment streams determine the direction. Planned checks include a
`log1p(total_paid_amount_usd)` rotation and leave-one-unit-out stability checks.

### Updated implementation plan

1. Aggregate `paid_amount_usd` and `gave_money` by `talent_name` and `video_id`
   to create `total_paid_amount_usd` and `paid_event_count`.
2. Join the unit-level payment summary to `tma_model$meta.data`, preserve the
   model's row order, and validate one complete payment value per model unit.
3. Construct `payment_x_var` with untransformed `total_paid_amount_usd` as its
   first and only column.
4. Create a second ENA set using
   `rotation.by = rENA::ena.rotate.by.generalized` and
   `rotation.params = list(x_var = payment_x_var)`. Preserve the original
   SVD-based `tma_set` for comparison.
5. Confirm that the first coordinate increases with
   `total_paid_amount_usd`. If necessary, reverse the first rotation vector so
   lower-payment streams appear on the left and higher-payment streams appear
   on the right.
6. Plot the payment-rotated points and mean network. Label the x-axis
   **Payment-aligned network dimension** and use a continuous point-color scale
   for the literal `total_paid_amount_usd` values.
7. Report the correlation between `payment_x_coordinate` and
   `total_paid_amount_usd` as an in-sample alignment diagnostic, not as
   independent evidence that the network predicts payment.
8. Compare the original SVD plot with the payment-oriented GMR plot, then run
   the no-`gave_money`, `log1p()` target, and leave-one-unit-out sensitivity
   checks before interpreting the gradient.