---
title: "Variance Project: TMA Monetary Axis"
format:
  html:
    code-tools: false
    embed-resources: true
execute:
  echo: false
  message: false
  warning: false
---

```{r libraries_and_utils}
library(here)
knitr::opts_knit$set(root.dir = here::here())

library(dplyr)
library(tma)

source(here::here("r_scripts", "lib", "utils", "datalake_root.r"))
source(here::here("r_scripts", "lib", "duckdb", "db_connect.R"))
source(here::here("r_scripts", "lib", "import_data", "qualitative_transcripts.R"))
source(here::here("r_scripts", "lib", "transcript_analysis", "qualitative_codes.R"))
source(here::here("r_scripts", "lib", "transcript_analysis", "money_stream_selection.R"))
source(here::here("r_scripts", "lib", "utils", "dt_utils.R"))
```




## Introduction
Live streamers and content creators have become a more common occurence.

```{r import_paths}
qualitative_dataset_id <- "chat_monetary_growth_variance_30_video"
qualitative_codebook_id <- "chat_monetary_growth_v1"
qualitative_db_path <- talent_lakehouse_db_path()

variance_talent_labels <- c(
  AVA1 = "Ava",
  KAT2 = "Katya",
  LEI3 = "Leia"
)

variance_streamer_handles <- c(
  AVA1 = "@AvaritiaHawthorne",
  KAT2 = "@KatyaSable",
  LEI3 = "@LeiaMemoria"
)
```

```{r importing_qualitative_data}
import_data <- load_qualitative_transcripts_wide(
  codebook_id = qualitative_codebook_id,
  dataset_id = qualitative_dataset_id,
  pipeline_run_id = "latest",
  response_status = NULL,
  db_path = qualitative_db_path
) %>%
  dplyr::mutate(
    talent_name = dplyr::recode(
      .data$talent_code,
      !!!variance_talent_labels
    ),
    row_number = .data$line_number
  ) %>%
  dplyr::select(
    source_file,
    talent_code,
    talent_name,
    video_id,
    row_number,
    timecode,
    source,
    speaker,
    paid_amount_text,
    paid_amount_value,
    paid_currency,
    message_type,
    text,
    starts_with("code_")
  )
```


## Clean transcript speaker labels

The `source` value remains `subtitle` because it identifies the TMA modality.
For subtitle rows, placeholder speaker values such as `STREAM` and `subtitle`
are replaced with the corresponding streamer's handle. The original value is
retained in `speaker_raw` for auditing.

```{r clean_transcript_speakers}
placeholder_streamer_speakers <- c("STREAM", "SUBTITLE")

import_data <- import_data %>%
  dplyr::mutate(
    speaker_raw = .data$speaker,
    speaker_key = toupper(trimws(dplyr::coalesce(.data$speaker, ""))),
    streamer_handle = unname(
      variance_streamer_handles[.data$talent_code]
    ),
    speaker = dplyr::if_else(
      .data$source == "subtitle" &
        .data$speaker_key %in% placeholder_streamer_speakers &
        !is.na(.data$streamer_handle),
      .data$streamer_handle,
      .data$speaker
    )
  ) %>%
  dplyr::select(-speaker_key, -streamer_handle)

unmapped_streamer_speakers <- import_data %>%
  dplyr::filter(
    .data$source == "subtitle",
    toupper(trimws(dplyr::coalesce(.data$speaker, ""))) %in%
      placeholder_streamer_speakers
  )

if (nrow(unmapped_streamer_speakers) > 0L) {
  stop(
    "Some subtitle rows still have placeholder speaker labels. ",
    "Add their talent codes and handles to variance_streamer_handles.",
    call. = FALSE
  )
}

subtitle_speaker_cleaning_summary <- import_data %>%
  dplyr::filter(.data$source == "subtitle") %>%
  dplyr::count(
    .data$talent_name,
    .data$speaker_raw,
    .data$speaker,
    name = "transcript_rows"
  ) %>%
  dplyr::arrange(.data$talent_name)

DTSettings(
  subtitle_speaker_cleaning_summary,
  options = list(pageLength = 10)
)
```







## Introduction
There are two issues with the original ENA model
1. I set an ininfite stanza window, which is an issue because I lose a lot of granularity and control across my dataset. WHile it is fair to assume that conversations from the beginning of the stream are related to the end of the stream, the general scope is just too large to be able to support any kind of analysis.
1. ENA doesn't handle this multimodal data as well, I do have my data split by streamer and chat. But I got some suggestions that ...
    1. I should just have chat as one massive entity. While chat data is available I'm not particularly interested in the
    1. While I originally made this model to simply quantify the qualitative qualities from the stream
1. Also another issue, I need to update my chat data so that the streamers sentences are all put together as full sentences rather than as segmented chunks. It's very unnatural and it will mess up the any network analysis.

## Qualitative Codebook

```{r qualitative_codebook}
codebook_data <- load_qualitative_codebook(
  codebook_id = qualitative_codebook_id,
  db_path = qualitative_db_path
)

codebook_display <- codebook_data %>%
  dplyr::mutate(
    code_id = dplyr::if_else(
      is.na(.data[["Secondary Code ID"]]) | !nzchar(trimws(.data[["Secondary Code ID"]])),
      .data[["Primary Code ID"]],
      .data[["Secondary Code ID"]]
    ),
    code_label = dplyr::if_else(
      is.na(.data[["Secondary Code"]]) | !nzchar(trimws(.data[["Secondary Code"]])),
      .data[["Primary Code"]],
      .data[["Secondary Code"]]
    )
  ) %>%
  dplyr::transmute(
    code_id,
    code_label,
    definition = .data[["Definition"]]
  ) %>%
  dplyr::arrange(.data$code_id)

DTSettings(
  codebook_display,
  scroll_x = TRUE,
  options = list(pageLength = 10)
)
```






## Prepare data for TMA
Note I need to fix the data. Streamer text data because it's disjointed. I also have events that are happening simultaneously and technically in two modalities the stream and the chat. There are times where the stream and the chat engage with one another and there are times they do not.

```{r prepare_tma_data}
code_window_size_back <- 4L
selected_code_cols <- select_frequent_code_pairs(
  data = import_data,
  codebook = codebook_data,
  n = 8L,
  window_size_back = code_window_size_back,
  prefer = "secondary"
)$selected_code_cols

removed_low_frequency_code_col <- selected_code_cols[[length(selected_code_cols)]]
selected_code_cols <- c(
  selected_code_cols[-length(selected_code_cols)],
  "gave_money"
)

tma_input_data <- import_data %>%
  normalize_text_playback_paid_amounts() %>%
  dplyr::mutate(
    paid_amount_value = .data$paid_amount_native,
    paid_currency = .data$paid_currency_norm,
    gave_money = !is.na(.data$paid_amount_value) & .data$paid_amount_value > 0
  ) %>%
  dplyr::select(
    source_file,
    talent_name,
    video_id,
    row_number,
    timecode,
    source,
    speaker,
    message_type,
    text,
    paid_amount_text,
    paid_amount_value,
    paid_currency,
    paid_amount_usd,
    dplyr::all_of(selected_code_cols)
  )
```


The model retains eight nodes. `gave_money` replaces
`r removed_low_frequency_code_col`, the lowest-ranked member of the previous
eight qualitative codes based on windowed pair participation.





## TMA Setup

Chat and subtitle rows are modeled as separate modalities. Each talent-stream
combination is a unit of analysis. The flexible horizon below makes the
observation boundary modality-specific while keeping both modalities within the
unit's own stream:

- Chat contributes the collective chat activity for the talent-video unit.
- Subtitles contribute the streamer's speech for the same talent-video unit.
- Events from other talents or videos remain outside the unit's horizon.

```{r tma_setup}
flexible_horizon_rules <- tma::rules(
  source == "chat" &
    talent_name %in% UNIT$talent_name &
    video_id %in% UNIT$video_id,
  source == "subtitle" &
    talent_name %in% UNIT$talent_name &
    video_id %in% UNIT$video_id
)

context_model <- tma::contexts(
  x = tma_input_data,
  units_by = c("talent_name", "video_id"),
  hoo_rules = flexible_horizon_rules
)

context_window_tensor <- tma::context_tensor(
  df = tma_input_data,
  mode_column = "source",
  default_window = 4,
  default_weight = 1
)

# context_window_tensor["chat", "window"] <- 4
# context_window_tensor["subtitle", "window"] <- 1
```



The horizon rules determine which events a unit can observe. The tensor
determines how far an observed event can influence connections. The current
model uses a four-row window for both chat and subtitles. The commented
assignments show where modality-specific windows can be restored if the
substantive model changes. Because every row is already assigned to a
talent-video unit, these horizon rules formalize the stream boundary but do not
expand it.


## Visualize the TMA

Accumulate the code connections using the modality-specific windows above, then
project the resulting unit networks into a two-dimensional ENA space.

```{r tma_accumulation}
tma_model <- tma::accumulate(
  context_model = context_model,
  codes = selected_code_cols,
  tensor = context_window_tensor,
  ordered = FALSE,
  binary = TRUE
)

tma_set <- rENA::ena.make.set(tma_model)

tma_unit_display <- tibble::tibble(
  talent_name = as.vector(tma_model$meta.data[["talent_name"]]),
  video_id = as.vector(tma_model$meta.data[["video_id"]])
) %>%
  dplyr::left_join(
    tma_input_data %>%
      dplyr::group_by(.data$talent_name, .data$video_id) %>%
      dplyr::summarise(
        source_file = dplyr::first(.data$source_file),
        source_file_count = dplyr::n_distinct(.data$source_file),
        total_paid_amount_usd = sum(.data$paid_amount_usd, na.rm = TRUE),
        .groups = "drop"
      ),
    by = c("talent_name", "video_id")
  )

if (
  any(tma_unit_display$source_file_count != 1L) ||
    any(is.na(tma_unit_display$source_file)) ||
    any(!is.finite(tma_unit_display$total_paid_amount_usd))
) {
  stop(
    "Each TMA unit must have one source file and one finite USD total.",
    call. = FALSE
  )
}

tma_unit_display <- tma_unit_display %>%
  dplyr::mutate(
    source_file_label = tools::file_path_sans_ext(
      basename(.data$source_file)
    ),
    stream_name = dplyr::if_else(
      endsWith(
        .data$source_file_label,
        paste0("_", .data$video_id)
      ),
      substr(
        .data$source_file_label,
        1L,
        nchar(.data$source_file_label) - nchar(.data$video_id) - 1L
      ),
      .data$source_file_label
    ),
    stream_name = trimws(gsub("_+", " ", .data$stream_name))
  ) %>%
  dplyr::select(-dplyr::all_of("source_file_count"))

wrap_tooltip_title <- function(title, width = 42L) {
  vapply(
    title,
    function(value) {
      paste(strwrap(value, width = width), collapse = "<br>")
    },
    character(1)
  )
}

tma_unit_display <- tma_unit_display %>%
  dplyr::mutate(
    tooltip = sprintf(
      "<b>%s</b><br>Streamer: %s<br>Total payment: USD %.2f",
      wrap_tooltip_title(.data$stream_name),
      .data$talent_name,
      .data$total_paid_amount_usd
    )
  )

set_tma_point_tooltips <- function(enaplot, tooltips) {
  built_plot <- plotly::plotly_build(enaplot$plot)
  point_trace_indices <- which(
    vapply(
      built_plot$x$data,
      function(trace) {
        length(trace$hoverinfo) == 1L &&
          identical(trace$hoverinfo, "x+y+name")
      },
      logical(1)
    )
  )

  if (length(point_trace_indices) != length(tooltips)) {
    stop(
      "The number of TMA point traces does not match the tooltip labels.",
      call. = FALSE
    )
  }

  for (point_index in seq_along(point_trace_indices)) {
    trace_index <- point_trace_indices[[point_index]]
    built_plot$x$data[[trace_index]]$hoverinfo <- "text"
    built_plot$x$data[[trace_index]]$hovertemplate <- paste0(
      tooltips[[point_index]],
      "<extra></extra>"
    )
    built_plot$x$data[[trace_index]]$hoverlabel <- list(align = "left")
  }

  enaplot$plot <- built_plot
  enaplot
}
```




The points represent talent-stream units, while the network summarizes the mean
code connections across all units. Point tooltips show the readable stream name
derived from `source_file`, the streamer, and the stream's total USD payment.
Coordinates and `video_id` are hidden from the tooltip, although `video_id`
remains available in `tma_unit_display` as the internal join key. Edge thickness
indicates connection strength.

```{r tma_visualization}
tma_plot <- rENA::ena.plot(
  tma_set,
  title = "TMA: Chat and Subtitle Code Connections"
  ) |>
  rENA::ena.plot.points(
    points = tma_set$points,
    labels = tma_unit_display$stream_name,
    show.legend = FALSE
  ) |>
  rENA::add_network(
    colors = "#0072B2",
    edge.multiplier = 1
  )

tma_plot <- set_tma_point_tooltips(
  enaplot = tma_plot,
  tooltips = tma_unit_display$tooltip
)

tma_plot
```


## TMA monetary axis

The default `tma_set` uses an SVD rotation, so its first dimension describes
the largest source of variation in the unit networks. To answer the monetary
question directly, the same accumulated `tma_model` can instead be rotated
toward total payment with `rENA::ena.rotate.by.generalized()`.

This requires three steps:

1. Aggregate `paid_amount_usd` to the talent-video level and arrange those
   values in the same order as `tma_model$meta.data`.
2. Create the generalized-rotation ENA set with the payment target as `x_var`.
3. Plot the payment-oriented set.

The rotation changes the orientation of the existing network space. It does not
rebuild the TMA connections or convert the ENA coordinate into dollars.

### 1. Create the payment target

`paid_amount_usd` is used instead of `paid_amount_value` because the latter
contains native-currency amounts. `tma_unit_display` already follows the
model's row order and contains the cleaned `source_file` label, the retained
`video_id` join key, and the stream's USD total.

```{r payment_target}
payment_x_var <- tma_unit_display %>%
  dplyr::select(.data$total_paid_amount_usd) %>%
  as.data.frame()

if (
  nrow(payment_x_var) != nrow(tma_model$meta.data) ||
    any(!is.finite(payment_x_var$total_paid_amount_usd))
) {
  stop(
    "Each TMA unit must have one finite total_paid_amount_usd value.",
    call. = FALSE
  )
}
```

### 2. Apply the generalized rotation

This is the complete monetary-axis model. `payment_x_var` is a one-column data
frame because `ena.rotate.by.generalized()` uses its first column as the
continuous rotation target.

```{r payment_rotation}
tma_money_set <- rENA::ena.make.set(
  enadata = tma_model,
  rotation.by = rENA::ena.rotate.by.generalized,
  rotation.params = list(x_var = payment_x_var)
)
```

The first coordinate now represents the network direction associated with
increasing total payment. The second coordinate is the leading residual SVD
dimension produced by the generalized rotation.

### 3. Plot the payment-oriented TMA

The horizontal coordinate is a normalized network score—not a dollar amount.
The hover label supplies the corresponding unit-level USD total.

```{r payment_plot}
tma_money_plot <- rENA::ena.plot(
  tma_money_set,
  title = "TMA: Payment-Aligned Network",
  dimension.labels = c(
    "Payment-aligned network dimension",
    "Residual SVD dimension"
  )
  ) |>
  rENA::ena.plot.points(
    points = tma_money_set$points,
    labels = tma_unit_display$stream_name,
    show.legend = FALSE
  ) |>
  rENA::add_network(
    colors = "#0072B2",
    edge.multiplier = 1
  )

tma_money_plot <- set_tma_point_tooltips(
  enaplot = tma_money_plot,
  tooltips = tma_unit_display$tooltip
)

tma_money_plot
```

### Goodness of fit

`rENA::ena.correlations()` reports the co-registration goodness of fit between
the plotted unit points and their corresponding network centroids. Pearson and
Spearman correlations are reported separately for each plotted dimension.
Values closer to one indicate that the visualization more faithfully
represents the underlying network model.

```{r payment_goodness_of_fit}
tma_money_goodness_of_fit <- rENA::ena.correlations(
  tma_money_set,
  dims = c(1, 2)
)

rownames(tma_money_goodness_of_fit) <- c(
  "Payment-aligned network dimension",
  "Residual SVD dimension"
)

knitr::kable(
  tma_money_goodness_of_fit,
  digits = 3,
  caption = "TMA co-registration goodness of fit"
)
```

These correlations evaluate the fit of the network visualization to the
underlying model. They do not measure how much variance in USD payment is
explained by the monetary axis.

Read points farther to the right as units whose connection patterns are more
strongly associated with higher total payment, and points farther to the left
as units whose patterns are more strongly associated with lower total payment.
This is an associational network gradient; it is not a literal USD axis or a
causal estimate.
