---
title: "BundleA"
author: "Jonathon Sun"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float: true
    toc_depth: 3
params:
  talent: "Ava"
  window_days: null
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo     = FALSE,
  message  = FALSE, 
  warning  = FALSE,
  fig.align = "center"
)

plot_w_std <- 10
plot_h_std <- 6
plot_w_facet <- 11
plot_h_facet <- 8
plot_w_dense <- 12
plot_h_dense <- 8

knitr::opts_knit$set(root.dir = here::here())

if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(
    fig.width  = 14,
    fig.height = 8,
    out.width  = "0.8\\linewidth"
  )
} else {
  knitr::opts_chunk$set(
    fig.width  = plot_w_std,
    fig.height = plot_h_std
  )
}


```

```{r libraries, include=FALSE}

library(tidyverse)
library(purrr)
library(here)
library(ggplot2)
library(DT)
library(plotly)

```

```{r modules, include=FALSE}

source("scripts/lib/utils/staging_root.R")

list.files(here("scripts","lib","plots","report","bundle_A"), full.names = TRUE) %>%
    walk(source)
list.files(here("scripts","lib","utils"), full.names = TRUE) %>%
    walk(source)
list.files(here("scripts", "lib", "import_data"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
list.files(here("scripts", "lib", "report_tables"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
source(here("scripts","lib","plots","PlottingThemes.R"))

clean_data_dir <- here::here("scripts", "lib", "clean_data")
source(file.path(clean_data_dir, "analytics_core.R"))
source(file.path(clean_data_dir, "analytics_join.R"))
source(file.path(clean_data_dir, "clean_columns.R"))
source(file.path(clean_data_dir, "video_prep.R"))
source(file.path(clean_data_dir, "title_classification_join.R"))

root <- get_staging_root()
```

```{r load_data, include = FALSE}
talent_root <- list.files(root, full.names = TRUE)

Talent <- as.character(params$talent)
if (length(Talent) != 1 || is.na(Talent) || !nzchar(trimws(Talent))) {
  stop("`params$talent` must be a single non-empty talent name.")
}
Talent <- trimws(Talent)

window_days <- params$window_days
if (is.null(window_days) || (length(window_days) == 1 && is.na(window_days))) {
  window_days <- NA_integer_
} else {
  window_days <- suppressWarnings(as.integer(window_days))
  if (length(window_days) != 1 || is.na(window_days) || window_days <= 0) {
    stop("`params$window_days` must be NULL/NA or a single positive integer.")
  }
}

window_end_date <- Sys.Date()
window_start_date <- if (is.na(window_days)) {
  as.Date(NA)
} else {
  window_end_date - as.integer(window_days) + 1
}

talent_root <- select_talent(Talent)
files <- TalentFiles(talent_root)

titles <- load_title_classifications(talent = Talent)
preps <- video_preps_with_titles(
  files = files,
  titles = titles,
  talent = Talent,
  dedupe = TRUE,
  key_cols = "Video ID",
  sort_cols = c("confidence", "published_at", "Published At"),
  dedupe_sets = c("analytics", "monetary", "demo")
)

analytics <- preps$analytics
monetary  <- preps$monetary
demo      <- preps$demo

apply_days_back_window <- function(df, days_back) {
  if (is.na(days_back) || nrow(df) == 0) {
    return(df)
  }

  date_col <- bundle_a_optional_col(
    df,
    candidates = c("publish_date", "Published At", "date"),
    label = "analysis window date column"
  )
  if (is.null(date_col)) {
    return(df)
  }

  df %>%
    mutate(.window_date = bundle_a_as_date(.data[[date_col]])) %>%
    filter(
      !is.na(.data$.window_date),
      .data$.window_date >= window_start_date,
      .data$.window_date <= window_end_date
    ) %>%
    select(-.window_date)
}

analytics <- apply_days_back_window(analytics, window_days)
monetary  <- apply_days_back_window(monetary, window_days)
demo      <- apply_days_back_window(demo, window_days)

if (nrow(analytics) == 0 || nrow(monetary) == 0) {
  stop(
    "No data after applying the selected window. ",
    "At least analytics and monetary data are required. ",
    "Try a larger `window_days` value or set it to NULL for all available data."
  )
}

demo_available <- nrow(demo) > 0

# Backward-compatible alias used by some legacy chunks.
df <- analytics
```

# Start Here: How To Use This Report
This report is designed for quick scanning by managers and talent teams.  
Use the floating table of contents to jump directly to the section tied to your decision.

## Quick Paths by Role
1. **Manager fast scan (5-10 minutes):** Overall Performance Snapshot -> Trends Over Time -> Collaboration Effectiveness -> Wrap-up.
2. **Talent optimization path:** Engagement Distribution -> Timing Effects -> Topic Performance -> Tag Performance.
3. **Audience strategy path:** Audience Age + Gender Trends -> Core Audience Stability.

## How to Interpret Responsibly
- This report is **observational**, not causal. It shows patterns, not proof of cause-and-effect.
- Tag and topic metrics can be influenced by timing, promotion, seasonality, and posting volume.
- Core and Potential audience shares are complementary (`Potential = 100% - Core`), so inverse movement is expected.
- Tag totals are directional because tags can overlap across videos.

## Standard vs Customized Content
The structure and chart explanations are standardized for consistency across talents.  
Use the **Wrap-up** section to add talent-specific narrative and recommendations.

## Active Analysis Window
```{r analysis-window-summary}
if (is.na(window_days)) {
  cat("**Window setting:** All available staged data (no days-back filter).")
} else {
  cat(
    "**Window setting:** Last ", window_days, " days ",
    "(", format(window_start_date, "%Y-%m-%d"), " to ", format(window_end_date, "%Y-%m-%d"), ").",
    sep = ""
  )
}

cat("\n\n")
cat(
  "**Rows in active window:** ",
  "analytics=", nrow(analytics), ", ",
  "monetary=", nrow(monetary), ", ",
  "demographics=", nrow(demo),
  ".",
  sep = ""
)
```

# Overall Performance Snapshot
**Section goal:** Establish a shared baseline of total scale, per-video efficiency, and revenue mix.

## Views by Content Type (Total vs Average)
**What this chart shows:** Total views and average views per video for each content type in one side-by-side view.  
**How to read it:** Use the Total panel to see overall volume and the Average panel to see per-upload performance, then compare formats across both.

```{r views by content comparison, fig.width=plot_w_facet, fig.height=plot_h_facet}
ggplotly(
  views_content_type_comparison(analytics, Talent) +
  theme_nyt()
)

```

## Combined Performance Trends (Views + Revenue)
**What this chart shows:** How views and revenue move over time across the reporting period.  
**How to read it:** Look for rises, drops, and turning points to see when performance accelerated or slowed.

```{r combined performance trends, fig.width=plot_w_std, fig.height=plot_h_std}
ggplotly(
  performance_trends_over_time(
    analytics_df = analytics,
    monetary_df = monetary,
    talent = Talent,
    freq = "month",
    value_mode = "raw"
  )
)
```

## Total Revenue by content type 
**What this chart shows:** Total estimated revenue grouped by content type for each month.  
**How to read it:** Larger segments indicate where more revenue was generated in that month.

```{r views by content over time, fig.width=plot_w_std, fig.height=plot_h_std}
ggplotly(
  total_metric_content_type(
    monetary,
    Talent,
    metric_col = "Estimated Revenue",
    metric_label = "Revenue",
    window_months = 1,
    bar_position = "stack",
    show_counts = TRUE
  )
)

```

## Engagement Distribution by Content Type
**What this chart shows:** Distribution of per-video engagement for each content type.  
**How to read it:** Each dot is a video; the box shows the middle range, the center line is the median, and the spread shows consistency vs volatility.

```{r engagement distribution, fig.width=plot_w_std, fig.height=plot_h_std}
analytics_eng <- analytics %>%
  mutate(avg_view_prop = averageViewPercentage / 100)

ggplotly(
  engagement_distribution_content_type(
    analytics_eng,
    Talent,
    metric_col = "avg_view_prop",
    metric_label = "Average View %",
    y_as_percent = TRUE
  ),
  tooltip = "text"
)
```

## Median Engagement by Content Type
**What this chart shows:** Median engagement level by content type, with variability shown around that median.  
**How to read it:** Higher bars mean stronger typical engagement; wider error bars mean outcomes vary more between videos.

```{r engagement summary by content, fig.width=plot_w_std, fig.height=plot_h_std}
eng_summary <- engagement_summary_content_type_prep(
  analytics_eng,
  metric_col = "avg_view_prop"
)

ggplotly(
  engagement_summary_content_type_plot(
    eng_summary,
    Talent,
    metric_label = "Average View %",
    y_as_percent = TRUE
  )
)
```

```{r}
factorCols <- if (exists("factorCols")) factorCols else c("Content Type")

UIdf<- df %>%
  select(
    Title,
    publish_date,
    `Content Type`,
    matches("estimated|average", ignore.case = TRUE)
  ) %>%
  mutate(across(any_of(factorCols), as.factor))

DTSettings(UIdf)
```

# Trends Over Time
**Section goal:** Show whether performance patterns are improving, stable, or declining over time.

## Views over time by content type
**What this chart shows:** How views change over time for each content type.  
**How to read it:** Compare trend lines to see which formats are growing, stable, or declining over time.

```{r import monetary data, fig.width=plot_w_facet, fig.height=plot_h_facet}
ggplotly(
  Content_duration_views(df, Talent) +
  theme_nyt()
)

```

## Revenue over time by content type
**What this chart shows:** How estimated revenue changes over time for each content type.  
**How to read it:** Compare trajectories to identify which formats are contributing more monetization over time.

```{r monetary data by content, fig.width=plot_w_facet, fig.height=plot_h_facet}

ggplotly(
  content_duration_metric(monetary, Talent, "Estimated Revenue") +
  theme_nyt()

)


```

# Audience Composition
**Section goal:** Clarify who the audience is and whether the audience mix is concentrating or broadening.

## Audience Age + Gender Trends
**What this chart shows:** Audience share trends over time by age and gender segments.  
**How to read it:** Track which segments are growing, shrinking, or staying stable month to month.

```{r audience age and gender trends, fig.width=plot_w_facet, fig.height=plot_h_facet}
if (!isTRUE(demo_available)) {
  cat("No audience demographics data available in the selected window.")
} else {
  tryCatch(
    {
      plot_df <- audience_age_gender_trends_prep(
        demo_df = demo,
        freq = "month"
      )
      if (nrow(plot_df) == 0) {
        cat("No audience trend rows available in the selected window.")
      } else {
        ggplotly(
          audience_age_gender_trends_plot(
            plot_df = plot_df,
            talent = Talent
          )
        )
      }
    },
    error = function(e) {
      cat("Audience trend section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

## Core Audience Stability

**What this chart shows:**  
- **Core audience share:** the monthly share of your largest audience segment (top age + gender group).  
- **Potential audience share:** everyone else combined (all non-core segments).

**How to read it:**  
- If **Core** rises and **Potential** falls, your audience is becoming more concentrated in one segment.  
- If **Core** falls and **Potential** rises, your audience is broadening across more segments.  
- Stable lines suggest a steady audience mix month to month.
- Both lines are on the same 0-100% scale so month-to-month comparisons are direct.

**Why this view is easier:**  
It turns a technical concentration metric into two plain-language shares that are easier to explain to non-technical readers.

```{r audience stability, fig.width=plot_w_facet, fig.height=plot_h_facet}
if (!isTRUE(demo_available)) {
  cat("No audience demographics data available in the selected window.")
} else {
  tryCatch(
    {
      core_stability <- audience_core_segment_stability_prep(
        demo_df = demo,
        freq = "month"
      )
      if (nrow(core_stability) == 0) {
        cat("No core audience rows available in the selected window.")
      } else {
        ggplotly(
          audience_core_segment_stability_plot(
            stability_df = core_stability,
            talent = Talent
          ),
          tooltip = "text"
        )
      }
    },
    error = function(e) {
      cat("Core audience section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

# Monetization Quality (Views to Dollars)
**Section goal:** Connect consumption performance to monetization efficiency.
```{r monetary data table}

Table <- revenue_stream_ratio_table(monetary)

DTSettings(
  Table,
  class = "display stripe hover",
  scroll_x = TRUE
)

```

# Content Strategy Deep Dive
**Section goal:** Turn performance patterns into actionable choices across timing, collaboration, topics, and tags.

## Timing Effects: Weekend vs Weekday
**What this chart shows:** Per-video distributions of views and revenue for weekend vs weekday uploads.  
**How to read it:** Each dot is a video; compare medians, mean points, and spread to see whether one day type is typically stronger or more consistent.

```{r weekend-vs-weekday, fig.width=plot_w_facet, fig.height=plot_h_facet}
wk_summary <- weekend_vs_weekday_prep(analytics, monetary)
wk_dist <- weekend_vs_weekday_distribution_prep(analytics, monetary)

ggplotly(
  weekend_vs_weekday_distribution_plot(
    wk_dist,
    Talent
  ),
  tooltip = "text"
)
```

```{r weekend-vs-weekday-table}
DTSettings(wk_summary, class = "display stripe hover", scroll_x = TRUE)
```

## Timing Effects: Day-of-Week Distribution
**What this chart shows:** Share of total views and revenue attributed to each weekday.  
**How to read it:** Larger bars mean that weekday contributes a bigger portion of overall performance.

```{r day-of-week-share, fig.width=plot_w_facet, fig.height=plot_h_facet}
dow_summary <- day_of_week_performance_prep(analytics, monetary)

if (nrow(dow_summary) == 0) {
  cat("No day-of-week performance rows available in the selected window.")
} else {
  tryCatch(
    {
      ggplotly(
        day_of_week_performance_plot(
          dow_summary,
          Talent,
          as_share = TRUE
        )
      )
    },
    error = function(e) {
      cat("Day-of-week section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

```{r day-of-week-table}
DTSettings(dow_summary, class = "display stripe hover", scroll_x = TRUE)
```

## Collaboration Effectiveness
**What this chart shows:** Average views per video and average revenue per video for collaborative vs non-collaborative uploads.  
**How to read it:** Compare bar heights to see which approach performs better per upload, not just by total volume.

```{r collaboration-effectiveness, fig.width=plot_w_facet, fig.height=plot_h_facet}
collab_summary <- collaboration_effectiveness_prep(analytics, monetary)

if (nrow(collab_summary) == 0) {
  cat("No collaboration rows available in the selected window.")
} else {
  tryCatch(
    {
      ggplotly(
        collaboration_effectiveness_plot(
          collab_summary,
          Talent,
          as_share = FALSE
        )
      )
    },
    error = function(e) {
      cat("Collaboration section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

```{r collaboration-table}
if (nrow(collab_summary) == 0) {
  cat("No collaboration table rows available in the selected window.")
} else {
  collab_table <- collab_summary %>%
    select(
      collab_group,
      VideoCountViews,
      VideoCountRevenue,
      TotalViews,
      TotalRevenue,
      AverageViewsPerVideo,
      AverageRevenuePerVideo,
      AvgViewsLiftVsNonCollab,
      AvgRevenueLiftVsNonCollab
    )

  DTSettings(collab_table, class = "display stripe hover", scroll_x = TRUE)
}
```

## Topic Performance (Views + Revenue)
**What this chart shows:** Performance comparison by topic using both views and revenue.  
**How to read it:** Higher values indicate topics that contribute more overall performance.

```{r topic-breakdown, fig.width=plot_w_facet, fig.height=plot_h_facet}
topic_summary <- topic_performance_prep(analytics, monetary, top_n = 8)

if (nrow(topic_summary) == 0) {
  cat("No topic rows available in the selected window.")
} else {
  tryCatch(
    {
      ggplotly(
        topic_performance_plot(
          topic_summary,
          Talent,
          as_share = FALSE
        )
      )
    },
    error = function(e) {
      cat("Topic section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

```{r topic-table}
if (nrow(topic_summary) == 0) {
  cat("No topic table rows available in the selected window.")
} else {
  DTSettings(topic_summary, class = "display stripe hover", scroll_x = TRUE)
}
```

## Tag Performance (Top Tags by Views + Revenue)
**What this chart shows:** Performance by top tags using views and revenue signals.  
**How to read it:** Bigger values indicate higher-performing tags; tags can overlap across videos, so totals are directional rather than mutually exclusive.

```{r tag-breakdown, fig.width=plot_w_dense, fig.height=plot_h_dense}
tag_summary <- tag_performance_prep(
  analytics,
  monetary,
  top_n = 15,
  min_videos = 2
)

if (nrow(tag_summary) == 0) {
  cat("No tag rows available in the selected window.")
} else {
  tryCatch(
    {
      ggplotly(
        tag_performance_plot(
          tag_summary,
          Talent,
          as_share = FALSE
        )
      )
    },
    error = function(e) {
      cat("Tag section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

## Average Views per Tag
**What this chart shows:** Average views per video for each top tag (how many views a tagged video gets on average).  
**How to read it:** Taller bars indicate tags that tend to perform better per tagged upload, independent of total posting volume.

```{r tag-average-views, fig.width=plot_w_dense, fig.height=plot_h_dense}
if (nrow(tag_summary) == 0) {
  cat("No tag-average rows available in the selected window.")
} else {
  tryCatch(
    {
      ggplotly(
        tag_average_views_plot(
          tag_summary,
          Talent
        ),
        tooltip = "text"
      )
    },
    error = function(e) {
      cat("Tag-average section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

```{r tag-table}
if (nrow(tag_summary) == 0) {
  cat("No tag table rows available in the selected window.")
} else {
  DTSettings(tag_summary, class = "display stripe hover", scroll_x = TRUE)
}
```

# Wrap-up: What this means
Use this section to add tailored commentary after reviewing the standard charts above.

**Default executive summary template (edit for each talent):**
1. **Performance direction:** Views and revenue are [rising/stable/declining], led by [top formats].
2. **Efficiency signal:** Per-video performance is strongest in [formats/topics/tags], while [areas] underperform.
3. **Audience signal:** Core audience is [stable/concentrating/broadening]; potential audience is [rising/falling].
4. **Operating signal:** [Weekday/weekend/day] and [collab/non-collab] content currently show higher average outcomes.
5. **Recommended next 30 days:** Double down on [2-3 actions], test [1-2 experiments], and monitor [key risks].
