---
title: "BundleA"
author: "Jonathon Sun"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float: true
    toc_depth: 3
params:
  talent: "Ava"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo     = FALSE,
  message  = FALSE, 
  warning  = FALSE,
  fig.align = "center"
)

plot_w_std <- 10
plot_h_std <- 6
plot_w_facet <- 11
plot_h_facet <- 8
plot_w_dense <- 12
plot_h_dense <- 8

knitr::opts_knit$set(root.dir = here::here())

if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(
    fig.width  = 14,
    fig.height = 8,
    out.width  = "0.8\\linewidth"
  )
} else {
  knitr::opts_chunk$set(
    fig.width  = plot_w_std,
    fig.height = plot_h_std
  )
}


```

```{r libraries, include=FALSE}

library(tidyverse)
library(purrr)
library(here)
library(ggplot2)
library(DT)
library(plotly)

```

```{r modules, include=FALSE}

source("scripts/lib/utils/staging_root.R")

list.files(here("scripts","lib","plots","report","bundle_A"), full.names = TRUE) %>%
    walk(source)
list.files(here("scripts","lib","utils"), full.names = TRUE) %>%
    walk(source)
list.files(here("scripts", "lib", "import_data"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
list.files(here("scripts", "lib", "report_tables"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
source(here("scripts","lib","plots","PlottingThemes.R"))

clean_data_dir <- here::here("scripts", "lib", "clean_data")
source(file.path(clean_data_dir, "analytics_core.R"))
source(file.path(clean_data_dir, "analytics_join.R"))
source(file.path(clean_data_dir, "clean_columns.R"))
source(file.path(clean_data_dir, "video_prep.R"))
source(file.path(clean_data_dir, "title_classification_join.R"))

root <- get_staging_root()
```

```{r load_data, include = FALSE}
talent_root <- list.files(root, full.names = TRUE)

Talent <- as.character(params$talent)
if (length(Talent) != 1 || is.na(Talent) || !nzchar(trimws(Talent))) {
  stop("`params$talent` must be a single non-empty talent name.")
}
Talent <- trimws(Talent)

talent_root <- select_talent(Talent)
files <- TalentFiles(talent_root)

titles <- load_title_classifications(talent = Talent)
preps <- video_preps_with_titles(
  files = files,
  titles = titles,
  talent = Talent,
  dedupe = TRUE,
  key_cols = "Video ID",
  sort_cols = c("confidence", "published_at", "Published At"),
  dedupe_sets = c("analytics", "monetary", "demo")
)

analytics <- preps$analytics
monetary  <- preps$monetary
demo      <- preps$demo

# Backward-compatible alias used by some legacy chunks.
df <- analytics
```
# Overall Performance Snapshot

## Views by Content Type (Total vs Average)
**What this chart shows:** Total views and average views per video for each content type in one side-by-side view.  
**How to read it:** Use the Total panel to see overall volume and the Average panel to see per-upload performance, then compare formats across both.

```{r views by content comparison, fig.width=plot_w_facet, fig.height=plot_h_facet}
ggplotly(
  views_content_type_comparison(analytics, Talent) +
  theme_nyt()
)

```

## Combined Performance Trends (Views + Revenue)
**What this chart shows:** How views and revenue move over time across the reporting period.  
**How to read it:** Look for rises, drops, and turning points to see when performance accelerated or slowed.

```{r combined performance trends, fig.width=plot_w_std, fig.height=plot_h_std}
ggplotly(
  performance_trends_over_time(
    analytics_df = analytics,
    monetary_df = monetary,
    talent = Talent,
    freq = "month",
    value_mode = "raw"
  )
)
```

## Total Revenue by content type 
**What this chart shows:** Total estimated revenue grouped by content type for each month.  
**How to read it:** Larger segments indicate where more revenue was generated in that month.

```{r views by content over time, fig.width=plot_w_std, fig.height=plot_h_std}
ggplotly(
  total_metric_content_type(
    monetary,
    Talent,
    metric_col = "Estimated Revenue",
    metric_label = "Revenue",
    window_months = 1,
    bar_position = "stack",
    show_counts = TRUE
  )
)

```

## Engagement Distribution by Content Type
**What this chart shows:** Distribution of per-video engagement for each content type.  
**How to read it:** Each dot is a video; the box shows the middle range, the center line is the median, and the spread shows consistency vs volatility.

```{r engagement distribution, fig.width=plot_w_std, fig.height=plot_h_std}
analytics_eng <- analytics %>%
  mutate(avg_view_prop = averageViewPercentage / 100)

ggplotly(
  engagement_distribution_content_type(
    analytics_eng,
    Talent,
    metric_col = "avg_view_prop",
    metric_label = "Average View %",
    y_as_percent = TRUE
  ),
  tooltip = "text"
)
```

## Median Engagement by Content Type
**What this chart shows:** Median engagement level by content type, with variability shown around that median.  
**How to read it:** Higher bars mean stronger typical engagement; wider error bars mean outcomes vary more between videos.

```{r engagement summary by content, fig.width=plot_w_std, fig.height=plot_h_std}
eng_summary <- engagement_summary_content_type_prep(
  analytics_eng,
  metric_col = "avg_view_prop"
)

ggplotly(
  engagement_summary_content_type_plot(
    eng_summary,
    Talent,
    metric_label = "Average View %",
    y_as_percent = TRUE
  )
)
```

```{r}
factorCols <- if (exists("factorCols")) factorCols else c("Content Type")

UIdf<- df %>%
  select(
    Title,
    publish_date,
    `Content Type`,
    matches("estimated|average", ignore.case = TRUE)
  ) %>%
  mutate(across(any_of(factorCols), as.factor))

DTSettings(UIdf)
```

# Trends Over Time

## Views over time by content type
**What this chart shows:** How views change over time for each content type.  
**How to read it:** Compare trend lines to see which formats are growing, stable, or declining over time.

```{r import monetary data, fig.width=plot_w_facet, fig.height=plot_h_facet}
ggplotly(
  Content_duration_views(df, Talent) +
  theme_nyt()
)

```

## Revenue over time by content type
**What this chart shows:** How estimated revenue changes over time for each content type.  
**How to read it:** Compare trajectories to identify which formats are contributing more monetization over time.

```{r monetary data by content, fig.width=plot_w_facet, fig.height=plot_h_facet}

ggplotly(
  content_duration_metric(monetary, Talent, "Estimated Revenue") +
  theme_nyt()

)


```

# Audience Composition

## Audience Age + Gender Trends
**What this chart shows:** Audience share trends over time by age and gender segments.  
**How to read it:** Track which segments are growing, shrinking, or staying stable month to month.

```{r audience age and gender trends, fig.width=plot_w_facet, fig.height=plot_h_facet}
ggplotly(
  audience_age_gender_trends(
    demo_df = demo,
    talent = Talent,
    freq = "month"
  )
)
```

## Core Audience Stability

**What this chart shows:**  
- **Core audience share:** the monthly share of your largest audience segment (top age + gender group).  
- **Potential audience share:** everyone else combined (all non-core segments).

**How to read it:**  
- If **Core** rises and **Potential** falls, your audience is becoming more concentrated in one segment.  
- If **Core** falls and **Potential** rises, your audience is broadening across more segments.  
- Stable lines suggest a steady audience mix month to month.
- Both lines are on the same 0-100% scale so month-to-month comparisons are direct.

**Why this view is easier:**  
It turns a technical concentration metric into two plain-language shares that are easier to explain to non-technical readers.

```{r audience stability, fig.width=plot_w_facet, fig.height=plot_h_facet}
core_stability <- audience_core_segment_stability_prep(
  demo_df = demo,
  freq = "month"
)

ggplotly(
  audience_core_segment_stability_plot(
    stability_df = core_stability,
    talent = Talent
  ),
  tooltip = "text"
)
```

# Monetization Quality (Views to Dollars)
```{r monetary data table}

Table <- revenue_stream_ratio_table(monetary)

DTSettings(
  Table,
  class = "display stripe hover",
  scroll_x = TRUE
)

```

# Content-Type Deep Dive

## Timing Effects: Weekend vs Weekday
**What this chart shows:** Per-video distributions of views and revenue for weekend vs weekday uploads.  
**How to read it:** Each dot is a video; compare medians, mean points, and spread to see whether one day type is typically stronger or more consistent.

```{r weekend-vs-weekday, fig.width=plot_w_facet, fig.height=plot_h_facet}
wk_summary <- weekend_vs_weekday_prep(analytics, monetary)
wk_dist <- weekend_vs_weekday_distribution_prep(analytics, monetary)

ggplotly(
  weekend_vs_weekday_distribution_plot(
    wk_dist,
    Talent
  ),
  tooltip = "text"
)
```

```{r weekend-vs-weekday-table}
DTSettings(wk_summary, class = "display stripe hover", scroll_x = TRUE)
```

## Timing Effects: Day-of-Week Distribution
**What this chart shows:** Share of total views and revenue attributed to each weekday.  
**How to read it:** Larger bars mean that weekday contributes a bigger portion of overall performance.

```{r day-of-week-share, fig.width=plot_w_facet, fig.height=plot_h_facet}
dow_summary <- day_of_week_performance_prep(analytics, monetary)

ggplotly(
  day_of_week_performance_plot(
    dow_summary,
    Talent,
    as_share = TRUE
  )
)
```

```{r day-of-week-table}
DTSettings(dow_summary, class = "display stripe hover", scroll_x = TRUE)
```

## Collaboration Effectiveness
**What this chart shows:** Average views per video and average revenue per video for collaborative vs non-collaborative uploads.  
**How to read it:** Compare bar heights to see which approach performs better per upload, not just by total volume.

```{r collaboration-effectiveness, fig.width=plot_w_facet, fig.height=plot_h_facet}
collab_summary <- collaboration_effectiveness_prep(analytics, monetary)

ggplotly(
  collaboration_effectiveness_plot(
    collab_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r collaboration-table}
collab_table <- collab_summary %>%
  select(
    collab_group,
    VideoCountViews,
    VideoCountRevenue,
    TotalViews,
    TotalRevenue,
    AverageViewsPerVideo,
    AverageRevenuePerVideo,
    AvgViewsLiftVsNonCollab,
    AvgRevenueLiftVsNonCollab
  )

DTSettings(collab_table, class = "display stripe hover", scroll_x = TRUE)
```

## Topic Performance (Views + Revenue)
**What this chart shows:** Performance comparison by topic using both views and revenue.  
**How to read it:** Higher values indicate topics that contribute more overall performance.

```{r topic-breakdown, fig.width=plot_w_facet, fig.height=plot_h_facet}
topic_summary <- topic_performance_prep(analytics, monetary, top_n = 8)

ggplotly(
  topic_performance_plot(
    topic_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r topic-table}
DTSettings(topic_summary, class = "display stripe hover", scroll_x = TRUE)
```

## Tag Performance (Top Tags by Views + Revenue)
**What this chart shows:** Performance by top tags using views and revenue signals.  
**How to read it:** Bigger values indicate higher-performing tags; tags can overlap across videos, so totals are directional rather than mutually exclusive.

```{r tag-breakdown, fig.width=plot_w_dense, fig.height=plot_h_dense}
tag_summary <- tag_performance_prep(
  analytics,
  monetary,
  top_n = 15,
  min_videos = 2
)

ggplotly(
  tag_performance_plot(
    tag_summary,
    Talent,
    as_share = FALSE
  )
)
```

## Average Views per Tag
**What this chart shows:** Average views per video for each top tag (how many views a tagged video gets on average).  
**How to read it:** Taller bars indicate tags that tend to perform better per tagged upload, independent of total posting volume.

```{r tag-average-views, fig.width=plot_w_dense, fig.height=plot_h_dense}
ggplotly(
  tag_average_views_plot(
    tag_summary,
    Talent
  ),
  tooltip = "text"
)
```

```{r tag-table}
DTSettings(tag_summary, class = "display stripe hover", scroll_x = TRUE)
```

# Wrap-up: What this means
