---
title: "BundleA"
author: "Jonathon Sun"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo     = TRUE,
  message  = FALSE, 
  warning  = FALSE,
  fig.align = "center"
)

knitr::opts_knit$set(root.dir = here::here())

if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(
    fig.width  = 14,
    fig.height = 7,
    out.width  = "0.8\\linewidth"
  )
} else {
  knitr::opts_chunk$set(
    fig.width  = 10,
    fig.height = 5
  )
}


```

```{r libraries, include=FALSE}

library(tidyverse)
library(purrr)
library(here)
library(ggplot2)
library(DT)
library(plotly)

```

```{r modules, include=FALSE}

source("scripts/lib/utils/staging_root.R")

list.files(here("scripts","lib","plots","report","bundle_A"), full.names = TRUE) %>%
    walk(source)
list.files(here("scripts","lib","utils"), full.names = TRUE) %>%
    walk(source)
list.files(here("scripts", "lib", "import_data"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
list.files(here("scripts", "lib", "report_tables"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
source(here("scripts","lib","plots","PlottingThemes.R"))

clean_data_dir <- here::here("scripts", "lib", "clean_data")
source(file.path(clean_data_dir, "analytics_core.R"))
source(file.path(clean_data_dir, "analytics_join.R"))
source(file.path(clean_data_dir, "clean_columns.R"))
source(file.path(clean_data_dir, "video_prep.R"))
source(file.path(clean_data_dir, "title_classification_join.R"))

if (!exists("DTSettings")) {
  DTSettings <- function(df, class = NULL, scroll_x = FALSE, ...) {
    DT::datatable(
      df,
      class = class,
      options = list(scrollX = isTRUE(scroll_x)),
      ...
    )
  }
}

root <- get_staging_root()
```

```{r load_data, include = FALSE}
talent_root <- list.files(root, full.names = TRUE)

Talent <- c("Ava")

talent_root <- select_talent(Talent)
files <- TalentFiles(talent_root)

titles <- load_title_classifications(talent = Talent)
preps <- video_preps_with_titles(
  files = files,
  titles = titles,
  talent = Talent,
  dedupe = TRUE,
  key_cols = "Video ID",
  sort_cols = c("confidence", "published_at", "Published At"),
  dedupe_sets = c("analytics", "monetary", "demo")
)

analytics <- preps$analytics
monetary  <- preps$monetary
demo      <- preps$demo

# Backward-compatible alias used by some legacy chunks.
df <- analytics
```
# Overall Performance Snapshot

## Overall views by Content Type
```{r views by content, fig.width=10}
ggplotly(
  total_views_content_type(analytics, Talent) +
  theme_nyt()
)

```

## Combined Performance Trends (Views + Revenue)
```{r combined performance trends, fig.width=10, fig.height=8}
ggplotly(
  performance_trends_over_time(
    analytics_df = analytics,
    monetary_df = monetary,
    talent = Talent,
    freq = "month",
    value_mode = "raw"
  )
)
```

## Total Revenue by content type 
```{r views by content over time, fig.width=10, fig.height=10}
ggplotly(
  total_metric_content_type(
    monetary,
    Talent,
    metric_col = "Estimated Revenue",
    metric_label = "Revenue",
    bar_position = "stack",
    show_counts = TRUE
  )
)

```

## Engagement Distribution by Content Type
```{r engagement distribution, fig.width=10, fig.height=8}
analytics_eng <- analytics %>%
  mutate(avg_view_prop = averageViewPercentage / 100)

ggplotly(
  engagement_distribution_content_type(
    analytics_eng,
    Talent,
    metric_col = "avg_view_prop",
    metric_label = "Average View %",
    y_as_percent = TRUE
  )
)
```

## Median Engagement by Content Type
```{r engagement summary by content, fig.width=10, fig.height=8}
eng_summary <- engagement_summary_content_type_prep(
  analytics_eng,
  metric_col = "avg_view_prop"
)

ggplotly(
  engagement_summary_content_type_plot(
    eng_summary,
    Talent,
    metric_label = "Average View %",
    y_as_percent = TRUE
  )
)
```

```{r}
factorCols <- if (exists("factorCols")) factorCols else c("Content Type")

UIdf<- df %>%
  select(
    Title,
    publish_date,
    `Content Type`,
    matches("estimated|average", ignore.case = TRUE)
  ) %>%
  mutate(across(any_of(factorCols), as.factor))

decimal_cols <- detect_decimals(UIdf)

DTSettings(UIdf) %>%
  DT::formatRound(columns = decimal_cols)
```

# Trends Over Time

## Views over time by content type
```{r import monetary data}
ggplotly(
  Content_duration_views(df, Talent) +
  theme_nyt()
)

```

## Revenue over time by content type
```{r monetary data by content}

ggplotly(
  content_duration_metric(monetary, Talent, "Estimated Revenue") +
  theme_nyt()

)


```

# Audience Composition

## Audience Age + Gender Trends
```{r audience age and gender trends, fig.width=10, fig.height=9}
ggplotly(
  audience_age_gender_trends(
    demo_df = demo,
    talent = Talent,
    freq = "month"
  )
)
```

## Core Audience Stability
```{r audience stability, fig.width=10, fig.height=9}
core_stability <- audience_core_segment_stability_prep(
  demo_df = demo,
  freq = "month"
)

ggplotly(
  audience_core_segment_stability_plot(
    stability_df = core_stability,
    talent = Talent
  )
)
```

# Monetization Quality (Views to Dollars)
```{r monetary data table}

Table <- revenue_stream_ratio_table(monetary)

decimal_cols <- detect_decimals(Table)

DTSettings(
  Table,
  class = "display stripe hover",
  scroll_x = TRUE
) %>%
  formatRound(columns = decimal_cols , digits = 2)

```

# Content-Type Deep Dive

## Timing Effects: Weekend vs Weekday
```{r weekend-vs-weekday, fig.width=10, fig.height=8}
wk_summary <- weekend_vs_weekday_prep(analytics, monetary)

ggplotly(
  weekend_vs_weekday_plot(
    wk_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r weekend-vs-weekday-table}
decimal_cols <- detect_decimals(wk_summary)
DTSettings(wk_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  formatRound(columns = decimal_cols, digits = 3)
```

## Timing Effects: Day-of-Week Distribution
```{r day-of-week-share, fig.width=10, fig.height=8}
dow_summary <- day_of_week_performance_prep(analytics, monetary)

ggplotly(
  day_of_week_performance_plot(
    dow_summary,
    Talent,
    as_share = TRUE
  )
)
```

```{r day-of-week-table}
decimal_cols <- detect_decimals(dow_summary)
DTSettings(dow_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  formatRound(columns = decimal_cols, digits = 3)
```

## Collaboration Effectiveness
```{r collaboration-effectiveness, fig.width=10, fig.height=8}
collab_summary <- collaboration_effectiveness_prep(analytics, monetary)

ggplotly(
  collaboration_effectiveness_plot(
    collab_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r collaboration-table}
collab_table <- collab_summary %>%
  select(
    collab_group,
    VideoCountViews,
    VideoCountRevenue,
    TotalViews,
    TotalRevenue,
    AverageViewsPerVideo,
    AverageRevenuePerVideo,
    AvgViewsLiftVsNonCollab,
    AvgRevenueLiftVsNonCollab
  )

decimal_cols <- detect_decimals(collab_table)
DTSettings(collab_table, class = "display stripe hover", scroll_x = TRUE) %>%
  formatRound(columns = decimal_cols, digits = 3)
```

## Topic Performance (Views + Revenue)
```{r topic-breakdown, fig.width=10, fig.height=8}
topic_summary <- topic_performance_prep(analytics, monetary, top_n = 8)

ggplotly(
  topic_performance_plot(
    topic_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r topic-table}
decimal_cols <- detect_decimals(topic_summary)
DTSettings(topic_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  formatRound(columns = decimal_cols, digits = 3)
```

## Tag Performance (Top Tags by Views + Revenue)
```{r tag-breakdown, fig.width=12, fig.height=9}
tag_summary <- tag_performance_prep(
  analytics,
  monetary,
  top_n = 15,
  min_videos = 2
)

ggplotly(
  tag_performance_plot(
    tag_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r tag-table}
decimal_cols <- detect_decimals(tag_summary)
DTSettings(tag_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  formatRound(columns = decimal_cols, digits = 3)
```

# Wrap-up: What this means
