---
title: "BundleA"
author: "Jonathon Sun"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo     = FALSE,
  message  = FALSE, 
  warning  = FALSE,
  fig.align = "center"
)

knitr::opts_knit$set(root.dir = here::here())

if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(
    fig.width  = 14,
    fig.height = 7,
    out.width  = "0.8\\linewidth"
  )
} else {
  knitr::opts_chunk$set(
    fig.width  = 10,
    fig.height = 5
  )
}


```

```{r libraries, include=FALSE}

library(tidyverse)
library(purrr)
library(here)
library(ggplot2)
library(DT)
library(plotly)

```

```{r modules, include=FALSE}

source("scripts/lib/utils/staging_root.R")

list.files(here("scripts","lib","plots","report","bundle_A"), full.names = TRUE) %>%
    walk(source)
list.files(here("scripts","lib","utils"), full.names = TRUE) %>%
    walk(source)
list.files(here("scripts", "lib", "import_data"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
list.files(here("scripts", "lib", "report_tables"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
source(here("scripts","lib","plots","PlottingThemes.R"))

clean_data_dir <- here::here("scripts", "lib", "clean_data")
source(file.path(clean_data_dir, "analytics_core.R"))
source(file.path(clean_data_dir, "analytics_join.R"))
source(file.path(clean_data_dir, "clean_columns.R"))
source(file.path(clean_data_dir, "video_prep.R"))
source(file.path(clean_data_dir, "title_classification_join.R"))

if (!exists("DTSettings")) {
  DTSettings <- function(df, class = NULL, scroll_x = FALSE, ...) {
    DT::datatable(
      df,
      class = class,
      options = list(scrollX = isTRUE(scroll_x)),
      ...
    )
  }
}

root <- get_staging_root()
```

```{r load_data, include = FALSE}
talent_root <- list.files(root, full.names = TRUE)

Talent <- c("Ava")

talent_root <- select_talent(Talent)
files <- TalentFiles(talent_root)

titles <- load_title_classifications(talent = Talent)
preps <- video_preps_with_titles(
  files = files,
  titles = titles,
  talent = Talent,
  dedupe = TRUE,
  key_cols = "Video ID",
  sort_cols = c("confidence", "published_at", "Published At"),
  dedupe_sets = c("analytics", "monetary", "demo")
)

analytics <- preps$analytics
monetary  <- preps$monetary
demo      <- preps$demo

# Backward-compatible alias used by some legacy chunks.
df <- analytics
```
# Overall Performance Snapshot

## Overall views by Content Type
**What this chart shows:** Total views summed across all videos in each content type (for example: short, video, live).  
**How to read it:** Taller bars mean more total views from that format overall.

```{r views by content, fig.width=10}
ggplotly(
  total_views_content_type(analytics, Talent) +
  theme_nyt()
)

```

## Average views by Content Type
**What this chart shows:** Average views per video for each content type.  
**How to read it:** Taller bars mean that format tends to get more views per upload, independent of how many videos were posted.

```{r average views by content, fig.width=10}
ggplotly(
  average_views_content_type(analytics, Talent) +
  theme_nyt()
)

```

## Combined Performance Trends (Views + Revenue)
**What this chart shows:** How views and revenue move over time across the reporting period.  
**How to read it:** Look for rises, drops, and turning points to see when performance accelerated or slowed.

```{r combined performance trends, fig.width=10, fig.height=8}
ggplotly(
  performance_trends_over_time(
    analytics_df = analytics,
    monetary_df = monetary,
    talent = Talent,
    freq = "month",
    value_mode = "raw"
  )
)
```

## Total Revenue by content type 
**What this chart shows:** Total estimated revenue grouped by content type across time windows.  
**How to read it:** Larger segments indicate where more revenue was generated overall.

```{r views by content over time, fig.width=10, fig.height=10}
ggplotly(
  total_metric_content_type(
    monetary,
    Talent,
    metric_col = "Estimated Revenue",
    metric_label = "Revenue",
    bar_position = "stack",
    show_counts = TRUE
  )
)

```

## Engagement Distribution by Content Type
**What this chart shows:** Distribution of per-video engagement for each content type.  
**How to read it:** Each dot is a video; the box shows the middle range, the center line is the median, and the spread shows consistency vs volatility.

```{r engagement distribution, fig.width=10, fig.height=8}
analytics_eng <- analytics %>%
  mutate(avg_view_prop = averageViewPercentage / 100)

ggplotly(
  engagement_distribution_content_type(
    analytics_eng,
    Talent,
    metric_col = "avg_view_prop",
    metric_label = "Average View %",
    y_as_percent = TRUE
  ),
  tooltip = "text"
)
```

## Median Engagement by Content Type
**What this chart shows:** Median engagement level by content type, with variability shown around that median.  
**How to read it:** Higher bars mean stronger typical engagement; wider error bars mean outcomes vary more between videos.

```{r engagement summary by content, fig.width=10, fig.height=8}
eng_summary <- engagement_summary_content_type_prep(
  analytics_eng,
  metric_col = "avg_view_prop"
)

ggplotly(
  engagement_summary_content_type_plot(
    eng_summary,
    Talent,
    metric_label = "Average View %",
    y_as_percent = TRUE
  )
)
```

```{r}
factorCols <- if (exists("factorCols")) factorCols else c("Content Type")

UIdf<- df %>%
  select(
    Title,
    publish_date,
    `Content Type`,
    matches("estimated|average", ignore.case = TRUE)
  ) %>%
  mutate(across(any_of(factorCols), as.factor))

decimal_cols <- detect_decimals(UIdf)

DTSettings(UIdf) %>%
  DT::formatRound(columns = decimal_cols)
```

# Trends Over Time

## Views over time by content type
**What this chart shows:** How views change over time for each content type.  
**How to read it:** Compare trend lines to see which formats are growing, stable, or declining over time.

```{r import monetary data}
ggplotly(
  Content_duration_views(df, Talent) +
  theme_nyt()
)

```

## Revenue over time by content type
**What this chart shows:** How estimated revenue changes over time for each content type.  
**How to read it:** Compare trajectories to identify which formats are contributing more monetization over time.

```{r monetary data by content}

ggplotly(
  content_duration_metric(monetary, Talent, "Estimated Revenue") +
  theme_nyt()

)


```

# Audience Composition

## Audience Age + Gender Trends
**What this chart shows:** Audience share trends over time by age and gender segments.  
**How to read it:** Track which segments are growing, shrinking, or staying stable month to month.

```{r audience age and gender trends, fig.width=10, fig.height=9}
ggplotly(
  audience_age_gender_trends(
    demo_df = demo,
    talent = Talent,
    freq = "month"
  )
)
```

## Core Audience Stability

**What is Audience Concentration (HHIx Scaled)?**  
This number shows how concentrated your audience is across age + gender groups in each month.

**How it is calculated in this report**  
1. Take each audience segment's share for the month (for example, 20%, 15%, etc.).  
2. Square each share and add them together to get an HHI concentration score.  
3. Scale that score by dividing by the highest HHI month in this report, so the chart reads like a 0-100% index.

**How to read it**  
Higher values mean your audience is more concentrated in fewer segments. Lower values mean your audience mix is more spread out.

**Why this is used here**  
It is the best fit for stability because it uses all audience segments at once (not just one group), making month-to-month changes easier to compare and less noisy.

**What this chart shows:** Audience concentration and top-segment share over time.  
**How to read it:** A higher concentration line means the audience is centered in fewer segments; a lower line means audience mix is broader.

```{r audience stability, fig.width=10, fig.height=9}
core_stability <- audience_core_segment_stability_prep(
  demo_df = demo,
  freq = "month"
)

ggplotly(
  audience_core_segment_stability_plot(
    stability_df = core_stability,
    talent = Talent
  )
)
```

# Monetization Quality (Views to Dollars)
```{r monetary data table}

Table <- revenue_stream_ratio_table(monetary)

decimal_cols <- detect_decimals(Table)

DTSettings(
  Table,
  class = "display stripe hover",
  scroll_x = TRUE
) %>%
  formatRound(columns = decimal_cols , digits = 2)

```

# Content-Type Deep Dive

## Timing Effects: Weekend vs Weekday
**What this chart shows:** Per-video distributions of views and revenue for weekend vs weekday uploads.  
**How to read it:** Each dot is a video; compare medians, mean points, and spread to see whether one day type is typically stronger or more consistent.

```{r weekend-vs-weekday, fig.width=10, fig.height=8}
wk_summary <- weekend_vs_weekday_prep(analytics, monetary)
wk_dist <- weekend_vs_weekday_distribution_prep(analytics, monetary)

ggplotly(
  weekend_vs_weekday_distribution_plot(
    wk_dist,
    Talent
  ),
  tooltip = "text"
)
```

```{r weekend-vs-weekday-table}
decimal_cols <- detect_decimals(wk_summary)
DTSettings(wk_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  formatRound(columns = decimal_cols, digits = 3)
```

## Timing Effects: Day-of-Week Distribution
**What this chart shows:** Share of total views and revenue attributed to each weekday.  
**How to read it:** Larger bars mean that weekday contributes a bigger portion of overall performance.

```{r day-of-week-share, fig.width=10, fig.height=8}
dow_summary <- day_of_week_performance_prep(analytics, monetary)

ggplotly(
  day_of_week_performance_plot(
    dow_summary,
    Talent,
    as_share = TRUE
  )
)
```

```{r day-of-week-table}
decimal_cols <- detect_decimals(dow_summary)
DTSettings(dow_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  formatRound(columns = decimal_cols, digits = 3)
```

## Collaboration Effectiveness
**What this chart shows:** Average views per video and average revenue per video for collaborative vs non-collaborative uploads.  
**How to read it:** Compare bar heights to see which approach performs better per upload, not just by total volume.

```{r collaboration-effectiveness, fig.width=10, fig.height=8}
collab_summary <- collaboration_effectiveness_prep(analytics, monetary)

ggplotly(
  collaboration_effectiveness_plot(
    collab_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r collaboration-table}
collab_table <- collab_summary %>%
  select(
    collab_group,
    VideoCountViews,
    VideoCountRevenue,
    TotalViews,
    TotalRevenue,
    AverageViewsPerVideo,
    AverageRevenuePerVideo,
    AvgViewsLiftVsNonCollab,
    AvgRevenueLiftVsNonCollab
  )

decimal_cols <- detect_decimals(collab_table)
DTSettings(collab_table, class = "display stripe hover", scroll_x = TRUE) %>%
  formatRound(columns = decimal_cols, digits = 3)
```

## Topic Performance (Views + Revenue)
**What this chart shows:** Performance comparison by topic using both views and revenue.  
**How to read it:** Higher values indicate topics that contribute more overall performance.

```{r topic-breakdown, fig.width=10, fig.height=8}
topic_summary <- topic_performance_prep(analytics, monetary, top_n = 8)

ggplotly(
  topic_performance_plot(
    topic_summary,
    Talent,
    as_share = FALSE
  )
)
```

```{r topic-table}
decimal_cols <- detect_decimals(topic_summary)
DTSettings(topic_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  formatRound(columns = decimal_cols, digits = 3)
```

## Tag Performance (Top Tags by Views + Revenue)
**What this chart shows:** Performance by top tags using views and revenue signals.  
**How to read it:** Bigger values indicate higher-performing tags; tags can overlap across videos, so totals are directional rather than mutually exclusive.

```{r tag-breakdown, fig.width=12, fig.height=9}
tag_summary <- tag_performance_prep(
  analytics,
  monetary,
  top_n = 15,
  min_videos = 2
)

ggplotly(
  tag_performance_plot(
    tag_summary,
    Talent,
    as_share = FALSE
  )
)
```

## Average Views per Tag
**What this chart shows:** Average views per video for each top tag (how many views a tagged video gets on average).  
**How to read it:** Taller bars indicate tags that tend to perform better per tagged upload, independent of total posting volume.

```{r tag-average-views, fig.width=12, fig.height=9}
ggplotly(
  tag_average_views_plot(
    tag_summary,
    Talent
  ),
  tooltip = "text"
)
```

```{r tag-table}
decimal_cols <- detect_decimals(tag_summary)
DTSettings(tag_summary, class = "display stripe hover", scroll_x = TRUE) %>%
  formatRound(columns = decimal_cols, digits = 3)
```

# Wrap-up: What this means
