---
title: "`r { t <- params$talent; if (!(length(t) == 1 && !is.na(t) && nzchar(trimws(as.character(t))))) t <- 'Talent'; t <- trimws(as.character(t)); t_clean <- trimws(gsub('\\s*[\\[【].*$', '', t)); paste0('Performance and Growth Overview Report: ', t_clean) }`"
subtitle: "`r { r <- params$included_date_range; if (!(length(r) == 1 && !is.na(r) && nzchar(trimws(as.character(r))))) r <- 'All available dates'; paste0('Data Range: ', as.character(r)) }`"
author: "Author: Zhuni Excel & Jonathon Sun"
date: "`r { x <- params$render_generated_at; if (length(x) == 1 && !is.na(x) && nzchar(trimws(as.character(x)))) { x <- trimws(as.character(x)); x_date <- sub('^([0-9]{4}-[0-9]{2}-[0-9]{2}).*$', '\\\\1', x); if (grepl('^[0-9]{4}-[0-9]{2}-[0-9]{2}$', x_date)) paste0('Report Date: ', x_date) else paste0('Report Date: ', format(Sys.Date(), '%Y-%m-%d')) } else paste0('Report Date: ', format(Sys.Date(), '%Y-%m-%d')) }`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float: true
    toc_depth: 3
params:
  talent: "Ava"
  data_source: "staging"
  data_root: null
  render_generated_at: null
  included_date_range: null
  render_cli: null
  render_output_dir: null
  render_output_prefix: null
  window_days: null
  start_date: null
  end_date: null
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo     = FALSE,
  message  = FALSE, 
  warning  = FALSE,
  fig.align = "center"
)

plot_w_std <- 10
plot_h_std <- 6
plot_w_facet <- 11
plot_h_facet <- 8
plot_w_dense <- 12
plot_h_dense <- 8

knitr::opts_knit$set(root.dir = here::here())

if (knitr::is_latex_output()) {
  knitr::opts_chunk$set(
    fig.width  = 14,
    fig.height = 8,
    out.width  = "0.8\\linewidth"
  )
} else {
  knitr::opts_chunk$set(
    fig.width  = plot_w_std,
    fig.height = plot_h_std
  )
}


```

```{r libraries, include=FALSE}

library(tidyverse)
library(purrr)
library(here)
library(ggplot2)
library(DT)
library(plotly)

```

```{r report_layout_style, echo=FALSE, results='asis'}
cat(
  "<style>
  .main-container {
    max-width: 1200px !important;
  }
  .section.level1,
  .section.level2,
  .section.level3 {
    max-width: 100%;
    overflow-x: hidden;
  }
  .html-widget,
  .plotly.html-widget,
  .js-plotly-plot,
  .plot-container,
  .svg-container {
    max-width: 100% !important;
  }
  .plotly.html-widget {
    width: 100% !important;
  }
  .dataTables_wrapper {
    width: 100%;
    max-width: 100%;
  }
  .dataTables_wrapper .dataTables_scroll {
    overflow-x: auto;
  }
  table.dataTable {
    width: 100% !important;
  }
  .dataTables_wrapper table.dataTable thead th,
  .dataTables_wrapper table.dataTable thead td {
    white-space: normal !important;
    line-height: 1.2;
    vertical-align: bottom;
  }
  </style>"
)
```

```{r plotly_helpers, include=FALSE}
bundle_a_ggplotly <- function(plot_obj, tooltip = NULL, rotate_y_axis_title = FALSE) {
  p <- if (is.null(tooltip)) {
    plotly::ggplotly(plot_obj)
  } else {
    plotly::ggplotly(plot_obj, tooltip = tooltip)
  }

  if (!inherits(plot_obj, "ggplot")) {
    return(p)
  }

  title_txt <- plot_obj$labels$title
  subtitle_txt <- plot_obj$labels$subtitle

  clean_talent_name <- function(x) {
    if (is.null(x) || length(x) == 0) {
      return("Unknown")
    }
    t <- trimws(as.character(x[[1]]))
    if (!nzchar(t)) {
      return("Unknown")
    }
    t <- gsub("\\s*[\\[【].*$", "", t)
    t <- trimws(t)
    if (!nzchar(t)) "Unknown" else t
  }

  fallback_talent <- NULL
  if (exists("Talent", inherits = TRUE)) {
    fallback_talent <- get("Talent", inherits = TRUE)
  } else if (exists("params", inherits = TRUE) &&
             is.list(get("params", inherits = TRUE)) &&
             !is.null(get("params", inherits = TRUE)$talent)) {
    fallback_talent <- get("params", inherits = TRUE)$talent
  }
  fallback_talent <- paste0("Talent: ", clean_talent_name(fallback_talent))

  wrap_for_plotly <- function(x, width = 80) {
    txt <- trimws(as.character(x))
    if (!nzchar(txt)) {
      return("")
    }
    txt <- gsub("\\s+", " ", txt)
    paste(strwrap(txt, width = width), collapse = "\n")
  }

  title_txt <- if (is.null(title_txt) || !nzchar(trimws(as.character(title_txt)))) {
    ""
  } else {
    as.character(title_txt[[1]])
  }
  subtitle_txt <- if (is.null(subtitle_txt) || !nzchar(trimws(as.character(subtitle_txt)))) {
    fallback_talent
  } else {
    as.character(subtitle_txt[[1]])
  }

  if (nzchar(fallback_talent) && !grepl("(^|\\|)\\s*Talent\\s*:", subtitle_txt, perl = TRUE)) {
    subtitle_txt <- paste0(fallback_talent, " | ", subtitle_txt)
  }

  title_plain <- wrap_for_plotly(title_txt, width = 54)
  subtitle_plain <- wrap_for_plotly(subtitle_txt, width = 88)

  title_txt <- gsub("\n", "<br>", htmltools::htmlEscape(title_plain), fixed = TRUE)
  subtitle_txt <- gsub("\n", "<br>", htmltools::htmlEscape(subtitle_plain), fixed = TRUE)

  title_lines <- max(1L, length(strsplit(title_plain, "\n", fixed = TRUE)[[1]]))
  subtitle_lines <- if (nzchar(subtitle_plain)) {
    length(strsplit(subtitle_plain, "\n", fixed = TRUE)[[1]])
  } else {
    0L
  }

  current_top <- p$x$layout$margin$t
  if (is.null(current_top) || !is.finite(current_top)) {
    current_top <- 60
  }
  needed_top <- 58 + (title_lines * 24) + (subtitle_lines * 18) + 16
  top_margin <- max(as.numeric(current_top), as.numeric(needed_top))

  combined_title <- if (nzchar(subtitle_txt)) {
    paste0(
      "<b>", title_txt, "</b>",
      "<br><span style='font-size:0.78em;'>", subtitle_txt, "</span>"
    )
  } else {
    paste0("<b>", title_txt, "</b>")
  }

  if (isTRUE(rotate_y_axis_title) && length(p$x$layout$annotations) > 0) {
    anns <- p$x$layout$annotations
    for (i in seq_along(anns)) {
      ann <- anns[[i]]
      ann_x <- if (is.null(ann$x)) NA_real_ else suppressWarnings(as.numeric(ann$x))
      ann_y <- if (is.null(ann$y)) NA_real_ else suppressWarnings(as.numeric(ann$y))
      is_axis_annot <- identical(ann$annotationType, "axis")
      is_y_axis_title <- isTRUE(is_axis_annot) &&
        is.finite(ann_x) && is.finite(ann_y) &&
        abs(ann_x - 0) < 1e-9 &&
        abs(ann_y - 0.5) < 1e-9

      if (is_y_axis_title) {
        anns[[i]]$textangle <- -90
        anns[[i]]$xanchor <- "center"
        anns[[i]]$yanchor <- "middle"
        anns[[i]]$xshift <- -55
      }
    }
    p$x$layout$annotations <- anns
  }

  margin_cfg <- list(t = top_margin)
  if (isTRUE(rotate_y_axis_title)) {
    current_left <- p$x$layout$margin$l
    if (is.null(current_left) || !is.finite(current_left)) {
      current_left <- 120
    }
    margin_cfg$l <- max(as.numeric(current_left), 140)
  }

  p %>%
    plotly::layout(
      title = list(
        text = combined_title,
        x = 0,
        xanchor = "left",
        y = 0.96,
        yanchor = "top",
        pad = list(t = 10, b = 8)
      ),
      margin = margin_cfg,
      autosize = TRUE
    ) %>%
    plotly::config(responsive = TRUE)
}
```

```{r modules, include=FALSE}

source("scripts/lib/utils/staging_root.R")
source("scripts/lib/utils/datalake_root.r")

list.files(here("scripts","lib","plots","report","bundle_A"), full.names = TRUE) %>%
    walk(source)
list.files(here("scripts","lib","utils"), full.names = TRUE) %>%
    walk(source)
list.files(here("scripts", "lib", "import_data"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
list.files(here("scripts", "lib", "report_tables"), pattern = "[rR]$", full.names = TRUE) %>%
  walk(source)
source(here("scripts","lib","plots","PlottingThemes.R"))

clean_data_dir <- here::here("scripts", "lib", "clean_data")
source(file.path(clean_data_dir, "analytics_core.R"))
source(file.path(clean_data_dir, "analytics_join.R"))
source(file.path(clean_data_dir, "clean_columns.R"))
source(file.path(clean_data_dir, "video_prep.R"))
source(file.path(clean_data_dir, "title_classification_join.R"))

```

```{r load_data, include = FALSE}
data_source <- tolower(trimws(as.character(params$data_source)))
if (!nzchar(data_source)) {
  data_source <- "staging"
}
if (!(data_source %in% c("staging", "datalake"))) {
  stop("`params$data_source` must be one of: 'staging', 'datalake'.")
}

data_root_param <- if (is.null(params$data_root) || (length(params$data_root) == 1 && is.na(params$data_root))) {
  ""
} else {
  trimws(as.character(params$data_root[[1]]))
}

root <- if (nzchar(data_root_param)) {
  data_root_param
} else if (identical(data_source, "datalake")) {
  get_datalake_root()
} else {
  get_staging_root()
}

if (!dir.exists(root)) {
  stop("Resolved data root does not exist: ", root)
}

Talent <- as.character(params$talent)
if (length(Talent) != 1 || is.na(Talent) || !nzchar(trimws(Talent))) {
  stop("`params$talent` must be a single non-empty talent name.")
}
Talent <- trimws(Talent)

window_days <- params$window_days
if (is.null(window_days) || (length(window_days) == 1 && is.na(window_days))) {
  window_days <- NA_integer_
} else {
  window_days <- suppressWarnings(as.integer(window_days))
  if (length(window_days) != 1 || is.na(window_days) || window_days <= 0) {
    stop("`params$window_days` must be NULL/NA or a single positive integer.")
  }
}

parse_optional_date <- function(x, label) {
  if (is.null(x) || (length(x) == 1 && is.na(x)) || !nzchar(trimws(as.character(x)))) {
    return(as.Date(NA))
  }
  d <- suppressWarnings(as.Date(as.character(x)))
  if (is.na(d)) {
    stop("`params$", label, "` must be in YYYY-MM-DD format when provided.")
  }
  d
}

start_date_param <- parse_optional_date(params$start_date, "start_date")
end_date_param <- parse_optional_date(params$end_date, "end_date")

if (!is.na(start_date_param) || !is.na(end_date_param)) {
  if (is.na(start_date_param)) {
    start_date_param <- as.Date("1900-01-01")
  }
  if (is.na(end_date_param)) {
    end_date_param <- Sys.Date()
  }
  if (start_date_param > end_date_param) {
    stop("`params$start_date` cannot be after `params$end_date`.")
  }
  window_start_date <- start_date_param
  window_end_date <- end_date_param
  window_mode <- "explicit_range"
} else if (!is.na(window_days)) {
  window_end_date <- Sys.Date()
  window_start_date <- window_end_date - as.integer(window_days) + 1
  window_mode <- "days_back"
} else {
  window_start_date <- as.Date(NA)
  window_end_date <- as.Date(NA)
  window_mode <- "all_data"
}

talent_root <- select_talent(Talent, root = root)
files <- TalentFiles(talent_root)

titles <- load_title_classifications(talent = Talent)
preps <- video_preps_with_titles(
  files = files,
  titles = titles,
  talent = Talent,
  dedupe = TRUE,
  key_cols = "Video ID",
  sort_cols = c("confidence", "published_at", "Published At"),
  dedupe_sets = c("analytics", "monetary")
)

analytics <- preps$analytics
monetary  <- preps$monetary
demo      <- preps$demo

apply_days_back_window <- function(df, days_back) {
  if (window_mode == "all_data" || nrow(df) == 0) {
    return(df)
  }

  date_col <- bundle_a_optional_col(
    df,
    candidates = c("publish_date", "Published At", "date"),
    label = "analysis window date column"
  )
  if (is.null(date_col)) {
    return(df)
  }

  df %>%
    mutate(.window_date = bundle_a_as_date(.data[[date_col]])) %>%
    filter(
      !is.na(.data$.window_date),
      .data$.window_date >= window_start_date,
      .data$.window_date <= window_end_date
    ) %>%
    select(-.window_date)
}

analytics <- apply_days_back_window(analytics, window_days)
monetary  <- apply_days_back_window(monetary, window_days)
demo      <- apply_days_back_window(demo, window_days)

if (nrow(analytics) == 0 || nrow(monetary) == 0) {
  stop(
    "No data after applying the selected window. ",
    "At least analytics and monetary data are required. ",
    "Try a larger `window_days` value or set it to NULL for all available data."
  )
}

demo_available <- nrow(demo) > 0

# Backward-compatible alias used by some legacy chunks.
df <- analytics
```

# Start Here: How To Use This Report
This report is designed to support quick, practical decisions for managers and talent teams.  
Use the floating table of contents to jump directly to the section that matches the decision you need to make now.

## Quick Paths by Role
1. **Manager fast scan (5-10 minutes):** Overall Performance Snapshot -> Trends Over Time -> Collaboration Effectiveness -> Wrap-up.
2. **Talent optimization path:** Engagement Distribution -> Timing Effects -> Topic Performance -> Tag Performance.
3. **Audience strategy path:** Audience Age + Gender Trends.

## How to Interpret Responsibly
- This report is **observational**, not causal. It shows patterns, not proof of cause-and-effect.
- Tag and topic metrics can be influenced by timing, promotion, seasonality, and posting volume.
- Tag totals are directional because tags can overlap across videos.

## Standard vs Customized Content
The structure and chart explanations are standardized for consistency across talents.  
Use the **Wrap-up** section to add talent-specific narrative and recommendations.

## Active Analysis Window
```{r analysis-window-summary}
pick_col <- function(df, candidates) {
  hit <- intersect(candidates, names(df))
  if (length(hit) == 0) return(NA_character_)
  hit[[1]]
}

safe_unique_videos <- function(df) {
  id_col <- pick_col(df, c("Video ID"))
  if (is.na(id_col) || nrow(df) == 0) return(NA_integer_)
  dplyr::n_distinct(df[[id_col]])
}

safe_date_span <- function(df) {
  date_col <- pick_col(df, c("publish_date", "Published At", "date"))
  if (is.na(date_col) || nrow(df) == 0) return("N/A")
  d <- suppressWarnings(as.Date(df[[date_col]]))
  d <- d[!is.na(d)]
  if (length(d) == 0) return("N/A")
  paste0(format(min(d), "%Y-%m-%d"), " to ", format(max(d), "%Y-%m-%d"))
}

window_setting <- if (window_mode == "explicit_range") {
  "Explicit date range"
} else if (window_mode == "days_back") {
  paste0("Last ", window_days, " days")
} else {
  "All available dates"
}

included_range <- if (window_mode == "all_data") {
  "All available dates"
} else {
  paste0(format(window_start_date, "%Y-%m-%d"), " to ", format(window_end_date, "%Y-%m-%d"))
}

demo_gender_col <- pick_col(demo, c("Gender", "gender"))
demo_age_col <- pick_col(demo, c("Age", "age"))
audience_segment_count <- if (!is.na(demo_gender_col) && !is.na(demo_age_col) && nrow(demo) > 0) {
  demo %>%
    dplyr::transmute(.seg = paste(.data[[demo_gender_col]], .data[[demo_age_col]], sep = " | ")) %>%
    dplyr::filter(!is.na(.data$.seg), nzchar(.data$.seg)) %>%
    dplyr::summarise(n = dplyr::n_distinct(.data$.seg)) %>%
    dplyr::pull(.data$n)
} else {
  NA_integer_
}

import_summary <- tibble::tibble(
  Metric = c(
    "Window setting",
    "Included date range",
    "Analytics rows",
    "Monetary rows",
    "Audience demographic rows",
    "Unique videos (analytics)",
    "Unique videos (monetary)",
    "Distinct audience segments (age x gender)",
    "Analytics date span",
    "Monetary date span",
    "Demographics date span"
  ),
  Value = c(
    window_setting,
    included_range,
    scales::comma(nrow(analytics)),
    scales::comma(nrow(monetary)),
    scales::comma(nrow(demo)),
    ifelse(is.na(safe_unique_videos(analytics)), "N/A", scales::comma(safe_unique_videos(analytics))),
    ifelse(is.na(safe_unique_videos(monetary)), "N/A", scales::comma(safe_unique_videos(monetary))),
    ifelse(is.na(audience_segment_count), "N/A", scales::comma(audience_segment_count)),
    safe_date_span(analytics),
    safe_date_span(monetary),
    safe_date_span(demo)
  )
)

DT::datatable(
  import_summary,
  rownames = FALSE,
  class = "compact stripe hover",
  colnames = if (exists("dt_pretty_colnames", mode = "function")) dt_pretty_colnames(import_summary) else names(import_summary),
  options = list(
    dom = "t",
    paging = FALSE,
    ordering = FALSE,
    searching = FALSE,
    info = FALSE
  )
)
```

# Overall Performance Snapshot
This section establishes a common baseline for current channel health. It combines total views (scale), average views per video (efficiency), revenue (monetization), and engagement distribution (retention quality and consistency) so decisions are based on both volume and quality, not just one metric.

## Views by Content Type (Total vs Average)
**What this chart shows:** Total views and average views per video for each content type in one side-by-side view.  
**How to read it:** Use the Total panel to see overall volume and the Average panel to see per-upload performance, then compare formats across both.

```{r views by content comparison, fig.width=plot_w_facet, fig.height=plot_h_facet}
bundle_a_ggplotly(
  views_content_type_comparison(analytics, Talent) +
  theme_nyt()
)

```

## Combined Performance Trends (Views + Revenue)
**What this chart shows:** How views and revenue move over time across the reporting period.  
**How to read it:** Look for rises, drops, and turning points to see when performance accelerated or slowed.

```{r combined performance trends, fig.width=plot_w_std, fig.height=plot_h_std}
bundle_a_ggplotly(
  performance_trends_over_time(
    analytics_df = analytics,
    monetary_df = monetary,
    talent = Talent,
    freq = "month",
    value_mode = "raw"
  )
)
```

## Total Revenue by content type 
**What this chart shows:** Total estimated revenue by content type for videos published in each month.  
**How to read it:** This is a publish-month cohort view (lifetime revenue-to-date per cohort), not cash earned only inside that calendar month.

```{r views by content over time, fig.width=plot_w_std, fig.height=plot_h_std}
revenue_monthly_ct <- total_metric_content_type_with_data(
  monetary,
  Talent,
  metric_col = "Estimated Revenue",
  metric_label = "Revenue",
  window_months = 1,
  bar_position = "stack",
  show_counts = TRUE,
  unique_bar_colors = TRUE
)

bundle_a_ggplotly(revenue_monthly_ct$plot)

```

```{r revenue-by-content-table}
revenue_monthly_table <- revenue_monthly_ct$data %>%
  mutate(
    Period = as.character(.data$window_label),
    `Total Revenue` = .data$Total,
    `Video Count` = .data$VideoCount,
    `Avg Revenue per Video` = dplyr::if_else(
      .data$VideoCount > 0,
      .data$Total / .data$VideoCount,
      NA_real_
    )
  ) %>%
  arrange(.data$.window_start, .data$`Content Type`) %>%
  select(
    .data$Period,
    .data$`Content Type`,
    .data$`Total Revenue`,
    .data$`Video Count`,
    .data$`Avg Revenue per Video`
  )

DTSettings(
  revenue_monthly_table,
  class = "display stripe hover",
  scroll_x = TRUE
)
```

## Engagement Distribution and Successful Videos by Content Type
**What this chart shows:** Per-video Average View % distribution by content type, with top-quartile videos highlighted.  
**How to read it:** Boxes show baseline performance and consistency by format; highlighted points show standout videos within each format.

**How to use this in two contexts:**  
1. **Average View % distribution context (format reliability):** Use the median line and box spread to decide which content type is most consistently retaining viewers.  
2. **Successful video context (replicable winners):** Use highlighted points to identify high-performing outlier videos, then review titles/topics to replicate winning patterns.

```{r engagement summary by content, fig.width=plot_w_std, fig.height=plot_h_std}
analytics_eng <- analytics %>%
  mutate(avg_view_prop = averageViewPercentage / 100)

eng_success_df <- engagement_distribution_content_type_prep(
  analytics_eng,
  metric_col = "avg_view_prop"
)

eng_success_df <- eng_success_df %>%
  dplyr::group_by(.data$.content) %>%
  dplyr::mutate(
    .success_cut = stats::quantile(.data$.metric, probs = 0.75, na.rm = TRUE),
    .is_success = .data$.metric >= .data$.success_cut
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    .metric_fmt = scales::label_percent(accuracy = 0.1)(.data$.metric),
    .hover_text = paste0(
      "Video: ", .data$.video_label,
      "<br>Content Type: ", .data$.content,
      "<br>Average View %: ", .data$.metric_fmt
    )
  )

p_eng_success <- ggplot2::ggplot(
  eng_success_df,
  ggplot2::aes(x = .data$.content, y = .data$.metric, fill = .data$.content)
) +
  ggplot2::geom_boxplot(
    color = sun_data_brand_colors()[["midnight"]],
    alpha = 0.65,
    outlier.shape = NA,
    width = 0.62
  ) +
  ggplot2::geom_jitter(
    data = dplyr::filter(eng_success_df, .data$.is_success),
    ggplot2::aes(text = .data$.hover_text),
    width = 0.16,
    alpha = 0.85,
    size = 2.0,
    color = sun_data_brand_colors()[["orange"]]
  ) +
  scale_fill_sun_data(variant = "brand") +
  ggplot2::guides(fill = "none") +
  theme_nyt() +
  ggplot2::labs(
    title = bundle_a_wrap_text("Average View % Distribution by Content Type", width = 58),
    subtitle = bundle_a_talent_subtitle(
      Talent,
      "Highlighted points are top-quartile videos within each content type."
    ),
    x = "Content type",
    y = "Average View %"
  ) +
  ggplot2::scale_y_continuous(labels = scales::label_percent(accuracy = 1))

bundle_a_ggplotly(
  p_eng_success,
  tooltip = "text"
)
```

```{r}
factorCols <- if (exists("factorCols")) factorCols else c("Content Type")

UIdf<- df %>%
  select(
    Title,
    publish_date,
    `Content Type`,
    matches("estimated|average", ignore.case = TRUE)
  ) %>%
  mutate(across(any_of(factorCols), as.factor))

DTSettings(UIdf)
```

# Trends Over Time
This section shows momentum: whether performance is improving, flattening, or declining over time. By tracking views and revenue together, it becomes easier to spot turning points early and separate audience demand shifts from monetization changes that a single-period snapshot might hide.

## Revenue over time by content type
**What this chart shows:** How estimated revenue changes over time for each content type.  
**How to read it:** Compare trajectories to identify which formats are contributing more monetization over time.

```{r revenue over time by content, fig.width=plot_w_facet, fig.height=plot_h_facet}

bundle_a_ggplotly(
  content_duration_metric(monetary, Talent, "Estimated Revenue") +
  theme_nyt(),
  rotate_y_axis_title = TRUE

)


```

## Total Views over time by content type
**What this chart shows:** How total views change over time for each content type using the same trend format as the revenue chart above.  
**How to read it:** Compare month-to-month direction and volatility by format, then read alongside revenue to see whether monetization changes are backed by view demand.

```{r total views over time by content, fig.width=plot_w_facet, fig.height=plot_h_facet}
bundle_a_ggplotly(
  content_duration_metric(
    analytics,
    Talent,
    metric_col = "views",
    metric_label = "Views"
  ) +
    theme_nyt(),
  rotate_y_axis_title = TRUE
)

```

# Audience Composition
This section explains who is watching and how that audience is changing month to month. Age and gender share trends provide a stable baseline for creative positioning, partnership fit, and identifying where the audience is expanding or contracting.

## Audience Age + Gender Trends
**What this chart shows:** Audience share trends over time by age and gender segments.  
**How to read it:** Track which segments are growing, shrinking, or staying stable month to month.

```{r audience age and gender trends, fig.width=plot_w_facet, fig.height=plot_h_facet}
if (!isTRUE(demo_available)) {
  cat("No audience demographics data available in the selected window.")
} else {
  tryCatch(
    {
      plot_df <- audience_age_gender_trends_prep(
        demo_df = demo,
        freq = "month"
      )
      if (nrow(plot_df) == 0) {
        cat("No audience trend rows available in the selected window.")
      } else {
        bundle_a_ggplotly(
          audience_age_gender_trends_plot(
            plot_df = plot_df,
            talent = Talent
          ),
          rotate_y_axis_title = TRUE
        )
      }
    },
    error = function(e) {
      cat("Audience trend section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

# Content Strategy Deep Dive
This section turns the performance signal into operating choices for upcoming uploads. Timing, collaboration, topic, and tag analyses focus on controllable levers so teams can prioritize high-impact experiments and make clearer trade-offs in the next publishing cycle.

## Timing Effects: Weekend vs Weekday
**What this chart shows:** Per-video distributions of views and revenue for weekend vs weekday uploads.  
**How to read it:** Each dot is a video; compare medians, mean points, and spread to see whether one day type is typically stronger or more consistent.

```{r weekend-vs-weekday, fig.width=plot_w_facet, fig.height=plot_h_facet}
wk_summary <- weekend_vs_weekday_prep(analytics, monetary)
wk_dist <- weekend_vs_weekday_distribution_prep(analytics, monetary)

bundle_a_ggplotly(
  weekend_vs_weekday_distribution_plot(
    wk_dist,
    Talent
  ),
  tooltip = "text",
  rotate_y_axis_title = TRUE
)
```

```{r weekend-vs-weekday-table}
wk_metric_order <- c(
  "TotalViews",
  "AverageViewsPerVideo",
  "MedianViewsPerVideo",
  "TotalRevenue",
  "AverageRevenuePerVideo",
  "MedianRevenuePerVideo",
  "VideoCountViews",
  "VideoCountRevenue",
  "ShareViews",
  "ShareRevenue"
)

wk_day_col <- intersect(c("Day Type", "weekend_group", "Weekend Group", "day_type"), names(wk_summary))
if (length(wk_day_col) == 0) {
  stop("Weekend vs weekday summary missing day-type column.")
}
wk_day_col <- wk_day_col[[1]]

wk_compact <- wk_summary %>%
  dplyr::transmute(
    .day_type = as.character(.data[[wk_day_col]]),
    dplyr::across(
      dplyr::any_of(wk_metric_order),
      ~ suppressWarnings(as.numeric(.x))
    )
  ) %>%
  tidyr::pivot_longer(
    cols = dplyr::any_of(wk_metric_order),
    names_to = "Metric",
    values_to = "Value"
  ) %>%
  dplyr::mutate(
    .metric_key = tolower(gsub("[^a-z0-9]+", "", .data$Metric)),
    .metric_rank = match(.data$Metric, wk_metric_order),
    Metric = if (exists("dt_display_label", mode = "function")) {
      vapply(.data$Metric, dt_display_label, character(1))
    } else {
      .data$Metric
    },
    Value = dplyr::case_when(
      grepl("share", .data$.metric_key) ~ scales::percent(.data$Value, accuracy = 0.1),
      grepl("revenue", .data$.metric_key) ~ scales::dollar(.data$Value, accuracy = 0.01),
      grepl("count", .data$.metric_key) ~ scales::comma(round(.data$Value)),
      TRUE ~ scales::number(.data$Value, accuracy = 0.01, big.mark = ",")
    )
  ) %>%
  tidyr::pivot_wider(
    names_from = .data$.day_type,
    values_from = Value
  ) %>%
  dplyr::arrange(.data$.metric_rank) %>%
  dplyr::select(
    .data$Metric,
    dplyr::any_of(c("Weekday", "Weekend"))
  )

DT::datatable(
  wk_compact,
  rownames = FALSE,
  class = "compact stripe hover",
  colnames = if (exists("dt_pretty_colnames", mode = "function")) dt_pretty_colnames(wk_compact) else names(wk_compact),
  extensions = "Buttons",
  filter = "none",
  options = list(
    dom = "Bt",
    buttons = dt_export_buttons(),
    paging = FALSE,
    ordering = FALSE,
    searching = FALSE,
    info = FALSE,
    autoWidth = TRUE
  )
)
```

## Timing Effects: Day-of-Week Distribution
**What this chart shows:** Share of total views and revenue attributed to each weekday.  
**How to read it:** Larger bars mean that weekday contributes a bigger portion of overall performance.

```{r day-of-week-share, fig.width=plot_w_facet, fig.height=plot_h_facet}
dow_summary <- day_of_week_performance_prep(analytics, monetary)

if (nrow(dow_summary) == 0) {
  cat("No day-of-week performance rows available in the selected window.")
} else {
  tryCatch(
    {
      bundle_a_ggplotly(
        day_of_week_performance_plot(
          dow_summary,
          Talent,
          as_share = TRUE
        )
      )
    },
    error = function(e) {
      cat("Day-of-week section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

```{r day-of-week-table}
DTSettings(dow_summary, class = "display stripe hover", scroll_x = TRUE)
```

## Collaboration Effectiveness
**What this chart shows:** Average views per video and average revenue per video for collaborative vs non-collaborative uploads.  
**How to read it:** Compare bar heights to see which approach performs better per upload, not just by total volume.

```{r collaboration-effectiveness, fig.width=plot_w_facet, fig.height=plot_h_facet}
collab_summary <- collaboration_effectiveness_prep(analytics, monetary)

if (nrow(collab_summary) == 0) {
  cat("No collaboration rows available in the selected window.")
} else {
  tryCatch(
    {
      bundle_a_ggplotly(
        collaboration_effectiveness_plot(
          collab_summary,
          Talent,
          as_share = FALSE
        ),
        rotate_y_axis_title = TRUE
      )
    },
    error = function(e) {
      cat("Collaboration section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

```{r collaboration-table}
if (nrow(collab_summary) == 0) {
  cat("No collaboration table rows available in the selected window.")
} else {
  collab_metric_order <- c(
    "VideoCountViews",
    "VideoCountRevenue",
    "TotalViews",
    "TotalRevenue",
    "AverageViewsPerVideo",
    "AverageRevenuePerVideo",
    "AvgViewsLiftVsNonCollab",
    "AvgRevenueLiftVsNonCollab"
  )

  collab_group_col <- intersect(c("collab_group", "Collaboration Type", "collaboration_type"), names(collab_summary))
  if (length(collab_group_col) == 0) {
    stop("Collaboration summary missing group column.")
  }
  collab_group_col <- collab_group_col[[1]]

  collab_compact <- collab_summary %>%
    dplyr::transmute(
      .group = as.character(.data[[collab_group_col]]),
      dplyr::across(
        dplyr::any_of(collab_metric_order),
        ~ suppressWarnings(as.numeric(.x))
      )
    ) %>%
    tidyr::pivot_longer(
      cols = dplyr::any_of(collab_metric_order),
      names_to = "Metric",
      values_to = "Value"
    ) %>%
    dplyr::mutate(
      .metric_key = tolower(gsub("[^a-z0-9]+", "", .data$Metric)),
      .metric_rank = match(.data$Metric, collab_metric_order),
      Metric = if (exists("dt_display_label", mode = "function")) {
        vapply(.data$Metric, dt_display_label, character(1))
      } else {
        .data$Metric
      },
      Value = dplyr::case_when(
        grepl("lift", .data$.metric_key) ~ scales::percent(.data$Value, accuracy = 0.1),
        grepl("revenue", .data$.metric_key) ~ scales::dollar(.data$Value, accuracy = 0.01),
        grepl("count", .data$.metric_key) ~ scales::comma(round(.data$Value)),
        TRUE ~ scales::number(.data$Value, accuracy = 0.01, big.mark = ",")
      )
    ) %>%
    tidyr::pivot_wider(
      names_from = .data$.group,
      values_from = .data$Value
    ) %>%
    dplyr::arrange(.data$.metric_rank) %>%
    dplyr::select(
      .data$Metric,
      dplyr::any_of(c("Non-collaborative", "Collaborative"))
    )

  collab_display_colnames <- names(collab_compact)
  collab_display_colnames[collab_display_colnames == "Non-collaborative"] <- "Non-collab"
  collab_display_colnames[collab_display_colnames == "Collaborative"] <- "Collab"

  DT::datatable(
    collab_compact,
    rownames = FALSE,
    class = "compact stripe hover",
    colnames = collab_display_colnames,
    extensions = "Buttons",
    filter = "none",
    options = list(
      dom = "Bt",
      buttons = dt_export_buttons(),
      paging = FALSE,
      ordering = FALSE,
      searching = FALSE,
      info = FALSE,
      autoWidth = TRUE
    )
  )
}
```

## Topic Performance (Views + Revenue)
**What this chart shows:** Performance comparison by topic using both views and revenue.  
**How to read it:** Higher values indicate topics that contribute more overall performance.

```{r topic-breakdown, fig.width=plot_w_facet, fig.height=plot_h_facet}
topic_summary <- topic_performance_prep(analytics, monetary, top_n = 8)

if (nrow(topic_summary) == 0) {
  cat("No topic rows available in the selected window.")
} else {
  tryCatch(
    {
      bundle_a_ggplotly(
        topic_performance_plot(
          topic_summary,
          Talent,
          as_share = FALSE
        )
      )
    },
    error = function(e) {
      cat("Topic section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

```{r topic-table}
if (nrow(topic_summary) == 0) {
  cat("No topic table rows available in the selected window.")
} else {
  DTSettings(topic_summary, class = "display stripe hover", scroll_x = TRUE)
}
```

## Tag Performance (Top Tags by Views + Revenue)
**What this chart shows:** Performance by top tags using views and revenue signals.  
**How to read it:** Bigger values indicate higher-performing tags; tags can overlap across videos, so totals are directional rather than mutually exclusive.

```{r tag-breakdown, fig.width=plot_w_dense, fig.height=plot_h_dense}
tag_summary <- tag_performance_prep(
  analytics,
  monetary,
  top_n = 15,
  min_videos = 2
)

if (nrow(tag_summary) == 0) {
  cat("No tag rows available in the selected window.")
} else {
  tryCatch(
    {
      bundle_a_ggplotly(
        tag_performance_plot(
          tag_summary,
          Talent,
          as_share = FALSE
        )
      )
    },
    error = function(e) {
      cat("Tag section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

## Average Views per Tag
**What this chart shows:** Average views per video for each top tag (how many views a tagged video gets on average).  
**How to read it:** Taller bars indicate tags that tend to perform better per tagged upload, independent of total posting volume.

```{r tag-average-views, fig.width=plot_w_dense, fig.height=plot_h_dense}
if (nrow(tag_summary) == 0) {
  cat("No tag-average rows available in the selected window.")
} else {
  tryCatch(
    {
      bundle_a_ggplotly(
        tag_average_views_plot(
          tag_summary,
          Talent
        ),
        tooltip = "text"
      )
    },
    error = function(e) {
      cat("Tag-average section unavailable for the selected window:", conditionMessage(e))
    }
  )
}
```

```{r tag-table}
if (nrow(tag_summary) == 0) {
  cat("No tag table rows available in the selected window.")
} else {
  DTSettings(tag_summary, class = "display stripe hover", scroll_x = TRUE)
}
```
